### 2010-11-28 notes/properties/properties.tex
First commit.

\documentclass{article}
\usepackage{joyce-math}
\numberwithin{equation}{section}

\begin{document}
\title{The Properties of the Standard Skew Normal}
\date{}
\maketitle

The four properties of the skew normal listed in section 2 of ``A Note on Improved Approx \ldots''.

\section{Property 1}
\begin{thm*}
  If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
\end{thm*}

\begin{proof}

  The standard normal pdf is an even function: $\phi(-x) = \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} =
  \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} = \phi(x)$. The standard normal cdf, however, $\Phi(x) =
  \int_{-\infty}^\infty \phi(x)$, is not, being 0 near $-\infty$ and 1 near $\infty$. Thus,

  \begin{align*}
    f_{(-Z)}(x) &= f_Z(-x) \\
    & = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\
    & = 2 \cdot \phi(x) \cdot \Phi (-\lambda x)
  \end{align*}
  which is the pdf of $SN(0, 1, -\lambda)$.
\end{proof}

\section{Property 2}
\begin{thm*}
  As $\lambda \to \pm \infty$, $SN(0, 1, \lambda)$ tends to the half normal distribution.
\end{thm*}

To prove our theorem, it is helpful to formally define the half normal distribution:

\begin{lemma*}
  Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal random variable
  with parameter $\sigma$ and

  \[
  f_{|X|}(x) =
  \begin{dcases*}
    2 \cdot f_{N(0, \sigma^2)}(x) & when $0 < x < \infty$ \\
    0 & everywhere else
  \end{dcases*}
  \]
\end{lemma*}

\begin{proof}
  Let $X \sim N(0, \sigma^2)$, defined over $A = (-\infty, \infty)$.

  Define

  \[
  Y = |X| =
  \begin{dcases*}
    -x & if $x < 0$ \\
    0 & if $x = 0$ \\
    x & if $x > 0$ \\
  \end{dcases*}
  \]

  $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such that $A = A_1 \cup A_2
  \cup A_3$ and $Y$ is one-to-one over each $A_i$. We can then transform each piece separately
  using Theorem 6.3.2:

  On $A_1$: $y = -x \lra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1| = 1$, yielding
  \begin{align*}
    f_Y(y) &= f_x(x) \cdot \J\\
    &= f_x(-y) \cdot 1 \\
    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma}} \\
    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma}} \\
    &= f_{N(0, \sigma^2)}(y)
  \end{align*}
  over the domain $A_1: -\infty < x < 0 \lra -\infty < -y < 0 \lra 0 < y < \infty :B_1$.

  Similarly, on $A_2$: $y = x \lra x = y$ and $\J = \left| \frac{dx}{dy} \right| = |1| = 1$,
  yielding
  \begin{align*}
    f_Y(y) &= f_x(x) \cdot \J\\
    &= f_x(y) \cdot 1 \\
    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma}} \\
    &= f_{N(0, \sigma^2)}(y)
  \end{align*}
  over the domain $A_2: 0 < x < \infty \lra 0 < y < \infty :B_2$.

  On $A_3$, we have $x = 0, y = 0$ and $\J = \left| \frac{dx}{dy} \right| = |0| = 0$, yielding
  $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.

  Then, by Theorem 6.3.10,
  \begin{align*}
    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \\
    &= f_{N(0, \sigma^2)}(y) + f_{N(0, \sigma^2)}(y) \\
    &= 2 \cdot f_{N(0, \sigma^2)}(y)
  \end{align*}
  over $B = B_1 \cup B_2 = (0, \infty)$, and 0 otherwise.
\end{proof}

With this result, we can easily show our property:

\begin{proof}
  Let $X \sim SN(0,1,\lambda)$. Recall that $f_X(x) = 2 \cdot \phi(x) \cdot \Phi(\lambda x)$.

  Consider $\lim_{\lambda \to \infty} f_X(x)$. When $x$ is negative, $\lambda x \to -\infty$ and
  thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however, $\lambda x \to \infty$ and
  $\Phi(\lambda x) \to 1$. Thus we have

  \[
  \lim_{\lambda \to \infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) =
  \begin{dcases*}
    0 & when $x \leq 0$ \\
    2 \cdot \phi(x) & when $x > 0$
  \end{dcases*}
  \]

  In $\lim_{\lambda \to -\infty} f_X(x)$, the signs are reversed. When $x$ is negative, $\lambda x
  \to \infty$ and $\Phi(\lambda x) \to 1$. When $x$ is positive, $\lambda x \to -\infty$ and
  $\Phi(\lambda x) \to 0$. Thus,

  \[
  \lim_{\lambda \to -\infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) =
  \begin{dcases*}
    2 \cdot \phi(x) & when $x < 0$ \\
    0 & when $x \geq 0$
  \end{dcases*}
  \]

\end{proof}

\section{Property 3}
\begin{thm*}
  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
\end{thm*}

\begin{proof}
  To prove our result, we make use of a lemma in Azzalini (2005):

  \begin{lemma}
    If $f_0$ is a one-dimensional probability density function symmetric about 0, and $G$ is a
    one-dimensional distribution function such that $G'$ exists and is a density symmetric about
    0, then

    \begin{equation} \label{azzalini-lemma}
      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
    \end{equation}

    is a density function for any odd function $w(\cdot)$.
  \end{lemma}

  Notice that $\phi(x)$ is a one-dimensional probability density function symmetric about 0, and
  $\Phi(x)$ is a one-dimensional distribution function such that $\Phi'$ exists and is a density
  symmetric about 0. Furthermore, $\lambda x$ is an odd function. Thus, $f_Z(z) = 2 \cdot \phi(z)
  \cdot \Phi(\lambda z)$ conforms to equation \ref{azzalini-lemma}. With that in mind, the corollary
  to this lemma provides a very useful result:

  \begin{cor*}[Perturbation Invariance]
    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the notation
    $\overset{d}{=}$ denotes equality in distribution.    
  \end{cor*}

  Thus, we can treat $\phi$ and $Z$ as being equal in distribution. We will now show that $\phi^2
  \sim \chi^2_1$:
  \begin{align}
    M_{\phi^2}(t) &= E[e^{tx^2}] \nonumber \\
    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx
    \nonumber \\
    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \nonumber \\
    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \nonumber \\
    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \label{before-sub}
  \end{align}

  Let $u = (\sqrt{1-2t}) \; x$; then we have $du = \sqrt{1-2t}$, \enspace $dx =
  \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty \Ra u \to -\infty$ and $x
  \to \infty \Ra u \to \infty$. Now we can rewrite equation \ref{before-sub} as

  \begin{align}
    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}}
    \right) du \nonumber \\
    &= \frac{1}{\sqrt{1-2t}} \; \left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2}
      \; du \right) \label{phi-pdf}
  \end{align}

  Notice that $\frac{1}{\sqrt{2\pi}} \; e^{-u^2/2}$ is the pdf of the standard normal, which
  integrated over $(-\infty, \infty)$ equals 1. Thus equation \ref{phi-pdf} reduces to
  $\frac{1}{\sqrt{1-2t}} = (1-2t)^{-1/2}$, which is the MGF of the $\chi^2_1$.

  Since $Z$ is equal in distribution to $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$.
\end{proof}

\section{Property 4}
\begin{thm*}
  The MGF of $SN(0, 1, \lambda)$ is $M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2}$ where
  $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
\end{thm*}

According to equation 5 in Azzalini (2005), the MGF of $SN(\mu, \sigma^2, \lambda)$ is
\begin{equation}
  M(t) = E\{e^{tY}\} = 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma
  t)
\end{equation}
where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$.

It follows that the MGF of the $SN(0, 1, \lambda)$ is
\begin{equation}
  2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) =
  2 \cdot e^{t^2/2} \cdot \Phi(\delta t)
\end{equation}
where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$.

\end{document}

### 2010-12-03 pieces/deriving-the-skew/deriving-the-skew.tex
Rearranged. Extensively.

\documentclass{article}
\usepackage {joyce-math}

\begin{document}
\title {Deriving $\lambda$ with the Method of Moments}
\author {Joyce Tipping}
\date{}
\maketitle

\section{Method of Moments}

Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
approximations for $\mu$, $\sigma$, and $\lambda$ by comparing the first,
second, and third moments about the mean of $B$ and $Y$.

\subsection{The Moments of the Binomial}

The first two moments, the mean and variance, are simply

\begin{equation*}
  E(B) = np, \quad Var(B) = np(1-p)
\end{equation*}

We can also easily find

\begin{equation*}
  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2
\end{equation*}

which we will need for the third moment. We will also need $E(B^3)$, which we
will get via the third factorial moment:

\begin{align*}
  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\
  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
  \intertext{Let $y=x-3$. Then $x=y+3$, and $x=3 \rightarrow y=0$ and $x=n \rightarrow y=n-3$.}
  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\text{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
  &= n(n-1)(n-2)p^3 \\
  &= n^3p^3 - 3n^2p^3 + 2np^3 \\
  \intertext{Further expanding the left side and solving for $E(B^3)$,}
  E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\
  E(B^3) - 3E(B^2) + 2E(B) &= \\
  E(B^3) - 3(np - np^2 + n^2p^2) + 2np &= \\
  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 + 3np - 3np^2 + 3n^2p^2 - 2np \\
  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np
\end{align*}

With these results (and a bit of elbow grease), we can obtain the third moment
without too much trouble:

\begin{align*}
  E \left( [B - E(B)]^3 \right) &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
  &= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\
  &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
  &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) - 3np(np - np^2 + n^2p^2) + 2n^3p^3 \\
  &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
  &= 2np^3 - 3np^2 + np \\
  &= np(p-1)(2p-1)
\end{align*}

Our hard-earned results, restated for convenience:

\begin{align}
  E(B) &= np \nonumber \\
  E([B - E(B)]^2) &= np(1-p) \\
  E([B - E(B)]^3) &= np(p-1)(2p-1) \nonumber
\end{align}

\subsection{The Moments of the Skew Normal}

Now we'll take a look at the moments of the skew normal. According to Equation
1 in Pewsey (2000)

\begin{align*}
  E(Y) &= \mu + b \delta \sigma \\
  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 \\
  Var(Y) &= \sigma^2 (1 - b^2 \delta^2) \\
  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \nonumber
\end{align*}

where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
\lambda^2}}$. This takes care of our first two moments; again the third is a
little more complicated:

\begin{align*}
  E([Y - E(Y)]^3) &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
  &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) \\
  & \quad + 2\;(\mu + b \delta \sigma)^3 \\
  &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{9 b \delta \mu^2 \sigma} -
    \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} \\
  & \quad - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
  &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
  &= b \delta^3 \sigma^3 (2b^2 - 1)
\end{align*}

We restate our results:

\begin{alignat}{4}
  E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \nonumber \\
  E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \\
  E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \nonumber
\end{alignat}

\subsection{Solving for $\mu$, $\sigma$, $\lambda$}

Now we set the two sets of moments equal to each other and, taking $n$ and $p$
as constants, solve for $\mu$, $\sigma$ and $\lambda$.

\begin{subequations}
\begin{align}
  np &= \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \label{eq:first-moment-set} \\
  np(1-p) &= \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:second-moment-set} \\
  np(p-1)(2p-1) &= \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \label{eq:third-moment-set}
\end{align}
\end{subequations}

To get $\lambda$, we divide the cube of \eqref{eq:second-moment-set} by the
square of \eqref{eq:third-moment-set}:

\begin{align}
  \frac{\sigma^6 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right)^3}{\sigma^6 \cdot \frac{2}{\pi} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^6 \left(
    \frac{4}{\pi} - 1 \right)^2} &= \frac{n^3p^3(1-p)^3}{n^2p^2(p-1)^2(2p-1)^2} \nonumber \\
  \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
    \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \label{eq:solving-for-lambda}
\end{align}

The above equation \eqref{eq:solving-for-lambda} is a rational expression in
$\lambda^2$ that can be solved with either a considerable amount of manual
labor or, more efficiently, with a computer algebra system. Once we have
$\lambda^2$, then $\lambda$ is simply either the positive or negative square
root, as determined by the sign of $(1-2p)$: When $p < 0.5$, the binomial skews
left, so $\lambda$ should be negative; when $p > 0.5$, the binomial skews
right, so $\lambda$ should be positive. Thus:

\begin{equation}
  \label{eq:lambda-solved}
  \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}
\end{equation}

\textbf{\textit{Note to Dr. Guffey:} I am trying to find an algebraic reason
for the sign, but I'm not seeing it in equation \eqref{eq:solving-for-lambda}
nor its algebraic expansion, which I put in in appendix
\ref{sec:solving-for-lambda} as it ended up providing little insight into this
conclusion.}

Having secured $\lambda$, we can find $\sigma$ using
\eqref{eq:second-moment-set}:

\begin{equation}
  \label{eq:sigma-solved}
  np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}}
\end{equation}

Similarly, with both $\lambda$ and $\sigma$, \eqref{eq:first-moment-set} yields
$\mu$:

\begin{equation}
  \label{eq:mu-solved}
  np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}}
\end{equation}

\textbf{\textit{Another note to Dr. Guffey:} The author mentions here that when
$p=0.5$, it forces $\lambda$ to be 0, bringing us back to the regular normal
approximation. This seems like it ought to be a simple fact, but I can't figure
out how he's getting it from these equations. He refers to his equation (c),
which is my equation \eqref{eq:mu-solved}. Substituting $p=0.5$ into
\eqref{eq:mu-solved}, however, doesn't get me anywhere; neither does
substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
into \eqref{eq:mu-solved}. As far as I can tell, equation
\eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}

\subsection{Restrictions}

If we let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u$, we can rewrite the
left hand side of \eqref{eq:solving-for-lambda} as

\begin{gather}
  \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. \nonumber \\
  \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 \nonumber \\
  \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \nonumber \\
  \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \label{eq:lhs-solving-for-lambda}
\end{gather}

we can see that it is increasing in $v$, which is always $\geq 1$. Therefore:

\begin{equation}
  \min_{v} \textnormal{\{Eq. \eqref{eq:lhs-solving-for-lambda}\}} = \textnormal{\{Eq. \eqref{eq:lhs-solving-for-lambda}\}} |_{v=1} = 
  \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1
\end{equation}

This means that the right hand side of \eqref{eq:solving-for-lambda}, which is
supposed to be equal to the left hand side of \eqref{eq:solving-for-lambda},
can't ever be less than 1. Unfortunately, it sometimes is; in particular,
$\frac{np(1-p)}{(1-2p)^2} \rightarrow 0$ both when $p \rightarrow 0$ and $p
\rightarrow 1$. So if we want a solution, we must restrict $n$ and $p$ such
that

\begin{align}
  \textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\
  \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
  np(1-p) &\geq (1-2p)^2 \nonumber \\
  np - np^2 &\geq 1 - 4p + 4p^2 \nonumber \\
  1 - 4p + 4p^2 - np + np^2 &\leq 0 \nonumber \\
  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq:solving-the-restriction}
\end{align}

If we let $n$ be a constant, we can solve for $p$ with the quadratic formula,
taking $a = n+4$, $b = -(n+4)$, and $c = 1$

\begin{gather*}
  \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
  \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
  \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n-4)} \\
  \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
  \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}}
\end{gather*}

Let $r_1 = \frac12 - \frac12 \sqrt{\frac{n}{n+4}}$ and $r_2 = \frac12 + \frac12
\sqrt{\frac{n}{n+4}}$. Note that $r_1 < r_2$. Now we can rewrite
\eqref{eq:solving-the-restriction} as

\begin{equation*}
  (p - r_1)(p - r_2) \leq 0
\end{equation*}

Examining the left hand side, when $p < r_1$, both terms are negative and so
their product is positive; when $p > r_2$, both terms are positive, again
leading the product to be positive. Therefore, our solution lies where $r_1
\leq p \leq r_2$, or more explicitly:

\begin{equation}
 \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}}
\end{equation}

For sufficiently large $n$, this interval becomes almost $(0, 1)$. For example,
when $n=100$, our interval is $(0.00971, 0.99029)$; when $n=500$, it is
(0.00199, 0.99801).

For $p$ so close to 0 or 1 that this solution will not work, our authors
suggest a Poission approximation.

\appendix
\section{Solving for $\lambda$}
\label{sec:solving-for-lambda}

Hoping that it would provide some insight into \eqref{eq:lambda-solved}, I
expanded \eqref{eq:solving-for-lambda} after moving all terms to the left hand
side:

\begin{gather*}
  \left. \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3 \middle/ \left[ \frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
    \right)^2 \right] \right. \;-\; \frac{np(1-p)}{(1-2p)^2} \\
  \left. \left( \frac{\pi(1+\lambda^2) - 2\lambda^2}{\pi(1+\lambda^2)} \right)^3 \middle/ \left( \frac{2(4-\pi)^2\lambda^6} {\pi^3(1+\lambda^2)^3} \right) \right. \;-\; \frac{np(1-p)}{(1-2p)^2} \\
  \left( \frac{\pi^3(1+\lambda^2)^3 - 3\pi^2(1+\lambda^2)^2 \cdot 2\lambda^2 + 3\pi(1+\lambda^2) \cdot 4\lambda^4 - 8\lambda^6}{\cancel{\pi^3 (1+\lambda^2)^3}} \right) \cdot \left(
    \frac{\cancel{\pi^3(1+\lambda^2)^3}}{2(4-\pi)^2\lambda^6} \right) \;-\; \frac{np(1-p)}{(1-2p)^2} \\
  \frac{\pi^3(1+3\lambda^2+3\lambda^4+\lambda^6) - 6\pi^2\lambda^2(1+2\lambda^2+4\lambda^4) + 12\pi\lambda^4(1+\lambda^2) - 8\lambda^6}{2(4-\pi)^2\lambda^6} \;-\; \frac{np(1-p)}{(1-2p)^2} \\
  \frac{\pi^3 + 3\pi^3\lambda^2 + 3\pi^3\lambda^4 + \pi^3\lambda^6 - 6\pi^2\lambda^2 - 12\pi^2\lambda^4 - 24\pi^2\lambda^6 + 12\pi\lambda^4 + 12\pi\lambda^6 - 8\lambda^6}{2(4-\pi)^2\lambda^6}
    \;-\; \frac{np(1-p)}{(1-2p)^2} \\
  \frac{\lambda^6(\pi^3-24\pi^2+12\pi-8) + \lambda^4(3\pi^3-12\pi^2+12\pi) + \lambda^2(3\pi^3-6\pi^2) + \pi^3}{2(4-\pi)^2\lambda^6} \;-\; \frac{np(1-p)}{(1-2p)^2}
  \intertext{Taking $c_1 = \pi^3 - 24\pi^2 + 12\pi - 8$, $c_2 = 3\pi^3 - 12\pi^2 + 12\pi$, $c_3 = 3\pi^3 - 6\pi^2$, $c_4 = \pi^3$, and $c_5 = 2(4-\pi)^2$, we can simplify this to}
  \frac{c_1\lambda^6 + c_2\lambda^4 + c_3\lambda^2 + c_4}{c_5\lambda^6} - \frac{np(1-p)}{(1-2p)^2} \\
  \frac{c_1(1-2p)^2\lambda^6 + c_2(1-2p)^2\lambda^4 + c_3(1-2p)^2\lambda^2 + c_4(1-2p)^2 - c_5\;np(1-p)\lambda^6}{c_5(1-2p)^2\lambda^6} \\
  \frac{\left[c_1(1-2p)^2 - c_5\;np(1-p)\right]\lambda^6 + \left[c_2(1-2p)^2\right]\lambda^4 + \left[c_3(1-2p)^2\right]\lambda^2 + c_4(1-2p)^2}{c_5(1-2p)^2\;\lambda^6}
\end{gather*}

\section{Curiosity}

As a curiosity, I was unable to get Pewsey and Azzalini to agree with each
other on $E(Z^3)$. According to Pewsey (2000),

\begin{equation} \label{eq:ey3-pewsey}
  E(Y^3) = \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3
\end{equation}

where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
\lambda^2}} \in (-1, 1)$. Since $Y = \mu + \sigma Z$, by the linearity of
expected value, we also have

\begin{align}
  E(Y^3) &= E \left[ (\mu + \sigma Z)^3 \right] \nonumber \\
  &= E (\mu^3 + 3 \mu^2 \sigma Z + 3 \mu \sigma^2 Z^2 + \sigma^3 Z^3) \nonumber \\
  &= \mu^3 + 3 \mu^2 \sigma\;E(Z) + 3 \mu \sigma^2\;E(Z^2) + \sigma^3\;E(Z^3) \nonumber \\
  &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + \sigma^3\;E(Z^3) \label{eq:ey3-linear-expansion}
\end{align}

By comparing equations \eqref{eq:ey3-pewsey} and
\eqref{eq:ey3-linear-expansion} and eliminating terms, we arrive at

\begin{align}
  \sigma^3\;E(Z^3) &= 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \nonumber \\
  \Rightarrow \quad E(Z^3) &= 3 b \delta - b \delta^3 \nonumber \\
  &= b \delta (3 - \delta^2) \nonumber \\
  &= \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \cdot \left( 3 - \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:ez3-pewsey-derived}
\end{align}

However, according to equation (6.5?) in Azzalini (2005),

\begin{equation}
  E(Z^r) =
  \begin{dcases*}
    1 \times 3 \times \cdots \times (r -1) & if r is even \\
    \frac{\sqrt{2}\;(2k + 1)!\;\lambda}{\sqrt{\pi}\;(1 + \lambda^2)^{k + 1/2}\;2^k} \sum_{m=0}^k\;\frac{m!\;(2\lambda)^{2m}}{(2m+1)!\;(k-m)!} & if $r = 2k+1$ and $k = 0, 1, ...$
  \end{dcases*}
\end{equation}

So, for $E(Z^3)$, we have $r = 2k + 1 = 3$ and $k = 1$:

\begin{align}
  E(Z^3) &= \frac{\sqrt{2} \cdot 3! \cdot \lambda}{\sqrt{\pi} \cdot (1 + \lambda^2)^{3/2} \cdot 2} \; \sum_{m=0}^1 \frac{m!\;(2\lambda)^{2m}}{(2m + 1)!\;(1 - m)!} \nonumber \\
  &= \frac{3\sqrt{2}}{\sqrt{\pi}} \cdot \frac{\lambda}{(1 + \lambda^2)^{3/2}} \cdot \left( \frac{0! (2\lambda)^0}{1!1!} + \frac{1! (2\lambda)^2}{3!0!} \right) \nonumber \\
  &= \frac{3\sqrt{2}}{\sqrt{\pi}} \cdot \frac{\lambda}{(1 + \lambda^2)^{3/2}} \cdot \left( 1 + \frac{2}{3}\lambda^2 \right) \nonumber \\
  &= \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{(\sqrt{1 + \lambda^2})^3} \cdot (3 + 2 \lambda^2) \label{eq:ez3-azzalini}
\end{align}

Unfortunately, equations \eqref{eq:ez3-pewsey-derived} and
\eqref{eq:ez3-azzalini} do not really line up.

\end{document}

### 2010-12-03 pieces/properties/_region_.tex
Rearranged. Extensively.

--- 2010-11-28 notes/properties/properties.tex
@@
-\documentclass{article}
+\message{ !name(properties.tex)}\documentclass{article}
 \usepackage{joyce-math}
-\numberwithin{equation}{section}
 
 \begin{document}
-\title{The Properties of the Standard Skew Normal}
+
+\message{ !name(properties.tex) !offset(-3) }
+
+\title{Update 1}
 \date{}
@@
 
-\section{Property 1}
+\begin{itemize}
+\item Property 1
   \begin{thm*}
@@
 
-  The standard normal pdf is an even function: $\phi(-x) = \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} =
-  \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} = \phi(x)$. The standard normal cdf, however, $\Phi(x) =
-  \int_{-\infty}^\infty \phi(x)$, is not, being 0 near $-\infty$ and 1 near $\infty$. Thus,
+    The standard normal pdf is an even function: $\phi(-x) =
+    \frac{1}{\sqrt{2\pi}}\;e^{-\frac{(-x)^2}{2}} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
+    \phi(x)$. However, $\Phi(x) \eq \int_{-\infty}^\infty \phi(x)$ is odd. Thus,
 
@@
 
-\section{Property 2}
+\item Property 2
   \begin{thm*}
-  As $\lambda \to \pm \infty$, $SN(0, 1, \lambda)$ tends to the half normal distribution.
+    As $\lambda \to \pm \infty$, $SN(0, 1, \lambda)$ tends to the half normal distribution: the $\pm
+    |N(0,1)|$ distribution.
   \end{thm*}
 
-To prove our theorem, it is helpful to formally define the half normal distribution:
+  To prove our theorem, it is helpful to have on hand a formal pdf for the half normal distribution.
 
@@
     Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal random variable
-  with parameter $\sigma$ and
-
-  \[
-  f_{|X|}(x) =
-  \begin{dcases*}
-    2 \cdot f_{N(0, \sigma^2)}(x) & when $0 < x < \infty$ \\
-    0 & everywhere else
-  \end{dcases*}
-  \]
+    with parameter $\sigma$ and $f_{|X|}(x) = 2 \cdot \phi(x)$ when $0 < x < \infty$, and 0
+    everywhere else.
   \end{lemma*}
@@
       &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma}} \\
-    &= f_{N(0, \sigma^2)}(y)
+      &= \phi(y)
     \end{align*}
@@
 
-  On $A_3$, we have $x = 0, y = 0$ and $\J = \left| \frac{dx}{dy} \right| = |0| = 0$, yielding
-  $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
+    Since $y$ is 0 on $A_3$, it can be excluded from our transformation.
 
@@
       f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \\
-    &= f_{N(0, \sigma^2)}(y) + f_{N(0, \sigma^2)}(y) \\
-    &= 2 \cdot f_{N(0, \sigma^2)}(y)
+      &= \phi(y) + \phi(y) \\
+      &= 2 \cdot \phi(y)
     \end{align*}
-  over $B = B_1 \cup B_2 = (0, \infty)$, and 0 otherwise.
+    over $B = B_1 \cup B_2 = (0, \infty)$.    
   \end{proof}
@@
   \begin{proof}
-  Let $X \sim SN(0,1,\lambda)$. Recall that $f_X(x) = 2 \cdot \phi(x) \cdot \Phi(\lambda x)$.
+    Let $X \sim SN(0,1,\lambda)$. Then $f_X(x) = 2 \cdot \phi(x) \cdot \Phi(\lambda x)$.
 
@@
     \begin{dcases*}
-    0 & when $x \leq 0$ \\
-    2 \cdot \phi(x) & when $x > 0$
+      0 & when $x < 0$ \\
+      2 \cdot \phi(x) & when $x \geq 0$
     \end{dcases*}
@@
     \begin{dcases*}
-    2 \cdot \phi(x) & when $x < 0$ \\
-    0 & when $x \geq 0$
+      2 \cdot \phi(x) & when $x \leq 0$ \\
+      0 & when $x > 0$
     \end{dcases*}
@@
 
-\section{Property 3}
+\item Property 3
   \begin{thm*}
-  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
+    If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 df).
   \end{thm*}
@@
       0, then
-
-    \begin{equation} \label{azzalini-lemma}
-      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
-    \end{equation}
-
-    is a density function for any odd function $w(\cdot)$.
+      \[
+      f(z) = 2 f_0(z) G\{w(z)\} \quad (-\infty < z < \infty)
+      \]
     \end{lemma}
-
-  Notice that $\phi(x)$ is a one-dimensional probability density function symmetric about 0, and
-  $\Phi(x)$ is a one-dimensional distribution function such that $\Phi'$ exists and is a density
-  symmetric about 0. Furthermore, $\lambda x$ is an odd function. Thus, $f_Z(z) = 2 \cdot \phi(z)
-  \cdot \Phi(\lambda z)$ conforms to equation \ref{azzalini-lemma}. With that in mind, the corollary
-  to this lemma provides a very useful result:
-
-  \begin{cor*}[Perturbation Invariance]
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the notation
-    $\overset{d}{=}$ denotes equality in distribution.    
-  \end{cor*}
-
-  Thus, we can treat $\phi$ and $Z$ as being equal in distribution. We will now show that $\phi^2
-  \sim \chi^2_1$:
-  \begin{align}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \nonumber \\
-    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx
-    \nonumber \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \nonumber \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \nonumber \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \label{before-sub}
-  \end{align}
-
-  Let $u = (\sqrt{1-2t}) \; x$; then we have $du = \sqrt{1-2t}$, \enspace $dx =
-  \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty \Ra u \to -\infty$ and $x
-  \to \infty \Ra u \to \infty$. Now we can rewrite equation \ref{before-sub} as
-
-  \begin{align}
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}}
-    \right) du \nonumber \\
-    &= \frac{1}{\sqrt{1-2t}} \; \left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2}
-      \; du \right) \label{phi-pdf}
-  \end{align}
-
-  Notice that $\frac{1}{\sqrt{2\pi}} \; e^{-u^2/2}$ is the pdf of the standard normal, which
-  integrated over $(-\infty, \infty)$ equals 1. Thus equation \ref{phi-pdf} reduces to
-  $\frac{1}{\sqrt{1-2t}} = (1-2t)^{-1/2}$, which is the MGF of the $\chi^2_1$.
-
-  Since $Z$ is equal in distribution to $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$.
+    Notice that $phi(x)$ is a one-dimensional probability density function
+    \[
+    M_{Z^2}(t) = E[e^{tZ^2}] = 2 \; \int_{-\infty}^\infty \; e^{tZ^2} \cdot \phi (z) \cdot \Phi
+    (\lambda z) \; dz \quad = \quad ?
+    \]
   \end{proof}
 
-\section{Property 4}
+\item Property 4
   \begin{thm*}
@@
 
-According to equation 5 in Azzalini (2005), the MGF of $SN(\mu, \sigma^2, \lambda)$ is
-\begin{equation}
-  M(t) = E\{e^{tY}\} = 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma
-  t)
-\end{equation}
-where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$.
+  \[
+  2 \int_{-\infty}^\infty \; e^{tx} \cdot \phi (x) \cdot \Phi (\lambda x) \; dx \quad = \quad ?
+  \]
 
-It follows that the MGF of the $SN(0, 1, \lambda)$ is
-\begin{equation}
-  2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) =
-  2 \cdot e^{t^2/2} \cdot \Phi(\delta t)
-\end{equation}
-where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$.
-
+\end{itemize}
 \end{document}
+\message{ !name(properties.tex) !offset(-164) }

### 2010-12-03 pieces/z-n-transform/z-n-transform.tex
Rearranged. Extensively.

\documentclass{article}
\usepackage{joyce-math}

\begin{document}
\title{Hello World!}
\author{Joyce Tipping}
\date{}
\maketitle

Let $\Z$ be the standard normal distribution. Show that $\X = \mu + \Z\sigma$ has a normal
distribution with mean $\mu$ and standard deviation $\sigma$.

\begin{proof}
\begin{align*}
M_{\X}(t) & = e^{\mu t} \cdot M_{\Z}(\sigma t) \\
& = e^{\mu t} \cdot e^{\frac{(\sigma t)^2}{2}} \\
& = e^{\mu t + \frac{1}{2}\sigma^2t^2} \\
& = M_{\N}(t)
\end{align*}
\end{proof}
\end{document}

### 2010-12-03 pieces/method-of-moments/method-of-moments.tex
Renamed a bunch of files. Tweaked method of moments.

--- 2010-12-03 pieces/deriving-the-skew/deriving-the-skew.tex
@@
 \begin{document}
-\title {Deriving $\lambda$ with the Method of Moments}
+\title {The Method of Moments}
 \author {Joyce Tipping}
@@
 
-\section{Method of Moments}
+\section{The Method of Moments}
 
 Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
-approximations for $\mu$, $\sigma$, and $\lambda$ by comparing the first,
-second, and third moments about the mean of $B$ and $Y$.
+approximations for $\mu$, $\sigma$, and $\lambda$ by comparing their first,
+second, and third moments about the mean.
 
@@
 
-We can also easily find
+Having these, we can easily find
 
@@
 $\lambda^2$, then $\lambda$ is simply either the positive or negative square
-root, as determined by the sign of $(1-2p)$: When $p < 0.5$, the binomial skews
-left, so $\lambda$ should be negative; when $p > 0.5$, the binomial skews
-right, so $\lambda$ should be positive. Thus:
+root, as determined by the sign of $(1-2p)$: When $p \rightarrow 0$, the
+binomial skews left and converges on the positive half normal, so $\lambda$
+should be positive; when $p \rightarrow 1$, the binomial skews right and
+converges on the negative half normal, so $\lambda$ should be negative; and
+when $p = 0.5$, the binomial is symmetric and $\lambda$ is 0, eliminating the
+need for a sign. Thus:
 
@@
 
-Similarly, with both $\lambda$ and $\sigma$, \eqref{eq:first-moment-set} yields
-$\mu$:
+Similarly, with both $\lambda$ and $\sigma$, a simple rearrangement of
+\eqref{eq:first-moment-set} yields $\mu$:
 
@@
 substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
-into \eqref{eq:mu-solved}. As far as I can tell, equation
+into \eqref{eq:mu-solved}. And as far as I can tell, equation
 \eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}
@@
 \begin{equation}
-  \min_{v} \textnormal{\{Eq. \eqref{eq:lhs-solving-for-lambda}\}} = \textnormal{\{Eq. \eqref{eq:lhs-solving-for-lambda}\}} |_{v=1} = 
+  \min_{v} \textnormal{\{Eq. \ref{eq:lhs-solving-for-lambda}\}} = \textnormal{\{Eq. \ref{eq:lhs-solving-for-lambda}\}} |_{v=1} = 
   \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1

### 2010-12-10 pieces/mabs/mabs.tex
Added skew-normal restrictions graphs.

\documentclass{article}
\usepackage{joyce-math}

\begin{document}
\section{Demonstrating Improved Accuracy}

\subsection{Maximal Absolute Error}

Define the maximal absolute error of the approximation to be

\begin{equation}
  MABS(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{appr(n,p)}(k + 0.5) \right|
\end{equation}

where $F_{B(n,p)}$ is the cdf of the binomial and $F_{appr(n,p)}$ is the cdf of
either the normal or skew-normal approximation; the 0.5 is a continuity
correction.

\end{document}

### 2010-12-10 pieces/method-of-moments/method-of-moments.tex
Added skew-normal restrictions graphs.

@@
 \begin{document}
-\title {The Method of Moments}
-\author {Joyce Tipping}
-\date{}
-\maketitle
-
 \section{The Method of Moments}
@@
   \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
-  np(1-p) &\geq (1-2p)^2 \nonumber \\
+  np(1-p) &\geq (1-2p)^2 \label{eq:solving-the-restriction}
+\end{align}
+
+From here, given a constant $p$, finding $n$ is very simple:
+
+\begin{equation}
+  n \geq \frac{(1-2p)^2}{p(1-p)} \label{eq: n for a given p}
+\end{equation}
+
+If, however, we wish to fix $n$ and solve for $p$, we further factor \eqref{eq:solving-the-restriction}
+
+\begin{align}
   np - np^2 &\geq 1 - 4p + 4p^2 \nonumber \\
   1 - 4p + 4p^2 - np + np^2 &\leq 0 \nonumber \\
-  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq:solving-the-restriction}
+  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq: solving for p}
 \end{align}
 
-If we let $n$ be a constant, we can solve for $p$ with the quadratic formula,
-taking $a = n+4$, $b = -(n+4)$, and $c = 1$
+and apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
 
@@
 Let $r_1 = \frac12 - \frac12 \sqrt{\frac{n}{n+4}}$ and $r_2 = \frac12 + \frac12
-\sqrt{\frac{n}{n+4}}$. Note that $r_1 < r_2$. Now we can rewrite
-\eqref{eq:solving-the-restriction} as
+\sqrt{\frac{n}{n+4}}$. (Note that $r_1 < r_2$.) Now we can rewrite \eqref{eq:
+solving for p} as
 

### 2010-12-10 pieces/graphs/flot/data/comparison-headers.js

@@ -1,3 +1,3 @@
 var binomial = {}; var normal = {}; var sn = {};
 var ns = ["25", "50", "100"];
-var ps = ["0.05", "0.1", "0.2", "0.3"];
+var ps = ["0.05", "0.1", "0.2"];

### 2010-12-10 pieces/graphs/flot/data/comparison-n100p005.js

@@ -1,0 +1,3 @@
+binomial.n100p005 = [[0, 0.0059205292203340226], [1, 0.03116068010702119], [2, 0.081181771857765733], [3, 0.13957567793089548], [4, 0.1781426415696955], [5, 0.18001782727042917], [6, 0.15001485605869097], [7, 0.10602553736478915], [8, 0.064870887992930129], [9, 0.034901296464032595], [10, 0.016715884095931416], [11, 0.0071982276011187795], [12, 0.0028098344583314594]];
+normal.n100p005 = [[-1.8999999999999986, 0.0012191641358520961], [-1.7999999999999972, 0.0014082897370225509], [-1.6999999999999957, 0.0016233327334031285], [-1.5999999999999943, 0.0018672771100609077], [-1.5, 0.0021433628389205886], [-1.3999999999999986, 0.0024550950794230628], [-1.2999999999999972, 0.0028062517606520752], [-1.1999999999999957, 0.0032008892034407583], [-1.0999999999999943, 0.0036433454218266445], [-1.0, 0.0041382407277875443], [-0.89999999999999858, 0.0046904752523049759], [-0.79999999999999716, 0.0053052229903312936], [-0.69999999999999574, 0.0059879219780468217], [-0.59999999999999432, 0.0067442602187242594], [-0.5, 0.0075801569893693115], [-0.39999999999999858, 0.0085017391848058645], [-0.29999999999999716, 0.0095153123896468701], [-0.19999999999999574, 0.010627326412148358], [-0.099999999999994316, 0.011844335067623455], [0.0, 0.01317295006307056], [0.10000000000000142, 0.014619788908898479], [0.20000000000000284, 0.016191416867835845], [0.30000000000000426, 0.017894283044771704], [0.40000000000000568, 0.019734650823578642], [0.5, 0.021718522966855038], [0.60000000000000142, 0.023851561810614121], [0.70000000000000284, 0.026139005106600447], [0.80000000000000426, 0.028585578188213685], [0.90000000000000568, 0.031195403259776221], [1.0, 0.033971906730703126], [1.1000000000000014, 0.036917725633414937], [1.2000000000000028, 0.040034614273825014], [1.3000000000000043, 0.043323352363105534], [1.4000000000000057, 0.04678365596628304], [1.5, 0.050414092674208842], [1.6000000000000014, 0.054212002457823774], [1.7000000000000028, 0.058173425694812882], [1.8000000000000043, 0.062293039866414518], [1.9000000000000057, 0.0665641064042
[…]

### 2010-12-10 pieces/graphs/flot/data/comparison-n100p01.js

@@ -1,0 +1,3 @@
+binomial.n100p01 = [[1, 0.00029512665430652746], [2, 0.0016231965986859026], [3, 0.0058916024693043837], [4, 0.015874595542292355], [5, 0.033865803823557056], [6, 0.059578728948850357], [7, 0.088895246368125971], [8, 0.11482302655882932], [9, 0.13041627707916414], [10, 0.13186534682448822], [11, 0.11987758802226202], [12, 0.098788012351678889], [13, 0.074302094760237095], [14, 0.051303827334449471], [15, 0.03268243815379742], [16, 0.019291716965783169], [17, 0.01059153088317509], [18, 0.0054265250821205662], [19, 0.0026021933142332601], [20, 0.0011709869914049665]];
+normal.n100p01 = [[0.10000000000000142, 0.00057418964635122809], [0.20000000000000284, 0.0006405993231173386], [0.30000000000000426, 0.00071389615734425915], [0.40000000000000568, 0.0007946960671549524], [0.5, 0.00088365865147670174], [0.60000000000000142, 0.00098148904012778813], [0.70000000000000284, 0.0010889396853999758], [0.80000000000000426, 0.0012068120760064351], [0.90000000000000568, 0.001335958352772122], [1.0, 0.0014772828039793357], [1.1000000000000014, 0.0016317432168629802], [1.2000000000000028, 0.0018003520603981317], [1.3000000000000043, 0.0019841774732586269], [1.4000000000000057, 0.002184344029671186], [1.5, 0.0024020332548697412], [1.6000000000000014, 0.0026384838609933262], [1.7000000000000028, 0.0028949916735929748], [1.8000000000000043, 0.0031729092184457413], [1.9000000000000057, 0.0034736449381408832], [2.0, 0.0037986620079324806], [2.1000000000000014, 0.0041494767206680721], [2.2000000000000028, 0.0045276564112285483], [2.3000000000000043, 0.0049348168918754536], [2.4000000000000057, 0.005372619371216354], [2.5, 0.0058427668311895132], [2.6000000000000014, 0.0063469998385500956], [2.7000000000000028, 0.006887091769826088], [2.8000000000000043, 0.0074648434316143229], [2.9000000000000057, 0.0080820770614091521], [3.0, 0.0087406296979031604], [3.1000000000000014, 0.0094423459138670701], [3.2000000000000028, 0.010189069909295179], [3.3000000000000043, 0.010982636967484792], [3.40000000
[…]

### 2010-12-10 pieces/graphs/flot/data/comparison-n100p02.js

@@ -1,0 +1,3 @@
+binomial.n100p02 = [[1, 5.0925899408361951e-09], [2, 6.3020800517847603e-08], [3, 5.1466987089575957e-07], [4, 3.1201860923055465e-06], [5, 1.4976893243066604e-05], [6, 5.9283535753805477e-05], [7, 0.00019902329860206099], [8, 0.0005784114615622392], [9, 0.0014781626239923893], [10, 0.0033628199695826867], [11, 0.0068784953923282143], [12, 0.012753876873275253], [13, 0.021583483939388855], [14, 0.033531483977264888], [15, 0.048061793700746272], [16, 0.063832069758803622], [17, 0.07885138029028689], [18, 0.090898118945747383], [19, 0.098074286230937988], [20, 0.099300214808824699], [21, 0.094571633151261603], [22, 0.084899534306246222], [23, 0.071980039955295727], [24, 0.057733990380810084], [25, 0.043877832689415662], [26, 0.031642667804867075], [27, 0.021681087199631102], [28, 0.014131422906902455], [29, 0.0087712280111808347], [30, 0.0051896432399486528], [31, 0.0029296373128742349], [32, 0.0015792576139712665]];
+normal.n100p02 = [[0.10000000000000142, 4.2103688497921958e-07], [0.20000000000000284, 4.7665022578070438e-07], [0.30000000000000426, 5.392721945591147e-07], [0.40000000000000568, 6.0974018647334344e-07], [0.5, 6.8898564938749303e-07], [0.60000000000000142, 7.7804389478723611e-07], [0.70000000000000284, 8.780648418045741e-07], [0.80000000000000426, 9.9032477275802412e-07], [0.90000000000000568, 1.1162391840711678e-06], [1.0, 1.2573768221481113e-06], [1.1000000000000014, 1.4154749997587146e-06], [1.2000000000000028, 1.5924562947167809e-06], [1.3000000000000043, 1.7904467391169912e-06], [1.4000000000000057, 2.0117956141230878e-06], [1.5, 2.2590969722628434e-06], [1.6000000000000014, 2.5352130163716896e-06], [1.7000000000000028, 2.8432994717216791e-06], [1.8000000000000043, 3.1868330954583774e-06], [1.9000000000000057, 3.569641475221975e-06], [2.0, 3.9959352767263687e-06], [2.1000000000000014, 4.4703431080810919e-06], [2.2000000000000028, 4.9979491767307147e-06], [
[…]

### 2010-12-10 pieces/graphs/flot/data/comparison-n25p005.js

@@ -1,0 +1,3 @@
+binomial.n25p005 = [[0, 0.27738957312183404], [1, 0.36498628042346593], [2, 0.2305176507937679], [3, 0.09301589417994148], [4, 0.026925653578404096], [5, 0.005951986580489327]];
+normal.n25p005 = [[-2.2999999999999989, 0.0018158902218712231], [-2.1999999999999993, 0.0024383282717041922], [-2.0999999999999996, 0.0032466654668062431], [-2.0, 0.0042867256778411772], [-1.8999999999999986, 0.0056125035213041505], [-1.7999999999999989, 0.0072866908436532603], [-1.6999999999999993, 0.0093809505046099518], [-1.5999999999999996, 0.011975843956093591], [-1.5, 0.015160313978738623], [-1.3999999999999986, 0.01903062477929374], [-1.2999999999999989, 0.023688670135246819], [-1.1999999999999993, 0.029239577817796958], [-1.0999999999999996, 0.035788566089543263], [-1.0, 0.043437045933710075], [-0.89999999999999858, 0.052278010213200894], [-0.79999999999999893, 0.062390806519552228], [-0.69999999999999929, 0.073835451266829874], [-0.59999999999999964, 0.086646704726210833], [-0.5, 0.10082818534841768], [-0.39999999999999858, 0.11634685138962576], [-0.29999999999999893, 0.13312821280856266], [-0.19999999999999929, 0.15105265119043998], [-0.099999999999999645, 0.16995321550470713], [0.0, 0.18961522371860304], [0.10000000000000142, 0.20977793357596308], [0.20000000000000107, 0.23013845153193152], [0.30000000000000071, 0.2503579308476519], [0.40000000000000036, 0.27006997470594329], [0.5, 0.28889101667248257], [0.60000000000000142, 0.30643230931771337], [0.70000000000000107, 0.32231302358107095], [0.80000000000000071, 0.33617385758162033], [0.90000000000000036, 0.34769048390524482], [1.0, 0.35658613652140003], [1.1000000000000014, 0.36264265688118158], [1.2000000000000011, 0.3657093841944532], [1.3000000000000007, 0.3657093841944532], [1.4000000000000004, 0.36264265688118147], [1.5, 0.35658613652140003], [1.6000000000000014, 0.34769048390524465], [1.7000000000000011, 0.33617385758162011], [1.8000000000000007, 0.32231302358107067], [1.9000000000000004, 0.30643230931771309], [2.0, 0.288891016672
[…]

### 2010-12-10 pieces/graphs/flot/data/comparison-n25p01.js

@@ -1,0 +1,3 @@
+binomial.n25p01 = [[0, 0.071789798769185287], [1, 0.19941610769218129], [2, 0.26588814358957502], [3, 0.2264973075022306], [4, 0.1384150212513631], [5, 0.064593676583969487], [6, 0.023923583919988702], [7, 0.0072150491187267475], [8, 0.0018037622796816882]];
+normal.n25p01 = [[-2.3999999999999986, 0.0012811986462346772], [-2.2999999999999989, 0.0015893921343098992], [-2.1999999999999993, 0.0019629780802555763], [-2.0999999999999996, 0.0024136241520128598], [-2.0, 0.0029545656079586714], [-1.8999999999999986, 0.0036007041207962633], [-1.7999999999999989, 0.0043686880593423599], [-1.6999999999999993, 0.0052769677219866524], [-1.5999999999999996, 0.0063458184368914653], [-1.5, 0.0075973240158649612], [-1.3999999999999986, 0.0090553128224570966], [-1.2999999999999989, 0.010745238742432675], [-1.1999999999999993, 0.012693999677100191], [-1.0999999999999996, 0.014929686863228599], [-1.0, 0.017481259395806321], [-0.89999999999999858, 0.020378139818590359], [-0.79999999999999893, 0.023649728564154322], [-0.69999999999999929, 0.027324837363481486], [-0.59999999999999964, 0.03143104447724774], [-0.5, 0.035993977675458706], [-0.39999999999999858, 0.041036534232898242], [-0.29999999999999893, 0.046578050713943504], [-0.19999999999999929, 0.052633438867262808], [-0.099999999999999645, 0.059212307393727931], [0.0, 0.066318092528499115], [0.10000000000000142, 0.073947223119637168], [0.20000000000000107, 0.082088348017233137], [0.30000000000000071, 0.090721654941518792], [0.40000000000000036, 0.099818310423829965], [0.5, 0.10934004978399575], [0.60000000000000142, 0.11923894432969383], [0.70000000000000107, 0.12945736998880875], [0.80000000000000071, 0.13992819741648291], [0.90000000000000036, 0.15057521831141635], [1.0, 0.16131381634609557], [1.1000000000000014, 0.17205188393549195], [1.2000000000000011, 0.18269097826468578], [1.3000000000000007, 0.19312770184098857], [1.4000000000000004, 0.20325528464034481], [1.5, 0.2129653370149015], [1.6000000000000014, 0.22214973526119988], [1.7000000000000011, 
[…]

### 2010-12-10 pieces/graphs/flot/data/comparison-n25p02.js

@@ -1,0 +1,3 @@
+binomial.n25p02 = [[0, 0.0037778931862957207], [1, 0.023611832414348225], [2, 0.070835497243044665], [3, 0.13576803638250232], [4, 0.18668105002594063], [5, 0.19601510252723772], [6, 0.16334591877269811], [7, 0.11084187345290229], [8, 0.062348553817257506], [9, 0.029442372635927135], [10, 0.011776949054370864], [11, 0.0040148689958082462], [12, 0.00117100345711074]];
+normal.n25p02 = [[-1.3999999999999986, 0.0011920441007324243], [-1.2999999999999989, 0.001397129207439726], [-1.1999999999999993, 0.0016334095280999624], [-1.0999999999999996, 0.0019048810491109052], [-1.0, 0.0022159242059690038], [-0.89999999999999858, 0.0025713204615269761], [-0.79999999999999893, 0.0029762662098879321], [-0.69999999999999929, 0.0034363833453069891], [-0.59999999999999964, 0.0039577257914899843], [-0.5, 0.0045467812507955264], [-0.39999999999999858, 0.0052104674072113071], [-0.29999999999999893, 0.0059561218038025974], [-0.19999999999999929, 0.0067914846168428168], [-0.099999999999999645, 0.0077246735671975871], [0.0, 0.0087641502467842702], [0.10000000000000142, 0.009918677195897679], [0.20000000000000107, 0.011197265147421465], [0.30000000000000071, 0.012609109957597208], [0.40000000000000036, 0.014163518870800593], [0.5, 0.015869825917833709], [0.60000000000000142, 0.017737296423115743], [0.70000000000000107, 0.019775020794685131], [0.80000000000000071, 0.021991797990213616], [0.90000000000000036, 0.024396009289591382], [1.0, 0.026995483256594031], [1.1000000000000014, 0.029797353034408083], [1.2000000000000011, 0.032807907387338332], [1.3000000000000007, 0.03603243716810902], [1.4000000000000004, 0.039475079150447089], [1.5, 0.043138659413255766], [1.6000000000000014, 0.047024538688443522], [1.7000000000000011, 0.051132462281989047], [1.8000000000000007, 0.055460417339727813], [1.9000000000000004, 0.060004500348492827], [2.0, 0.064758797832945872], [2.1000000000000014, 0.06971528322268021], [2.2000000000000011, 0.074863732817872494], [2.3000000000000007, 0.08019166367095984], [2.4000000000000004, 0.085684296023903705], [2.5,
[…]

### 2010-12-10 pieces/graphs/flot/data/comparison-n50p005.js

@@ -1,0 +1,3 @@
+binomial.n50p005 = [[0, 0.076944975276713304], [1, 0.20248677704398246], [2, 0.26110137039881948], [3, 0.21987483823058485], [4, 0.13597522890575636], [5, 0.065840637154366277], [6, 0.025989725192513007], [7, 0.0085981045749667171], [8, 0.0024323585310761071]];
+normal.n50p005 = [[-2.5, 0.0013406574558021095], [-2.3999999999999986, 0.0016513302660337973], [-2.2999999999999972, 0.0020254496215480859], [-2.1999999999999993, 0.0024738897542732939], [-2.0999999999999979, 0.0030089199233940414], [-2.0, 0.0036442848002950072], [-1.8999999999999986, 0.0043952682008083343], [-1.7999999999999972, 0.0052787348015545825], [-1.6999999999999993, 0.0063131440461368007], [-1.5999999999999979, 0.0075185301389666783], [-1.5, 0.008916441877914209], [-1.3999999999999986, 0.010529836130576051], [-1.2999999999999972, 0.012382919050131915], [-1.1999999999999993, 0.014500929689324172], [-1.0999999999999979, 0.016909861532898293], [-1.0, 0.019636118649264615], [-0.89999999999999858, 0.022706104669576822], [-0.79999999999999716, 0.026145744631882722], [-0.69999999999999929, 0.029979941859107882], [-0.59999999999999787, 0.03423197443496339], [-0.5, 0.038922838446123091], [-0.39999999999999858, 0.044070547898868148], [-0.29999999999999716, 0.049689404003351985], [-0.19999999999999929, 0.055789249243008349], [-0.099999999999997868, 0.06237472419243404], [0.0, 0.069444547288254582], [0.10000000000000142, 0.076990839564886129], [0.20000000000000284, 0.084998517614416694], [0.30000000000000071, 0.093444778600168213], [0.40000000000000213, 0.10229870094607199], [0.5, 0.1115209832610139], [0.60000000000000142, 0.12106384209020657], [0.70000000000000284, 0.13087108620049576], [0.80000000000000071, 0.14087838132833658], [0.90000000000000213, 0.15101371471431424], [1.0, 0.16119806342500592], [1.1000000000000014, 0.17134626457065114], [1.2000000000000028, 0.18136807925119974], [1.3000000000000007, 0.19116943562042285], [1.4000000000000021, 0.2006538300870899], [1.5, 0.20972385962599882], [1.6000000000000014, 0.21828285270
[…]

### 2010-12-10 pieces/graphs/flot/data/comparison-n50p01.js

@@ -1,0 +1,3 @@
+binomial.n50p01 = [[0, 0.0051537752073201179], [1, 0.028632084485111745], [2, 0.077942896653915281], [3, 0.13856514960696054], [4, 0.18090450087575399], [5, 0.18492460089521523], [6, 0.15410383407934602], [7, 0.10762807459509882], [8, 0.064277877883183995], [9, 0.033329270013502797], [10, 0.015183334117262396], [11, 0.0061346804514191425], [12, 0.0022153012741235843]];
+normal.n50p01 = [[-1.6999999999999993, 0.0012827423789119243], [-1.5999999999999979, 0.0014870258441527051], [-1.5, 0.0017200160169201504], [-1.3999999999999986, 0.0019850953262349094], [-1.2999999999999972, 0.0022859416666344795], [-1.1999999999999993, 0.0026265388064731147], [-1.0999999999999979, 0.0030111847408909502], [-1.0, 0.00344449755901534], [-0.89999999999999858, 0.0039314183717502815], [-0.79999999999999716, 0.0044772108284731023], [-0.69999999999999929, 0.0050874567392413068], [-0.59999999999999787, 0.0057680473148802461], [-0.5, 0.0065251695417308121], [-0.39999999999999858, 0.007365287222001856], [-0.29999999999999716, 0.0082951162356284368], [-0.19999999999999929, 0.0093215936162154012], [-0.099999999999997868, 0.010451840082811418], [0.0, 0.011693115731494954], [0.10000000000000142, 0.013052768666405475], [0.20000000000000284, 0.014538176438990937], [0.30000000000000071, 0.01615668026663878], [0.40000000000000213, 0.017915512116933648], [0.5, 0.019821714870604891], [0.60000000000000142, 0.021882055913474675], [0.70000000000000284, 0.024102934653665142], [0.80000000000000071, 0.026490284612879656], [0.90000000000000213, 0.029049470897229448], [1.0, 0.031785184010991327], [1.1000000000000014, 0.034701331132678315], [1.2000000000000028, 0.03780092612341629], [1.3000000000000007, 0.04108597967919389], [1.4000000000000021, 0.044557391167256599], [1.5, 0.048214843798882606], [1.6000000000000014, 0.052056704882168875], [1.7000000000000028, 0.056079932965540813], [1.8000000000000007, 0.060279993722034561], [1.9000000000000021, 0.064650786432834936], [2.0, 0.069184582903432448], [2.1000000000000014, 0.073871980584982025], [2.20000000000
[…]

### 2010-12-10 pieces/graphs/flot/data/comparison-n50p02.js

@@ -1,0 +1,3 @@
+binomial.n50p02 = [[1, 0.00017840596158824417], [2, 0.0010927365147280004], [3, 0.004370946058912006], [4, 0.012839654048054001], [5, 0.029531204310524219], [6, 0.055371008082232921], [7, 0.087011584129223205], [8, 0.11692181617364357], [9, 0.13640878553591751], [10, 0.13981900517431545], [11, 0.12710818652210495], [12, 0.10327540154921028], [13, 0.07547048574749983], [14, 0.04986442808316955], [15, 0.02991865684990171], [16, 0.016361765464789985], [17, 0.0081808827323950062], [18, 0.0037495712523476997], [19, 0.0015787668430937746]];
+normal.n50p02 = [[0.10000000000000142, 0.00030834714854106589], [0.20000000000000284, 0.00034874857737636071], [0.30000000000000071, 0.00039395088884201855], [0.40000000000000213, 0.00044445608510971965], [0.5, 0.00050080973270877826], [0.60000000000000142, 0.00056360364869912326], [0.70000000000000284, 0.00063347862237011078], [0.80000000000000071, 0.00071112715531567144], [0.90000000000000213, 0.00079729620040513299], [1.0, 0.0008927898777522479], [1.1000000000000014, 0.00099847214330080875], [1.2000000000000028, 0.0011152693831145296], [1.3000000000000007, 0.0012441729039068441], [1.4000000000000021, 0.0013862412877997726], [1.5, 0.0015426025767917133], [1.6000000000000014, 0.0017144562499758578], [1.7000000000000028, 0.0019030749542206786], [1.8000000000000007, 0.0021098059468425165], [1.9000000000000021, 0.0023360722068095311], [2.0, 0.0025833731692615088], [2.1000000000000014, 0.0028532850366584754], [2.2000000000000028, 0.0031474606187300966], [2.3000000000000007, 0.0034676286526377988], [2.4000000000000021, 0.0038155925544309877], [2.5, 0.0041932285530270133], [2.6000000000000014, 0.0046024831586201249], [2.7000000000000028, 0.0050453699186720847], [2.8000000000000007, 0.0055239654165013911], [2.9000000000000021, 0.0060404044700066934], [3.0, 0.0065968744912687964], [3.1000000000000014, 0.007195608971703845], [3.2000000000000028, 0.0078388800621085712], [3.3000000000000007, 0.0085289902223649027], [3.4000000000000021, 0.00926
[…]

### 2010-12-10 pieces/graphs/flot/data/comparison.js

@@ -1,0 +1,33 @@
+var binomial = {}; var normal = {}; var sn = {};
+var ns = ["25", "50", "100"];
+var ps = ["0.05", "0.1", "0.2"];
+var binomial = {}; var normal = {}; var sn = {};
+var ns = ["25", "50", "100"];
+var ps = ["0.05", "0.1", "0.2"];
+binomial.n100p005 = [[0, 0.0059205292203340226], [1, 0.03116068010702119], [2, 0.081181771857765733], [3, 0.13957567793089548], [4, 0.1781426415696955], [5, 0.18001782727042917], [6, 0.15001485605869097], [7, 0.10602553736478915], [8, 0.064870887992930129], [9, 0.034901296464032595], [10, 0.016715884095931416], [11, 0.0071982276011187795], [12, 0.0028098344583314594]];
+normal.n100p005 = [[-1.8999999999999986, 0.0012191641358520961], [-1.7999999999999972, 0.0014082897370225509], [-1.6999999999999957, 0.0016233327334031285], [-1.5999999999999943, 0.0018672771100609077], [-1.5, 0.0021433628389205886], [-1.3999999999999986, 0.0024550950794230628], [-1.2999999999999972, 0.0028062517606520752], [-1.1999999999999957, 0.0032008892034407583], [-1.0999999999999943, 0.0036433454218266445], [-1.0, 0.0041382407277875443], [-0.89999999999999858, 0.0046904752523049759], [-0.79999999999999716, 0.0053052229903312936], [-0.69999999999999574, 0.0059879219780468217], [-0.59999999999999432, 0.0067442602187242594], [-0.5, 0.0075801569893693115], [-0.39999999999999858, 0.0085017391848058645], [-0.29999999999999716, 0.0095153123896468701], [-0.19999999999999574, 0.010627326412148358], [-0.099999999999994316, 0.011844335067623455], [0.0, 0.01317295006307056], [0.10000000000000142, 0.014619788908898479], [0.20000000000000284, 0.016191416867835845], [0.30000000000000426, 0.017894283044771704], [0.40000000000000568, 0.019734650823578642], [0.5, 0.021718522966855038], [0.60000000000000142, 0.023851561810614121], [0.70000000000000284, 0.026139005106600447], [0.80000000000000426, 0.028585578188213685], [0.90000000000000568, 0.031195403259776221], [1.0, 0.033971906730703126], [1.1000000000000014, 0.036917725633414937], [1.20000000000
[…]

### 2010-12-10 pieces/graphs/flot/data/mabs-headers.js

@@ -1,0 +1,3 @@
+var normal = {}; var sn = {};
+var ns = ["25", "100"];
+var ps = ["005", "01"];

### 2010-12-10 pieces/graphs/flot/data/mabs-n100.js

@@ -1,0 +1,2 @@
+sn.n100 = [[0.019709662154539891, 0.0069206165930497665], [0.029709662154539893, 0.0050456440483724052], [0.039709662154539888, 0.0039757942590482043], [0.04970966215453989, 0.0032820657744922488], [0.059709662154539891, 0.0028626210230579541], [0.069709662154539886, 0.0028377401959075454], [0.079709662154539895, 0.0027186106445759861], [0.089709662154539904, 0.0025668038617868705], [0.099709662154539885, 0.002408189730698812], [0.10970966215453989, 0.0022537798857286684], [0.1197096621545399, 0.0021080343182064698], [0.12970966215453988, 0.0019724221432679545], [0.13970966215453989, 0.0018470414216291975], [0.1497096621545399, 0.0017313722983716973], [0.15970966215453991, 0.0016246547814472989], [0.16970966215453989, 0.001526059895853471], [0.1797096621545399, 0.0014347769503024743], [0.18970966215453991, 0.0013500496566723474], [0.19970966215453989, 0.001271193852114938], [0.2097096621545399, 0.0012050466986987529], [0.21970966215453991, 0.0011479739734885086], [0.22970966215453989, 0.001092061611453421], [0.2397096621545399, 0.0010374946972736276], [0.24970966215453991, 0.00098437936338635623], [0.25970966215453989, 0.00093276711303491577], [0.2697096621545399, 0.00088267133099353967], [0.27970966215453991, 0.00083408029220938262], [0.28970966215453992, 0.00078696502019903747], [0.29970966215453992, 0.00074128628969041821], [0.30970966215453988, 0.00069699856852742381], [0.31970966215453989, 0.00065405387898431755], [0.3297096621545399, 0.00061240403149653844], [0.3397096621545399, 0.00057200256289002827], [0.34970966215453991, 0.00053280634695807016], [0.35970966215453992, 0.00049477686886334471], [0.36970966215453993, 0.00045788152667466941], [0.37970966215453988, 0.00042209470737047949], [0.38970966215453989, 0.00038739926510134026], [0.3997096621545399, 0.0003537882538213466], [0.40970966215453991, 0.00032126707401192167], [0.41970966215453992, 0.00030337074998354474], [0.42970966215453993, 0.00029638103932283499], [0.43970966215453988, 0.00028984225968553545], [0.44970966215453989, 0.00028489030032019524], [0.4597096621545399, 0.00028088232160639048], [0.4697096621545399
[…]

### 2010-12-10 pieces/graphs/flot/data/mabs-n25.js

@@ -1,0 +1,2 @@
+sn.n25 = [[0.04576165455737035, 0.0076707886207594278], [0.055761654557370352, 0.0056998856478755466], [0.065761654557370347, 0.0081118679633594704], [0.075761654557370356, 0.0067610317876842796], [0.085761654557370351, 0.0041226562692983915], [0.095761654557370346, 0.0039345383905926568], [0.10576165455737035, 0.0051430519792643181], [0.11576165455737036, 0.0051447549440509222], [0.12576165455737034, 0.004326466568962406], [0.13576165455737035, 0.0031076552766322596], [0.14576165455737036, 0.0039130477517766438], [0.15576165455737034, 0.0040862622688435379], [0.16576165455737035, 0.0037487635462088997], [0.17576165455737036, 0.0030608685753005516], [0.18576165455737037, 0.0031453091989917525], [0.19576165455737035, 0.0033235390045406876], [0.20576165455737036, 0.0031554228868615197], [0.21576165455737037, 0.0027230872295835595], [0.22576165455737035, 0.0025857881681195516], [0.23576165455737036, 0.0027324160230712824], [0.24576165455737037, 0.0026293377248905736], [0.25576165455737032, 0.0023253863233147765], [0.26576165455737033, 0.0021406750372194305], [0.27576165455737034, 0.0022481712633557471], [0.28576165455737035, 0.0021681078989882752], [0.29576165455737036, 0.0019329705605580227], [0.30576165455737037, 0.0017652939395343403], [0.31576165455737037, 0.0018343261740297878], [0.32576165455737038, 0.0017587160079293451], [0.33576165455737034, 0.0015620608688619586], [0.34576165455737035, 0.0014354729958023227], [0.35576165455737035, 0.0014693348627546343], [0.36576165455737036, 0.00139000628384231], [0.37576165455737037, 0.001215838848954709], [0.38576165455737038, 0.0011836179174229411], [0.39576165455737039, 0.0011408554757689204], [0.40576165455737034, 0.0011218144675472219], [0.41576165455737035, 0.001140029271661791], [0.42576165455737036, 0.0011292492919786623], [0.43576165455737037, 0.0010888001043022344], [0.44576165455737038, 0.0010822763492390752], [0.45576165455737039, 0.001104390606557426], [0.46576165455737034, 0.0011038755072330098], [0.47576165455737035, 0.0010798829307170354], [0.48576165455737036, 0.0010602297572412933], [0.49576165455737037, 0.0010966022
[…]

### 2010-12-10 pieces/graphs/flot/data/mabs-p005.js

@@ -1,0 +1,2 @@
+sn.p005 = [[18, 0.0080695146795372041], [23, 0.0075582492795404077], [28, 0.0055311444228898221], [33, 0.0078827958756394756], [38, 0.0070466999868247782], [43, 0.0049009668832437209], [48, 0.0036757803722735627], [53, 0.0044764215153411113], [58, 0.0050876275372231661], [63, 0.0048598812712371264], [68, 0.0040899775103753477], [73, 0.0031685057754435308], [78, 0.003903644470671791], [83, 0.0041393672785301205], [88, 0.0039665822920267602], [93, 0.0034974965436802563], [98, 0.0031461336809829876], [103, 0.0035155219345159583], [108, 0.003589742864307105], [113, 0.0034187551309338426], [118, 0.0030617826717353192], [123, 0.0030275345392536956], [128, 0.0032113816229867032], [133, 0.00319942723315364], [138, 0.0030241414775116215], [143, 0.0027225002002202459], [148, 0.002879352509362415], [153, 0.0029555134221951884], [158, 0.0028928513322859506], [163, 0.0027145056959977654], [168, 0.0025970902383762318], [173, 0.0027231041310544768], [178, 0.0027318309874033719], [183, 0.0026378624009835427], [188, 0.0024586332975732039], [193, 0.0025124549116604389], [198, 0.002567228225213436]];
[…]

### 2010-12-10 pieces/graphs/flot/data/mabs-p01.js

@@ -1,0 +1,2 @@
+sn.p01 = [[8, 0.0082143136918395587], [13, 0.0070733617898700862], [18, 0.0072476797267480575], [23, 0.0035193521242329329], [28, 0.0052388262152361087], [33, 0.003955724279050471], [38, 0.0039723749844487455], [43, 0.0038663005967027597], [48, 0.0031667556334776803], [53, 0.0034961807167636083], [58, 0.0028811869834089454], [63, 0.0031195684512512201], [68, 0.0028618733316133904], [73, 0.0027888156990080737], [78, 0.0027433388447820894], [83, 0.0025081955095563324], [88, 0.0025921527169648628], [93, 0.002280926509532738], [98, 0.0024356492835662658], [103, 0.0022513919853785758], [108, 0.0022850895767289048], [113, 0.0021929653951576755], [118, 0.0021447939285834938], [123, 0.0021202161431108368], [128, 0.0020159762506221091], [133, 0.0020413566246103854], [138, 0.0018984849890800737], [143, 0.0019610558679556689], [148, 0.0018404467562605498], [153, 0.0018819546885684157], [158, 0.0018040977678382975], [163, 0.0018055086264969489], [168, 0.0017622170504175971], [173, 0.0017324732509724494], [178, 0.0017172501167735943], [183, 0.0016631853709518085], [188, 0.0016708412953861107], [193, 0.0015977321461745353], [198, 0.001624097761914578]];
[…]

### 2010-12-10 pieces/graphs/flot/data/mabs.js

@@ -1,0 +1,14 @@
+var normal = {}; var sn = {};
+var ns = ["25", "100"];
+var ps = ["005", "01"];
+var normal = {}; var sn = {};
+var ns = ["25", "100"];
+var ps = ["005", "01"];
+sn.n100 = [[0.019709662154539891, 0.0069206165930497665], [0.029709662154539893, 0.0050456440483724052], [0.039709662154539888, 0.0039757942590482043], [0.04970966215453989, 0.0032820657744922488], [0.059709662154539891, 0.0028626210230579541], [0.069709662154539886, 0.0028377401959075454], [0.079709662154539895, 0.0027186106445759861], [0.089709662154539904, 0.0025668038617868705], [0.099709662154539885, 0.002408189730698812], [0.10970966215453989, 0.0022537798857286684], [0.1197096621545399, 0.0021080343182064698], [0.12970966215453988, 0.0019724221432679545], [0.13970966215453989, 0.0018470414216291975], [0.1497096621545399, 0.0017313722983716973], [0.15970966215453991, 0.0016246547814472989], [0.16970966215453989, 0.001526059895853471], [0.1797096621545399, 0.0014347769503024743], [0.18970966215453991, 0.0013500496566723474], [0.19970966215453989, 0.001271193852114938], [0.2097096621545399, 0.0012050466986987529], [0.21970966215453991, 0.0011479739734885086], [0.22970966215453989, 0.001092061611453421], [0.2397096621545399, 0.0010374946972736276], [0.24970966215453991, 0.00098437936338635623], [0.25970966215453989, 0.00093276711303491577], [0.2697096621545399, 0.00088267133099353967], [0.27970966215453991, 0.00083408029220938262], [0.28970966215453992, 0.00078696502019903747], [0.29970966215453992, 0.00074128628969041821], [0.30970966215453988, 0.00069699856852742381], [0.31970966215453989, 0.00065405387898431755], [0.3297096621545399, 0.00061240403149653844], [0.3397096621545399, 0.00057200256289002827], [0.34970966215453991, 0.00053280634695807016], [0.35970966215453992, 0.00049477686886334471], [0.36970966215453993, 0.00045788152667466941], [0.37970966215453988, 0.00042209470737047949], [0.38970966215453989, 0.00038739926510134026], [0.3997096621545399, 0.0003537882538213466], [0.40970966215453991, 0.00032126707401192167], [0.41970966215453992, 0.00030337074998354474], [0.42970966215453993, 0.0002
[…]

### 2010-12-10 pieces/graphs/flot/data/restriction-least-n.js

@@ -1,0 +1,1 @@
+var least_n_points = [[0.01, 98], [0.02, 48], [0.029999999999999999, 31], [0.040000000000000001, 23], [0.050000000000000003, 18], [0.060000000000000005, 14], [0.069999999999999993, 12], [0.080000000000000002, 10], [0.089999999999999997, 9], [0.099999999999999992, 8], [0.11, 7], [0.12, 6], [0.13, 5], [0.14000000000000001, 5], [0.15000000000000002, 4], [0.16, 4], [0.17000000000000001, 4], [0.18000000000000002, 3], [0.19, 3], [0.20000000000000001, 3], [0.21000000000000002, 3], [0.22, 2], [0.23000000000000001, 2], [0.24000000000000002, 2], [0.25, 2], [0.26000000000000001, 2], [0.27000000000000002, 2], [0.28000000000000003, 1], [0.29000000000000004, 1], [0.29999999999999999, 1], [0.31, 1], [0.32000000000000001, 1], [0.33000000000000002, 1], [0.34000000000000002, 1], [0.35000000000000003, 1], [0.36000000000000004, 1], [0.37, 1], [0.38, 1], [0.39000000000000001, 1], [0.40000000000000002, 1], [0.41000000000000003, 1], [0.42000000000000004, 1], [0.42999999999999999, 1], [0.44, 1], [0.45000000000000001, 1], [0.46000000000000002, 1], [0.47000000000000003, 1], [0.48000000000000004, 1], [0.48999999999999999, 1], [0.5, 0]];

### 2010-12-10 pieces/graphs/flot/data/restriction-p-range.js

@@ -1,0 +1,3 @@
+var p_range_bars = [[0, 0.5, 0.5], [1, 0.27639320225002106, 0.72360679774997894], [2, 0.21132486540518713, 0.78867513459481287], [3, 0.17267316464601146, 0.82732683535398854], [4, 0.14644660940672621, 0.85355339059327373], [5, 0.12732200375003505, 0.87267799624996489], [6, 0.1127016653792583, 0.8872983346207417], [7, 0.1011379823912672, 0.89886201760873274], [8, 0.091751709536136983, 0.90824829046386302], [9, 0.083974852831078139, 0.91602514716892181], [10, 0.077422872635741713, 0.92257712736425823], [11, 0.071825580711162407, 0.92817441928883759], [12, 0.066987298107780702, 0.9330127018922193], [13, 0.062762683902396921, 0.93723731609760308], [14, 0.059041448155901566, 0.94095855184409838], [15, 0.055738341680680703, 0.9442616583193193], [16, 0.052786404500042072, 0.94721359549995787], [17, 0.050132294578781322, 0.94986770542121868], [18, 0.047732983133354556, 0.95226701686664539], [19, 0.045553370426807127, 0.95444662957319282], [20, 0.043564535412361549, 0.95643546458763851], [21, 0.041742430504416006, 0.95825756949558394], [22, 0.040066894496100069, 0.95993310550389999], [23, 0.038520896504551372, 0.96147910349544863], [24, 0.03708995011372429, 0.96291004988627571], [25, 0.035761654557370348, 0.96423834544262965], [26, 0.034525331874368625, 0.96547466812563143], [27, 0.033371737371308607, 0.96662826262869139], [28, 0.032292826653257334, 0.96770717334674261], [29, 0.031281566719453979, 0.96871843328054608], [30, 0.030331781686137871, 0.96966821831386207], [31, 0.029438025942839896, 0.97056197405716005], [32, 0.028595479208968322, 0.97140452079103168], [33, 0.027799859198482491, 0.97220014080151751], [34, 0.027047348536541338, 0.97295265146345866], [35, 0.026334533284329054, 0.973665466715671], [36, 0.025658350974743116, 0.97434164902525688], [37, 0.025016046484135468, 0.97498395351586453], [38, 0.024405134394329064, 0.97559486560567099], [39, 0.023823366757133257, 0.97617663324286674], [40, 0.023268705377203824, 0.97673129462279618], [41, 0.022739297890788213, 0.97
[…]

### 2010-12-10 pieces/graphs/flot/data/restriction.js

@@ -1,0 +1,4 @@
+var least_n_points = [[0.01, 98], [0.02, 48], [0.029999999999999999, 31], [0.040000000000000001, 23], [0.050000000000000003, 18], [0.060000000000000005, 14], [0.069999999999999993, 12], [0.080000000000000002, 10], [0.089999999999999997, 9], [0.099999999999999992, 8], [0.11, 7], [0.12, 6], [0.13, 5], [0.14000000000000001, 5], [0.15000000000000002, 4], [0.16, 4], [0.17000000000000001, 4], [0.18000000000000002, 3], [0.19, 3], [0.20000000000000001, 3], [0.21000000000000002, 3], [0.22, 2], [0.23000000000000001, 2], [0.24000000000000002, 2], [0.25, 2], [0.26000000000000001, 2], [0.27000000000000002, 2], [0.28000000000000003, 1], [0.29000000000000004, 1], [0.29999999999999999, 1], [0.31, 1], [0.32000000000000001, 1], [0.33000000000000002, 1], [0.34000000000000002, 1], [0.35000000000000003, 1], [0.36000000000000004, 1], [0.37, 1], [0.38, 1], [0.39000000000000001, 1], [0.40000000000000002, 1], [0.41000000000000003, 1], [0.42000000000000004, 1], [0.42999999999999999, 1], [0.44, 1], [0.45000000000000001, 1], [0.46000000000000002, 1], [0.47000000000000003, 1], [0.48000000000000004, 1], [0.48999999999999999, 1], [0.5, 0]];
[…]

### 2010-12-10 pieces/graphs/flot/json/mabs-headers.js

@@ -1,2 +1,0 @@
-var normal = {}; var sn = {};
-var ns = ["25", "50", "100", "200"];

### 2010-12-10 pieces/graphs/flot/json/mabs.js

@@ -1,10 +1,0 @@
-var normal = {}; var sn = {};
-var ns = ["25", "50", "100", "200"];
-sn.n100 = [[0.019709662154539891, 0.0069206165930497665], [0.029709662154539893, 0.0050456440483724052], [0.039709662154539888, 0.0039757942590482043], [0.04970966215453989, 0.0032820657744922488], [0.059709662154539891, 0.0028626210230579541], [0.069709662154539886, 0.0028377401959075454], [0.079709662154539895, 0.0027186106445759861], [0.089709662154539904, 0.0025668038617868705], [0.099709662154539885, 0.002408189730698812], [0.10970966215453989, 0.0022537798857286684], [0.1197096621545399, 0.0021080343182064698], [0.12970966215453988, 0.0019724221432679545], [0.13970966215453989, 0.0018470414216291975], [0.1497096621545399, 0.0017313722983716973], [0.15970966215453991, 0.0016246547814472989], [0.16970966215453989, 0.001526059895853471], [0.1797096621545399, 0.0014347769503024743], [0.18970966215453991, 0.0013500496566723474], [0.19970966215453989, 0.001271193852114938], [0.2097096621545399, 0.0012050466986987529], [0.21970966215453991, 0.0011479739734885086], [0.22970966215453989, 0.001092061611453421], [0.2397096621545399, 0.0010374946972736276], [0.24970966215453991, 0.00098437936338635623], [0.25970966215453989, 0.00093276711303491577], [0.2697096621545399, 0.00088267133099353967], [0.27970966215453991, 0.00083408029220938262], [0.28970966215453992, 0.00078696502019903747], [0.29970966215453992, 0.00074128628969041821], [0.30970966215453988, 0.00069699856852742381], [0.31970966215453989, 0.00065405387898431755], [0.3297096621545399, 0.00061240403149653844], [0.3397096621545399, 0.00057200256289002827], [0.34970966215453991, 0.00053280634695807016], [0.35970966215453992, 0.00049477686886334471], [0.36970966215453993, 0.00045788152667466941], [0.37970966215453988, 0.00042209470737047949], [0.38970966215453989, 0.00038739926510134026], [0.3997096621545399, 0.0003537882538213466], [0.40970966215453991, 0.00032126707401192167], [0.41970966215453992, 0.00030337074998354474], [0.42970966215453993, 0.00029638103932283499], [0.43970966215453988, 0.00028984225968553545], [0.44970966215453989, 0.00028489030032019524
[…]

### 2010-12-10 pieces/graphs/flot_data.py

@@ -4,6 +4,36 @@ import json
 from stats import *
 
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
+# Skew-normal Restriction Graphs
+#
+def sn_restriction_p_range_graph ():
+  def range_pt (n):
+    range = sn_restriction_p_range(n)
+    return [n, range[0], range[1]]
+  ns = r.seq(0, 50)
+  p_range_bars = map(range_pt, ns)
+  p_top_points = map(lambda range_pt: [range_pt[0], range_pt[1]], p_range_bars)
+  p_bottom_points = map(lambda range_pt: [range_pt[0], range_pt[2]], p_range_bars)
+
+  f = open('flot/data/restriction-p-range.js', 'w');
+  f.write('var p_range_bars = ' + json.dumps(p_range_bars) + ';\n')
+  f.write('var p_top_points = ' + json.dumps(p_top_points) + ';\n')
+  f.write('var p_bottom_points = ' + json.dumps(p_bottom_points) + ';\n')
+  f.close()
+
+def sn_restriction_least_n_graph ():
+  ps = r.seq(0.01, 0.5, 0.01)
+  points = map(lambda p: [p, sn_restriction_least_n(p)], ps)
+
+  f = open('flot/data/restriction-least-n.js', 'w')
+  f.write('var least_n_points = ' + json.dumps(points) + ';\n')
+  f.close()
+
+def compile_sn_restriction_data ():
+  sn_restriction_p_range_graph()
+  sn_restriction_least_n_graph()
+
+#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # Comparison Graphs
 #
 def comparison_graph (n, p):
@@ -13,11 +43,11 @@ def comparison_graph (n, p):
   (binomial, normal, sn) = frame( binomial_pmf(n, p, pairs=True),
                                   normal_pdf(n, p, pairs=True),
                                   sn_pdf(n, p, pairs=True) )
-  def np (): return 'n' + str(n) + 'p' + str(p).replace('.', '')
-  f = open('flot/json/comparison-' + np() + '.json', 'w')
[…]

### 2010-12-10 pieces/graphs/stats.py

@@ -47,7 +47,11 @@ def sn_pdf (n, p, pairs=False):
   ys = r.dsn(xs, mu, sigma, skew)
   return pair(xs, ys) if pairs else {'xs':xs, 'ys':ys}
 
-def sn_p_range (n):
+def sn_restriction_least_n (p):
+  # Given p, finds the least viable n
+  return int(math.ceil( (1-2*p)**2 / (p*(1-p)) ))
+
+def sn_restriction_p_range (n):
   # Given n, finds the upper and lower bound of viable p's
   a = 1/2
   b = 1/2 * math.sqrt(n/(n+4))

### 2010-12-12 pieces/mabs/mabs.tex
Implemented bibliography, wrote mabs section

@@
-\documentclass{article}
-\usepackage{joyce-math}
+\section{Demonstrating Improved Accuracy}
 
-\begin{document}
-\section{Demonstrating Improved Accuracy}
+We have gone to considerable trouble to develop our skew-normal approximation
+for the binomial; now comes the time to justify our efforts by demonstrating
+its improved accuracy over the regular normal one.
+
+\subsection{Visual Comparison}
+
+The first, and most obvious, way of judging accuracy is by visual inspection.
+Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
+\ref{fig:comparison-n100} compare the binomial, normal, and skew-normal at
+small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively. It is not
+hard to see that, especially at very small $n$ and $p$, our skew-normal curve
+follows the shape of the binomial much more accurately.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/comparison-n25.png}
+  \caption{Binomial, normal, and skew-normal, $n=25$}
+  \label{fig:comparison-n25}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/comparison-n50.png}
+  \caption{Binomial, normal, and skew-normal, $n=50$}
+  \label{fig:comparison-n50}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/comparison-n100.png}
+  \caption{Binomial, normal, and skew-normal, $n=100$}
+  \label{fig:comparison-n100}
+\end{figure}
 
@@
 
-Define the maximal absolute error of the approximation to be
+Another more numerical method would be to compare the maximal absolute errors
+of our two approximations, defined by \citet{mabs} as
 
 \begin{equation}
-  MABS(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{appr(n,p)}(k + 0.5) \right|
+  \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
 \end{equation}
 
-where $F_{B(n,p)}$ is the cdf of the binomial and $F_{appr(n,p)}$ is the cdf of
-either the normal or skew-normal approximation; the 0.5 is a continuity
-correction.
+where $F_{B(n,p)}$ is the cdf of the binomial and $F_{\textnormal{appr}(n,p)}$
+is the cdf of either the normal or skew-normal approximation; the 0.5 is a
+continuity correction.
 
-\end{document}
+Figure \ref{fig:mabs-fixed-n} shows the MABS as a function of $p$, for $n=25$
+and $n=100$. Figure \ref{fig:mabs-fixed-p}, on the other hand, shows the MABS
+as a function of $n$, for $p=0.05$ and $p=0.1$. Again, the skew-normal
+outperforms the normal considerably in the extreme ranges, with the two
+approximations converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
+  \caption{MABS as a function of p}
+  \label{fig:mabs-fixed-n}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-p.png}
+  \caption{MABS as a function of n}
+  \label{fig:mabs-fixed-p}
+\end{figure}
+
+\nocite{*}

### 2010-12-12 pieces/mabs/output.tex
Reorganized in preparation of compiling final paper.
Implemented bibliography, wrote mabs section

--- 2010-12-10 pieces/mabs/mabs.tex
@@
 \documentclass{article}
-\usepackage{joyce-math}
+\usepackage{joyce-math, joyce-bib, joyce-graphics}
+\bibpunct{(}{)}{;}{a}{,}{,}
+\begin{document}
 
-\begin{document}
 \section{Demonstrating Improved Accuracy}
+
+We have gone to considerable trouble to develop our skew-normal approximation
+for the binomial; now comes the time to justify our efforts by demonstrating
+its improved accuracy over the regular normal one.
+
+\subsection{Visual Comparison}
+
+The first, and most obvious, way of judging accuracy is by visual inspection.
+Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
+\ref{fig:comparison-n100} compare the binomial, normal, and skew-normal at
+small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively. It is not
+hard to see that, especially at very small $n$ and $p$, our skew-normal curve
+follows the shape of the binomial much more accurately.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/comparison-n25.png}
+  \caption{Binomial, normal, and skew-normal, $n=25$}
+  \label{fig:comparison-n25}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/comparison-n50.png}
+  \caption{Binomial, normal, and skew-normal, $n=50$}
+  \label{fig:comparison-n50}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/comparison-n100.png}
+  \caption{Binomial, normal, and skew-normal, $n=100$}
+  \label{fig:comparison-n100}
+\end{figure}
 
@@
 
-Define the maximal absolute error of the approximation to be
+Another more numerical method would be to compare the maximal absolute errors
+of our two approximations, defined by \citet{mabs} as
 
 \begin{equation}
-  MABS(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{appr(n,p)}(k + 0.5) \right|
+  \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
 \end{equation}
 
-where $F_{B(n,p)}$ is the cdf of the binomial and $F_{appr(n,p)}$ is the cdf of
-either the normal or skew-normal approximation; the 0.5 is a continuity
-correction.
+where $F_{B(n,p)}$ is the cdf of the binomial and $F_{\textnormal{appr}(n,p)}$
+is the cdf of either the normal or skew-normal approximation; the 0.5 is a
+continuity correction.
 
+Figure \ref{fig:mabs-fixed-n} shows the MABS as a function of $p$, for $n=25$
+and $n=100$. Figure \ref{fig:mabs-fixed-p}, on the other hand, shows the MABS
+as a function of $n$, for $p=0.05$ and $p=0.1$. Again, the skew-normal
+outperforms the normal considerably in the extreme ranges, with the two
+approximations converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
+  \caption{MABS as a function of p}
+  \label{fig:mabs-fixed-n}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-p.png}
+  \caption{MABS as a function of n}
+  \label{fig:mabs-fixed-p}
+\end{figure}
+
+\nocite{*}
+
+\bibliography{/home/joycetipping/projects/capstone/pieces/bibliography/bibliography.bib}
+\bibliographystyle{plainnat}
 \end{document}

### 2010-12-13 pieces/final-paper/intro.tex
Final paper written, compiled, and tweaked to death.

\title{The Skew-Normal Approximation of the Binomial Distribution}
\author{Joyce Tipping}
\date{2010}
\maketitle

\section{Introduction}

One of the most basic distributions in statistics is the binomial, $X \sim
Bin(n,p)$, with pdf

\begin{equation*}
  f_X(x) = \binom{n}{x} p^x q^{n-x}
\end{equation*}

Calculating the binomial cdf, $F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by
hand is manageable for small $n$ but quickly becomes cumbersome as $n$ grows
even mediumly large. A common strategy is to use the normal distribution as an
approximation:

\begin{equation}
  F_X(x) \approx \Phi \left( \frac{k + 0.5 - \mu}{\sigma} \right)
\end{equation}

where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
\sqrt{np(1-p)}$.

This approximation works well when either $n$ is very large (invoking the
Central Limit Theorem) or when $p$ is close to 0.5 (making $X$ roughly
symmetric). These rules of thumb are captured in a requirement, often stated as

\begin{equation*}
  np(1-p) > 9
\end{equation*}

or

\begin{align*}
      np &> 5 \quad \textnormal{for} \quad  0 < p \leq 0.5, \\
  n(1-p) &> 5 \quad \textnormal{for} \quad  0.5 < p < 1
\end{align*}

However, when $n$ is not large and $p$ is close to 0 or 1, the binomial
distribution is skewed and even if the above requrements are met, the
approximation can be inaccurate; sometimes, as demonstrated by \citet{mabs},
rather substantially. In these cases, the skew-normal approximation can provide
an alternative -- and considerably more accurate -- method of approximation.

### 2010-12-13 pieces/final-paper/output.tex
Final paper written, compiled, and tweaked to death.

\documentclass{article}
\usepackage{jcapstone}
\begin{document}

\title{The Skew-Normal Approximation of the Binomial Distribution}
\author{Joyce Tipping}
\date{2010}
\maketitle

\section{Introduction}

One of the most basic distributions in statistics is the binomial, $X \sim
Bin(n,p)$, with pdf

\begin{equation*}
  f_X(x) = \binom{n}{x} p^x q^{n-x}
\end{equation*}

Calculating the binomial cdf, $F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by
hand is manageable for small $n$ but quickly becomes cumbersome as $n$ grows
even mediumly large. A common strategy is to use the normal distribution as an
approximation:

\begin{equation}
  F_X(x) \approx \Phi \left( \frac{k + 0.5 - \mu}{\sigma} \right)
\end{equation}

where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
\sqrt{np(1-p)}$.

This approximation works well when either $n$ is very large (invoking the
Central Limit Theorem) or when $p$ is close to 0.5 (making $X$ roughly
symmetric). These rules of thumb are captured in a requirement, often stated as

\begin{equation*}
  np(1-p) > 9
\end{equation*}

or

\begin{align*}
      np &> 5 \quad \textnormal{for} \quad  0 < p \leq 0.5, \\
  n(1-p) &> 5 \quad \textnormal{for} \quad  0.5 < p < 1
\end{align*}

However, when $n$ is not large and $p$ is close to 0 or 1, the binomial
distribution is skewed and even if the above requrements are met, the
approximation can be inaccurate; sometimes, as demonstrated by \citet{mabs},
rather substantially. In these cases, the skew-normal approximation can provide
an alternative -- and considerably more accurate -- method of approximation.

\section{The Skew-Normal}

The skew-normal distribution is similar to the normal but with an added
parameter for skew. In this section, we'll introduce

\subsection{Basics}

Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$, denoted
$SN(\mu, \sigma, \lambda)$. Then $Y$ has pdf

\begin{equation} \label{eq:sn-pdf}
  f_Y(x) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right)
\end{equation}

where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal cdf.
Some other basic properties of $Y$, given by \citet{pewsey}, are

\begin{align}
  E(Y) &= \mu + b \delta \sigma \nonumber \\
  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 \label{eq:sn-basic-properties} \\
  Var(Y) &= \sigma^2 (1 - b^2 \delta^2) \nonumber \\
  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \nonumber
\end{align}

where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
\lambda^2}}$.

The $SN(0,1,\lambda)$ distribution is called the standard skew-normal, and has
pdf

\begin{equation} \label{eq:standard-sn-pdf}
  f_z(x) = 2 \cdot \phi(x) \cdot \Phi (-\lambda x)
\end{equation}

Like the normal and standard normal, you can arrive at the standard skew normal
by applying the transformation $\frac{Y - \mu}{\sigma}$.

A natural question to ask is how the skew-normal relates to the normal.
Fortunately, the connection is very intuitive: When $\lambda = 0$, Equation
\eqref{eq:sn-pdf} reverts to the normal pdf:

\begin{align*}
  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
  &= \frac{1}{\sqrt{2\pi\sigma^2}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right)
\end{align*}

\subsection{Four Properties}
\label{subsec:four-properties}

\citet{main} gives four handy properties of the skew-normal distribution:

\begin{property} \label{prop:1}
  If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
\end{property}

\begin{proof}
  The standard normal pdf is an even function: $\phi(-x) =
  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) =
  \int_{-\infty}^\infty \phi(x)$, \thinspace is not, being 0 near $-\infty$ and
  1 near $\infty$. Thus,

  \begin{align*}
    f_{(-Z)}(x) &= f_Z(-x) \\
    & = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\
    & = 2 \cdot \phi(x) \cdot \Phi (-\lambda x)
  \end{align*}

  which is the pdf of $SN(0, 1, -\lambda)$.
\end{proof}

\begin{property} \label{prop:2}
  As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
\end{property}

To prove our theorem, it is helpful to formally define the half normal distribution:

\begin{helper-lem} \label{lem:p2-half-normal}
  Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal
  random variable with parameter $\sigma$ and

  \begin{equation*}
    f_{|X|}(x) =
    \begin{dcases*}
      2 \cdot f_X(x) & when $0 < x < \infty$ \\
      0 & everywhere else
    \end{dcases*}
  \end{equation*}
\end{helper-lem}

\begin{proof}
  Let $X \sim N(0, \sigma^2)$, defined over $A = (-\infty, \infty)$. Define

  \begin{equation*}
    Y = |X| =
    \begin{dcases*}
      -x & if $x < 0$ \\
      0 & if $x = 0$ \\
      x & if $x > 0$ \\
    \end{dcases*}
  \end{equation*}

  $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such
  that $A = A_1 \cup A_2 \cup A_3$ and $Y$ is one-to-one over each $A_i$. We
  can then transform each piece separately using Theorem 6.3.2 from
  \citet{textbook}:

  On $A_1$: $y = -x \lra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1|
  = 1$, yielding

  \begin{align}
    f_Y(y) &= f_X(x) \cdot \J \nonumber \\
    &= f_X(-y) \cdot 1 \nonumber \\
    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma}} \nonumber \\
    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma}} \nonumber \\
    &= f_X(y) \label{eq:p2-transform-a1}
  \end{align}

  over the domain $A_1: -\infty < x < 0 \lra -\infty < -y < 0 \lra 0 < y < \infty :B_1$.

  Similarly, on $A_2$: $y = x \lra x = y$ and $\J = \left| \frac{dx}{dy}
  \right| = |1| = 1$, yielding

  \begin{align}
    f_Y(y) &= f_X(x) \cdot \J \nonumber \\
    &= f_X(y) \cdot 1 \nonumber \\
    &= f_X(y) \label{eq:p2-transform-a2}
  \end{align}

  over the domain $A_2: 0 < x < \infty \lra 0 < y < \infty :B_2$.

  On $A_3$, we have $x = 0, y = 0$ and $\J = \left| \frac{dx}{dy} \right| = |0|
  = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.

  Now, by Theorem 6.3.10 from \citet{textbook}, we achieve our result by simply
  summing \eqref{eq:p2-transform-a1} and \eqref{eq:p2-transform-a2}.

  \begin{align}
    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \nonumber \\
    &= f_X(y) + f_X(y) \nonumber \\
    &= 2 \cdot f_X(y) \label{eq:p2-transform-result}
  \end{align}

  over $B = B_1 \cup B_2 = (0, \infty)$, and 0 otherwise.
\end{proof}

With Lemma \ref{lem:p2-half-normal}, we can easily show our property:

\begin{proof}[Proof of Property 2]
  Let $Z \sim SN(0,1,\lambda)$. Recall that $f_z(x) = 2 \cdot \phi(x) \cdot
  \Phi(\lambda x)$.

  Consider $\lim_{\lambda \to \infty} f_X(x)$. When $x$ is negative, $\lambda x
  \to -\infty$ and thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however,
  $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. Thus

  \begin{equation}
    \label{eq:p2-positive-half-normal}
    \lim_{\lambda \to \infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
    \begin{dcases*}
      0 & when $x \leq 0$ \\
      2 \cdot \phi(x) & when $x > 0$
    \end{dcases*}
    \eq |N(0,1)|
  \end{equation}

  In $\lim_{\lambda \to -\infty} f_X(x)$, the signs are reversed. When $x$ is
  negative, $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. When $x$ is
  positive, $\lambda x \to -\infty$ and $\Phi(\lambda x) \to 0$. Thus,

  \begin{equation}
    \label{eq:p2-negative-half-normal}
    \lim_{\lambda \to -\infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
    \begin{dcases*}
      2 \cdot \phi(x) & when $x < 0$ \\
      0 & when $x \geq 0$
    \end{dcases*}
    \eq -|N(0,1)|
  \end{equation}
\end{proof}

\begin{property} \label{prop:3}
  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
\end{property}

\begin{proof}
  To prove our result, we make use of Lemma 1 in \citet{azzalini}:

  \begin{helper-lem}
    If $f_0$ is a one-dimensional probability density function symmetric about
    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
    and is a density symmetric about 0, then

    \begin{equation}
      \label{eq:azzalini-perturbation-invariance}
      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
    \end{equation}

    is a density function for any odd function $w(\cdot)$.
  \end{helper-lem}

  Notice that $\phi(x)$ is a one-dimensional probability density function
  symmetric about 0, and $\Phi(x)$ is a one-dimensional distribution function
  such that $\Phi'$ exists and is a density symmetric about 0. Furthermore,
  $\lambda x$ is an odd function. Thus, $f_z(z) = 2 \cdot \phi(z) \cdot
  \Phi(\lambda z)$ conforms to equation
  \eqref{eq:azzalini-perturbation-invariance}. With that in mind, the corollary
  to this lemma provides a very useful result:

  \begin{helper-cor}[Perturbation Invariance]
    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
    notation $\overset{d}{=}$ denotes equality in distribution.    
  \end{helper-cor}

  Thus, we can treat $\phi$ and $Z$ as being equal in distribution. We will now
  show that $\phi^2 \sim \chi^2_1$:

  \begin{align*}
    M_{\phi^2}(t) &= E[e^{tx^2}] \\
    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \\
    \intertext{Let $u = (\sqrt{1-2t}) \, x$; then we have $du = \sqrt{1-2t}$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty \Ra u \to -\infty$
      and $x \to \infty \Ra u \to \infty$.}
    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} \right) du \\
    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
    &= \frac{1}{\sqrt{1-2t}}
  \end{align*}

  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}

\begin{property} \label{prop:4}
  The MGF of $SN(0,1,\lambda)$ is

  \begin{equation} \label{eq:p4-sn-mgf}
    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2}
  \end{equation}

  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
\end{property}

\begin{proof}
  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma^2,
  \lambda)$ is

  \begin{equation*}
    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t)
  \end{equation*}

  where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$. It follows that
  the MGF of the $SN(0, 1, \lambda)$ is

  \begin{equation*}
    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t)
  \end{equation*}
\end{proof}

\section{Developing an Approximation}

Next, we develop our skew-normal approximation of the binomial. Let $B \sim
Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find estimates for
$\mu$, $\sigma$, and $\lambda$ by comparing their first, second, and third
moments about the mean.

\subsection{The Moments of the Binomial}

We begin by examining the moments of the binomial. The first two, the mean and
variance, are simply

\begin{equation*}
  E(B) = np, \quad Var(B) = np(1-p)
\end{equation*}

Having these, we can easily find

\begin{equation*}
  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2
\end{equation*}

which we will need for the third moment. We will also need $E(B^3)$, which we
will get via the third factorial moment:

\begin{align*}
  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\
  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
  \intertext{Let $y=x-3$. Then $x=y+3$, and $x=3 \rightarrow y=0$ and $x=n \rightarrow y=n-3$.}
  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
  &= n(n-1)(n-2)p^3 \\
  &= n^3p^3 - 3n^2p^3 + 2np^3 \\
  \intertext{Further expanding the left side and solving for $E(B^3)$,}
  E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\
  E(B^3) - 3E(B^2) + 2E(B) &= \\
  E(B^3) - 3(np - np^2 + n^2p^2) + 2np &= \\
  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 + 3np - 3np^2 + 3n^2p^2 - 2np \\
  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np
\end{align*}

With these results (and a bit of elbow grease), we can obtain the third moment
without too much trouble:

\begin{align*}
  E \left( [B - E(B)]^3 \right) &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
  &= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\
  &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
  &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) - 3np(np - np^2 + n^2p^2) + 2n^3p^3 \\
  &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
  &= 2np^3 - 3np^2 + np \\
  &= np(p-1)(2p-1)
\end{align*}

Our hard-earned results, restated for convenience:

\begin{align}
  E(B) &= np \nonumber \\
  E([B - E(B)]^2) &= np(1-p) \\
  E([B - E(B)]^3) &= np(p-1)(2p-1) \nonumber
\end{align}

\subsection{The Moments of the Skew Normal}

Now we'll take a look at the moments of the skew normal. Equation
\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
third moment is a little more complicated:

\begin{align*}
  E([Y - E(Y)]^3) &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
  &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) \\
  & \quad + 2\;(\mu + b \delta \sigma)^3 \\
  &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{9 b \delta \mu^2 \sigma} -
    \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} \\
  & \quad - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
  &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
  &= b \delta^3 \sigma^3 (2b^2 - 1)
\end{align*}

We restate our results:

\begin{alignat}{4}
  E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \nonumber \\
  E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \\
  E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \nonumber
\end{alignat}

\subsection{Solving for $\mu$, $\sigma$, $\lambda$}

Now we set the two sets of moments equal to each other and, taking $n$ and $p$
as constants, solve for $\mu$, $\sigma$ and $\lambda$.

\begin{subequations}
\begin{align}
  np &= \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \label{eq:first-moment-set} \\
  np(1-p) &= \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:second-moment-set} \\
  np(p-1)(2p-1) &= \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \label{eq:third-moment-set}
\end{align}
\end{subequations}

To get $\lambda$, we divide the cube of \eqref{eq:second-moment-set} by the
square of \eqref{eq:third-moment-set}:

\begin{align}
  \frac{\sigma^6 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right)^3}{\sigma^6 \cdot \frac{2}{\pi} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^6 \left(
    \frac{4}{\pi} - 1 \right)^2} &= \frac{n^3p^3(1-p)^3}{n^2p^2(p-1)^2(2p-1)^2} \nonumber \\
  \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
    \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \label{eq:solving-for-lambda}
\end{align}

The above equation \eqref{eq:solving-for-lambda} is a rational expression in
$\lambda^2$ that can be solved with either a considerable amount of manual
labor or, more efficiently, with a computer algebra system. Once we have
$\lambda^2$, then $\lambda$ is simply either the positive or negative square
root, as determined by the sign of $(1-2p)$. This can be explained with a
little assistance from Property \ref{prop:3}: When $p \to 0$, the binomial
skews left and converges toward the positive half normal, which by
\eqref{eq:p2-positive-half-normal} corresponds to a positive $\lambda$. When $p
\to 1$, the binomial skews right and converges toward the negative half normal,
which by \eqref{eq:p2-negative-half-normal} corresponds to a negative
$\lambda$. When $p = 0.5$, the binomial is symmetric and $\lambda$ is 0,
eliminating the need for a sign. Thus:

\begin{equation}
  \label{eq:lambda-solved}
  \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}
\end{equation}

%\textbf{\textit{Note to Dr. Guffey:} I am trying to find an algebraic reason
%for the sign, but I'm not seeing it in equation \eqref{eq:solving-for-lambda}
%nor its algebraic expansion, which I put in in appendix
%\ref{sec:solving-for-lambda} as it ended up providing little insight into this
%conclusion.}

Having secured $\lambda$, we can find $\sigma$ using
\eqref{eq:second-moment-set}:

\begin{equation}
  \label{eq:sigma-solved}
  np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}}
\end{equation}

Similarly, with both $\lambda$ and $\sigma$, a simple rearrangement of
\eqref{eq:first-moment-set} yields $\mu$:

\begin{equation}
  \label{eq:mu-solved}
  np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}}
\end{equation}

When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
the mean therefore to be $n/2$. From \eqref{eq:mu-solved}, this implies that
$\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} =
0 \Ra$ either $\sigma = 0$ or $\lambda = 0$. Since the former is impossible, we
must conclude the latter, which brings us back to the normal distribution.

%\textbf{\textit{Another note to Dr. Guffey:} The author mentions here that when
%$p=0.5$, it forces $\lambda$ to be 0, bringing us back to the regular normal
%approximation. This seems like it ought to be a simple fact, but I can't figure
%out how he's getting it from these equations. He refers to his equation (c),
%which is my equation \eqref{eq:mu-solved}. Substituting $p=0.5$ into
%\eqref{eq:mu-solved}, however, doesn't get me anywhere; neither does
%substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
%into \eqref{eq:mu-solved}. And as far as I can tell, equation
%\eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}

\subsection{Restrictions}

To obtain an estimate for $\lambda$, we must put a few restrictions on $n$ and
$p$.

If we let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u$, we can rewrite the
left hand side of \eqref{eq:solving-for-lambda} as

\begin{gather}
  \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. \nonumber \\
  \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 \nonumber \\
  \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \nonumber \\
  \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \label{eq:lhs-solving-for-lambda}
\end{gather}

we can see that it is increasing in $v$, which is always $\geq 1$. Therefore:

\begin{equation}
  \min_{v} \textnormal{\{Eq. \ref{eq:lhs-solving-for-lambda}\}} = \textnormal{\{Eq. \ref{eq:lhs-solving-for-lambda}\}} |_{v=1} = 
  \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1
\end{equation}

This means that the right hand side of \eqref{eq:solving-for-lambda}, which is
supposed to be equal to the left hand side of \eqref{eq:solving-for-lambda},
can't ever be less than 1. Unfortunately, it sometimes is; in particular,
$\frac{np(1-p)}{(1-2p)^2} \to 0$ both when $p \to 0$ and $p \to 1$. So if we
want a solution, we must restrict $n$ and $p$ such that

\begin{align}
  \textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\
  \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
  np(1-p) &\geq (1-2p)^2 \label{eq:solving-the-restriction}
\end{align}

From here, given a constant $p$, finding $n$ is very simple:

\begin{equation}
  n \geq \frac{(1-2p)^2}{p(1-p)} \label{eq: n for a given p}
\end{equation}

Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
estimate $\lambda$, given a fixed $p$. As expected, the least $n$ is quite
large when $p$ is small and $\to 0$ as $p \to 0.5$. For example, when $p =
0.01$, $n \geq 98$; but at $p = 0.2$, $n$ must only be $\geq 3$, a trivial
requirement to meet.

\begin{figure}
  \centering
  \subfloat[Least possible $n$, given a fixed $p$]{\label{fig:sn-restriction-least-n}\includegraphics[width=0.45\textwidth]{../graphs/images/restriction-least-n.png}}
  \quad
  \subfloat[Range of possible $p$, given a fixed $n$]{\label{fig:sn-restriction-p-range}\includegraphics[width=0.45\textwidth]{../graphs/images/restriction-p-range.png}}
  \caption{Restrictions on $n$ and $p$ for estimating $\lambda$}
  \label{fig:sn-restriction}
\end{figure}

It is also possible to fix $n$ and solve for $p$. We return to
\eqref{eq:solving-the-restriction} for further factoring

\begin{align}
  np - np^2 &\geq 1 - 4p + 4p^2 \nonumber \\
  1 - 4p + 4p^2 - np + np^2 &\leq 0 \nonumber \\
  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq: solving for p}
\end{align}

and apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:

\begin{gather*}
  \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
  \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
  \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n-4)} \\
  \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
  \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}}
\end{gather*}

Let $r_1 = \frac12 - \frac12 \sqrt{\frac{n}{n+4}}$ and $r_2 = \frac12 + \frac12
\sqrt{\frac{n}{n+4}}$. (Note that $r_1 < r_2$.) Now we can rewrite \eqref{eq:
solving for p} as

\begin{equation*}
  (p - r_1)(p - r_2) \leq 0
\end{equation*}

Examining the left hand side, when $p < r_1$, both terms are negative and so
their product is positive; when $p > r_2$, both terms are positive, again
leading the product to be positive. Therefore, our solution lies where $r_1
\leq p \leq r_2$, or more explicitly:

\begin{equation}
 \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}}
\end{equation}

As shown in figure \ref{fig:sn-restriction-p-range}, this interval grows
quickly as $n$ increases, and for sufficiently large $n$, it becomes almost
$(0, 1)$. For example, when $n=100$, our interval is $(0.00971, 0.99029)$; when
$n=500$, it is (0.00199, 0.99801).

For $p$ so close to 0 or 1 that this solution will not work, our authors
suggest a Poission approximation.

\section{Demonstrating Improved Accuracy}

Having taken the trouble to develop our skew-normal approximation for the
binomial, we now justify our efforts by demonstrating its improved accuracy
over the regular normal approximation.

\subsection{Visual Comparison}

The first, and most obvious, way of judging accuracy is by visual inspection.
Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
\ref{fig:comparison-n100} compare the binomial, normal, and skew-normal at
small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively. It is not
hard to see that, especially at very small $n$ and $p$, our skew-normal curve
follows the shape of the binomial much more accurately.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../graphs/images/comparison-n25.png}
  \caption{Binomial, normal, and skew-normal, $n=25$}
  \label{fig:comparison-n25}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../graphs/images/comparison-n50.png}
  \caption{Binomial, normal, and skew-normal, $n=50$}
  \label{fig:comparison-n50}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../graphs/images/comparison-n100.png}
  \caption{Binomial, normal, and skew-normal, $n=100$}
  \label{fig:comparison-n100}
\end{figure}

\subsection{Maximal Absolute Error}

Another more numerical method would be to compare the maximal absolute errors
of our two approximations, defined by \citet{mabs} as

\begin{equation}
  \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
\end{equation}

where $F_{B(n,p)}$ is the cdf of the binomial and $F_{\textnormal{appr}(n,p)}$
is the cdf of either the normal or skew-normal approximation; the 0.5 is a
continuity correction.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
  \caption{MABS as a function of p}
  \label{fig:mabs-fixed-n}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-p.png}
  \caption{MABS as a function of n}
  \label{fig:mabs-fixed-p}
\end{figure}

Figure \ref{fig:mabs-fixed-n} shows the MABS as a function of $p$, for $n=25$
and $n=100$. Figure \ref{fig:mabs-fixed-p}, on the other hand, shows the MABS
as a function of $n$, for $p=0.05$ and $p=0.1$. Again, the skew-normal
outperforms the normal considerably in the extreme ranges, with the two
approximations converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.

\clearpage

\bibliography{/home/joycetipping/projects/capstone/pieces/bibliography/bibliography.bib}
\bibliographystyle{plainnat}
\end{document}

### 2010-12-13 pieces/mabs/mabs.tex
Final paper written, compiled, and tweaked to death.

@@
 
-We have gone to considerable trouble to develop our skew-normal approximation
-for the binomial; now comes the time to justify our efforts by demonstrating
-its improved accuracy over the regular normal one.
+Having taken the trouble to develop our skew-normal approximation for the
+binomial, we now justify our efforts by demonstrating its improved accuracy
+over the regular normal approximation.
 
@@
 
-\begin{figure}[h]
+\begin{figure}
   \centering
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
+  \caption{MABS as a function of p}
+  \label{fig:mabs-fixed-n}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-p.png}
+  \caption{MABS as a function of n}
+  \label{fig:mabs-fixed-p}
+\end{figure}
+
 Figure \ref{fig:mabs-fixed-n} shows the MABS as a function of $p$, for $n=25$
@@
 
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
-  \caption{MABS as a function of p}
-  \label{fig:mabs-fixed-n}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-p.png}
-  \caption{MABS as a function of n}
-  \label{fig:mabs-fixed-p}
-\end{figure}
-
-\nocite{*}
+\clearpage

### 2010-12-13 pieces/method-of-moments/method-of-moments.tex
Final paper written, compiled, and tweaked to death.

@@
-\documentclass{article}
-\usepackage {joyce-math}
+\section{Developing an Approximation}
 
-\begin{document}
-\section{The Method of Moments}
-
-Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
-approximations for $\mu$, $\sigma$, and $\lambda$ by comparing their first,
-second, and third moments about the mean.
+Next, we develop our skew-normal approximation of the binomial. Let $B \sim
+Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find estimates for
+$\mu$, $\sigma$, and $\lambda$ by comparing their first, second, and third
+moments about the mean.
 
@@
 
-The first two moments, the mean and variance, are simply
+We begin by examining the moments of the binomial. The first two, the mean and
+variance, are simply
 
@@
   &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\text{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
+  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
   &= n(n-1)(n-2)p^3 \\
@@
 
-Now we'll take a look at the moments of the skew normal. According to Equation
-1 in Pewsey (2000)
-
-\begin{align*}
-  E(Y) &= \mu + b \delta \sigma \\
-  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 \\
-  Var(Y) &= \sigma^2 (1 - b^2 \delta^2) \\
-  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \nonumber
-\end{align*}
-
-where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}}$. This takes care of our first two moments; again the third is a
-little more complicated:
+Now we'll take a look at the moments of the skew normal. Equation
+\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
+third moment is a little more complicated:
 
@@
 $\lambda^2$, then $\lambda$ is simply either the positive or negative square
-root, as determined by the sign of $(1-2p)$: When $p \rightarrow 0$, the
-binomial skews left and converges on the positive half normal, so $\lambda$
-should be positive; when $p \rightarrow 1$, the binomial skews right and
-converges on the negative half normal, so $\lambda$ should be negative; and
-when $p = 0.5$, the binomial is symmetric and $\lambda$ is 0, eliminating the
-need for a sign. Thus:
+root, as determined by the sign of $(1-2p)$. This can be explained with a
+little assistance from Property \ref{prop:3}: When $p \to 0$, the binomial
+skews left and converges toward the positive half normal, which by
+\eqref{eq:p2-positive-half-normal} corresponds to a positive $\lambda$. When $p
+\to 1$, the binomial skews right and converges toward the negative half normal,
+which by \eqref{eq:p2-negative-half-normal} corresponds to a negative
+$\lambda$. When $p = 0.5$, the binomial is symmetric and $\lambda$ is 0,
+eliminating the need for a sign. Thus:
 
@@
 
-\textbf{\textit{Note to Dr. Guffey:} I am trying to find an algebraic reason
-for the sign, but I'm not seeing it in equation \eqref{eq:solving-for-lambda}
-nor its algebraic expansion, which I put in in appendix
-\ref{sec:solving-for-lambda} as it ended up providing little insight into this
-conclusion.}
+%\textbf{\textit{Note to Dr. Guffey:} I am trying to find an algebraic reason
+%for the sign, but I'm not seeing it in equation \eqref{eq:solving-for-lambda}
+%nor its algebraic expansion, which I put in in appendix
+%\ref{sec:solving-for-lambda} as it ended up providing little insight into this
+%conclusion.}
 
@@
 
-\textbf{\textit{Another note to Dr. Guffey:} The author mentions here that when
-$p=0.5$, it forces $\lambda$ to be 0, bringing us back to the regular normal
-approximation. This seems like it ought to be a simple fact, but I can't figure
-out how he's getting it from these equations. He refers to his equation (c),
-which is my equation \eqref{eq:mu-solved}. Substituting $p=0.5$ into
-\eqref{eq:mu-solved}, however, doesn't get me anywhere; neither does
-substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
-into \eqref{eq:mu-solved}. And as far as I can tell, equation
-\eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}
+When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
+the mean therefore to be $n/2$. From \eqref{eq:mu-solved}, this implies that
+$\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} =
+0 \Ra$ either $\sigma = 0$ or $\lambda = 0$. Since the former is impossible, we
+must conclude the latter, which brings us back to the normal distribution.
+
+%\textbf{\textit{Another note to Dr. Guffey:} The author mentions here that when
+%$p=0.5$, it forces $\lambda$ to be 0, bringing us back to the regular normal
+%approximation. This seems like it ought to be a simple fact, but I can't figure
+%out how he's getting it from these equations. He refers to his equation (c),
+%which is my equation \eqref{eq:mu-solved}. Substituting $p=0.5$ into
+%\eqref{eq:mu-solved}, however, doesn't get me anywhere; neither does
+%substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
+%into \eqref{eq:mu-solved}. And as far as I can tell, equation
+%\eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}
 
 \subsection{Restrictions}
+
+To obtain an estimate for $\lambda$, we must put a few restrictions on $n$ and
+$p$.
 
@@
 can't ever be less than 1. Unfortunately, it sometimes is; in particular,
-$\frac{np(1-p)}{(1-2p)^2} \rightarrow 0$ both when $p \rightarrow 0$ and $p
-\rightarrow 1$. So if we want a solution, we must restrict $n$ and $p$ such
-that
+$\frac{np(1-p)}{(1-2p)^2} \to 0$ both when $p \to 0$ and $p \to 1$. So if we
+want a solution, we must restrict $n$ and $p$ such that
 
@@
 
-If, however, we wish to fix $n$ and solve for $p$, we further factor \eqref{eq:solving-the-restriction}
+Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
+estimate $\lambda$, given a fixed $p$. As expected, the least $n$ is quite
+large when $p$ is small and $\to 0$ as $p \to 0.5$. For example, when $p =
+0.01$, $n \geq 98$; but at $p = 0.2$, $n$ must only be $\geq 3$, a trivial
+requirement to meet.
+
+\begin{figure}
+  \centering
+  \subfloat[Least possible $n$, given a fixed $p$]{\label{fig:sn-restriction-least-n}\includegraphics[width=0.45\textwidth]{../graphs/images/restriction-least-n.png}}
+  \quad
+  \subfloat[Range of possible $p$, given a fixed $n$]{\label{fig:sn-restriction-p-range}\includegraphics[width=0.45\textwidth]{../graphs/images/restriction-p-range.png}}
+  \caption{Restrictions on $n$ and $p$ for estimating $\lambda$}
+  \label{fig:sn-restriction}
+\end{figure}
+
+It is also possible to fix $n$ and solve for $p$. We return to
+\eqref{eq:solving-the-restriction} for further factoring
 
@@
 
-For sufficiently large $n$, this interval becomes almost $(0, 1)$. For example,
-when $n=100$, our interval is $(0.00971, 0.99029)$; when $n=500$, it is
-(0.00199, 0.99801).
+As shown in figure \ref{fig:sn-restriction-p-range}, this interval grows
+quickly as $n$ increases, and for sufficiently large $n$, it becomes almost
+$(0, 1)$. For example, when $n=100$, our interval is $(0.00971, 0.99029)$; when
+$n=500$, it is (0.00199, 0.99801).
 
@@
 suggest a Poission approximation.
-
-\appendix
-\section{Solving for $\lambda$}
-\label{sec:solving-for-lambda}
-
-Hoping that it would provide some insight into \eqref{eq:lambda-solved}, I
-expanded \eqref{eq:solving-for-lambda} after moving all terms to the left hand
-side:
-
-\begin{gather*}
-  \left. \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3 \middle/ \left[ \frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-    \right)^2 \right] \right. \;-\; \frac{np(1-p)}{(1-2p)^2} \\
-  \left. \left( \frac{\pi(1+\lambda^2) - 2\lambda^2}{\pi(1+\lambda^2)} \right)^3 \middle/ \left( \frac{2(4-\pi)^2\lambda^6} {\pi^3(1+\lambda^2)^3} \right) \right. \;-\; \frac{np(1-p)}{(1-2p)^2} \\
-  \left( \frac{\pi^3(1+\lambda^2)^3 - 3\pi^2(1+\lambda^2)^2 \cdot 2\lambda^2 + 3\pi(1+\lambda^2) \cdot 4\lambda^4 - 8\lambda^6}{\cancel{\pi^3 (1+\lambda^2)^3}} \right) \cdot \left(
-    \frac{\cancel{\pi^3(1+\lambda^2)^3}}{2(4-\pi)^2\lambda^6} \right) \;-\; \frac{np(1-p)}{(1-2p)^2} \\
-  \frac{\pi^3(1+3\lambda^2+3\lambda^4+\lambda^6) - 6\pi^2\lambda^2(1+2\lambda^2+4\lambda^4) + 12\pi\lambda^4(1+\lambda^2) - 8\lambda^6}{2(4-\pi)^2\lambda^6} \;-\; \frac{np(1-p)}{(1-2p)^2} \\
-  \frac{\pi^3 + 3\pi^3\lambda^2 + 3\pi^3\lambda^4 + \pi^3\lambda^6 - 6\pi^2\lambda^2 - 12\pi^2\lambda^4 - 24\pi^2\lambda^6 + 12\pi\lambda^4 + 12\pi\lambda^6 - 8\lambda^6}{2(4-\pi)^2\lambda^6}
-    \;-\; \frac{np(1-p)}{(1-2p)^2} \\
-  \frac{\lambda^6(\pi^3-24\pi^2+12\pi-8) + \lambda^4(3\pi^3-12\pi^2+12\pi) + \lambda^2(3\pi^3-6\pi^2) + \pi^3}{2(4-\pi)^2\lambda^6} \;-\; \frac{np(1-p)}{(1-2p)^2}
-  \intertext{Taking $c_1 = \pi^3 - 24\pi^2 + 12\pi - 8$, $c_2 = 3\pi^3 - 12\pi^2 + 12\pi$, $c_3 = 3\pi^3 - 6\pi^2$, $c_4 = \pi^3$, and $c_5 = 2(4-\pi)^2$, we can simplify this to}
-  \frac{c_1\lambda^6 + c_2\lambda^4 + c_3\lambda^2 + c_4}{c_5\lambda^6} - \frac{np(1-p)}{(1-2p)^2} \\
-  \frac{c_1(1-2p)^2\lambda^6 + c_2(1-2p)^2\lambda^4 + c_3(1-2p)^2\lambda^2 + c_4(1-2p)^2 - c_5\;np(1-p)\lambda^6}{c_5(1-2p)^2\lambda^6} \\
-  \frac{\left[c_1(1-2p)^2 - c_5\;np(1-p)\right]\lambda^6 + \left[c_2(1-2p)^2\right]\lambda^4 + \left[c_3(1-2p)^2\right]\lambda^2 + c_4(1-2p)^2}{c_5(1-2p)^2\;\lambda^6}
-\end{gather*}
-
-\section{Curiosity}
-
-As a curiosity, I was unable to get Pewsey and Azzalini to agree with each
-other on $E(Z^3)$. According to Pewsey (2000),
-
-\begin{equation} \label{eq:ey3-pewsey}
-  E(Y^3) = \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3
-\end{equation}
-
-where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}} \in (-1, 1)$. Since $Y = \mu + \sigma Z$, by the linearity of
-expected value, we also have
-
-\begin{align}
-  E(Y^3) &= E \left[ (\mu + \sigma Z)^3 \right] \nonumber \\
-  &= E (\mu^3 + 3 \mu^2 \sigma Z + 3 \mu \sigma^2 Z^2 + \sigma^3 Z^3) \nonumber \\
-  &= \mu^3 + 3 \mu^2 \sigma\;E(Z) + 3 \mu \sigma^2\;E(Z^2) + \sigma^3\;E(Z^3) \nonumber \\
-  &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + \sigma^3\;E(Z^3) \label{eq:ey3-linear-expansion}
-\end{align}
-
-By comparing equations \eqref{eq:ey3-pewsey} and
-\eqref{eq:ey3-linear-expansion} and eliminating terms, we arrive at
-
-\begin{align}
-  \sigma^3\;E(Z^3) &= 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \nonumber \\
-  \Rightarrow \quad E(Z^3) &= 3 b \delta - b \delta^3 \nonumber \\
-  &= b \delta (3 - \delta^2) \nonumber \\
-  &= \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \cdot \left( 3 - \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:ez3-pewsey-derived}
-\end{align}
-
-However, according to equation (6.5?) in Azzalini (2005),
-
-\begin{equation}
-  E(Z^r) =
-  \begin{dcases*}
-    1 \times 3 \times \cdots \times (r -1) & if r is even \\
-    \frac{\sqrt{2}\;(2k + 1)!\;\lambda}{\sqrt{\pi}\;(1 + \lambda^2)^{k + 1/2}\;2^k} \sum_{m=0}^k\;\frac{m!\;(2\lambda)^{2m}}{(2m+1)!\;(k-m)!} & if $r = 2k+1$ and $k = 0, 1, ...$
-  \end{dcases*}
-\end{equation}
-
-So, for $E(Z^3)$, we have $r = 2k + 1 = 3$ and $k = 1$:
-
-\begin{align}
-  E(Z^3) &= \frac{\sqrt{2} \cdot 3! \cdot \lambda}{\sqrt{\pi} \cdot (1 + \lambda^2)^{3/2} \cdot 2} \; \sum_{m=0}^1 \frac{m!\;(2\lambda)^{2m}}{(2m + 1)!\;(1 - m)!} \nonumber \\
-  &= \frac{3\sqrt{2}}{\sqrt{\pi}} \cdot \frac{\lambda}{(1 + \lambda^2)^{3/2}} \cdot \left( \frac{0! (2\lambda)^0}{1!1!} + \frac{1! (2\lambda)^2}{3!0!} \right) \nonumber \\
-  &= \frac{3\sqrt{2}}{\sqrt{\pi}} \cdot \frac{\lambda}{(1 + \lambda^2)^{3/2}} \cdot \left( 1 + \frac{2}{3}\lambda^2 \right) \nonumber \\
-  &= \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{(\sqrt{1 + \lambda^2})^3} \cdot (3 + 2 \lambda^2) \label{eq:ez3-azzalini}
-\end{align}
-
-Unfortunately, equations \eqref{eq:ez3-pewsey-derived} and
-\eqref{eq:ez3-azzalini} do not really line up.
-
-\end{document}

### 2010-12-13 pieces/method-of-moments/output.tex
Reorganized in preparation of compiling final paper.
Final paper written, compiled, and tweaked to death.

--- 2010-12-10 pieces/method-of-moments/method-of-moments.tex
@@
 \documentclass{article}
-\usepackage {joyce-math}
+\usepackage{jcapstone}
+\begin{document}
 
-\begin{document}
 \section{The Method of Moments}
@@
 Now we'll take a look at the moments of the skew normal. According to Equation
-1 in Pewsey (2000)
+1 in \citet{pewsey}
 
@@
 $\lambda^2$, then $\lambda$ is simply either the positive or negative square
-root, as determined by the sign of $(1-2p)$: When $p \rightarrow 0$, the
-binomial skews left and converges on the positive half normal, so $\lambda$
-should be positive; when $p \rightarrow 1$, the binomial skews right and
-converges on the negative half normal, so $\lambda$ should be negative; and
-when $p = 0.5$, the binomial is symmetric and $\lambda$ is 0, eliminating the
-need for a sign. Thus:
+root, as determined by the sign of $(1-2p)$. This can be explained by Property
+3 in Section \ref{sec:p3}: When $p \to 0$, the binomial skews left and
+converges toward the positive half normal, which by
+\eqref{eq:p2-positive-half-normal} corresponds to a positive $\lambda$. When $p
+\to 1$, the binomial skews right and converges toward the negative half normal,
+which by \eqref{eq:p2-negative-half-normal} corresponds to a negative
+$\lambda$. When $p = 0.5$, the binomial is symmetric and $\lambda$ is 0,
+eliminating the need for a sign. Thus:
 
@@
 
-\textbf{\textit{Another note to Dr. Guffey:} The author mentions here that when
-$p=0.5$, it forces $\lambda$ to be 0, bringing us back to the regular normal
-approximation. This seems like it ought to be a simple fact, but I can't figure
-out how he's getting it from these equations. He refers to his equation (c),
-which is my equation \eqref{eq:mu-solved}. Substituting $p=0.5$ into
-\eqref{eq:mu-solved}, however, doesn't get me anywhere; neither does
-substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
-into \eqref{eq:mu-solved}. And as far as I can tell, equation
-\eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}
+When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
+the mean therefore to be $n/2$. From \eqref{eq:mu-solved}, this implies that
+$\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} =
+0 \Ra$ either $\sigma = 0$ or $\lambda = 0$ Since the former is impossible, we
+must conclude the latter, which brings us back to the familiar normal
+approximation.
+
+%\textbf{\textit{Another note to Dr. Guffey:} The author mentions here that when
+%$p=0.5$, it forces $\lambda$ to be 0, bringing us back to the regular normal
+%approximation. This seems like it ought to be a simple fact, but I can't figure
+%out how he's getting it from these equations. He refers to his equation (c),
+%which is my equation \eqref{eq:mu-solved}. Substituting $p=0.5$ into
+%\eqref{eq:mu-solved}, however, doesn't get me anywhere; neither does
+%substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
+%into \eqref{eq:mu-solved}. And as far as I can tell, equation
+%\eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}
 
@@
 
-If, however, we wish to fix $n$ and solve for $p$, we further factor \eqref{eq:solving-the-restriction}
+Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
+estimate $\lambda$, given a fixed $p$. As expected, the least $n$ is quite
+large when $p$ is small and $\to 0$ as $p \to 0.5$. For example, when $p =
+0.01$, $n \geq 98$; but at $p = 0.2$, $n$ must only be $\geq 3$, a trivial
+requirement to meet.
+
+It is also possible to fix $n$ and solve for $p$. We return to
+\eqref{eq:solving-the-restriction} for further factoring
 
@@
 suggest a Poission approximation.
+
+\begin{figure}[h]
+  \centering
+  \subfloat[Least possible $n$, given a fixed $p$]{\label{fig:sn-restriction-least-n}\includegraphics[width=0.45\textwidth]{../graphs/images/restriction-least-n.png}}
+  \quad
+  \subfloat[Range of possible $p$, given a fixed $n$]{\label{fig:sn-restriction-p-range}\includegraphics[width=0.45\textwidth]{../graphs/images/restriction-p-range.png}}
+  \caption{Restrictions on $n$ and $p$ for estimating $\lambda$}
+  \label{fig:sn-restriction}
+\end{figure}
 
@@
 
+\bibliography{/home/joycetipping/projects/capstone/pieces/bibliography/bibliography.bib}
+\bibliographystyle{plainnat}
 \end{document}

### 2010-12-13 pieces/properties/output.tex
Reorganized in preparation of compiling final paper.
Final paper written, compiled, and tweaked to death.

--- 2010-11-28 notes/properties/properties.tex
@@
 \documentclass{article}
-\usepackage{joyce-math}
-\numberwithin{equation}{section}
+\usepackage{jcapstone}
+\begin{document}
 
-\begin{document}
-\title{The Properties of the Standard Skew Normal}
-\date{}
-\maketitle
+\section{The Skew-Normal}
 
-The four properties of the skew normal listed in section 2 of ``A Note on Improved Approx \ldots''.
+The skew-normal distribution is similar to the normal but with an added
+parameter for skew. In this section, we'll introduce
 
-\section{Property 1}
-\begin{thm*}
+\subsection{Basics}
+
+Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
+scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$, denoted
+$SN(\mu, \sigma, \lambda)$. Then $Y$ has pdf
+
+\begin{equation} \label{eq:sn-pdf}
+  f_Y(x) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right)
+\end{equation}
+
+where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal cdf.
+Some other basic properties of $Y$, given by \citet{pewsey}, are
+
+\begin{align}
+  E(Y) &= \mu + b \delta \sigma \nonumber \\
+  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 \label{eq:sn-basic-properties} \\
+  Var(Y) &= \sigma^2 (1 - b^2 \delta^2) \nonumber \\
+  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \nonumber
+\end{align}
+
+where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
+\lambda^2}}$.
+
+The $SN(0,1,\lambda)$ distribution is called the standard skew-normal, and has
+pdf
+
+\begin{equation} \label{eq:standard-sn-pdf}
+  f_z(x) = 2 \cdot \phi(x) \cdot \Phi (-\lambda x)
+\end{equation}
+
+Like the normal and standard normal, you can arrive at the standard skew normal
+by applying the transformation $\frac{Y - \mu}{\sigma}$ to the skew-normal
+distribution.
+
+A natural question to ask is how the skew-normal relates to the normal.
+Fortunately, the connection is very intuitive: Letting $\lambda = 0$ in
+\eqref{eq:sn-pdf} returns us to the normal pdf:
+
+\begin{align*}
+  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \Phi(0) \\
+  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
+  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
+  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
+  &= \frac{1}{\sqrt{2\pi\sigma^2}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right)
+\end{align*}
+
+\subsection{Four Properties}
+\label{subsec:four-properties}
+
+\citet{main} gives four handy properties of the skew-normal distribution:
+
+\begin{property} \label{prop:1}
   If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
-\end{thm*}
+\end{property}
 
 \begin{proof}
-
-  The standard normal pdf is an even function: $\phi(-x) = \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} =
-  \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} = \phi(x)$. The standard normal cdf, however, $\Phi(x) =
-  \int_{-\infty}^\infty \phi(x)$, is not, being 0 near $-\infty$ and 1 near $\infty$. Thus,
+  The standard normal pdf is an even function: $\phi(-x) =
+  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
+  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) =
+  \int_{-\infty}^\infty \phi(x)$, \thinspace is not, being 0 near $-\infty$ and
+  1 near $\infty$. Thus,
 
@@
   \end{align*}
+
   which is the pdf of $SN(0, 1, -\lambda)$.
@@
 
-\section{Property 2}
-\begin{thm*}
-  As $\lambda \to \pm \infty$, $SN(0, 1, \lambda)$ tends to the half normal distribution.
-\end{thm*}
+\begin{property} \label{prop:2}
+  As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
+\end{property}
 
@@
 
-\begin{lemma*}
-  Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal random variable
-  with parameter $\sigma$ and
+\begin{helper-lem} \label{lem:p2-half-normal}
+  Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal
+  random variable with parameter $\sigma$ and
 
-  \[
+  \begin{equation*}
     f_{|X|}(x) =
     \begin{dcases*}
-    2 \cdot f_{N(0, \sigma^2)}(x) & when $0 < x < \infty$ \\
+      2 \cdot f_X(x) & when $0 < x < \infty$ \\
       0 & everywhere else
     \end{dcases*}
-  \]
-\end{lemma*}
+  \end{equation*}
+\end{helper-lem}
 
 \begin{proof}
-  Let $X \sim N(0, \sigma^2)$, defined over $A = (-\infty, \infty)$.
+  Let $X \sim N(0, \sigma^2)$, defined over $A = (-\infty, \infty)$. Define
 
-  Define
-
-  \[
+  \begin{equation*}
     Y = |X| =
@@
     \end{dcases*}
-  \]
+  \end{equation*}
 
   $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
-  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such that $A = A_1 \cup A_2
-  \cup A_3$ and $Y$ is one-to-one over each $A_i$. We can then transform each piece separately
-  using Theorem 6.3.2:
+  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such
+  that $A = A_1 \cup A_2 \cup A_3$ and $Y$ is one-to-one over each $A_i$. We
+  can then transform each piece separately using Theorem 6.3.2 from
+  \citet{textbook}:
 
-  On $A_1$: $y = -x \lra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1| = 1$, yielding
-  \begin{align*}
-    f_Y(y) &= f_x(x) \cdot \J\\
-    &= f_x(-y) \cdot 1 \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma}} \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma}} \\
-    &= f_{N(0, \sigma^2)}(y)
-  \end{align*}
+  On $A_1$: $y = -x \lra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1|
+  = 1$, yielding
+
+  \begin{align}
+    f_Y(y) &= f_X(x) \cdot \J \nonumber \\
+    &= f_X(-y) \cdot 1 \nonumber \\
+    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma}} \nonumber \\
+    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma}} \nonumber \\
+    &= f_X(y) \label{eq:p2-transform-a1}
+  \end{align}
+
   over the domain $A_1: -\infty < x < 0 \lra -\infty < -y < 0 \lra 0 < y < \infty :B_1$.
 
-  Similarly, on $A_2$: $y = x \lra x = y$ and $\J = \left| \frac{dx}{dy} \right| = |1| = 1$,
-  yielding
-  \begin{align*}
-    f_Y(y) &= f_x(x) \cdot \J\\
-    &= f_x(y) \cdot 1 \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma}} \\
-    &= f_{N(0, \sigma^2)}(y)
-  \end{align*}
+  Similarly, on $A_2$: $y = x \lra x = y$ and $\J = \left| \frac{dx}{dy}
+  \right| = |1| = 1$, yielding
+
+  \begin{align}
+    f_Y(y) &= f_X(x) \cdot \J \nonumber \\
+    &= f_X(y) \cdot 1 \nonumber \\
+    &= f_X(y) \label{eq:p2-transform-a2}
+  \end{align}
+
   over the domain $A_2: 0 < x < \infty \lra 0 < y < \infty :B_2$.
 
-  On $A_3$, we have $x = 0, y = 0$ and $\J = \left| \frac{dx}{dy} \right| = |0| = 0$, yielding
-  $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
+  On $A_3$, we have $x = 0, y = 0$ and $\J = \left| \frac{dx}{dy} \right| = |0|
+  = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
 
-  Then, by Theorem 6.3.10,
-  \begin{align*}
-    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \\
-    &= f_{N(0, \sigma^2)}(y) + f_{N(0, \sigma^2)}(y) \\
-    &= 2 \cdot f_{N(0, \sigma^2)}(y)
-  \end{align*}
+  Now, by Theorem 6.3.10 from \citet{textbook}, we achieve our result by simply
+  summing \eqref{eq:p2-transform-a1} and \eqref{eq:p2-transform-a2}.
+
+  \begin{align}
+    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \nonumber \\
+    &= f_X(y) + f_X(y) \nonumber \\
+    &= 2 \cdot f_X(y) \label{eq:p2-transform-result}
+  \end{align}
+
   over $B = B_1 \cup B_2 = (0, \infty)$, and 0 otherwise.
@@
 
-With this result, we can easily show our property:
+With Lemma \ref{lem:p2-half-normal}, we can easily show our property:
 
-\begin{proof}
-  Let $X \sim SN(0,1,\lambda)$. Recall that $f_X(x) = 2 \cdot \phi(x) \cdot \Phi(\lambda x)$.
+\begin{proof}[Proof of Property 2]
+  Let $Z \sim SN(0,1,\lambda)$. Recall that $f_z(x) = 2 \cdot \phi(x) \cdot
+  \Phi(\lambda x)$.
 
-  Consider $\lim_{\lambda \to \infty} f_X(x)$. When $x$ is negative, $\lambda x \to -\infty$ and
-  thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however, $\lambda x \to \infty$ and
-  $\Phi(\lambda x) \to 1$. Thus we have
+  Consider $\lim_{\lambda \to \infty} f_X(x)$. When $x$ is negative, $\lambda x
+  \to -\infty$ and thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however,
+  $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. Thus
 
-  \[
-  \lim_{\lambda \to \infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) =
+  \begin{equation}
+    \label{eq:p2-positive-half-normal}
+    \lim_{\lambda \to \infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
     \begin{dcases*}
@@
     \end{dcases*}
-  \]
+    \eq |N(0,1)|
+  \end{equation}
 
-  In $\lim_{\lambda \to -\infty} f_X(x)$, the signs are reversed. When $x$ is negative, $\lambda x
-  \to \infty$ and $\Phi(\lambda x) \to 1$. When $x$ is positive, $\lambda x \to -\infty$ and
-  $\Phi(\lambda x) \to 0$. Thus,
+  In $\lim_{\lambda \to -\infty} f_X(x)$, the signs are reversed. When $x$ is
+  negative, $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. When $x$ is
+  positive, $\lambda x \to -\infty$ and $\Phi(\lambda x) \to 0$. Thus,
 
-  \[
-  \lim_{\lambda \to -\infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) =
+  \begin{equation}
+    \label{eq:p2-negative-half-normal}
+    \lim_{\lambda \to -\infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
     \begin{dcases*}
@@
     \end{dcases*}
-  \]
-
+    \eq -|N(0,1)|
+  \end{equation}
 \end{proof}
 
-\section{Property 3}
-\begin{thm*}
+\begin{property} \label{prop:3}
   If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
-\end{thm*}
+\end{property}
 
 \begin{proof}
-  To prove our result, we make use of a lemma in Azzalini (2005):
+  To prove our result, we make use of Lemma 1 in \citet{azzalini}:
 
-  \begin{lemma}
-    If $f_0$ is a one-dimensional probability density function symmetric about 0, and $G$ is a
-    one-dimensional distribution function such that $G'$ exists and is a density symmetric about
-    0, then
+  \begin{helper-lem}
+    If $f_0$ is a one-dimensional probability density function symmetric about
+    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
+    and is a density symmetric about 0, then
 
-    \begin{equation} \label{azzalini-lemma}
+    \begin{equation}
+      \label{eq:azzalini-perturbation-invariance}
       f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
@@
     is a density function for any odd function $w(\cdot)$.
-  \end{lemma}
+  \end{helper-lem}
 
-  Notice that $\phi(x)$ is a one-dimensional probability density function symmetric about 0, and
-  $\Phi(x)$ is a one-dimensional distribution function such that $\Phi'$ exists and is a density
-  symmetric about 0. Furthermore, $\lambda x$ is an odd function. Thus, $f_Z(z) = 2 \cdot \phi(z)
-  \cdot \Phi(\lambda z)$ conforms to equation \ref{azzalini-lemma}. With that in mind, the corollary
+  Notice that $\phi(x)$ is a one-dimensional probability density function
+  symmetric about 0, and $\Phi(x)$ is a one-dimensional distribution function
+  such that $\Phi'$ exists and is a density symmetric about 0. Furthermore,
+  $\lambda x$ is an odd function. Thus, $f_z(z) = 2 \cdot \phi(z) \cdot
+  \Phi(\lambda z)$ conforms to equation
+  \eqref{eq:azzalini-perturbation-invariance}. With that in mind, the corollary
   to this lemma provides a very useful result:
 
-  \begin{cor*}[Perturbation Invariance]
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the notation
-    $\overset{d}{=}$ denotes equality in distribution.    
-  \end{cor*}
+  \begin{helper-cor}[Perturbation Invariance]
+    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
+    notation $\overset{d}{=}$ denotes equality in distribution.    
+  \end{helper-cor}
 
-  Thus, we can treat $\phi$ and $Z$ as being equal in distribution. We will now show that $\phi^2
-  \sim \chi^2_1$:
-  \begin{align}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \nonumber \\
-    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx
-    \nonumber \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \nonumber \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \nonumber \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \label{before-sub}
-  \end{align}
+  Thus, we can treat $\phi$ and $Z$ as being equal in distribution. We will now
+  show that $\phi^2 \sim \chi^2_1$:
 
-  Let $u = (\sqrt{1-2t}) \; x$; then we have $du = \sqrt{1-2t}$, \enspace $dx =
-  \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty \Ra u \to -\infty$ and $x
-  \to \infty \Ra u \to \infty$. Now we can rewrite equation \ref{before-sub} as
+  \begin{align*}
+    M_{\phi^2}(t) &= E[e^{tx^2}] \\
+    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \\
+    \intertext{Let $u = (\sqrt{1-2t}) \, x$; then we have $du = \sqrt{1-2t}$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty \Ra u \to -\infty$
+      and $x \to \infty \Ra u \to \infty$.}
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} \right) du \\
+    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
+      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
+    &= \frac{1}{\sqrt{1-2t}}
+  \end{align*}
 
-  \begin{align}
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}}
-    \right) du \nonumber \\
-    &= \frac{1}{\sqrt{1-2t}} \; \left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2}
-      \; du \right) \label{phi-pdf}
-  \end{align}
+  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
+  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
 
-  Notice that $\frac{1}{\sqrt{2\pi}} \; e^{-u^2/2}$ is the pdf of the standard normal, which
-  integrated over $(-\infty, \infty)$ equals 1. Thus equation \ref{phi-pdf} reduces to
-  $\frac{1}{\sqrt{1-2t}} = (1-2t)^{-1/2}$, which is the MGF of the $\chi^2_1$.
+\begin{property} \label{prop:4}
+  The MGF of $SN(0,1,\lambda)$ is
 
-  Since $Z$ is equal in distribution to $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$.
+  \begin{equation} \label{eq:p4-sn-mgf}
+    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2}
+  \end{equation}
+
+  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
+\end{property}
+
+\begin{proof}
+  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma^2,
+  \lambda)$ is
+
+  \begin{equation*}
+    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t)
+  \end{equation*}
+
+  where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$. It follows that
+  the MGF of the $SN(0, 1, \lambda)$ is
+
+  \begin{equation*}
+    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t)
+  \end{equation*}
 \end{proof}
 
-\section{Property 4}
-\begin{thm*}
-  The MGF of $SN(0, 1, \lambda)$ is $M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2}$ where
-  $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
-\end{thm*}
-
-According to equation 5 in Azzalini (2005), the MGF of $SN(\mu, \sigma^2, \lambda)$ is
-\begin{equation}
-  M(t) = E\{e^{tY}\} = 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma
-  t)
-\end{equation}
-where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$.
-
-It follows that the MGF of the $SN(0, 1, \lambda)$ is
-\begin{equation}
-  2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) =
-  2 \cdot e^{t^2/2} \cdot \Phi(\delta t)
-\end{equation}
-where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$.
-
+\bibliography{/home/joycetipping/projects/capstone/pieces/bibliography/bibliography.bib}
+\bibliographystyle{plainnat}
 \end{document}

### 2010-12-13 pieces/properties/properties.tex
Reorganized in preparation of compiling final paper.
Final paper written, compiled, and tweaked to death.

--- 2010-11-28 notes/properties/properties.tex
@@
-\documentclass{article}
-\usepackage{joyce-math}
-\numberwithin{equation}{section}
+\section{The Skew-Normal}
 
-\begin{document}
-\title{The Properties of the Standard Skew Normal}
-\date{}
-\maketitle
+The skew-normal distribution is similar to the normal but with an added
+parameter for skew. In this section, we'll introduce
 
-The four properties of the skew normal listed in section 2 of ``A Note on Improved Approx \ldots''.
+\subsection{Basics}
 
-\section{Property 1}
-\begin{thm*}
+Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
+scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$, denoted
+$SN(\mu, \sigma, \lambda)$. Then $Y$ has pdf
+
+\begin{equation} \label{eq:sn-pdf}
+  f_Y(x) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right)
+\end{equation}
+
+where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal cdf.
+Some other basic properties of $Y$, given by \citet{pewsey}, are
+
+\begin{align}
+  E(Y) &= \mu + b \delta \sigma \nonumber \\
+  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 \label{eq:sn-basic-properties} \\
+  Var(Y) &= \sigma^2 (1 - b^2 \delta^2) \nonumber \\
+  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \nonumber
+\end{align}
+
+where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
+\lambda^2}}$.
+
+The $SN(0,1,\lambda)$ distribution is called the standard skew-normal, and has
+pdf
+
+\begin{equation} \label{eq:standard-sn-pdf}
+  f_z(x) = 2 \cdot \phi(x) \cdot \Phi (-\lambda x)
+\end{equation}
+
+Like the normal and standard normal, you can arrive at the standard skew normal
+by applying the transformation $\frac{Y - \mu}{\sigma}$.
+
+A natural question to ask is how the skew-normal relates to the normal.
+Fortunately, the connection is very intuitive: When $\lambda = 0$, Equation
+\eqref{eq:sn-pdf} reverts to the normal pdf:
+
+\begin{align*}
+  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
+  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
+  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
+  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
+  &= \frac{1}{\sqrt{2\pi\sigma^2}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right)
+\end{align*}
+
+\subsection{Four Properties}
+\label{subsec:four-properties}
+
+\citet{main} gives four handy properties of the skew-normal distribution:
+
+\begin{property} \label{prop:1}
   If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
-\end{thm*}
+\end{property}
 
 \begin{proof}
-
-  The standard normal pdf is an even function: $\phi(-x) = \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} =
-  \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} = \phi(x)$. The standard normal cdf, however, $\Phi(x) =
-  \int_{-\infty}^\infty \phi(x)$, is not, being 0 near $-\infty$ and 1 near $\infty$. Thus,
+  The standard normal pdf is an even function: $\phi(-x) =
+  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
+  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) =
+  \int_{-\infty}^\infty \phi(x)$, \thinspace is not, being 0 near $-\infty$ and
+  1 near $\infty$. Thus,
 
@@
     is a density function for any odd function $w(\cdot)$.
-  \end{lemma}
+  \end{helper-lem}
 
-  Notice that $\phi(x)$ is a one-dimensional probability density function symmetric about 0, and
-  $\Phi(x)$ is a one-dimensional distribution function such that $\Phi'$ exists and is a density
-  symmetric about 0. Furthermore, $\lambda x$ is an odd function. Thus, $f_Z(z) = 2 \cdot \phi(z)
-  \cdot \Phi(\lambda z)$ conforms to equation \ref{azzalini-lemma}. With that in mind, the corollary
+  Notice that $\phi(x)$ is a one-dimensional probability density function
+  symmetric about 0, and $\Phi(x)$ is a one-dimensional distribution function
+  such that $\Phi'$ exists and is a density symmetric about 0. Furthermore,
+  $\lambda x$ is an odd function. Thus, $f_z(z) = 2 \cdot \phi(z) \cdot
+  \Phi(\lambda z)$ conforms to equation
+  \eqref{eq:azzalini-perturbation-invariance}. With that in mind, the corollary
   to this lemma provides a very useful result:
 
-  \begin{cor*}[Perturbation Invariance]
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the notation
-    $\overset{d}{=}$ denotes equality in distribution.    
-  \end{cor*}
+  \begin{helper-cor}[Perturbation Invariance]
+    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
+    notation $\overset{d}{=}$ denotes equality in distribution.    
+  \end{helper-cor}
 
-  Thus, we can treat $\phi$ and $Z$ as being equal in distribution. We will now show that $\phi^2
-  \sim \chi^2_1$:
-  \begin{align}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \nonumber \\
-    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx
-    \nonumber \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \nonumber \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \nonumber \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \label{before-sub}
-  \end{align}
+  Thus, we can treat $\phi$ and $Z$ as being equal in distribution. We will now
+  show that $\phi^2 \sim \chi^2_1$:
 
-  Let $u = (\sqrt{1-2t}) \; x$; then we have $du = \sqrt{1-2t}$, \enspace $dx =
-  \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty \Ra u \to -\infty$ and $x
-  \to \infty \Ra u \to \infty$. Now we can rewrite equation \ref{before-sub} as
+  \begin{align*}
+    M_{\phi^2}(t) &= E[e^{tx^2}] \\
+    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \\
+    \intertext{Let $u = (\sqrt{1-2t}) \, x$; then we have $du = \sqrt{1-2t}$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty \Ra u \to -\infty$
+      and $x \to \infty \Ra u \to \infty$.}
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} \right) du \\
+    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
+      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
+    &= \frac{1}{\sqrt{1-2t}}
+  \end{align*}
 
-  \begin{align}
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}}
-    \right) du \nonumber \\
-    &= \frac{1}{\sqrt{1-2t}} \; \left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2}
-      \; du \right) \label{phi-pdf}
-  \end{align}
+  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
+  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
 
-  Notice that $\frac{1}{\sqrt{2\pi}} \; e^{-u^2/2}$ is the pdf of the standard normal, which
-  integrated over $(-\infty, \infty)$ equals 1. Thus equation \ref{phi-pdf} reduces to
-  $\frac{1}{\sqrt{1-2t}} = (1-2t)^{-1/2}$, which is the MGF of the $\chi^2_1$.
+\begin{property} \label{prop:4}
+  The MGF of $SN(0,1,\lambda)$ is
 
-  Since $Z$ is equal in distribution to $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$.
+  \begin{equation} \label{eq:p4-sn-mgf}
+    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2}
+  \end{equation}
+
+  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
+\end{property}
+
+\begin{proof}
+  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma^2,
+  \lambda)$ is
+
+  \begin{equation*}
+    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t)
+  \end{equation*}
+
+  where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$. It follows that
+  the MGF of the $SN(0, 1, \lambda)$ is
+
+  \begin{equation*}
+    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t)
+  \end{equation*}
 \end{proof}
-
-\section{Property 4}
-\begin{thm*}
-  The MGF of $SN(0, 1, \lambda)$ is $M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2}$ where
-  $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
-\end{thm*}
-
-According to equation 5 in Azzalini (2005), the MGF of $SN(\mu, \sigma^2, \lambda)$ is
-\begin{equation}
-  M(t) = E\{e^{tY}\} = 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma
-  t)
-\end{equation}
-where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$.
-
-It follows that the MGF of the $SN(0, 1, \lambda)$ is
-\begin{equation}
-  2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) =
-  2 \cdot e^{t^2/2} \cdot \Phi(\delta t)
-\end{equation}
-where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$.
-
-\end{document}

### 2010-12-19 pieces/final-paper/intro.tex
Checked the properties section.

@@
 \begin{equation}
-  F_X(x) \approx \Phi \left( \frac{k + 0.5 - \mu}{\sigma} \right)
+  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right)
 \end{equation}
@@
 Central Limit Theorem) or when $p$ is close to 0.5 (making $X$ roughly
-symmetric). These rules of thumb are captured in a requirement, often stated as
+symmetric). However, when $n$ is not large and $p$ is close to 0 or 1, the
+binomial distribution is skewed and the normal approximation can be inaccurate;
+sometimes, as demonstrated by \citet{mabs}, rather substantially. In these
+cases, the skew-normal approximation can provide an alternate -- and
+considerably more accurate -- method of approximation.
 
-\begin{equation*}
-  np(1-p) > 9
-\end{equation*}
+%\begin{equation*}
+%  np(1-p) > 9
+%\end{equation*}
+%
+%or
+%
+%\begin{align*}
+%      np &> 5 \quad \textnormal{for} \quad  0 < p \leq 0.5, \\
+%  n(1-p) &> 5 \quad \textnormal{for} \quad  0.5 < p < 1
+%\end{align*}
 
-or
-
-\begin{align*}
-      np &> 5 \quad \textnormal{for} \quad  0 < p \leq 0.5, \\
-  n(1-p) &> 5 \quad \textnormal{for} \quad  0.5 < p < 1
-\end{align*}
-
-However, when $n$ is not large and $p$ is close to 0 or 1, the binomial
-distribution is skewed and even if the above requrements are met, the
-approximation can be inaccurate; sometimes, as demonstrated by \citet{mabs},
-rather substantially. In these cases, the skew-normal approximation can provide
-an alternative -- and considerably more accurate -- method of approximation.
+%However, when $n$ is not large and $p$ is close to 0 or 1, the binomial
+%distribution is skewed and even if the above requirements are met, the
+%approximation can be inaccurate; sometimes, as demonstrated by \citet{mabs},
+%rather substantially. In these cases, the skew-normal approximation can
+%provide an alternate -- and considerably more accurate -- method of
+%approximation.

### 2010-12-19 pieces/final-paper/output.tex
Checked the properties section.

@@
 Central Limit Theorem) or when $p$ is close to 0.5 (making $X$ roughly
-symmetric). These rules of thumb are captured in a requirement, often stated as
+symmetric). However, when $n$ is not large and $p$ is close to 0 or 1, the
+binomial distribution is skewed and the normal approximation can be inaccurate;
+sometimes, as demonstrated by \citet{mabs}, rather substantially. In these
+cases, the skew-normal approximation can provide an alternate -- and
+considerably more accurate -- method of approximation.
 
-\begin{equation*}
-  np(1-p) > 9
-\end{equation*}
+%\begin{equation*}
+%  np(1-p) > 9
+%\end{equation*}
+%
+%or
+%
+%\begin{align*}
+%      np &> 5 \quad \textnormal{for} \quad  0 < p \leq 0.5, \\
+%  n(1-p) &> 5 \quad \textnormal{for} \quad  0.5 < p < 1
+%\end{align*}
 
-or
-
-\begin{align*}
-      np &> 5 \quad \textnormal{for} \quad  0 < p \leq 0.5, \\
-  n(1-p) &> 5 \quad \textnormal{for} \quad  0.5 < p < 1
-\end{align*}
-
-However, when $n$ is not large and $p$ is close to 0 or 1, the binomial
-distribution is skewed and even if the above requrements are met, the
-approximation can be inaccurate; sometimes, as demonstrated by \citet{mabs},
-rather substantially. In these cases, the skew-normal approximation can provide
-an alternative -- and considerably more accurate -- method of approximation.
+%However, when $n$ is not large and $p$ is close to 0 or 1, the binomial
+%distribution is skewed and even if the above requirements are met, the
+%approximation can be inaccurate; sometimes, as demonstrated by \citet{mabs},
+%rather substantially. In these cases, the skew-normal approximation can
+%provide an alternate -- and considerably more accurate -- method of
+%approximation.
 
@@
 The skew-normal distribution is similar to the normal but with an added
-parameter for skew. In this section, we'll introduce
+parameter for skew, allowing it to lean asymmetrically to the left or right. In
+this section, we'll acquaint ourselves with some of its basic properties.
 
@@
 Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
-scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$, denoted
-$SN(\mu, \sigma, \lambda)$. Then $Y$ has pdf
+scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$; we will
+denote it $SN(\mu, \sigma, \lambda)$. Then $Y$ has pdf
 
@@
   E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 \label{eq:sn-basic-properties} \\
-  Var(Y) &= \sigma^2 (1 - b^2 \delta^2) \nonumber \\
-  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \nonumber
+  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \nonumber \\
+  Var(Y) &= \sigma^2 (1 - b^2 \delta^2) \nonumber
 \end{align}
@@
 
-The $SN(0,1,\lambda)$ distribution is called the standard skew-normal, and has
-pdf
+The $SN(0,1,\lambda)$ distribution is called the standard skew-normal; its pdf
+is
 
 \begin{equation} \label{eq:standard-sn-pdf}
-  f_z(x) = 2 \cdot \phi(x) \cdot \Phi (-\lambda x)
+  f_z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x)
 \end{equation}
 
-Like the normal and standard normal, you can arrive at the standard skew normal
-by applying the transformation $\frac{Y - \mu}{\sigma}$.
+Similar to the normal and standard normal, $X = \frac{Y - \mu}{\sigma}$ and $Y
+= \sigma X + \mu$.
 
@@
 
-\citet{main} gives four handy properties of the skew-normal distribution:
+The following four properties of the skew-normal, given by \citet{main}, help
+shed some light on our enigmatic new distribution:
 
@@
 \begin{property} \label{prop:2}
+  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
+\end{property}
+
+\begin{proof}
+  To prove our result, we make use of Lemma 1 in \citet{azzalini}:
+
+  \begin{helper-lem}
+    If $f_0$ is a one-dimensional probability density function symmetric about
+    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
+    and is a density symmetric about 0, then
+
+    \begin{equation}
+      \label{eq:azzalini-perturbation-invariance}
+      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
+    \end{equation}
+
+    is a density function for any odd function $w(\cdot)$.
+  \end{helper-lem}
+
+  This lemma provides a very useful corollary:
+
+  \begin{helper-cor}[Perturbation Invariance]
+    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
+    notation $\overset{d}{=}$ denotes equality in distribution.    
+  \end{helper-cor}
+
+  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_z(z) = 2 \cdot \phi(z) \cdot
+  \Phi(\lambda z)$ conforms to equation
+  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $phi$
+  and $Z$ are equal in distribution.
+
+%  Notice that $\phi(x)$ is a one-dimensional probability density function
+%  symmetric about 0, and $\Phi(x)$ is a one-dimensional distribution function
+%  such that $\Phi'$ exists and is a density symmetric about 0. Furthermore,
+%  $\lambda x$ is an odd function. Thus, $f_z(z) = 2 \cdot \phi(z) \cdot
+%  \Phi(\lambda z)$ conforms to equation
+%  \eqref{eq:azzalini-perturbation-invariance}. With that in mind, the corollary
+%  to this lemma provides a very useful result:
+
+  We will now show that $\phi^2 \sim \chi^2_1$:
+
+  \begin{align*}
+    M_{\phi^2}(t) &= E[e^{tx^2}] \\
+    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \\
+    \intertext{Let $u = (\sqrt{1-2t}) \, x$; then $du = (\sqrt{1-2t}) \, dx$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty, x \to \infty \Ra
+      u \to -\infty, u \to \infty$.}
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} du \right) \\
+    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
+      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
+    &= \frac{1}{\sqrt{1-2t}}
+  \end{align*}
+
+  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
+  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
+
+\begin{property} \label{prop:3}
   As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
@@
     \begin{dcases*}
-      2 \cdot f_X(x) & when $0 < x < \infty$ \\
-      0 & everywhere else
+      0              & when $-\infty < x \leq 0$ \\
+      2 \cdot f_X(x) & when $0 < x < \infty$ 
     \end{dcases*}
@@
 
-  On $A_1$: $y = -x \lra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1|
+  On $A_1$: $y = -x \Ra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1|
   = 1$, yielding
 
-  \begin{align}
-    f_Y(y) &= f_X(x) \cdot \J \nonumber \\
-    &= f_X(-y) \cdot 1 \nonumber \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma}} \nonumber \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma}} \nonumber \\
-    &= f_X(y) \label{eq:p2-transform-a1}
-  \end{align}
+  \begin{align*}
+    f_Y(y) &= f_X(x) \cdot \J \\
+    &= f_X(-y) \cdot 1 \\
+    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma^2}} \\
+    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma^2}} \\
+    &= f_X(y)
+  \end{align*}
 
-  over the domain $A_1: -\infty < x < 0 \lra -\infty < -y < 0 \lra 0 < y < \infty :B_1$.
+  over the domain $A_1: -\infty < x < 0 \Ra -\infty < -y < 0 \Ra 0 < y < \infty :B_1$.
 
-  Similarly, on $A_2$: $y = x \lra x = y$ and $\J = \left| \frac{dx}{dy}
+  Similarly, on $A_2$: $y = x \Ra x = y$ and $\J = \left| \frac{dx}{dy}
   \right| = |1| = 1$, yielding
 
-  \begin{align}
-    f_Y(y) &= f_X(x) \cdot \J \nonumber \\
-    &= f_X(y) \cdot 1 \nonumber \\
-    &= f_X(y) \label{eq:p2-transform-a2}
-  \end{align}
+  \begin{align*}
+    f_Y(y) &= f_X(x) \cdot \J \\
+    &= f_X(y) \cdot 1 \\
+    &= f_X(y)
+  \end{align*}
 
-  over the domain $A_2: 0 < x < \infty \lra 0 < y < \infty :B_2$.
+  over the domain $A_2: 0 < x < \infty \Ra 0 < y < \infty :B_2$.
 
-  On $A_3$, we have $x = 0, y = 0$ and $\J = \left| \frac{dx}{dy} \right| = |0|
-  = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
+  On $A_3$, we have $x = 0 \Ra y = 0$ and $\J = \left| \frac{dx}{dy} \right| =
+  |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
 
-  Now, by Theorem 6.3.10 from \citet{textbook}, we achieve our result by simply
-  summing \eqref{eq:p2-transform-a1} and \eqref{eq:p2-transform-a2}.
+  Now, by Theorem 6.3.10 from \citet{textbook}
 
@@
 
-\begin{proof}[Proof of Property 2]
-  Let $Z \sim SN(0,1,\lambda)$. Recall that $f_z(x) = 2 \cdot \phi(x) \cdot
+\begin{proof}[Proof of Property 3]
+  Let $Z \sim SN(0,1,\lambda)$. Recall that $f_Z(x) = 2 \cdot \phi(x) \cdot
   \Phi(\lambda x)$.
@@
 
-\begin{property} \label{prop:3}
-  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
-\end{property}
-
-\begin{proof}
-  To prove our result, we make use of Lemma 1 in \citet{azzalini}:
-
-  \begin{helper-lem}
-    If $f_0$ is a one-dimensional probability density function symmetric about
-    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
-    and is a density symmetric about 0, then
-
-    \begin{equation}
-      \label{eq:azzalini-perturbation-invariance}
-      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
-    \end{equation}
-
-    is a density function for any odd function $w(\cdot)$.
-  \end{helper-lem}
-
-  Notice that $\phi(x)$ is a one-dimensional probability density function
-  symmetric about 0, and $\Phi(x)$ is a one-dimensional distribution function
-  such that $\Phi'$ exists and is a density symmetric about 0. Furthermore,
-  $\lambda x$ is an odd function. Thus, $f_z(z) = 2 \cdot \phi(z) \cdot
-  \Phi(\lambda z)$ conforms to equation
-  \eqref{eq:azzalini-perturbation-invariance}. With that in mind, the corollary
-  to this lemma provides a very useful result:
-
-  \begin{helper-cor}[Perturbation Invariance]
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
-    notation $\overset{d}{=}$ denotes equality in distribution.    
-  \end{helper-cor}
-
-  Thus, we can treat $\phi$ and $Z$ as being equal in distribution. We will now
-  show that $\phi^2 \sim \chi^2_1$:
-
-  \begin{align*}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \\
-    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \\
-    \intertext{Let $u = (\sqrt{1-2t}) \, x$; then we have $du = \sqrt{1-2t}$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty \Ra u \to -\infty$
-      and $x \to \infty \Ra u \to \infty$.}
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} \right) du \\
-    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
-      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
-    &= \frac{1}{\sqrt{1-2t}}
-  \end{align*}
-
-  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
-  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
-
 \begin{property} \label{prop:4}
@@
 
-  where $\delta = \frac{\lambda}{1 + \lambda^2} \in (-1, 1)$. It follows that
-  the MGF of the $SN(0, 1, \lambda)$ is
+  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}} \in (-1, 1)$. It follows
+  that the MGF of the $SN(0, 1, \lambda)$ is
 
@@
 
-Next, we develop our skew-normal approximation of the binomial. Let $B \sim
-Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find estimates for
-$\mu$, $\sigma$, and $\lambda$ by comparing their first, second, and third
-moments about the mean.
+Now that we have gotten to know our new distribution a little better, we can
+use it to develop an approximation for the binomial.
+
+Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
+estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
+and third moments about the mean of $B$ and $Y$.
 

### 2010-12-19 pieces/final-paper/output.tex
Finished fine-toothed combing.

@@
 
-We begin by examining the moments of the binomial. The first two, the mean and
-variance, are simply
+Let's start with the binomial. The first two moments are simply the mean and
+variance, which we can state from memory:
 
@@
   E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\
+  \intertext{Notice that the first three terms of our sum are zero, so we can rewrite our sum beginning at $x = 3$:}
   &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
@@
   &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
-  \intertext{Let $y=x-3$. Then $x=y+3$, and $x=3 \rightarrow y=0$ and $x=n \rightarrow y=n-3$.}
+  \intertext{Let $y=x-3$. Then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$.}
   &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
@@
 
-With these results (and a bit of elbow grease), we can obtain the third moment
-without too much trouble:
+Now, finally, we have all the building blocks necessary to obtain the third
+moment:
 
@@
   &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
-  &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) - 3np(np - np^2 + n^2p^2) + 2n^3p^3 \\
+  &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\
   &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
@@
   & \quad + 2\;(\mu + b \delta \sigma)^3 \\
-  &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{9 b \delta \mu^2 \sigma} -
-    \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} \\
+  &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} -
+    \cancel{6 b \delta \mu^2 \sigma} - \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} \\
   & \quad - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
@@
 When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
-the mean therefore to be $n/2$. From \eqref{eq:mu-solved}, this implies that
+therefore $\mu = np = n/2$. From \eqref{eq:mu-solved}, this implies that
 $\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} =
@@
 can't ever be less than 1. Unfortunately, it sometimes is; in particular,
-$\frac{np(1-p)}{(1-2p)^2} \to 0$ both when $p \to 0$ and $p \to 1$. So if we
-want a solution, we must restrict $n$ and $p$ such that
+$\frac{np(1-p)}{(1-2p)^2} \to 0$ when $p \to 0$ or $p \to 1$. So if we want a
+solution, we must restrict $n$ and $p$ such that
 
@@
 
-From here, given a constant $p$, finding $n$ is very simple:
+Here, two scenarios arise. The first is when we have a fixed $p$ and wish to
+find the minimum $n$ necessary to derive a skew-normal approximation. From
+\eqref{eq:solving-the-restriction}, this is very simple:
 
@@
 Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
-estimate $\lambda$, given a fixed $p$. As expected, the least $n$ is quite
-large when $p$ is small and $\to 0$ as $p \to 0.5$. For example, when $p =
-0.01$, $n \geq 98$; but at $p = 0.2$, $n$ must only be $\geq 3$, a trivial
-requirement to meet.
+estimate $\lambda$ as a function of $p$. As expected, it is quite large when
+$p$ is small and rapidly goes to 0 as $p$ increases; for example, when $p =
+0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a
+trivial requirement to meet.
 
@@
 
-It is also possible to fix $n$ and solve for $p$. We return to
-\eqref{eq:solving-the-restriction} for further factoring
+The second scenario is when $n$ is fixed and we wish to solve for $p$. In this
+case, we return to \eqref{eq:solving-the-restriction} for further factoring
 
@@
   \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
-  \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n-4)} \\
+  \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n+4)} \\
   \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
@@
 
-As shown in figure \ref{fig:sn-restriction-p-range}, this interval grows
-quickly as $n$ increases, and for sufficiently large $n$, it becomes almost
-$(0, 1)$. For example, when $n=100$, our interval is $(0.00971, 0.99029)$; when
-$n=500$, it is (0.00199, 0.99801).
+Shown in figure \ref{fig:sn-restriction-p-range} as a function of $n$, this
+interval grows quickly as $n$ increases, and for sufficiently large $n$, it
+becomes almost $(0, 1)$. For example, when $n=100$, our interval is $(0.00971,
+0.99029)$; when $n=500$, it is (0.00199, 0.99801).
 
-For $p$ so close to 0 or 1 that this solution will not work, our authors
-suggest a Poission approximation.
+For those unfortunate combinations of $n$ and $p$ so extreme that our
+skew-normal approximation will not work, our authors suggest a Poission
+approximation.
 
@@
 
-Having taken the trouble to develop our skew-normal approximation for the
-binomial, we now justify our efforts by demonstrating its improved accuracy
-over the regular normal approximation.
+Now comes the time to justify our efforts by comparing the accuracy of our
+skew-normal approximation to that of the normal.
 
@@
 
-The first, and most obvious, way of judging accuracy is by visual inspection.
+The first and most obvious way of judging accuracy is by visual inspection.
 Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
@@
 hard to see that, especially at very small $n$ and $p$, our skew-normal curve
-follows the shape of the binomial much more accurately.
+follows the shape of the binomial much more closely.
 
@@
 
-Figure \ref{fig:mabs-fixed-n} shows the MABS as a function of $p$, for $n=25$
-and $n=100$. Figure \ref{fig:mabs-fixed-p}, on the other hand, shows the MABS
-as a function of $n$, for $p=0.05$ and $p=0.1$. Again, the skew-normal
-outperforms the normal considerably in the extreme ranges, with the two
-approximations converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.
+Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
+skew-normal and normal approximations as a function of $p$ and $n$,
+respectively. Again, the skew-normal outperforms the normal considerably in the
+extreme ranges, with the two approximations converging as $n \rightarrow
+\infty$ or $p \rightarrow 0.5$.
 

### 2010-12-19 pieces/method-of-moments/method-of-moments.tex
Finished fine-toothed combing.

@@
 
-As shown in figure \ref{fig:sn-restriction-p-range}, this interval grows
-quickly as $n$ increases, and for sufficiently large $n$, it becomes almost
-$(0, 1)$. For example, when $n=100$, our interval is $(0.00971, 0.99029)$; when
-$n=500$, it is (0.00199, 0.99801).
+Shown in figure \ref{fig:sn-restriction-p-range} as a function of $n$, this
+interval grows quickly as $n$ increases, and for sufficiently large $n$, it
+becomes almost $(0, 1)$. For example, when $n=100$, our interval is $(0.00971,
+0.99029)$; when $n=500$, it is (0.00199, 0.99801).
 
-For $p$ so close to 0 or 1 that this solution will not work, our authors
-suggest a Poission approximation.
+For those unfortunate combinations of $n$ and $p$ so extreme that our
+skew-normal approximation will not work, our authors suggest a Poission
+approximation.

### 2010-12-19 pieces/final-paper/output.tex
Tweaks.

@@
 \begin{equation} \label{eq:standard-sn-pdf}
-  f_z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x)
+  f_Z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x)
 \end{equation}
 
-Similar to the normal and standard normal, $X = \frac{Y - \mu}{\sigma}$ and $Y
-= \sigma X + \mu$.
+Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
+= \sigma Z + \mu$.
 
@@
   &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
-  &= \frac{1}{\sqrt{2\pi\sigma^2}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right)
+  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right)
 \end{align*}
@@
 
-  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_z(z) = 2 \cdot \phi(z) \cdot
+  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
   \Phi(\lambda z)$ conforms to equation
@@
 %  such that $\Phi'$ exists and is a density symmetric about 0. Furthermore,
-%  $\lambda x$ is an odd function. Thus, $f_z(z) = 2 \cdot \phi(z) \cdot
+%  $\lambda x$ is an odd function. Thus, $f_Z(z) = 2 \cdot \phi(z) \cdot
 %  \Phi(\lambda z)$ conforms to equation
@@
 
-Now we set the two sets of moments equal to each other and, taking $n$ and $p$
-as constants, solve for $\mu$, $\sigma$ and $\lambda$.
+Now we can set the moments of our two distributions equal to each other and,
+taking $n$ and $p$ as constants, solve for $\mu$, $\sigma$ and $\lambda$.
 
@@
 
-Similarly, with both $\lambda$ and $\sigma$, a simple rearrangement of
+And with both $\lambda$ and $\sigma$, a simple rearrangement of
 \eqref{eq:first-moment-set} yields $\mu$:
@@
 
-Another more numerical method would be to compare the maximal absolute errors
-of our two approximations, defined by \citet{mabs} as
+A more numerical method would be to compare the maximal absolute errors of our
+two approximations, defined by \citet{mabs} as
 

### 2010-12-19 pieces/final-paper/output.tex
Tweaks.

@@
   \Phi(\lambda z)$ conforms to equation
-  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $phi$
+  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
   and $Z$ are equal in distribution.
@@
 
-  Now, by Theorem 6.3.10 from \citet{textbook}
+  Then, by Theorem 6.3.10 from \citet{textbook},
 
-  \begin{align}
-    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \nonumber \\
-    &= f_X(y) + f_X(y) \nonumber \\
-    &= 2 \cdot f_X(y) \label{eq:p2-transform-result}
-  \end{align}
+  \begin{align*}
+    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \\
+    &= f_X(y) + f_X(y) \\
+    &= 2 \cdot f_X(y)
+  \end{align*}
 

### 2010-12-19 pieces/properties/properties.tex
Tweaks.

@@
 
-  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_z(z) = 2 \cdot \phi(z) \cdot
+  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
   \Phi(\lambda z)$ conforms to equation
-  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $phi$
+  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
   and $Z$ are equal in distribution.

### 2010-12-24 pieces/final-paper/intro.tex
Added punctuation, support sets, made several small tweaks as suggested by Dr. Guffey.

--- 2010-12-13 pieces/final-paper/intro.tex
@@
 \begin{equation*}
-  f_X(x) = \binom{n}{x} p^x q^{n-x}
+  f_X(x) = \binom{n}{x} p^x q^{n-x}, \quad x = 0, 1, \ldots, n.
 \end{equation*}
@@
 hand is manageable for small $n$ but quickly becomes cumbersome as $n$ grows
-even mediumly large. A common strategy is to use the normal distribution as an
-approximation:
+even moderately large. A common strategy is to use the normal distribution as
+an approximation:
 
 \begin{equation}
-  F_X(x) \approx \Phi \left( \frac{k + 0.5 - \mu}{\sigma} \right)
+  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right),
 \end{equation}
@@
 
-This approximation works well when either $n$ is very large (invoking the
-Central Limit Theorem) or when $p$ is close to 0.5 (making $X$ roughly
-symmetric). These rules of thumb are captured in a requirement, often stated as
-
-\begin{equation*}
-  np(1-p) > 9
-\end{equation*}
-
-or
-
-\begin{align*}
-      np &> 5 \quad \textnormal{for} \quad  0 < p \leq 0.5, \\
-  n(1-p) &> 5 \quad \textnormal{for} \quad  0.5 < p < 1
-\end{align*}
-
-However, when $n$ is not large and $p$ is close to 0 or 1, the binomial
-distribution is skewed and even if the above requrements are met, the
-approximation can be inaccurate; sometimes, as demonstrated by \citet{mabs},
-rather substantially. In these cases, the skew-normal approximation can provide
-an alternative -- and considerably more accurate -- method of approximation.
+This approximation works best when the binomial is perfectly symmetrical, with
+$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
+becomes increasingly skewed, and one must either compensate by providing ever
+larger values of $n$ or face growing inaccuracy. In these cases, the
+skew-normal approximation can provide a better alternative.

### 2010-12-24 pieces/final-paper/output.tex
Tweaks.
Added punctuation, support sets, made several small tweaks as suggested by Dr. Guffey.

@@
 hand is manageable for small $n$ but quickly becomes cumbersome as $n$ grows
-even mediumly large. A common strategy is to use the normal distribution as an
-approximation:
+even moderately large. A common strategy is to use the normal distribution as
+an approximation:
 
 \begin{equation}
-  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right)
+  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right),
 \end{equation}
@@
 
-This approximation works well when either $n$ is very large (invoking the
-Central Limit Theorem) or when $p$ is close to 0.5 (making $X$ roughly
-symmetric). However, when $n$ is not large and $p$ is close to 0 or 1, the
-binomial distribution is skewed and the normal approximation can be inaccurate;
-sometimes, as demonstrated by \citet{mabs}, rather substantially. In these
-cases, the skew-normal approximation can provide an alternate -- and
-considerably more accurate -- method of approximation.
-
-%\begin{equation*}
-%  np(1-p) > 9
-%\end{equation*}
-%
-%or
-%
-%\begin{align*}
-%      np &> 5 \quad \textnormal{for} \quad  0 < p \leq 0.5, \\
-%  n(1-p) &> 5 \quad \textnormal{for} \quad  0.5 < p < 1
-%\end{align*}
-
-%However, when $n$ is not large and $p$ is close to 0 or 1, the binomial
-%distribution is skewed and even if the above requirements are met, the
-%approximation can be inaccurate; sometimes, as demonstrated by \citet{mabs},
-%rather substantially. In these cases, the skew-normal approximation can
-%provide an alternate -- and considerably more accurate -- method of
-%approximation.
+This approximation works best when the binomial is perfectly symmetrical, with
+$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
+becomes increasingly skewed, and one must either compensate by providing ever
+larger values of $n$ or face growing inaccuracy. In these cases, the
+skew-normal approximation can provide a better alternative.
 
@@
 \begin{equation} \label{eq:sn-pdf}
-  f_Y(x) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right)
+  f_Y(x) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
 \end{equation}
@@
 \begin{align}
-  E(Y) &= \mu + b \delta \sigma \nonumber \\
-  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 \label{eq:sn-basic-properties} \\
-  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \nonumber \\
-  Var(Y) &= \sigma^2 (1 - b^2 \delta^2) \nonumber
+  E(Y) &= \mu + b \delta \sigma, \nonumber \\
+  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-basic-properties} \\
+  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber \\
+  Var(Y) &= \sigma^2 (1 - b^2 \delta^2), \nonumber
 \end{align}
@@
 \begin{equation} \label{eq:standard-sn-pdf}
-  f_Z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x)
+  f_Z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
 \end{equation}
@@
 Fortunately, the connection is very intuitive: When $\lambda = 0$, Equation
-\eqref{eq:sn-pdf} reverts to the normal pdf:
+\eqref{eq:sn-pdf} becomes
 
@@
   &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
-  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right)
+  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
 \end{align*}
+
+which is the pdf of the normal distribution.
 
@@
 The following four properties of the skew-normal, given by \citet{main}, help
-shed some light on our enigmatic new distribution:
+shed light on our enigmatic new distribution:
 
@@
   \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) =
-  \int_{-\infty}^\infty \phi(x)$, \thinspace is not, being 0 near $-\infty$ and
-  1 near $\infty$. Thus,
+  \int_{-\infty}^\infty \phi(x)$, \thinspace is not even, being 0 near
+  $-\infty$ and 1 near $\infty$. Thus,
 
@@
     & = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\
-    & = 2 \cdot \phi(x) \cdot \Phi (-\lambda x)
+    & = 2 \cdot \phi(x) \cdot \Phi (-\lambda x),
   \end{align*}
@@
 \begin{proof}
-  To prove our result, we make use of Lemma 1 in \citet{azzalini}:
+  To prove our result, we make use of Lemma 1 in \citet{azzalini}, which we
+  restate here:
 
@@
 
-%  Notice that $\phi(x)$ is a one-dimensional probability density function
-%  symmetric about 0, and $\Phi(x)$ is a one-dimensional distribution function
-%  such that $\Phi'$ exists and is a density symmetric about 0. Furthermore,
-%  $\lambda x$ is an odd function. Thus, $f_Z(z) = 2 \cdot \phi(z) \cdot
-%  \Phi(\lambda z)$ conforms to equation
-%  \eqref{eq:azzalini-perturbation-invariance}. With that in mind, the corollary
-%  to this lemma provides a very useful result:
-
   We will now show that $\phi^2 \sim \chi^2_1$:
@@
     &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \\
-    \intertext{Let $u = (\sqrt{1-2t}) \, x$; then $du = (\sqrt{1-2t}) \, dx$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty, x \to \infty \Ra
-      u \to -\infty, u \to \infty$.}
+    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \;; \\
+    \intertext{let $u = (\sqrt{1-2t}) \, x$; then $du = (\sqrt{1-2t}) \, dx$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty, x \to \infty \Ra
+      u \to -\infty, u \to \infty$:}
     &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} du \right) \\
@@
       $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
-    &= \frac{1}{\sqrt{1-2t}}
+    &= \frac{1}{\sqrt{1-2t}} \;,
   \end{align*}
@@
     \end{dcases*}
+    .
   \end{equation*}
@@
   \to -\infty$ and thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however,
-  $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. Thus
+  $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. Thus,
 
@@
     \end{dcases*}
-    \eq |N(0,1)|
+    \eq |N(0,1)|.
   \end{equation}
@@
     \end{dcases*}
-    \eq -|N(0,1)|
+    \eq -|N(0,1)|.
   \end{equation}
@@
   \begin{equation} \label{eq:p4-sn-mgf}
-    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2}
+    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2},
   \end{equation}
@@
   \begin{equation*}
-    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t)
+    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t),
   \end{equation*}
@@
   \begin{equation*}
-    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t)
+    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t).
   \end{equation*}
@@
 \begin{equation*}
-  E(B) = np, \quad Var(B) = np(1-p)
+  E(B) = np, \quad Var(B) = np(1-p).
 \end{equation*}
@@
 \begin{equation*}
-  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2
+  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2,
 \end{equation*}
@@
 \begin{align*}
-  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\
-  \intertext{Notice that the first three terms of our sum are zero, so we can rewrite our sum beginning at $x = 3$:}
+  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \;; \\
+  \intertext{notice that the first three terms of this sum are zero, so we can rewrite our sum beginning at $x = 3$:}
   &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
   &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
-  \intertext{Let $y=x-3$. Then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$.}
+  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \\
+  \intertext{let $y=x-3$; then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$:}
   &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
@@
   &= n(n-1)(n-2)p^3 \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 \\
-  \intertext{Further expanding the left side and solving for $E(B^3)$,}
+  &= n^3p^3 - 3n^2p^3 + 2np^3 \;; \\
+  \intertext{further expanding the left side and solving for $E(B^3)$:}
   E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\
@@
   \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 + 3np - 3np^2 + 3n^2p^2 - 2np \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np
+  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np.
 \end{align*}
@@
   &= 2np^3 - 3np^2 + np \\
-  &= np(p-1)(2p-1)
+  &= np(p-1)(2p-1).
 \end{align*}
@@
 \begin{align}
-  E(B) &= np \nonumber \\
-  E([B - E(B)]^2) &= np(1-p) \\
-  E([B - E(B)]^3) &= np(p-1)(2p-1) \nonumber
+  E(B) &= np, \nonumber \\
+  E([B - E(B)]^2) &= np(1-p), \\
+  E([B - E(B)]^3) &= np(p-1)(2p-1). \nonumber
 \end{align}
@@
   &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
-  &= b \delta^3 \sigma^3 (2b^2 - 1)
+  &= b \delta^3 \sigma^3 (2b^2 - 1).
 \end{align*}
@@
 \begin{alignat}{4}
-  E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \nonumber \\
-  E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \\
-  E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \nonumber
+  E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;, \nonumber \\
+  E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right), \\
+  E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right). \nonumber
 \end{alignat}
@@
 Now we can set the moments of our two distributions equal to each other and,
-taking $n$ and $p$ as constants, solve for $\mu$, $\sigma$ and $\lambda$.
+taking $n$ and $p$ as constants, solve for $\mu$, $\sigma$ and $\lambda$:
 
@@
   \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-    \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \label{eq:solving-for-lambda}
+    \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \;. \label{eq:solving-for-lambda}
 \end{align}
@@
 $\lambda^2$, then $\lambda$ is simply either the positive or negative square
-root, as determined by the sign of $(1-2p)$. This can be explained with a
+root, as determined by the sign of $(1-2p)$. The sign can be explained with a
 little assistance from Property \ref{prop:3}: When $p \to 0$, the binomial
@@
   \label{eq:lambda-solved}
-  \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}
+  \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}.
 \end{equation}
-
-%\textbf{\textit{Note to Dr. Guffey:} I am trying to find an algebraic reason
-%for the sign, but I'm not seeing it in equation \eqref{eq:solving-for-lambda}
-%nor its algebraic expansion, which I put in in appendix
-%\ref{sec:solving-for-lambda} as it ended up providing little insight into this
-%conclusion.}
 
@@
   np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
-  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}}
+  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} \;.
 \end{equation}
@@
   np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
-  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}}
+  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;.
 \end{equation}
@@
 When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
-therefore $\mu = np = n/2$. From \eqref{eq:mu-solved}, this implies that
-$\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} =
-0 \Ra$ either $\sigma = 0$ or $\lambda = 0$. Since the former is impossible, we
-must conclude the latter, which brings us back to the normal distribution.
-
-%\textbf{\textit{Another note to Dr. Guffey:} The author mentions here that when
-%$p=0.5$, it forces $\lambda$ to be 0, bringing us back to the regular normal
-%approximation. This seems like it ought to be a simple fact, but I can't figure
-%out how he's getting it from these equations. He refers to his equation (c),
-%which is my equation \eqref{eq:mu-solved}. Substituting $p=0.5$ into
-%\eqref{eq:mu-solved}, however, doesn't get me anywhere; neither does
-%substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
-%into \eqref{eq:mu-solved}. And as far as I can tell, equation
-%\eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}
+therefore $\mu = np = n/2$. This equation, together with \eqref{eq:mu-solved},
+implies that $\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 +
+\lambda^2}} = 0 \Ra$ either $\sigma = 0$ or $\lambda = 0$. Since the former is
+impossible, we must conclude the latter, which brings us back to the normal
+distribution.
 
@@
 
-\begin{gather}
-  \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. \nonumber \\
-  \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 \nonumber \\
-  \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \nonumber \\
-  \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \label{eq:lhs-solving-for-lambda}
-\end{gather}
+\begin{alignat*}{3}
+  \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2}
+    &= \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. & \\
+  &= \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 & \\
+  &= \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) & \\
+  &= \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) &= g(v).
+\end{alignat*}
 
-we can see that it is increasing in $v$, which is always $\geq 1$. Therefore:
+We can see that $g(v)$ is increasing in $v$, which is always $\geq 1$.
+Therefore:
 
 \begin{equation}
-  \min_{v} \textnormal{\{Eq. \ref{eq:lhs-solving-for-lambda}\}} = \textnormal{\{Eq. \ref{eq:lhs-solving-for-lambda}\}} |_{v=1} = 
-  \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1
+  \min_{v} g(v) = g(v)|_{v=1} = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1,
 \end{equation}
 
-This means that the right hand side of \eqref{eq:solving-for-lambda}, which is
+which means that the right hand side of \eqref{eq:solving-for-lambda}, which is
 supposed to be equal to the left hand side of \eqref{eq:solving-for-lambda},
@@
   \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
-  np(1-p) &\geq (1-2p)^2 \label{eq:solving-the-restriction}
+  np(1-p) &\geq (1-2p)^2. \label{eq:solving-the-restriction}
 \end{align}
@@
 find the minimum $n$ necessary to derive a skew-normal approximation. From
-\eqref{eq:solving-the-restriction}, this is very simple:
+\eqref{eq:solving-the-restriction}, solving for $n$ is very simple:
 
 \begin{equation}
-  n \geq \frac{(1-2p)^2}{p(1-p)} \label{eq: n for a given p}
+  n \geq \frac{(1-2p)^2}{p(1-p)} \;. \label{eq: n for a given p}
 \end{equation}
@@
   \centering
-  \subfloat[Least possible $n$, given a fixed $p$]{\label{fig:sn-restriction-least-n}\includegraphics[width=0.45\textwidth]{../graphs/images/restriction-least-n.png}}
-  \quad
-  \subfloat[Range of possible $p$, given a fixed $n$]{\label{fig:sn-restriction-p-range}\includegraphics[width=0.45\textwidth]{../graphs/images/restriction-p-range.png}}
-  \caption{Restrictions on $n$ and $p$ for estimating $\lambda$}
-  \label{fig:sn-restriction}
+  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-least-n.png}
+  \caption{Least possible $n$, given a fixed $p$}
+  \label{fig:sn-restriction-least-n}
 \end{figure}
@@
 The second scenario is when $n$ is fixed and we wish to solve for $p$. In this
-case, we return to \eqref{eq:solving-the-restriction} for further factoring
+case, we return to \eqref{eq:solving-the-restriction} for further factoring:
 
 \begin{align}
+  np(1-p) &\geq (1-2p)^2 \nonumber \\
   np - np^2 &\geq 1 - 4p + 4p^2 \nonumber \\
   1 - 4p + 4p^2 - np + np^2 &\leq 0 \nonumber \\
-  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq: solving for p}
+  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq: solving for p}.
 \end{align}
 
-and apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
+We then apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
 
-\begin{gather*}
-  \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
-  \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
-  \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n+4)} \\
-  \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
-  \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}}
-\end{gather*}
+\begin{align*}
+  p &= \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
+  &= \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
+  &= \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n+4)} \\
+  &= \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
+  &= \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}} \;.
+\end{align*}
 
@@
 \begin{equation*}
-  (p - r_1)(p - r_2) \leq 0
+  (p - r_1)(p - r_2) \leq 0.
 \end{equation*}
@@
 leading the product to be positive. Therefore, our solution lies where $r_1
-\leq p \leq r_2$, or more explicitly:
+\leq p \leq r_2$, or more explicitly,
 
 \begin{equation}
- \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}}
+ \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}} \;.
 \end{equation}
@@
 
-For those unfortunate combinations of $n$ and $p$ so extreme that our
-skew-normal approximation will not work, our authors suggest a Poission
-approximation.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-p-range.png}
+  \caption{Range of possible $p$, given a fixed $n$}
+  \label{fig:sn-restriction-p-range}
+\end{figure}
 
@@
 
-A more numerical method would be to compare the maximal absolute errors of our
+A quantitative method would be to compare the maximal absolute errors of our
 two approximations, defined by \citet{mabs} as

### 2010-12-24 pieces/method-of-moments/method-of-moments.tex
Added punctuation, support sets, made several small tweaks as suggested by Dr. Guffey.

@@
 
-For those unfortunate combinations of $n$ and $p$ so extreme that our
-skew-normal approximation will not work, our authors suggest a Poission
-approximation.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-p-range.png}
+  \caption{Range of possible $p$, given a fixed $n$}
+  \label{fig:sn-restriction-p-range}
+\end{figure}

### 2010-12-24 pieces/method-of-moments/output.tex
Added punctuation, support sets, made several small tweaks as suggested by Dr. Guffey.

--- 2010-12-10 pieces/method-of-moments/method-of-moments.tex
@@
 \documentclass{article}
-\usepackage {joyce-math}
+\usepackage{jcapstone}
+\begin{document}
 
-\begin{document}
-\section{The Method of Moments}
+\section{Developing an Approximation}
+
+Now that we have gotten to know our new distribution a little better, we can
+use it to develop an approximation for the binomial.
 
 Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
-approximations for $\mu$, $\sigma$, and $\lambda$ by comparing their first,
-second, and third moments about the mean.
+estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
+and third moments about the mean of $B$ and $Y$.
 
@@
 
-The first two moments, the mean and variance, are simply
+Let's start with the binomial. The first two moments are simply the mean and
+variance, which we can state from memory:
 
@@
   &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
-  \intertext{Let $y=x-3$. Then $x=y+3$, and $x=3 \rightarrow y=0$ and $x=n \rightarrow y=n-3$.}
+  \intertext{Let $y=x-3$. Then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$.}
   &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\text{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
+  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
   &= n(n-1)(n-2)p^3 \\
@@
 \end{equation}
-
-\textbf{\textit{Note to Dr. Guffey:} I am trying to find an algebraic reason
-for the sign, but I'm not seeing it in equation \eqref{eq:solving-for-lambda}
-nor its algebraic expansion, which I put in in appendix
-\ref{sec:solving-for-lambda} as it ended up providing little insight into this
-conclusion.}
 
@@
 
-\textbf{\textit{Another note to Dr. Guffey:} The author mentions here that when
-$p=0.5$, it forces $\lambda$ to be 0, bringing us back to the regular normal
-approximation. This seems like it ought to be a simple fact, but I can't figure
-out how he's getting it from these equations. He refers to his equation (c),
-which is my equation \eqref{eq:mu-solved}. Substituting $p=0.5$ into
-\eqref{eq:mu-solved}, however, doesn't get me anywhere; neither does
-substituting $p=0.5$ into \eqref{eq:sigma-solved} and then substituting that
-into \eqref{eq:mu-solved}. And as far as I can tell, equation
-\eqref{eq:lambda-solved} is for all practical purposes useless. Alas.}
+When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
+therefore $\mu = np = n/2$. From \eqref{eq:mu-solved}, this implies that
+$\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} =
+0 \Ra$ either $\sigma = 0$ or $\lambda = 0$. Since the former is impossible, we
+must conclude the latter, which brings us back to the normal distribution.
 
 \subsection{Restrictions}
+
+To obtain an estimate for $\lambda$, we must put a few restrictions on $n$ and
+$p$.
 
@@
 
-\begin{gather}
-  \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. \nonumber \\
-  \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 \nonumber \\
-  \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \nonumber \\
-  \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \label{eq:lhs-solving-for-lambda}
-\end{gather}
+\begin{alignat*}{3}
+  \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2}
+    &= \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. & \\
+  &= \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 & \\
+  &= \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) & \\
+  &= \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) &= g(v).
+\end{alignat*}
 
-we can see that it is increasing in $v$, which is always $\geq 1$. Therefore:
+We can see that $g(v)$ is increasing in $v$, which is always $\geq 1$.
+Therefore:
 
 \begin{equation}
-  \min_{v} \textnormal{\{Eq. \ref{eq:lhs-solving-for-lambda}\}} = \textnormal{\{Eq. \ref{eq:lhs-solving-for-lambda}\}} |_{v=1} = 
-  \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1
+  \min_{v} g(v) = g(v)|_{v=1} = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1,
 \end{equation}
 
-This means that the right hand side of \eqref{eq:solving-for-lambda}, which is
+which means that the right hand side of \eqref{eq:solving-for-lambda}, which is
 supposed to be equal to the left hand side of \eqref{eq:solving-for-lambda},
 can't ever be less than 1. Unfortunately, it sometimes is; in particular,
-$\frac{np(1-p)}{(1-2p)^2} \rightarrow 0$ both when $p \rightarrow 0$ and $p
-\rightarrow 1$. So if we want a solution, we must restrict $n$ and $p$ such
-that
+$\frac{np(1-p)}{(1-2p)^2} \to 0$ when $p \to 0$ or $p \to 1$. So if we want a
+solution, we must restrict $n$ and $p$ such that
 
@@
 
-If, however, we wish to fix $n$ and solve for $p$, we further factor \eqref{eq:solving-the-restriction}
+Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
+estimate $\lambda$ as a function of $p$. As expected, it is quite large when
+$p$ is small and rapidly goes to 0 as $p$ increases; for example, when $p =
+0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a
+trivial requirement to meet.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-least-n.png}
+  \caption{Least possible $n$, given a fixed $p$}
+  \label{fig:sn-restriction-least-n}
+\end{figure}
+
+The second scenario is when $n$ is fixed and we wish to solve for $p$. In this
+case, we return to \eqref{eq:solving-the-restriction} for further factoring:
 
@@
 
-and apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
+We then apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
 
-\begin{gather*}
-  \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
-  \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
-  \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n-4)} \\
-  \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
-  \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}}
-\end{gather*}
+\begin{align*}
+  p &= \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
+  &= \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
+  &= \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n+4)} \\
+  &= \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
+  &= \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}}
+\end{align*}
 
@@
 
-For sufficiently large $n$, this interval becomes almost $(0, 1)$. For example,
-when $n=100$, our interval is $(0.00971, 0.99029)$; when $n=500$, it is
-(0.00199, 0.99801).
+Shown in figure \ref{fig:sn-restriction-p-range} as a function of $n$, this
+interval grows quickly as $n$ increases, and for sufficiently large $n$, it
+becomes almost $(0, 1)$. For example, when $n=100$, our interval is $(0.00971,
+0.99029)$; when $n=500$, it is (0.00199, 0.99801).
 
-For $p$ so close to 0 or 1 that this solution will not work, our authors
-suggest a Poission approximation.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-p-range.png}
+  \caption{Range of possible $p$, given a fixed $n$}
+  \label{fig:sn-restriction-p-range}
+\end{figure}
+
+For those unfortunate combinations of $n$ and $p$ so extreme that our
+skew-normal approximation will not work, our authors suggest a Poission
+approximation.
 

### 2010-12-24 pieces/final-paper/output.tex
Renamed graphs -> calculations. Fleshed out README. About to rearrange.

@@
 \begin{proof}
-  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma^2,
+  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma,
   \lambda)$ is
@@
 
-Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
+Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
 estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-least-n.png}
+  \includegraphics[width=0.6\textwidth]{../images/restriction-least-n.png}
   \caption{Least possible $n$, given a fixed $p$}
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-p-range.png}
+  \includegraphics[width=0.6\textwidth]{../images/restriction-p-range.png}
   \caption{Range of possible $p$, given a fixed $n$}
@@
   \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n25.png}
+  \includegraphics[width=\textwidth]{../images/comparison-n25.png}
   \caption{Binomial, normal, and skew-normal, $n=25$}
@@
   \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n50.png}
+  \includegraphics[width=\textwidth]{../images/comparison-n50.png}
   \caption{Binomial, normal, and skew-normal, $n=50$}
@@
   \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n100.png}
+  \includegraphics[width=\textwidth]{../images/comparison-n100.png}
   \caption{Binomial, normal, and skew-normal, $n=100$}
@@
   \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
+  \includegraphics[width=\textwidth]{../images/mabs-fixed-n.png}
   \caption{MABS as a function of p}
@@
   \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-p.png}
+  \includegraphics[width=\textwidth]{../images/mabs-fixed-p.png}
   \caption{MABS as a function of n}
@@
 
+\begin{sidewaystable}
+  \centering
+  \begin{tabular}{ l l l l l l l l l }
+    (  0.89,    2.2,   2.31) & (  2.97,   2.94,   1.74) & (  7.44,   3.94,    1.4) & ( 16.77,   5.33,   1.16) \\
+    (  3.23,   2.67,    1.5) & (  7.76,   3.61,   1.24) & ( 17.18,   4.89,   1.04) & ( 36.45,   6.68,   0.89) \\
+    (   5.8,   2.85,   1.12) & ( 12.86,   3.88,   0.95) & ( 27.31,   5.32,   0.82) & (  56.6,   7.32,   0.72) \\
+    (  8.59,   2.83,    0.8) & ( 18.23,   3.89,    0.7) & ( 37.76,   5.39,   0.61) & ( 77.18,   7.48,   0.54) \\
+    (  12.5,    2.5,    0.0) & (  25.0,   3.54,    0.0) & (  50.0,    5.0,    0.0) & ( 100.0,   7.07,    0.0) \\
+    ( 16.41,   2.83,   -0.8) & ( 31.77,   3.89,   -0.7) & ( 62.24,   5.39,  -0.61) & (122.82,   7.48,  -0.54) \\
+    (  19.2,   2.85,  -1.12) & ( 37.14,   3.88,  -0.95) & ( 72.69,   5.32,  -0.82) & ( 143.4,   7.32,  -0.72) \\
+    ( 21.77,   2.67,   -1.5) & ( 42.24,   3.61,  -1.24) & ( 82.82,   4.89,  -1.04) & (163.55,   6.68,  -0.89) \\
+    ( 24.11,    2.2,  -2.31) & ( 47.03,   2.94,  -1.74) & ( 92.56,   3.94,   -1.4) & (183.23,   5.33,  -1.16) \\
+  \end{tabular}
+  \caption{foobarbif}
+  \label{table:sn-approx-table}
+\end{sidewaystable}
+
 \bibliography{/home/joycetipping/projects/capstone/pieces/bibliography/bibliography.bib}

### 2010-12-24 pieces/mabs/mabs.tex
Tweaks.
Added punctuation, support sets, made several small tweaks as suggested by Dr. Guffey.
Renamed graphs -> calculations. Fleshed out README. About to rearrange.

@@
 
-Another more numerical method would be to compare the maximal absolute errors
-of our two approximations, defined by \citet{mabs} as
+A quantitative method would be to compare the maximal absolute errors of our
+two approximations, defined by \citet{mabs} as
 

### 2010-12-24 pieces/calculations/approx_table.py

@@ -1,0 +1,21 @@
+from stats import *
+
+#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
+# Approximation Table
+#
+
+def build_approximation_table (ns, ps):
+  f = open('approx-table/approx-table-data.txt', 'w');
+  for p in ps: f.write(' & '.join(table_row(ns, p)) + ' \\\\\n');
+  f.close()
+    
+def table_row (ns, p):
+  return map(lambda n: sn_params_pretty(n, p), ns)
+
+def sn_params_pretty (n, p):
+  params = map(lambda x: str(round(x, 2)).rjust(6), sn_params(n, p));
+  return '(' + params[0] + ', ' + params[1] + ', ' + params[2] + ')';
+
+ns = [25, 50, 100, 200]
+ps = [0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9]
+build_approximation_table(ns, ps);

### 2010-12-24 pieces/calculations/flot_data.py

@@ -7,6 +7,9 @@ from stats import *
 # Skew-normal Restriction Graphs
 #
 def sn_restriction_p_range_graph ():
+  # Builds data for the "fixed n, viable p range" graph and writes it to an
+  # appropriately named json file
+
   def range_pt (n):
     range = sn_restriction_p_range(n)
     return [n, range[0], range[1]]
@@ -22,6 +25,9 @@ def sn_restriction_p_range_graph ():
   f.close()
 
 def sn_restriction_least_n_graph ():
+  # Builds data for the "fixed p, least n" graph and writes it to an
+  # appropriately named json file
+
   ps = r.seq(0.01, 0.5, 0.01)
   points = map(lambda p: [p, sn_restriction_least_n(p)], ps)
 

### 2010-12-24 pieces/graphs/py_graphs.py

@@ -1,19 +1,0 @@
-# Python modules
-import pylab
-# My modules
-from stats import *
-
-def comparison (n, p):
-  # Generate comparison graph
-
-  binomial = binomial_pmf(n, p)
-  normal = normal_pdf(n, p)
-  sn = sn_pdf(n, p)
-
-  #pylab.vlines(binomial['xs'], 0, binomial['ys'], color=(0, 0.5, 0, 1))
-  pylab.vlines(binomial['xs'], 0, binomial['ys'])
-  pylab.plot(normal['xs'], normal['ys'], '--')
-  pylab.plot(sn['xs'], sn['ys'])
-  pylab.savefig('py-graphs/comparison-n' + str(n) + 'p' + str(p).replace('.', ''), format='png')
-
-comparison(25, 0.1)

### 2010-12-24 project/paper/mabs.tex
Rearranged. Added skew normal approximation table.

--- 2010-12-24 pieces/final-paper/output.tex
@@
-\documentclass{article}
-\usepackage{jcapstone}
-\begin{document}
-
-\title{The Skew-Normal Approximation of the Binomial Distribution}
-\author{Joyce Tipping}
-\date{2010}
-\maketitle
-
-\section{Introduction}
-
-One of the most basic distributions in statistics is the binomial, $X \sim
-Bin(n,p)$, with pdf
-
-\begin{equation*}
-  f_X(x) = \binom{n}{x} p^x q^{n-x}, \quad x = 0, 1, \ldots, n.
-\end{equation*}
-
-Calculating the binomial cdf, $F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by
-hand is manageable for small $n$ but quickly becomes cumbersome as $n$ grows
-even moderately large. A common strategy is to use the normal distribution as
-an approximation:
-
-\begin{equation}
-  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right),
-\end{equation}
-
-where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
-\sqrt{np(1-p)}$.
-
-This approximation works best when the binomial is perfectly symmetrical, with
-$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
-becomes increasingly skewed, and one must either compensate by providing ever
-larger values of $n$ or face growing inaccuracy. In these cases, the
-skew-normal approximation can provide a better alternative.
-
-\section{The Skew-Normal}
-
-The skew-normal distribution is similar to the normal but with an added
-parameter for skew, allowing it to lean asymmetrically to the left or right. In
-this section, we'll acquaint ourselves with some of its basic properties.
-
-\subsection{Basics}
-
-Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
-scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$; we will
-denote it $SN(\mu, \sigma, \lambda)$. Then $Y$ has pdf
-
-\begin{equation} \label{eq:sn-pdf}
-  f_Y(x) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
-\end{equation}
-
-where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal cdf.
-Some other basic properties of $Y$, given by \citet{pewsey}, are
-
-\begin{align}
-  E(Y) &= \mu + b \delta \sigma, \nonumber \\
-  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-basic-properties} \\
-  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber \\
-  Var(Y) &= \sigma^2 (1 - b^2 \delta^2), \nonumber
-\end{align}
-
-where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}}$.
-
-The $SN(0,1,\lambda)$ distribution is called the standard skew-normal; its pdf
-is
-
-\begin{equation} \label{eq:standard-sn-pdf}
-  f_Z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
-\end{equation}
-
-Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
-= \sigma Z + \mu$.
-
-A natural question to ask is how the skew-normal relates to the normal.
-Fortunately, the connection is very intuitive: When $\lambda = 0$, Equation
-\eqref{eq:sn-pdf} becomes
-
-\begin{align*}
-  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
-  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
-  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
-  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
-  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
-\end{align*}
-
-which is the pdf of the normal distribution.
-
-\subsection{Four Properties}
-\label{subsec:four-properties}
-
-The following four properties of the skew-normal, given by \citet{main}, help
-shed light on our enigmatic new distribution:
-
-\begin{property} \label{prop:1}
-  If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
-\end{property}
-
-\begin{proof}
-  The standard normal pdf is an even function: $\phi(-x) =
-  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
-  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) =
-  \int_{-\infty}^\infty \phi(x)$, \thinspace is not even, being 0 near
-  $-\infty$ and 1 near $\infty$. Thus,
-
-  \begin{align*}
-    f_{(-Z)}(x) &= f_Z(-x) \\
-    & = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\
-    & = 2 \cdot \phi(x) \cdot \Phi (-\lambda x),
-  \end{align*}
-
-  which is the pdf of $SN(0, 1, -\lambda)$.
-\end{proof}
-
-\begin{property} \label{prop:2}
-  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
-\end{property}
-
-\begin{proof}
-  To prove our result, we make use of Lemma 1 in \citet{azzalini}, which we
-  restate here:
-
-  \begin{helper-lem}
-    If $f_0$ is a one-dimensional probability density function symmetric about
-    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
-    and is a density symmetric about 0, then
-
-    \begin{equation}
-      \label{eq:azzalini-perturbation-invariance}
-      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
-    \end{equation}
-
-    is a density function for any odd function $w(\cdot)$.
-  \end{helper-lem}
-
-  This lemma provides a very useful corollary:
-
-  \begin{helper-cor}[Perturbation Invariance]
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
-    notation $\overset{d}{=}$ denotes equality in distribution.    
-  \end{helper-cor}
-
-  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
-  \Phi(\lambda z)$ conforms to equation
-  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
-  and $Z$ are equal in distribution.
-
-  We will now show that $\phi^2 \sim \chi^2_1$:
-
-  \begin{align*}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \\
-    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \;; \\
-    \intertext{let $u = (\sqrt{1-2t}) \, x$; then $du = (\sqrt{1-2t}) \, dx$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty, x \to \infty \Ra
-      u \to -\infty, u \to \infty$:}
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} du \right) \\
-    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
-      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
-    &= \frac{1}{\sqrt{1-2t}} \;,
-  \end{align*}
-
-  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
-  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
-
-\begin{property} \label{prop:3}
-  As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
-\end{property}
-
-To prove our theorem, it is helpful to formally define the half normal distribution:
-
-\begin{helper-lem} \label{lem:p2-half-normal}
-  Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal
-  random variable with parameter $\sigma$ and
-
-  \begin{equation*}
-    f_{|X|}(x) =
-    \begin{dcases*}
-      0              & when $-\infty < x \leq 0$ \\
-      2 \cdot f_X(x) & when $0 < x < \infty$ 
-    \end{dcases*}
-    .
-  \end{equation*}
-\end{helper-lem}
-
-\begin{proof}
-  Let $X \sim N(0, \sigma^2)$, defined over $A = (-\infty, \infty)$. Define
-
-  \begin{equation*}
-    Y = |X| =
-    \begin{dcases*}
-      -x & if $x < 0$ \\
-      0 & if $x = 0$ \\
-      x & if $x > 0$ \\
-    \end{dcases*}
-    .
-  \end{equation*}
-
-  $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
-  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such
-  that $A = A_1 \cup A_2 \cup A_3$ and $Y$ is one-to-one over each $A_i$. We
-  can then transform each piece separately using Theorem 6.3.2 from
-  \citet{textbook}:
-
-  On $A_1$: $y = -x \Ra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1|
-  = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
-    &= f_X(-y) \cdot 1 \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma^2}} \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma^2}} \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_1: -\infty < x < 0 \Ra -\infty < -y < 0 \Ra 0 < y < \infty :B_1$.
-
-  Similarly, on $A_2$: $y = x \Ra x = y$ and $\J = \left| \frac{dx}{dy}
-  \right| = |1| = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
-    &= f_X(y) \cdot 1 \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_2: 0 < x < \infty \Ra 0 < y < \infty :B_2$.
-
-  On $A_3$, we have $x = 0 \Ra y = 0$ and $\J = \left| \frac{dx}{dy} \right| =
-  |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
-
-  Then, by Theorem 6.3.10 from \citet{textbook},
-
-  \begin{align*}
-    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \\
-    &= f_X(y) + f_X(y) \\
-    &= 2 \cdot f_X(y)
-  \end{align*}
-
-  over $B = B_1 \cup B_2 = (0, \infty)$, and 0 otherwise.
-\end{proof}
-
-With Lemma \ref{lem:p2-half-normal}, we can easily show our property:
-
-\begin{proof}[Proof of Property 3]
-  Let $Z \sim SN(0,1,\lambda)$. Recall that $f_Z(x) = 2 \cdot \phi(x) \cdot
-  \Phi(\lambda x)$.
-
-  Consider $\lim_{\lambda \to \infty} f_X(x)$. When $x$ is negative, $\lambda x
-  \to -\infty$ and thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however,
-  $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-positive-half-normal}
-    \lim_{\lambda \to \infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      0 & when $x \leq 0$ \\
-      2 \cdot \phi(x) & when $x > 0$
-    \end{dcases*}
-    \eq |N(0,1)|.
-  \end{equation}
-
-  In $\lim_{\lambda \to -\infty} f_X(x)$, the signs are reversed. When $x$ is
-  negative, $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. When $x$ is
-  positive, $\lambda x \to -\infty$ and $\Phi(\lambda x) \to 0$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-negative-half-normal}
-    \lim_{\lambda \to -\infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      2 \cdot \phi(x) & when $x < 0$ \\
-      0 & when $x \geq 0$
-    \end{dcases*}
-    \eq -|N(0,1)|.
-  \end{equation}
-\end{proof}
-
-\begin{property} \label{prop:4}
-  The MGF of $SN(0,1,\lambda)$ is
-
-  \begin{equation} \label{eq:p4-sn-mgf}
-    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2},
-  \end{equation}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
-\end{property}
-
-\begin{proof}
-  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma^2,
-  \lambda)$ is
-
-  \begin{equation*}
-    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t),
-  \end{equation*}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}} \in (-1, 1)$. It follows
-  that the MGF of the $SN(0, 1, \lambda)$ is
-
-  \begin{equation*}
-    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t).
-  \end{equation*}
-\end{proof}
-
-\section{Developing an Approximation}
-
-Now that we have gotten to know our new distribution a little better, we can
-use it to develop an approximation for the binomial.
-
-Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
-estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
-and third moments about the mean of $B$ and $Y$.
-
-\subsection{The Moments of the Binomial}
-
-Let's start with the binomial. The first two moments are simply the mean and
-variance, which we can state from memory:
-
-\begin{equation*}
-  E(B) = np, \quad Var(B) = np(1-p).
-\end{equation*}
-
-Having these, we can easily find
-
-\begin{equation*}
-  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2,
-\end{equation*}
-
-which we will need for the third moment. We will also need $E(B^3)$, which we
-will get via the third factorial moment:
-
-\begin{align*}
-  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \;; \\
-  \intertext{notice that the first three terms of this sum are zero, so we can rewrite our sum beginning at $x = 3$:}
-  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \\
-  \intertext{let $y=x-3$; then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$:}
-  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
-  &= n(n-1)(n-2)p^3 \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 \;; \\
-  \intertext{further expanding the left side and solving for $E(B^3)$:}
-  E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\
-  E(B^3) - 3E(B^2) + 2E(B) &= \\
-  E(B^3) - 3(np - np^2 + n^2p^2) + 2np &= \\
-  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 + 3np - 3np^2 + 3n^2p^2 - 2np \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np.
-\end{align*}
-
-Now, finally, we have all the building blocks necessary to obtain the third
-moment:
-
-\begin{align*}
-  E \left( [B - E(B)]^3 \right) &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
-  &= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\
-  &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
-  &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\
-  &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
-  &= 2np^3 - 3np^2 + np \\
-  &= np(p-1)(2p-1).
-\end{align*}
-
-Our hard-earned results, restated for convenience:
-
-\begin{align}
-  E(B) &= np, \nonumber \\
-  E([B - E(B)]^2) &= np(1-p), \\
-  E([B - E(B)]^3) &= np(p-1)(2p-1). \nonumber
-\end{align}
-
-\subsection{The Moments of the Skew Normal}
-
-Now we'll take a look at the moments of the skew normal. Equation
-\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
-third moment is a little more complicated:
-
-\begin{align*}
-  E([Y - E(Y)]^3) &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
-  &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) \\
-  & \quad + 2\;(\mu + b \delta \sigma)^3 \\
-  &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} -
-    \cancel{6 b \delta \mu^2 \sigma} - \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} \\
-  & \quad - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
-  &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
-  &= b \delta^3 \sigma^3 (2b^2 - 1).
-\end{align*}
-
-We restate our results:
-
-\begin{alignat}{4}
-  E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;, \nonumber \\
-  E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right), \\
-  E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right). \nonumber
-\end{alignat}
-
-\subsection{Solving for $\mu$, $\sigma$, $\lambda$}
-
-Now we can set the moments of our two distributions equal to each other and,
-taking $n$ and $p$ as constants, solve for $\mu$, $\sigma$ and $\lambda$:
-
-\begin{subequations}
-\begin{align}
-  np &= \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \label{eq:first-moment-set} \\
-  np(1-p) &= \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:second-moment-set} \\
-  np(p-1)(2p-1) &= \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \label{eq:third-moment-set}
-\end{align}
-\end{subequations}
-
-To get $\lambda$, we divide the cube of \eqref{eq:second-moment-set} by the
-square of \eqref{eq:third-moment-set}:
-
-\begin{align}
-  \frac{\sigma^6 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right)^3}{\sigma^6 \cdot \frac{2}{\pi} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^6 \left(
-    \frac{4}{\pi} - 1 \right)^2} &= \frac{n^3p^3(1-p)^3}{n^2p^2(p-1)^2(2p-1)^2} \nonumber \\
-  \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-    \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \;. \label{eq:solving-for-lambda}
-\end{align}
-
-The above equation \eqref{eq:solving-for-lambda} is a rational expression in
-$\lambda^2$ that can be solved with either a considerable amount of manual
-labor or, more efficiently, with a computer algebra system. Once we have
-$\lambda^2$, then $\lambda$ is simply either the positive or negative square
-root, as determined by the sign of $(1-2p)$. The sign can be explained with a
-little assistance from Property \ref{prop:3}: When $p \to 0$, the binomial
-skews left and converges toward the positive half normal, which by
-\eqref{eq:p2-positive-half-normal} corresponds to a positive $\lambda$. When $p
-\to 1$, the binomial skews right and converges toward the negative half normal,
-which by \eqref{eq:p2-negative-half-normal} corresponds to a negative
-$\lambda$. When $p = 0.5$, the binomial is symmetric and $\lambda$ is 0,
-eliminating the need for a sign. Thus:
-
-\begin{equation}
-  \label{eq:lambda-solved}
-  \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}.
-\end{equation}
-
-Having secured $\lambda$, we can find $\sigma$ using
-\eqref{eq:second-moment-set}:
-
-\begin{equation}
-  \label{eq:sigma-solved}
-  np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
-  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} \;.
-\end{equation}
-
-And with both $\lambda$ and $\sigma$, a simple rearrangement of
-\eqref{eq:first-moment-set} yields $\mu$:
-
-\begin{equation}
-  \label{eq:mu-solved}
-  np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
-  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;.
-\end{equation}
-
-When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
-therefore $\mu = np = n/2$. This equation, together with \eqref{eq:mu-solved},
-implies that $\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 +
-\lambda^2}} = 0 \Ra$ either $\sigma = 0$ or $\lambda = 0$. Since the former is
-impossible, we must conclude the latter, which brings us back to the normal
-distribution.
-
-\subsection{Restrictions}
-
-To obtain an estimate for $\lambda$, we must put a few restrictions on $n$ and
-$p$.
-
-If we let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u$, we can rewrite the
-left hand side of \eqref{eq:solving-for-lambda} as
-
-\begin{alignat*}{3}
-  \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2}
-    &= \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. & \\
-  &= \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 & \\
-  &= \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) & \\
-  &= \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) &= g(v).
-\end{alignat*}
-
-We can see that $g(v)$ is increasing in $v$, which is always $\geq 1$.
-Therefore:
-
-\begin{equation}
-  \min_{v} g(v) = g(v)|_{v=1} = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1,
-\end{equation}
-
-which means that the right hand side of \eqref{eq:solving-for-lambda}, which is
-supposed to be equal to the left hand side of \eqref{eq:solving-for-lambda},
-can't ever be less than 1. Unfortunately, it sometimes is; in particular,
-$\frac{np(1-p)}{(1-2p)^2} \to 0$ when $p \to 0$ or $p \to 1$. So if we want a
-solution, we must restrict $n$ and $p$ such that
-
-\begin{align}
-  \textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\
-  \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
-  np(1-p) &\geq (1-2p)^2. \label{eq:solving-the-restriction}
-\end{align}
-
-Here, two scenarios arise. The first is when we have a fixed $p$ and wish to
-find the minimum $n$ necessary to derive a skew-normal approximation. From
-\eqref{eq:solving-the-restriction}, solving for $n$ is very simple:
-
-\begin{equation}
-  n \geq \frac{(1-2p)^2}{p(1-p)} \;. \label{eq: n for a given p}
-\end{equation}
-
-Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
-estimate $\lambda$ as a function of $p$. As expected, it is quite large when
-$p$ is small and rapidly goes to 0 as $p$ increases; for example, when $p =
-0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a
-trivial requirement to meet.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-least-n.png}
-  \caption{Least possible $n$, given a fixed $p$}
-  \label{fig:sn-restriction-least-n}
-\end{figure}
-
-The second scenario is when $n$ is fixed and we wish to solve for $p$. In this
-case, we return to \eqref{eq:solving-the-restriction} for further factoring:
-
-\begin{align}
-  np(1-p) &\geq (1-2p)^2 \nonumber \\
-  np - np^2 &\geq 1 - 4p + 4p^2 \nonumber \\
-  1 - 4p + 4p^2 - np + np^2 &\leq 0 \nonumber \\
-  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq: solving for p}.
-\end{align}
-
-We then apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
-
-\begin{align*}
-  p &= \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
-  &= \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
-  &= \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n+4)} \\
-  &= \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
-  &= \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}} \;.
-\end{align*}
-
-Let $r_1 = \frac12 - \frac12 \sqrt{\frac{n}{n+4}}$ and $r_2 = \frac12 + \frac12
-\sqrt{\frac{n}{n+4}}$. (Note that $r_1 < r_2$.) Now we can rewrite \eqref{eq:
-solving for p} as
-
-\begin{equation*}
-  (p - r_1)(p - r_2) \leq 0.
-\end{equation*}
-
-Examining the left hand side, when $p < r_1$, both terms are negative and so
-their product is positive; when $p > r_2$, both terms are positive, again
-leading the product to be positive. Therefore, our solution lies where $r_1
-\leq p \leq r_2$, or more explicitly,
-
-\begin{equation}
- \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}} \;.
-\end{equation}
-
-Shown in figure \ref{fig:sn-restriction-p-range} as a function of $n$, this
-interval grows quickly as $n$ increases, and for sufficiently large $n$, it
-becomes almost $(0, 1)$. For example, when $n=100$, our interval is $(0.00971,
-0.99029)$; when $n=500$, it is (0.00199, 0.99801).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-p-range.png}
-  \caption{Range of possible $p$, given a fixed $n$}
-  \label{fig:sn-restriction-p-range}
-\end{figure}
-
 \section{Demonstrating Improved Accuracy}
@@
 
+Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
+skew-normal and normal approximations as a function of $p$ and $n$,
+respectively. Again, the skew-normal outperforms the normal considerably in the
+extreme ranges, with the two approximations converging as $n \rightarrow
+\infty$ or $p \rightarrow 0.5$.
+
 \begin{figure}
   \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
+  \includegraphics[width=\textwidth]{../images/mabs-fixed-n.png}
   \caption{MABS as a function of p}
@@
 
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
-skew-normal and normal approximations as a function of $p$ and $n$,
-respectively. Again, the skew-normal outperforms the normal considerably in the
-extreme ranges, with the two approximations converging as $n \rightarrow
-\infty$ or $p \rightarrow 0.5$.
-
 \clearpage
-
-\bibliography{/home/joycetipping/projects/capstone/pieces/bibliography/bibliography.bib}
-\bibliographystyle{plainnat}
-\end{document}

### 2010-12-24 project/paper/properties.tex
Rearranged. Added skew normal approximation table.

--- 2010-12-24 pieces/final-paper/output.tex
@@
-\documentclass{article}
-\usepackage{jcapstone}
-\begin{document}
-
-\title{The Skew-Normal Approximation of the Binomial Distribution}
-\author{Joyce Tipping}
-\date{2010}
-\maketitle
-
-\section{Introduction}
-
-One of the most basic distributions in statistics is the binomial, $X \sim
-Bin(n,p)$, with pdf
-
-\begin{equation*}
-  f_X(x) = \binom{n}{x} p^x q^{n-x}, \quad x = 0, 1, \ldots, n.
-\end{equation*}
-
-Calculating the binomial cdf, $F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by
-hand is manageable for small $n$ but quickly becomes cumbersome as $n$ grows
-even moderately large. A common strategy is to use the normal distribution as
-an approximation:
-
-\begin{equation}
-  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right),
-\end{equation}
-
-where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
-\sqrt{np(1-p)}$.
-
-This approximation works best when the binomial is perfectly symmetrical, with
-$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
-becomes increasingly skewed, and one must either compensate by providing ever
-larger values of $n$ or face growing inaccuracy. In these cases, the
-skew-normal approximation can provide a better alternative.
-
 \section{The Skew-Normal}
@@
 \end{proof}
-
-\section{Developing an Approximation}
-
-Now that we have gotten to know our new distribution a little better, we can
-use it to develop an approximation for the binomial.
-
-Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
-estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
-and third moments about the mean of $B$ and $Y$.
-
-\subsection{The Moments of the Binomial}
-
-Let's start with the binomial. The first two moments are simply the mean and
-variance, which we can state from memory:
-
-\begin{equation*}
-  E(B) = np, \quad Var(B) = np(1-p).
-\end{equation*}
-
-Having these, we can easily find
-
-\begin{equation*}
-  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2,
-\end{equation*}
-
-which we will need for the third moment. We will also need $E(B^3)$, which we
-will get via the third factorial moment:
-
-\begin{align*}
-  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \;; \\
-  \intertext{notice that the first three terms of this sum are zero, so we can rewrite our sum beginning at $x = 3$:}
-  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \\
-  \intertext{let $y=x-3$; then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$:}
-  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
-  &= n(n-1)(n-2)p^3 \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 \;; \\
-  \intertext{further expanding the left side and solving for $E(B^3)$:}
-  E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\
-  E(B^3) - 3E(B^2) + 2E(B) &= \\
-  E(B^3) - 3(np - np^2 + n^2p^2) + 2np &= \\
-  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 + 3np - 3np^2 + 3n^2p^2 - 2np \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np.
-\end{align*}
-
-Now, finally, we have all the building blocks necessary to obtain the third
-moment:
-
-\begin{align*}
-  E \left( [B - E(B)]^3 \right) &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
-  &= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\
-  &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
-  &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\
-  &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
-  &= 2np^3 - 3np^2 + np \\
-  &= np(p-1)(2p-1).
-\end{align*}
-
-Our hard-earned results, restated for convenience:
-
-\begin{align}
-  E(B) &= np, \nonumber \\
-  E([B - E(B)]^2) &= np(1-p), \\
-  E([B - E(B)]^3) &= np(p-1)(2p-1). \nonumber
-\end{align}
-
-\subsection{The Moments of the Skew Normal}
-
-Now we'll take a look at the moments of the skew normal. Equation
-\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
-third moment is a little more complicated:
-
-\begin{align*}
-  E([Y - E(Y)]^3) &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
-  &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) \\
-  & \quad + 2\;(\mu + b \delta \sigma)^3 \\
-  &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} -
-    \cancel{6 b \delta \mu^2 \sigma} - \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} \\
-  & \quad - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
-  &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
-  &= b \delta^3 \sigma^3 (2b^2 - 1).
-\end{align*}
-
-We restate our results:
-
-\begin{alignat}{4}
-  E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;, \nonumber \\
-  E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right), \\
-  E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right). \nonumber
-\end{alignat}
-
-\subsection{Solving for $\mu$, $\sigma$, $\lambda$}
-
-Now we can set the moments of our two distributions equal to each other and,
-taking $n$ and $p$ as constants, solve for $\mu$, $\sigma$ and $\lambda$:
-
-\begin{subequations}
-\begin{align}
-  np &= \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \label{eq:first-moment-set} \\
-  np(1-p) &= \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:second-moment-set} \\
-  np(p-1)(2p-1) &= \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \label{eq:third-moment-set}
-\end{align}
-\end{subequations}
-
-To get $\lambda$, we divide the cube of \eqref{eq:second-moment-set} by the
-square of \eqref{eq:third-moment-set}:
-
-\begin{align}
-  \frac{\sigma^6 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right)^3}{\sigma^6 \cdot \frac{2}{\pi} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^6 \left(
-    \frac{4}{\pi} - 1 \right)^2} &= \frac{n^3p^3(1-p)^3}{n^2p^2(p-1)^2(2p-1)^2} \nonumber \\
-  \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-    \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \;. \label{eq:solving-for-lambda}
-\end{align}
-
-The above equation \eqref{eq:solving-for-lambda} is a rational expression in
-$\lambda^2$ that can be solved with either a considerable amount of manual
-labor or, more efficiently, with a computer algebra system. Once we have
-$\lambda^2$, then $\lambda$ is simply either the positive or negative square
-root, as determined by the sign of $(1-2p)$. The sign can be explained with a
-little assistance from Property \ref{prop:3}: When $p \to 0$, the binomial
-skews left and converges toward the positive half normal, which by
-\eqref{eq:p2-positive-half-normal} corresponds to a positive $\lambda$. When $p
-\to 1$, the binomial skews right and converges toward the negative half normal,
-which by \eqref{eq:p2-negative-half-normal} corresponds to a negative
-$\lambda$. When $p = 0.5$, the binomial is symmetric and $\lambda$ is 0,
-eliminating the need for a sign. Thus:
-
-\begin{equation}
-  \label{eq:lambda-solved}
-  \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}.
-\end{equation}
-
-Having secured $\lambda$, we can find $\sigma$ using
-\eqref{eq:second-moment-set}:
-
-\begin{equation}
-  \label{eq:sigma-solved}
-  np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
-  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} \;.
-\end{equation}
-
-And with both $\lambda$ and $\sigma$, a simple rearrangement of
-\eqref{eq:first-moment-set} yields $\mu$:
-
-\begin{equation}
-  \label{eq:mu-solved}
-  np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
-  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;.
-\end{equation}
-
-When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
-therefore $\mu = np = n/2$. This equation, together with \eqref{eq:mu-solved},
-implies that $\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 +
-\lambda^2}} = 0 \Ra$ either $\sigma = 0$ or $\lambda = 0$. Since the former is
-impossible, we must conclude the latter, which brings us back to the normal
-distribution.
-
-\subsection{Restrictions}
-
-To obtain an estimate for $\lambda$, we must put a few restrictions on $n$ and
-$p$.
-
-If we let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u$, we can rewrite the
-left hand side of \eqref{eq:solving-for-lambda} as
-
-\begin{alignat*}{3}
-  \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2}
-    &= \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. & \\
-  &= \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 & \\
-  &= \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) & \\
-  &= \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) &= g(v).
-\end{alignat*}
-
-We can see that $g(v)$ is increasing in $v$, which is always $\geq 1$.
-Therefore:
-
-\begin{equation}
-  \min_{v} g(v) = g(v)|_{v=1} = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1,
-\end{equation}
-
-which means that the right hand side of \eqref{eq:solving-for-lambda}, which is
-supposed to be equal to the left hand side of \eqref{eq:solving-for-lambda},
-can't ever be less than 1. Unfortunately, it sometimes is; in particular,
-$\frac{np(1-p)}{(1-2p)^2} \to 0$ when $p \to 0$ or $p \to 1$. So if we want a
-solution, we must restrict $n$ and $p$ such that
-
-\begin{align}
-  \textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\
-  \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
-  np(1-p) &\geq (1-2p)^2. \label{eq:solving-the-restriction}
-\end{align}
-
-Here, two scenarios arise. The first is when we have a fixed $p$ and wish to
-find the minimum $n$ necessary to derive a skew-normal approximation. From
-\eqref{eq:solving-the-restriction}, solving for $n$ is very simple:
-
-\begin{equation}
-  n \geq \frac{(1-2p)^2}{p(1-p)} \;. \label{eq: n for a given p}
-\end{equation}
-
-Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
-estimate $\lambda$ as a function of $p$. As expected, it is quite large when
-$p$ is small and rapidly goes to 0 as $p$ increases; for example, when $p =
-0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a
-trivial requirement to meet.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-least-n.png}
-  \caption{Least possible $n$, given a fixed $p$}
-  \label{fig:sn-restriction-least-n}
-\end{figure}
-
-The second scenario is when $n$ is fixed and we wish to solve for $p$. In this
-case, we return to \eqref{eq:solving-the-restriction} for further factoring:
-
-\begin{align}
-  np(1-p) &\geq (1-2p)^2 \nonumber \\
-  np - np^2 &\geq 1 - 4p + 4p^2 \nonumber \\
-  1 - 4p + 4p^2 - np + np^2 &\leq 0 \nonumber \\
-  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq: solving for p}.
-\end{align}
-
-We then apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
-
-\begin{align*}
-  p &= \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
-  &= \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
-  &= \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n+4)} \\
-  &= \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
-  &= \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}} \;.
-\end{align*}
-
-Let $r_1 = \frac12 - \frac12 \sqrt{\frac{n}{n+4}}$ and $r_2 = \frac12 + \frac12
-\sqrt{\frac{n}{n+4}}$. (Note that $r_1 < r_2$.) Now we can rewrite \eqref{eq:
-solving for p} as
-
-\begin{equation*}
-  (p - r_1)(p - r_2) \leq 0.
-\end{equation*}
-
-Examining the left hand side, when $p < r_1$, both terms are negative and so
-their product is positive; when $p > r_2$, both terms are positive, again
-leading the product to be positive. Therefore, our solution lies where $r_1
-\leq p \leq r_2$, or more explicitly,
-
-\begin{equation}
- \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}} \;.
-\end{equation}
-
-Shown in figure \ref{fig:sn-restriction-p-range} as a function of $n$, this
-interval grows quickly as $n$ increases, and for sufficiently large $n$, it
-becomes almost $(0, 1)$. For example, when $n=100$, our interval is $(0.00971,
-0.99029)$; when $n=500$, it is (0.00199, 0.99801).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-p-range.png}
-  \caption{Range of possible $p$, given a fixed $n$}
-  \label{fig:sn-restriction-p-range}
-\end{figure}
-
-\section{Demonstrating Improved Accuracy}
-
-Now comes the time to justify our efforts by comparing the accuracy of our
-skew-normal approximation to that of the normal.
-
-\subsection{Visual Comparison}
-
-The first and most obvious way of judging accuracy is by visual inspection.
-Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
-\ref{fig:comparison-n100} compare the binomial, normal, and skew-normal at
-small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively. It is not
-hard to see that, especially at very small $n$ and $p$, our skew-normal curve
-follows the shape of the binomial much more closely.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n25.png}
-  \caption{Binomial, normal, and skew-normal, $n=25$}
-  \label{fig:comparison-n25}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n50.png}
-  \caption{Binomial, normal, and skew-normal, $n=50$}
-  \label{fig:comparison-n50}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n100.png}
-  \caption{Binomial, normal, and skew-normal, $n=100$}
-  \label{fig:comparison-n100}
-\end{figure}
-
-\subsection{Maximal Absolute Error}
-
-A quantitative method would be to compare the maximal absolute errors of our
-two approximations, defined by \citet{mabs} as
-
-\begin{equation}
-  \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
-\end{equation}
-
-where $F_{B(n,p)}$ is the cdf of the binomial and $F_{\textnormal{appr}(n,p)}$
-is the cdf of either the normal or skew-normal approximation; the 0.5 is a
-continuity correction.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
-  \caption{MABS as a function of p}
-  \label{fig:mabs-fixed-n}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-p.png}
-  \caption{MABS as a function of n}
-  \label{fig:mabs-fixed-p}
-\end{figure}
-
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
-skew-normal and normal approximations as a function of $p$ and $n$,
-respectively. Again, the skew-normal outperforms the normal considerably in the
-extreme ranges, with the two approximations converging as $n \rightarrow
-\infty$ or $p \rightarrow 0.5$.
-
-\clearpage
-
-\bibliography{/home/joycetipping/projects/capstone/pieces/bibliography/bibliography.bib}
-\bibliographystyle{plainnat}
-\end{document}

### 2010-12-24 pieces/calculations/approx_table.py

@@ -1,21 +1,0 @@
-from stats import *
-
-#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
-# Approximation Table
-#
-
-def build_approximation_table (ns, ps):
-  f = open('approx-table/approx-table-data.txt', 'w');
-  for p in ps: f.write(' & '.join(table_row(ns, p)) + ' \\\\\n');
-  f.close()
-    
-def table_row (ns, p):
-  return map(lambda n: sn_params_pretty(n, p), ns)
-
-def sn_params_pretty (n, p):
-  params = map(lambda x: str(round(x, 2)).rjust(6), sn_params(n, p));
-  return '(' + params[0] + ', ' + params[1] + ', ' + params[2] + ')';
-
-ns = [25, 50, 100, 200]
-ps = [0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9]
-build_approximation_table(ns, ps);

### 2010-12-24 project/calc/approx_table.py

@@ -1,0 +1,25 @@
+from stats import *
+
+#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
+# Approximation Table
+#
+
+def build_approximation_table (ns, ps):
+  f = open('approx-table/approx-table-data.txt', 'w')
+  f.write('{ r r | ' + 'r@{}r@{,\\;}r@{,\\;}r@{}l '*len(ns) + '}\n')
+  f.write('\\hline \\hline\n')
+  f.write('& & ' + '\\multicolumn{5}{c}{} & '*2 + '\\multicolumn{5}{c}{$n$}' + ' & \\multicolumn{5}{c}{}'*2 + '\\\\\n')
+  f.write('\\multirow{' + str(len(ps) + 1) + '}{*}{$p$} & & ' + ' & '.join(map(lambda n: '\\multicolumn{5}{c}{' + str(n) + '}', ns)) + ' \\\\\n\\hline\n');
+  for p in ps: f.write('& ' + '{0:.2f}'.format(p) + ' & ' + ' & '.join(table_row(ns, p)) + ' \\\\\n');
+  f.close()
+    
+def table_row (ns, p):
+  return map(lambda n: sn_params_pretty(n, p), ns)
+
+def sn_params_pretty (n, p):
+  params = map(lambda x: '{0:.2f}'.format(x), sn_params(n, p));
+  return '( & ' + params[0] + ' & ' + params[1] + ' & ' + params[2] + ' & )';
+
+ns = [25, 50, 100, 250, 500]
+ps = r.seq(0.05, 0.95, 0.05)
+build_approximation_table(ns, ps);

### 2010-12-25 project/paper/appendices.tex
Finished demonstration of calculating sn by hand

\section{Calculating a Skew-Normal Approximation}
\label{app:calc-sn-approx}

Although easier with a computer program, calculating estimates for $\mu$,
$\sigma$, and $\lambda$ by hand is perfectly possible. Here, we will
demonstrate using $n=25$, $p=0.1$.

By far the largest battle is finding $\lambda$. We will use Equation
\eqref{eq:solving-for-lambda} but with the simplified left hand side given by
\eqref{eq:lhs-solving-for-lambda}:

\begin{equation}
  \label{eq:calculating-lambda}
  \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = \frac{np(1-p)}{(1-2p)^2} \;.
\end{equation}

The closed-formed solution to this equation is long, hideous, and hard to work
with, so for this demonstration, we will take a numerical approach.

The left hand side of \eqref{eq:calculating-lambda} is a function of lambda;
let us denote it $f(\lambda)$. The right hand side is a constant in $n$ and
$p$; let us call it $k_{n,p}$. Our goal is to find a value of lambda that comes
within a certain margin of error, $e$. Since we are computing by hand, we will
take $e$ to be a modest 0.01.

Recall that the sign of $\lambda$ is determined independently of the value. In
fact, $f$ is never affected by the sign of $\lambda$, as all terms are squared.
Thus, we can restrict our search for $\lambda$ to the interval $(0, \infty)$.

Next, by taking $f$'s derivative, we can show that it is monotonically
decreasing for positive $\lambda$:

\begin{align*}
  \frac{d}{d\lambda} \left[ \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \right] &= \left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot
    3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2 \cdot \left( \frac{2\lambda}{\lambda^2} - \frac{2(1+\lambda^2)}{\lambda^3} \right) \\
  &= \left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot 3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2 \cdot
    \left( \cancel{\frac{2}{\lambda}} - \frac{2}{\lambda^3} - \cancel{\frac{2}{\lambda}} \right) \\
  &= \underbrace{\left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot 3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2}_\textnormal{Always positive} \quad \cdot \quad
     \underbrace{\left( -\frac{2}{\lambda^3} \right)}_{\mathclap{\textnormal{Negative when $\lambda > 0$}}}.
\end{align*}

This convenient fact allows us to find lower and upper bounds for $\lambda$ and
repeatedly bisect our interval until we are within $e$ of $k_{n,p}$.

(For the following calculations, it is helpful to keep in mind that because $f$
is decreasing in $\lambda$, smaller values of $\lambda$ will produce larger
values of $f$, and vice versa.)

\begin{enumerate}
  \item \textit{Find $k_{n,p}$.}

    Our value: $\displaystyle k_{n,p} = \frac{25 \cdot 0.1 \cdot 0.9}{(1 - 2\cdot0.1)^2} = 3.5156$.

  \item \textit{Find $a,b$ such that $f(a) > k_{n,p} > f(b)$.}

    Our values: $a=1$, $b=3$.

  \item \textit{Bisect $(a,b)$ until $f(c)$ is within $e$ of $k_{n,p}$.}

    Calculate $c=\frac{a+b}{2}$.

    \begin{itemize}
      \item If $f(c) \leq k_{n,p} - 0.01$, we need a small value of $c$, so we
      take our new interval to be $(a, c)$.

      \item If $f(c) \geq k_{n,p} + 0.01$, we need a larger value of $c$, so we
      take our new interval to be $(c, b)$.
    \end{itemize}

    Repeat this step until $f(c)$ is within $e$ of $k_{n,p}$, or more precisely
    $k_{n,p} - 0.01 < f(c) < k_{n,p} + 0.01$.

    The following table shows our iterations:

    \renewcommand{\arraystretch}{1.3}
    \begin{center}
      \begin{tabular}{c c c c c c c}
        Iteration & $a$  & $b$   & $c$    & $f(c)$ & $f(c) \leq k_{n,p} - 0.01$ & $f(c) \geq k_{n,p} + 0.01$ \\
        \hline
        1         & 2.00 & 3.000 & 2.5000 & 3.0164 & True                       & False \\
        2         & 2.00 & 2.500 & 2.2500 & 3.7129 & False                      & True \\
        3         & 2.25 & 2.500 & 2.3750 & 3.3252 & True                       & False \\
        4         & 2.25 & 2.375 & 2.3125 & 3.5076 & False                      & False \\
      \end{tabular}
    \end{center}

    We take the last value of $c$: 2.3125.

  \item \textit{Find the sign of $(1-2p)$.}

    Our $p = 0.1 \Ra (1 - 2\cdot0.1) = 0.8 \Ra$ positive.

  \item \textit{Final answer: \{sign of $(1-2p)$\}$\lambda$}

    Our final answer: $\lambda = 2.3125$.
\end{enumerate}

Once we have $\lambda$, we can easily find $\sigma$:

\begin{equation*}
  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} = \sqrt{\frac{25 \cdot 0.1 \cdot 0.9}{1 - \frac{2}{\pi} \cdot \frac{2.3125^2}{1 + 2.3125^2}}} = 2.2029. \\
\end{equation*}

And with $\lambda$ and $\sigma$, we can also find $\mu$:

\begin{equation*}
  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} = 25 \cdot 0.1 - 2.2029 \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{2.3125}{\sqrt{1 + 2.3125^2}} = 0.8868.
\end{equation*}

\clearpage

### 2010-12-25 project/paper/method-of-moments.tex
Finished demonstration of calculating sn by hand

--- 2010-12-24 pieces/final-paper/output.tex
@@
-\documentclass{article}
-\usepackage{jcapstone}
-\begin{document}
-
-\title{The Skew-Normal Approximation of the Binomial Distribution}
-\author{Joyce Tipping}
-\date{2010}
-\maketitle
-
-\section{Introduction}
-
-One of the most basic distributions in statistics is the binomial, $X \sim
-Bin(n,p)$, with pdf
-
-\begin{equation*}
-  f_X(x) = \binom{n}{x} p^x q^{n-x}, \quad x = 0, 1, \ldots, n.
-\end{equation*}
-
-Calculating the binomial cdf, $F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by
-hand is manageable for small $n$ but quickly becomes cumbersome as $n$ grows
-even moderately large. A common strategy is to use the normal distribution as
-an approximation:
-
-\begin{equation}
-  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right),
-\end{equation}
-
-where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
-\sqrt{np(1-p)}$.
-
-This approximation works best when the binomial is perfectly symmetrical, with
-$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
-becomes increasingly skewed, and one must either compensate by providing ever
-larger values of $n$ or face growing inaccuracy. In these cases, the
-skew-normal approximation can provide a better alternative.
-
-\section{The Skew-Normal}
-
-The skew-normal distribution is similar to the normal but with an added
-parameter for skew, allowing it to lean asymmetrically to the left or right. In
-this section, we'll acquaint ourselves with some of its basic properties.
-
-\subsection{Basics}
-
-Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
-scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$; we will
-denote it $SN(\mu, \sigma, \lambda)$. Then $Y$ has pdf
-
-\begin{equation} \label{eq:sn-pdf}
-  f_Y(x) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
-\end{equation}
-
-where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal cdf.
-Some other basic properties of $Y$, given by \citet{pewsey}, are
-
-\begin{align}
-  E(Y) &= \mu + b \delta \sigma, \nonumber \\
-  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-basic-properties} \\
-  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber \\
-  Var(Y) &= \sigma^2 (1 - b^2 \delta^2), \nonumber
-\end{align}
-
-where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}}$.
-
-The $SN(0,1,\lambda)$ distribution is called the standard skew-normal; its pdf
-is
-
-\begin{equation} \label{eq:standard-sn-pdf}
-  f_Z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
-\end{equation}
-
-Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
-= \sigma Z + \mu$.
-
-A natural question to ask is how the skew-normal relates to the normal.
-Fortunately, the connection is very intuitive: When $\lambda = 0$, Equation
-\eqref{eq:sn-pdf} becomes
-
-\begin{align*}
-  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
-  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
-  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
-  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
-  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
-\end{align*}
-
-which is the pdf of the normal distribution.
-
-\subsection{Four Properties}
-\label{subsec:four-properties}
-
-The following four properties of the skew-normal, given by \citet{main}, help
-shed light on our enigmatic new distribution:
-
-\begin{property} \label{prop:1}
-  If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
-\end{property}
-
-\begin{proof}
-  The standard normal pdf is an even function: $\phi(-x) =
-  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
-  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) =
-  \int_{-\infty}^\infty \phi(x)$, \thinspace is not even, being 0 near
-  $-\infty$ and 1 near $\infty$. Thus,
-
-  \begin{align*}
-    f_{(-Z)}(x) &= f_Z(-x) \\
-    & = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\
-    & = 2 \cdot \phi(x) \cdot \Phi (-\lambda x),
-  \end{align*}
-
-  which is the pdf of $SN(0, 1, -\lambda)$.
-\end{proof}
-
-\begin{property} \label{prop:2}
-  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
-\end{property}
-
-\begin{proof}
-  To prove our result, we make use of Lemma 1 in \citet{azzalini}, which we
-  restate here:
-
-  \begin{helper-lem}
-    If $f_0$ is a one-dimensional probability density function symmetric about
-    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
-    and is a density symmetric about 0, then
-
-    \begin{equation}
-      \label{eq:azzalini-perturbation-invariance}
-      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
-    \end{equation}
-
-    is a density function for any odd function $w(\cdot)$.
-  \end{helper-lem}
-
-  This lemma provides a very useful corollary:
-
-  \begin{helper-cor}[Perturbation Invariance]
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
-    notation $\overset{d}{=}$ denotes equality in distribution.    
-  \end{helper-cor}
-
-  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
-  \Phi(\lambda z)$ conforms to equation
-  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
-  and $Z$ are equal in distribution.
-
-  We will now show that $\phi^2 \sim \chi^2_1$:
-
-  \begin{align*}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \\
-    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \;; \\
-    \intertext{let $u = (\sqrt{1-2t}) \, x$; then $du = (\sqrt{1-2t}) \, dx$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty, x \to \infty \Ra
-      u \to -\infty, u \to \infty$:}
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} du \right) \\
-    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
-      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
-    &= \frac{1}{\sqrt{1-2t}} \;,
-  \end{align*}
-
-  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
-  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
-
-\begin{property} \label{prop:3}
-  As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
-\end{property}
-
-To prove our theorem, it is helpful to formally define the half normal distribution:
-
-\begin{helper-lem} \label{lem:p2-half-normal}
-  Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal
-  random variable with parameter $\sigma$ and
-
-  \begin{equation*}
-    f_{|X|}(x) =
-    \begin{dcases*}
-      0              & when $-\infty < x \leq 0$ \\
-      2 \cdot f_X(x) & when $0 < x < \infty$ 
-    \end{dcases*}
-    .
-  \end{equation*}
-\end{helper-lem}
-
-\begin{proof}
-  Let $X \sim N(0, \sigma^2)$, defined over $A = (-\infty, \infty)$. Define
-
-  \begin{equation*}
-    Y = |X| =
-    \begin{dcases*}
-      -x & if $x < 0$ \\
-      0 & if $x = 0$ \\
-      x & if $x > 0$ \\
-    \end{dcases*}
-    .
-  \end{equation*}
-
-  $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
-  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such
-  that $A = A_1 \cup A_2 \cup A_3$ and $Y$ is one-to-one over each $A_i$. We
-  can then transform each piece separately using Theorem 6.3.2 from
-  \citet{textbook}:
-
-  On $A_1$: $y = -x \Ra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1|
-  = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
-    &= f_X(-y) \cdot 1 \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma^2}} \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma^2}} \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_1: -\infty < x < 0 \Ra -\infty < -y < 0 \Ra 0 < y < \infty :B_1$.
-
-  Similarly, on $A_2$: $y = x \Ra x = y$ and $\J = \left| \frac{dx}{dy}
-  \right| = |1| = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
-    &= f_X(y) \cdot 1 \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_2: 0 < x < \infty \Ra 0 < y < \infty :B_2$.
-
-  On $A_3$, we have $x = 0 \Ra y = 0$ and $\J = \left| \frac{dx}{dy} \right| =
-  |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
-
-  Then, by Theorem 6.3.10 from \citet{textbook},
-
-  \begin{align*}
-    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \\
-    &= f_X(y) + f_X(y) \\
-    &= 2 \cdot f_X(y)
-  \end{align*}
-
-  over $B = B_1 \cup B_2 = (0, \infty)$, and 0 otherwise.
-\end{proof}
-
-With Lemma \ref{lem:p2-half-normal}, we can easily show our property:
-
-\begin{proof}[Proof of Property 3]
-  Let $Z \sim SN(0,1,\lambda)$. Recall that $f_Z(x) = 2 \cdot \phi(x) \cdot
-  \Phi(\lambda x)$.
-
-  Consider $\lim_{\lambda \to \infty} f_X(x)$. When $x$ is negative, $\lambda x
-  \to -\infty$ and thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however,
-  $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-positive-half-normal}
-    \lim_{\lambda \to \infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      0 & when $x \leq 0$ \\
-      2 \cdot \phi(x) & when $x > 0$
-    \end{dcases*}
-    \eq |N(0,1)|.
-  \end{equation}
-
-  In $\lim_{\lambda \to -\infty} f_X(x)$, the signs are reversed. When $x$ is
-  negative, $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. When $x$ is
-  positive, $\lambda x \to -\infty$ and $\Phi(\lambda x) \to 0$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-negative-half-normal}
-    \lim_{\lambda \to -\infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      2 \cdot \phi(x) & when $x < 0$ \\
-      0 & when $x \geq 0$
-    \end{dcases*}
-    \eq -|N(0,1)|.
-  \end{equation}
-\end{proof}
-
-\begin{property} \label{prop:4}
-  The MGF of $SN(0,1,\lambda)$ is
-
-  \begin{equation} \label{eq:p4-sn-mgf}
-    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2},
-  \end{equation}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
-\end{property}
-
-\begin{proof}
-  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma^2,
-  \lambda)$ is
-
-  \begin{equation*}
-    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t),
-  \end{equation*}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}} \in (-1, 1)$. It follows
-  that the MGF of the $SN(0, 1, \lambda)$ is
-
-  \begin{equation*}
-    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t).
-  \end{equation*}
-\end{proof}
-
 \section{Developing an Approximation}
@@
 
-\begin{alignat*}{3}
+\begin{alignat}{3}
   \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2}
-    &= \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. & \\
-  &= \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 & \\
-  &= \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) & \\
-  &= \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) &= g(v).
-\end{alignat*}
+    &= \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. & \nonumber \\
+  &= \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 & \nonumber \\
+  &= \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) & \nonumber \\
+  &= \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) &= g(v). \label{eq:lhs-solving-for-lambda}
+\end{alignat}
 
@@
 \end{figure}
-
-\section{Demonstrating Improved Accuracy}
-
-Now comes the time to justify our efforts by comparing the accuracy of our
-skew-normal approximation to that of the normal.
-
-\subsection{Visual Comparison}
-
-The first and most obvious way of judging accuracy is by visual inspection.
-Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
-\ref{fig:comparison-n100} compare the binomial, normal, and skew-normal at
-small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively. It is not
-hard to see that, especially at very small $n$ and $p$, our skew-normal curve
-follows the shape of the binomial much more closely.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n25.png}
-  \caption{Binomial, normal, and skew-normal, $n=25$}
-  \label{fig:comparison-n25}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n50.png}
-  \caption{Binomial, normal, and skew-normal, $n=50$}
-  \label{fig:comparison-n50}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n100.png}
-  \caption{Binomial, normal, and skew-normal, $n=100$}
-  \label{fig:comparison-n100}
-\end{figure}
-
-\subsection{Maximal Absolute Error}
-
-A quantitative method would be to compare the maximal absolute errors of our
-two approximations, defined by \citet{mabs} as
-
-\begin{equation}
-  \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
-\end{equation}
-
-where $F_{B(n,p)}$ is the cdf of the binomial and $F_{\textnormal{appr}(n,p)}$
-is the cdf of either the normal or skew-normal approximation; the 0.5 is a
-continuity correction.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
-  \caption{MABS as a function of p}
-  \label{fig:mabs-fixed-n}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-p.png}
-  \caption{MABS as a function of n}
-  \label{fig:mabs-fixed-p}
-\end{figure}
-
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
-skew-normal and normal approximations as a function of $p$ and $n$,
-respectively. Again, the skew-normal outperforms the normal considerably in the
-extreme ranges, with the two approximations converging as $n \rightarrow
-\infty$ or $p \rightarrow 0.5$.
-
-\clearpage
-
-\bibliography{/home/joycetipping/projects/capstone/pieces/bibliography/bibliography.bib}
-\bibliographystyle{plainnat}
-\end{document}

### 2010-12-25 project/paper/output.tex
Rearranged. Added skew normal approximation table.
Finished demonstration of calculating sn by hand

--- 2010-12-24 pieces/final-paper/output.tex
@@
   Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
-  \Phi(\lambda z)$ conforms to equation
+  \Phi(\lambda z)$ conforms to Equation
   \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
@@
 
+Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
+skew-normal and normal approximations as a function of $p$ and $n$,
+respectively. Again, the skew-normal outperforms the normal considerably in the
+extreme ranges, with the two approximations converging as $n \rightarrow
+\infty$ or $p \rightarrow 0.5$.
+
 \begin{figure}
@@
 
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
-skew-normal and normal approximations as a function of $p$ and $n$,
-respectively. Again, the skew-normal outperforms the normal considerably in the
-extreme ranges, with the two approximations converging as $n \rightarrow
-\infty$ or $p \rightarrow 0.5$.
+\clearpage
+
+\section{Practical Resources}
+\label{sec:practical-resources}
+
+We leave you with a few practical resources:
+
+Table \ref{tab:sn-approx-table} shows estimations of $SN(\mu, \sigma, \lambda)$
+for common binomial distributions.
+
+Appendix \ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
+parameters by hand, for those who need an unusual combination not in the table.
+
+Finally, for rapidly approximating many binomial distributions, the author's
+Python library, which was used to compute all the values in this paper, is
+freely available online:
+
+\url{http://github.com/joycetipping/skew-normal-capstone/}
+
+\begin{sidewaystable}
+  \caption{Estimations of $SN(\mu, \sigma, \lambda)$ for $Bin(n,p)$}
+  \centering
+  \renewcommand{\arraystretch}{1.3}
+  \begin{tabular}
+    { r r | r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l }
+    \hline \hline
+    & & \multicolumn{5}{c}{} & \multicolumn{5}{c}{} & \multicolumn{5}{c}{$n$} & \multicolumn{5}{c}{} & \multicolumn{5}{c}{}\\
+    \multirow{20}{*}{$p$} & & \multicolumn{5}{c}{25} & \multicolumn{5}{c}{50} & \multicolumn{5}{c}{100} & \multicolumn{5}{c}{250} & \multicolumn{5}{c}{500} \\
+    \hline
+    & 0.05 & ( & -0.11 & 1.74 & 4.56 & ) & ( & 0.79 & 2.30 & 2.54 & ) & ( & 2.85 & 3.06 & 1.86 & ) & ( & 9.58 & 4.52 & 1.38 & ) & ( & 21.32 & 6.11 & 1.15 & ) \\
+    & 0.10 & ( & 0.89 & 2.20 & 2.31 & ) & ( & 2.97 & 2.94 & 1.74 & ) & ( & 7.44 & 3.94 & 1.40 & ) & ( & 21.53 & 5.88 & 1.10 & ) & ( & 45.62 & 8.01 & 0.94 & ) \\
+    & 0.15 & ( & 2.02 & 2.49 & 1.79 & ) & ( & 5.32 & 3.34 & 1.43 & ) & ( & 12.25 & 4.51 & 1.19 & ) & ( & 33.77 & 6.77 & 0.96 & ) & ( & 70.30 & 9.27 & 0.82 & ) \\
+    & 0.20 & ( & 3.23 & 2.67 & 1.50 & ) & ( & 7.76 & 3.61 & 1.24 & ) & ( & 17.18 & 4.89 & 1.04 & ) & ( & 46.18 & 7.39 & 0.85 & ) & ( & 95.18 & 10.16 & 0.74 & ) \\
+    & 0.25 & ( & 4.49 & 2.79 & 1.29 & ) & ( & 10.28 & 3.78 & 1.09 & ) & ( & 22.20 & 5.15 & 0.93 & ) & ( & 58.71 & 7.83 & 0.76 & ) & ( & 120.22 & 10.80 & 0.67 & ) \\
+    & 0.30 & ( & 5.80 & 2.85 & 1.12 & ) & ( & 12.86 & 3.88 & 0.95 & ) & ( & 27.31 & 5.32 & 0.82 & ) & ( & 71.34 & 8.12 & 0.68 & ) & ( & 145.39 & 11.24 & 0.60 & ) \\
+    & 0.35 & ( & 7.17 & 2.86 & 0.96 & ) & ( & 15.50 & 3.92 & 0.83 & ) & ( & 32.49 & 5.39 & 0.72 & ) & ( & 84.09 & 8.28 & 0.60 & ) & ( & 170.70 & 11.50 & 0.53 & ) \\
+    & 0.40 & ( & 8.59 & 2.83 & 0.80 & ) & ( & 18.23 & 3.89 & 0.70 & ) & ( & 37.76 & 5.39 & 0.61 & ) & ( & 96.96 & 8.32 & 0.51 & ) & ( & 196.18 & 11.60 & 0.45 & ) \\
+    & 0.45 & ( & 10.12 & 2.73 & 0.61 & ) & ( & 21.08 & 3.79 & 0.53 & ) & ( & 43.21 & 5.29 & 0.47 & ) & ( & 110.07 & 8.23 & 0.40 & ) & ( & 221.93 & 11.54 & 0.35 & ) \\
+    & 0.50 & ( & 12.50 & 2.50 & 0.00 & ) & ( & 25.00 & 3.54 & 0.00 & ) & ( & 50.00 & 5.00 & 0.00 & ) & ( & 125.00 & 7.91 & 0.00 & ) & ( & 250.00 & 11.18 & 0.00 & ) \\
+    & 0.55 & ( & 14.88 & 2.73 & -0.61 & ) & ( & 28.92 & 3.79 & -0.53 & ) & ( & 56.79 & 5.29 & -0.47 & ) & ( & 139.93 & 8.23 & -0.40 & ) & ( & 278.07 & 11.54 & -0.35 & ) \\
+    & 0.60 & ( & 16.41 & 2.83 & -0.80 & ) & ( & 31.77 & 3.89 & -0.70 & ) & ( & 62.24 & 5.39 & -0.61 & ) & ( & 153.04 & 8.32 & -0.51 & ) & ( & 303.82 & 11.60 & -0.45 & ) \\
+    & 0.65 & ( & 17.83 & 2.86 & -0.96 & ) & ( & 34.50 & 3.92 & -0.83 & ) & ( & 67.51 & 5.39 & -0.72 & ) & ( & 165.91 & 8.28 & -0.60 & ) & ( & 329.30 & 11.50 & -0.53 & ) \\
+    & 0.70 & ( & 19.20 & 2.85 & -1.12 & ) & ( & 37.14 & 3.88 & -0.95 & ) & ( & 72.69 & 5.32 & -0.82 & ) & ( & 178.66 & 8.12 & -0.68 & ) & ( & 354.61 & 11.24 & -0.60 & ) \\
+    & 0.75 & ( & 20.51 & 2.79 & -1.29 & ) & ( & 39.72 & 3.78 & -1.09 & ) & ( & 77.80 & 5.15 & -0.93 & ) & ( & 191.29 & 7.83 & -0.76 & ) & ( & 379.78 & 10.80 & -0.67 & ) \\
+    & 0.80 & ( & 21.77 & 2.67 & -1.50 & ) & ( & 42.24 & 3.61 & -1.24 & ) & ( & 82.82 & 4.89 & -1.04 & ) & ( & 203.82 & 7.39 & -0.85 & ) & ( & 404.82 & 10.16 & -0.74 & ) \\
+    & 0.85 & ( & 22.98 & 2.49 & -1.79 & ) & ( & 44.68 & 3.34 & -1.43 & ) & ( & 87.75 & 4.51 & -1.19 & ) & ( & 216.23 & 6.77 & -0.96 & ) & ( & 429.70 & 9.27 & -0.82 & ) \\
+    & 0.90 & ( & 24.11 & 2.20 & -2.31 & ) & ( & 47.03 & 2.94 & -1.74 & ) & ( & 92.56 & 3.94 & -1.40 & ) & ( & 228.47 & 5.88 & -1.10 & ) & ( & 454.38 & 8.01 & -0.94 & ) \\
+    & 0.95 & ( & 25.11 & 1.74 & -4.56 & ) & ( & 49.21 & 2.30 & -2.54 & ) & ( & 97.15 & 3.06 & -1.86 & ) & ( & 240.42 & 4.52 & -1.38 & ) & ( & 478.68 & 6.11 & -1.15 & ) \\
+  \end{tabular}
+  \label{tab:sn-approx-table}
+\end{sidewaystable}
 
@@
 
-\begin{sidewaystable}
-  \centering
-  \begin{tabular}{ l l l l l l l l l }
-    (  0.89,    2.2,   2.31) & (  2.97,   2.94,   1.74) & (  7.44,   3.94,    1.4) & ( 16.77,   5.33,   1.16) \\
-    (  3.23,   2.67,    1.5) & (  7.76,   3.61,   1.24) & ( 17.18,   4.89,   1.04) & ( 36.45,   6.68,   0.89) \\
-    (   5.8,   2.85,   1.12) & ( 12.86,   3.88,   0.95) & ( 27.31,   5.32,   0.82) & (  56.6,   7.32,   0.72) \\
-    (  8.59,   2.83,    0.8) & ( 18.23,   3.89,    0.7) & ( 37.76,   5.39,   0.61) & ( 77.18,   7.48,   0.54) \\
-    (  12.5,    2.5,    0.0) & (  25.0,   3.54,    0.0) & (  50.0,    5.0,    0.0) & ( 100.0,   7.07,    0.0) \\
-    ( 16.41,   2.83,   -0.8) & ( 31.77,   3.89,   -0.7) & ( 62.24,   5.39,  -0.61) & (122.82,   7.48,  -0.54) \\
-    (  19.2,   2.85,  -1.12) & ( 37.14,   3.88,  -0.95) & ( 72.69,   5.32,  -0.82) & ( 143.4,   7.32,  -0.72) \\
-    ( 21.77,   2.67,   -1.5) & ( 42.24,   3.61,  -1.24) & ( 82.82,   4.89,  -1.04) & (163.55,   6.68,  -0.89) \\
-    ( 24.11,    2.2,  -2.31) & ( 47.03,   2.94,  -1.74) & ( 92.56,   3.94,   -1.4) & (183.23,   5.33,  -1.16) \\
+\appendix
+\section{Calculating a Skew-Normal Approximation}
+\label{app:calc-sn-approx}
+
+Although easier with a computer program, calculating estimates for $\mu$,
+$\sigma$, and $\lambda$ by hand is perfectly possible. Here, we will
+demonstrate using $n=25$, $p=0.1$.
+
+By far the largest battle is finding $\lambda$. We will use Equation
+\eqref{eq:solving-for-lambda} but with the simplified left hand side given by
+\eqref{eq:lhs-solving-for-lambda}:
+
+\begin{equation}
+  \label{eq:calculating-lambda}
+  \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = \frac{np(1-p)}{(1-2p)^2} \;.
+\end{equation}
+
+The closed-formed solution to this equation is long, hideous, and hard to work
+with, so for this demonstration, we will take a numerical approach.
+
+The left hand side of \eqref{eq:calculating-lambda} is a function of lambda;
+let us denote it $f(\lambda)$. The right hand side is a constant in $n$ and
+$p$; let us call it $k_{n,p}$. Our goal is to find a value of lambda that comes
+within a certain margin of error, $e$. Since we are computing by hand, we will
+take $e$ to be a modest 0.01.
+
+Recall that the sign of $\lambda$ is determined independently of the value. In
+fact, $f$ is never affected by the sign of $\lambda$, as all terms are squared.
+Thus, we can restrict our search for $\lambda$ to the interval $(0, \infty)$.
+
+Next, by taking $f$'s derivative, we can show that it is monotonically
+decreasing for positive $\lambda$:
+
+\begin{align*}
+  \frac{d}{d\lambda} \left[ \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \right] &= \left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot
+    3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2 \cdot \left( \frac{2\lambda}{\lambda^2} - \frac{2(1+\lambda^2)}{\lambda^3} \right) \\
+  &= \left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot 3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2 \cdot
+    \left( \cancel{\frac{2}{\lambda}} - \frac{2}{\lambda^3} - \cancel{\frac{2}{\lambda}} \right) \\
+  &= \underbrace{\left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot 3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2}_\textnormal{Always positive} \quad \cdot \quad
+     \underbrace{\left( -\frac{2}{\lambda^3} \right)}_{\mathclap{\textnormal{Negative when $\lambda > 0$}}}.
+\end{align*}
+
+This convenient fact allows us to find lower and upper bounds for $\lambda$ and
+repeatedly bisect our interval until we are within $e$ of $k_{n,p}$.
+
+(For the following calculations, it is helpful to keep in mind that because $f$
+is decreasing in $\lambda$, smaller values of $\lambda$ will produce larger
+values of $f$, and vice versa.)
+
+\begin{enumerate}
+  \item \textit{Find $k_{n,p}$.}
+
+    Our value: $\displaystyle k_{n,p} = \frac{25 \cdot 0.1 \cdot 0.9}{(1 - 2\cdot0.1)^2} = 3.5156$.
+
+  \item \textit{Find $a,b$ such that $f(a) > k_{n,p} > f(b)$.}
+
+    Our values: $a=1$, $b=3$.
+
+  \item \textit{Bisect $(a,b)$ until $f(c)$ is within $e$ of $k_{n,p}$.}
+
+    Calculate $c=\frac{a+b}{2}$.
+
+    \begin{itemize}
+      \item If $f(c) \leq k_{n,p} - 0.01$, we need a small value of $c$, so we
+      take our new interval to be $(a, c)$.
+
+      \item If $f(c) \geq k_{n,p} + 0.01$, we need a larger value of $c$, so we
+      take our new interval to be $(c, b)$.
+    \end{itemize}
+
+    Repeat this step until $f(c)$ is within $e$ of $k_{n,p}$, or more precisely
+    $k_{n,p} - 0.01 < f(c) < k_{n,p} + 0.01$.
+
+    The following table shows our iterations:
+
+    \renewcommand{\arraystretch}{1.3}
+    \begin{center}
+      \begin{tabular}{c c c c c c c}
+        Iteration & $a$  & $b$   & $c$    & $f(c)$ & $f(c) \leq k_{n,p} - 0.01$ & $f(c) \geq k_{n,p} + 0.01$ \\
+        \hline
+        1         & 2.00 & 3.000 & 2.5000 & 3.0164 & True                       & False \\
+        2         & 2.00 & 2.500 & 2.2500 & 3.7129 & False                      & True \\
+        3         & 2.25 & 2.500 & 2.3750 & 3.3252 & True                       & False \\
+        4         & 2.25 & 2.375 & 2.3125 & 3.5076 & False                      & False \\
       \end{tabular}
-  \caption{foobarbif}
-  \label{table:sn-approx-table}
-\end{sidewaystable}
+    \end{center}
 
-\bibliography{/home/joycetipping/projects/capstone/pieces/bibliography/bibliography.bib}
+    We take the last value of $c$: 2.3125.
+
+  \item \textit{Find the sign of $(1-2p)$.}
+
+    Our $p = 0.1 \Ra (1 - 2\cdot0.1) = 0.8 \Ra$ positive.
+
+  \item \textit{Final answer: \{sign of $(1-2p)$\}$\lambda$}
+
+    Our final answer: $\lambda = 2.3125$.
+\end{enumerate}
+
+Once we have $\lambda$, we can easily find $\sigma$:
+
+\begin{equation*}
+  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} = \sqrt{\frac{25 \cdot 0.1 \cdot 0.9}{1 - \frac{2}{\pi} \cdot \frac{2.3125^2}{1 + 2.3125^2}}} = 2.2029. \\
+\end{equation*}
+
+And with $\lambda$ and $\sigma$, we can also find $\mu$:
+
+\begin{equation*}
+  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} = 25 \cdot 0.1 - 2.2029 \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{2.3125}{\sqrt{1 + 2.3125^2}} = 0.8868.
+\end{equation*}
+
+\clearpage
+\bibliography{bibliography.bib}
 \bibliographystyle{plainnat}

### 2010-12-25 project/calc/demo_calc.py

@@ -1,0 +1,67 @@
+# Written by Joyce Tipping <joyce@joycetipping.com>
+# License: MIT <http://www.opensource.org/licenses/mit-license.php>
+#
+# This library provides helpful functions for approximating the binomial with the skew normal
+
+from __future__ import division
+from rpy import r
+import math
+r.library('sn')
+
+def sn_skew (n, p):
+  # Given n and p, finds the skew parameter, lambda
+
+  if (p == 0.5): return 0
+  else:
+    # The left-hand-side is a decreasing function of the skew parameter
+    def lhs (skew):
+      a = 2 / math.pi
+      b = skew**2 / (1 + skew**2)
+      return (1 - a*b)**3 / (a * b**3 * (2*a - 1)**2)
+
+    # The right-hand-side is a constant in n and p
+    rhs = n * p * (1 - p) / (1 - 2*p)**2
+
+    # Find upper and lower bounds
+    left_bound = right_bound = 1
+    while (lhs(left_bound)  < rhs): left_bound  /= 2
+    while (lhs(right_bound) > rhs): right_bound += 1
+
+    print "rhs", rhs
+
+    # Calculate the skew (to within 0.00001) by repeatedly bisecting our range
+    error = 0.01
+    skew = (right_bound + left_bound) / 2
+    too_big = lhs(skew) < rhs - error
+    too_small = lhs(skew) > rhs + error
+    while (too_big or too_small):
+      if (too_big):
+        right_bound = skew
+        skew = (right_bound + left_bound) / 2
+      elif (too_small):
+        left_bound = skew
+        skew = (right_bound + left_bound) / 2
+      too_big = lhs(skew) < rhs - error
+      too_small = lhs(skew) > rhs + error
+      print '{0:.2f} & {1:.3f} & {2:.4f} & {3:.4f} & {4} & {5}'.format(left_bound, right_bound, skew, lhs(skew), too_big, too_small)
+
+    # Determine the sign from (1 - 2p)
+    if (1 - 2*p < 0): skew *= -1
+    return skew
+
+sn_skew(25, 0.1)
+
+def sn_sigma (n, p):
+  # Given n and p, finds the scale parameter, sigma
+  skew = sn_skew(n, p)
+  a = 2 / math.pi
+  b = skew**2 / (1 + skew**2)
+  return math.sqrt( n*p*(1-p) / (1 - a*b) )
+
[…]

### 2010-12-25 project/paper/intro.tex
Proofread new appendix section.

--- 2010-12-24 pieces/final-paper/output.tex
@@
-\documentclass{article}
-\usepackage{jcapstone}
-\begin{document}
-
 \title{The Skew-Normal Approximation of the Binomial Distribution}
@@
 One of the most basic distributions in statistics is the binomial, $X \sim
-Bin(n,p)$, with pdf
+Bin(n,p)$, $n \in \N$, $p \in (0, 1)$ with pdf
 
 \begin{equation*}
-  f_X(x) = \binom{n}{x} p^x q^{n-x}, \quad x = 0, 1, \ldots, n.
+  f_X(x) = \binom{n}{x} p^x q^{n-x}, \quad x = 0, 1, \ldots, n,
 \end{equation*}
 
-Calculating the binomial cdf, $F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by
-hand is manageable for small $n$ but quickly becomes cumbersome as $n$ grows
-even moderately large. A common strategy is to use the normal distribution as
-an approximation:
+where $q=1-p$. Calculating the binomial cdf, $F_X(x) = P(X \leq x) =
+\sum_{k=1}^x f_X(k)$, by hand is manageable for small $n$ but quickly becomes
+cumbersome as $n$ grows even moderately large. A common strategy is to use the
+normal distribution as an approximation:
 
@@
 $p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
-becomes increasingly skewed, and one must either compensate by providing ever
-larger values of $n$ or face growing inaccuracy. In these cases, the
-skew-normal approximation can provide a better alternative.
-
-\section{The Skew-Normal}
-
-The skew-normal distribution is similar to the normal but with an added
-parameter for skew, allowing it to lean asymmetrically to the left or right. In
-this section, we'll acquaint ourselves with some of its basic properties.
-
-\subsection{Basics}
-
-Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
-scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$; we will
-denote it $SN(\mu, \sigma, \lambda)$. Then $Y$ has pdf
-
-\begin{equation} \label{eq:sn-pdf}
-  f_Y(x) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
-\end{equation}
-
-where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal cdf.
-Some other basic properties of $Y$, given by \citet{pewsey}, are
-
-\begin{align}
-  E(Y) &= \mu + b \delta \sigma, \nonumber \\
-  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-basic-properties} \\
-  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber \\
-  Var(Y) &= \sigma^2 (1 - b^2 \delta^2), \nonumber
-\end{align}
-
-where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}}$.
-
-The $SN(0,1,\lambda)$ distribution is called the standard skew-normal; its pdf
-is
-
-\begin{equation} \label{eq:standard-sn-pdf}
-  f_Z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
-\end{equation}
-
-Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
-= \sigma Z + \mu$.
-
-A natural question to ask is how the skew-normal relates to the normal.
-Fortunately, the connection is very intuitive: When $\lambda = 0$, Equation
-\eqref{eq:sn-pdf} becomes
-
-\begin{align*}
-  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
-  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
-  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
-  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
-  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
-\end{align*}
-
-which is the pdf of the normal distribution.
-
-\subsection{Four Properties}
-\label{subsec:four-properties}
-
-The following four properties of the skew-normal, given by \citet{main}, help
-shed light on our enigmatic new distribution:
-
-\begin{property} \label{prop:1}
-  If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
-\end{property}
-
-\begin{proof}
-  The standard normal pdf is an even function: $\phi(-x) =
-  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
-  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) =
-  \int_{-\infty}^\infty \phi(x)$, \thinspace is not even, being 0 near
-  $-\infty$ and 1 near $\infty$. Thus,
-
-  \begin{align*}
-    f_{(-Z)}(x) &= f_Z(-x) \\
-    & = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\
-    & = 2 \cdot \phi(x) \cdot \Phi (-\lambda x),
-  \end{align*}
-
-  which is the pdf of $SN(0, 1, -\lambda)$.
-\end{proof}
-
-\begin{property} \label{prop:2}
-  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
-\end{property}
-
-\begin{proof}
-  To prove our result, we make use of Lemma 1 in \citet{azzalini}, which we
-  restate here:
-
-  \begin{helper-lem}
-    If $f_0$ is a one-dimensional probability density function symmetric about
-    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
-    and is a density symmetric about 0, then
-
-    \begin{equation}
-      \label{eq:azzalini-perturbation-invariance}
-      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
-    \end{equation}
-
-    is a density function for any odd function $w(\cdot)$.
-  \end{helper-lem}
-
-  This lemma provides a very useful corollary:
-
-  \begin{helper-cor}[Perturbation Invariance]
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
-    notation $\overset{d}{=}$ denotes equality in distribution.    
-  \end{helper-cor}
-
-  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
-  \Phi(\lambda z)$ conforms to equation
-  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
-  and $Z$ are equal in distribution.
-
-  We will now show that $\phi^2 \sim \chi^2_1$:
-
-  \begin{align*}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \\
-    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \;; \\
-    \intertext{let $u = (\sqrt{1-2t}) \, x$; then $du = (\sqrt{1-2t}) \, dx$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty, x \to \infty \Ra
-      u \to -\infty, u \to \infty$:}
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} du \right) \\
-    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
-      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
-    &= \frac{1}{\sqrt{1-2t}} \;,
-  \end{align*}
-
-  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
-  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
-
-\begin{property} \label{prop:3}
-  As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
-\end{property}
-
-To prove our theorem, it is helpful to formally define the half normal distribution:
-
-\begin{helper-lem} \label{lem:p2-half-normal}
-  Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal
-  random variable with parameter $\sigma$ and
-
-  \begin{equation*}
-    f_{|X|}(x) =
-    \begin{dcases*}
-      0              & when $-\infty < x \leq 0$ \\
-      2 \cdot f_X(x) & when $0 < x < \infty$ 
-    \end{dcases*}
-    .
-  \end{equation*}
-\end{helper-lem}
-
-\begin{proof}
-  Let $X \sim N(0, \sigma^2)$, defined over $A = (-\infty, \infty)$. Define
-
-  \begin{equation*}
-    Y = |X| =
-    \begin{dcases*}
-      -x & if $x < 0$ \\
-      0 & if $x = 0$ \\
-      x & if $x > 0$ \\
-    \end{dcases*}
-    .
-  \end{equation*}
-
-  $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
-  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such
-  that $A = A_1 \cup A_2 \cup A_3$ and $Y$ is one-to-one over each $A_i$. We
-  can then transform each piece separately using Theorem 6.3.2 from
-  \citet{textbook}:
-
-  On $A_1$: $y = -x \Ra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1|
-  = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
-    &= f_X(-y) \cdot 1 \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma^2}} \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma^2}} \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_1: -\infty < x < 0 \Ra -\infty < -y < 0 \Ra 0 < y < \infty :B_1$.
-
-  Similarly, on $A_2$: $y = x \Ra x = y$ and $\J = \left| \frac{dx}{dy}
-  \right| = |1| = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
-    &= f_X(y) \cdot 1 \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_2: 0 < x < \infty \Ra 0 < y < \infty :B_2$.
-
-  On $A_3$, we have $x = 0 \Ra y = 0$ and $\J = \left| \frac{dx}{dy} \right| =
-  |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
-
-  Then, by Theorem 6.3.10 from \citet{textbook},
-
-  \begin{align*}
-    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \\
-    &= f_X(y) + f_X(y) \\
-    &= 2 \cdot f_X(y)
-  \end{align*}
-
-  over $B = B_1 \cup B_2 = (0, \infty)$, and 0 otherwise.
-\end{proof}
-
-With Lemma \ref{lem:p2-half-normal}, we can easily show our property:
-
-\begin{proof}[Proof of Property 3]
-  Let $Z \sim SN(0,1,\lambda)$. Recall that $f_Z(x) = 2 \cdot \phi(x) \cdot
-  \Phi(\lambda x)$.
-
-  Consider $\lim_{\lambda \to \infty} f_X(x)$. When $x$ is negative, $\lambda x
-  \to -\infty$ and thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however,
-  $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-positive-half-normal}
-    \lim_{\lambda \to \infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      0 & when $x \leq 0$ \\
-      2 \cdot \phi(x) & when $x > 0$
-    \end{dcases*}
-    \eq |N(0,1)|.
-  \end{equation}
-
-  In $\lim_{\lambda \to -\infty} f_X(x)$, the signs are reversed. When $x$ is
-  negative, $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. When $x$ is
-  positive, $\lambda x \to -\infty$ and $\Phi(\lambda x) \to 0$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-negative-half-normal}
-    \lim_{\lambda \to -\infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      2 \cdot \phi(x) & when $x < 0$ \\
-      0 & when $x \geq 0$
-    \end{dcases*}
-    \eq -|N(0,1)|.
-  \end{equation}
-\end{proof}
-
-\begin{property} \label{prop:4}
-  The MGF of $SN(0,1,\lambda)$ is
-
-  \begin{equation} \label{eq:p4-sn-mgf}
-    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2},
-  \end{equation}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
-\end{property}
-
-\begin{proof}
-  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma^2,
-  \lambda)$ is
-
-  \begin{equation*}
-    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t),
-  \end{equation*}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}} \in (-1, 1)$. It follows
-  that the MGF of the $SN(0, 1, \lambda)$ is
-
-  \begin{equation*}
-    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t).
-  \end{equation*}
-\end{proof}
-
-\section{Developing an Approximation}
-
-Now that we have gotten to know our new distribution a little better, we can
-use it to develop an approximation for the binomial.
-
-Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma^2, \lambda)$. We will find
-estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
-and third moments about the mean of $B$ and $Y$.
-
-\subsection{The Moments of the Binomial}
-
-Let's start with the binomial. The first two moments are simply the mean and
-variance, which we can state from memory:
-
-\begin{equation*}
-  E(B) = np, \quad Var(B) = np(1-p).
-\end{equation*}
-
-Having these, we can easily find
-
-\begin{equation*}
-  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2,
-\end{equation*}
-
-which we will need for the third moment. We will also need $E(B^3)$, which we
-will get via the third factorial moment:
-
-\begin{align*}
-  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \;; \\
-  \intertext{notice that the first three terms of this sum are zero, so we can rewrite our sum beginning at $x = 3$:}
-  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \\
-  \intertext{let $y=x-3$; then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$:}
-  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
-  &= n(n-1)(n-2)p^3 \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 \;; \\
-  \intertext{further expanding the left side and solving for $E(B^3)$:}
-  E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\
-  E(B^3) - 3E(B^2) + 2E(B) &= \\
-  E(B^3) - 3(np - np^2 + n^2p^2) + 2np &= \\
-  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 + 3np - 3np^2 + 3n^2p^2 - 2np \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np.
-\end{align*}
-
-Now, finally, we have all the building blocks necessary to obtain the third
-moment:
-
-\begin{align*}
-  E \left( [B - E(B)]^3 \right) &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
-  &= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\
-  &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
-  &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\
-  &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
-  &= 2np^3 - 3np^2 + np \\
-  &= np(p-1)(2p-1).
-\end{align*}
-
-Our hard-earned results, restated for convenience:
-
-\begin{align}
-  E(B) &= np, \nonumber \\
-  E([B - E(B)]^2) &= np(1-p), \\
-  E([B - E(B)]^3) &= np(p-1)(2p-1). \nonumber
-\end{align}
-
-\subsection{The Moments of the Skew Normal}
-
-Now we'll take a look at the moments of the skew normal. Equation
-\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
-third moment is a little more complicated:
-
-\begin{align*}
-  E([Y - E(Y)]^3) &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
-  &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) \\
-  & \quad + 2\;(\mu + b \delta \sigma)^3 \\
-  &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} -
-    \cancel{6 b \delta \mu^2 \sigma} - \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} \\
-  & \quad - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
-  &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
-  &= b \delta^3 \sigma^3 (2b^2 - 1).
-\end{align*}
-
-We restate our results:
-
-\begin{alignat}{4}
-  E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;, \nonumber \\
-  E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right), \\
-  E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right). \nonumber
-\end{alignat}
-
-\subsection{Solving for $\mu$, $\sigma$, $\lambda$}
-
-Now we can set the moments of our two distributions equal to each other and,
-taking $n$ and $p$ as constants, solve for $\mu$, $\sigma$ and $\lambda$:
-
-\begin{subequations}
-\begin{align}
-  np &= \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \label{eq:first-moment-set} \\
-  np(1-p) &= \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:second-moment-set} \\
-  np(p-1)(2p-1) &= \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \label{eq:third-moment-set}
-\end{align}
-\end{subequations}
-
-To get $\lambda$, we divide the cube of \eqref{eq:second-moment-set} by the
-square of \eqref{eq:third-moment-set}:
-
-\begin{align}
-  \frac{\sigma^6 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right)^3}{\sigma^6 \cdot \frac{2}{\pi} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^6 \left(
-    \frac{4}{\pi} - 1 \right)^2} &= \frac{n^3p^3(1-p)^3}{n^2p^2(p-1)^2(2p-1)^2} \nonumber \\
-  \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-    \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \;. \label{eq:solving-for-lambda}
-\end{align}
-
-The above equation \eqref{eq:solving-for-lambda} is a rational expression in
-$\lambda^2$ that can be solved with either a considerable amount of manual
-labor or, more efficiently, with a computer algebra system. Once we have
-$\lambda^2$, then $\lambda$ is simply either the positive or negative square
-root, as determined by the sign of $(1-2p)$. The sign can be explained with a
-little assistance from Property \ref{prop:3}: When $p \to 0$, the binomial
-skews left and converges toward the positive half normal, which by
-\eqref{eq:p2-positive-half-normal} corresponds to a positive $\lambda$. When $p
-\to 1$, the binomial skews right and converges toward the negative half normal,
-which by \eqref{eq:p2-negative-half-normal} corresponds to a negative
-$\lambda$. When $p = 0.5$, the binomial is symmetric and $\lambda$ is 0,
-eliminating the need for a sign. Thus:
-
-\begin{equation}
-  \label{eq:lambda-solved}
-  \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}.
-\end{equation}
-
-Having secured $\lambda$, we can find $\sigma$ using
-\eqref{eq:second-moment-set}:
-
-\begin{equation}
-  \label{eq:sigma-solved}
-  np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
-  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} \;.
-\end{equation}
-
-And with both $\lambda$ and $\sigma$, a simple rearrangement of
-\eqref{eq:first-moment-set} yields $\mu$:
-
-\begin{equation}
-  \label{eq:mu-solved}
-  np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
-  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;.
-\end{equation}
-
-When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
-therefore $\mu = np = n/2$. This equation, together with \eqref{eq:mu-solved},
-implies that $\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 +
-\lambda^2}} = 0 \Ra$ either $\sigma = 0$ or $\lambda = 0$. Since the former is
-impossible, we must conclude the latter, which brings us back to the normal
-distribution.
-
-\subsection{Restrictions}
-
-To obtain an estimate for $\lambda$, we must put a few restrictions on $n$ and
-$p$.
-
-If we let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u$, we can rewrite the
-left hand side of \eqref{eq:solving-for-lambda} as
-
-\begin{alignat*}{3}
-  \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2}
-    &= \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. & \\
-  &= \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 & \\
-  &= \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) & \\
-  &= \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) &= g(v).
-\end{alignat*}
-
-We can see that $g(v)$ is increasing in $v$, which is always $\geq 1$.
-Therefore:
-
-\begin{equation}
-  \min_{v} g(v) = g(v)|_{v=1} = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1,
-\end{equation}
-
-which means that the right hand side of \eqref{eq:solving-for-lambda}, which is
-supposed to be equal to the left hand side of \eqref{eq:solving-for-lambda},
-can't ever be less than 1. Unfortunately, it sometimes is; in particular,
-$\frac{np(1-p)}{(1-2p)^2} \to 0$ when $p \to 0$ or $p \to 1$. So if we want a
-solution, we must restrict $n$ and $p$ such that
-
-\begin{align}
-  \textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\
-  \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
-  np(1-p) &\geq (1-2p)^2. \label{eq:solving-the-restriction}
-\end{align}
-
-Here, two scenarios arise. The first is when we have a fixed $p$ and wish to
-find the minimum $n$ necessary to derive a skew-normal approximation. From
-\eqref{eq:solving-the-restriction}, solving for $n$ is very simple:
-
-\begin{equation}
-  n \geq \frac{(1-2p)^2}{p(1-p)} \;. \label{eq: n for a given p}
-\end{equation}
-
-Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
-estimate $\lambda$ as a function of $p$. As expected, it is quite large when
-$p$ is small and rapidly goes to 0 as $p$ increases; for example, when $p =
-0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a
-trivial requirement to meet.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-least-n.png}
-  \caption{Least possible $n$, given a fixed $p$}
-  \label{fig:sn-restriction-least-n}
-\end{figure}
-
-The second scenario is when $n$ is fixed and we wish to solve for $p$. In this
-case, we return to \eqref{eq:solving-the-restriction} for further factoring:
-
-\begin{align}
-  np(1-p) &\geq (1-2p)^2 \nonumber \\
-  np - np^2 &\geq 1 - 4p + 4p^2 \nonumber \\
-  1 - 4p + 4p^2 - np + np^2 &\leq 0 \nonumber \\
-  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq: solving for p}.
-\end{align}
-
-We then apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
-
-\begin{align*}
-  p &= \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
-  &= \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
-  &= \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n+4)} \\
-  &= \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
-  &= \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}} \;.
-\end{align*}
-
-Let $r_1 = \frac12 - \frac12 \sqrt{\frac{n}{n+4}}$ and $r_2 = \frac12 + \frac12
-\sqrt{\frac{n}{n+4}}$. (Note that $r_1 < r_2$.) Now we can rewrite \eqref{eq:
-solving for p} as
-
-\begin{equation*}
-  (p - r_1)(p - r_2) \leq 0.
-\end{equation*}
-
-Examining the left hand side, when $p < r_1$, both terms are negative and so
-their product is positive; when $p > r_2$, both terms are positive, again
-leading the product to be positive. Therefore, our solution lies where $r_1
-\leq p \leq r_2$, or more explicitly,
-
-\begin{equation}
- \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}} \;.
-\end{equation}
-
-Shown in figure \ref{fig:sn-restriction-p-range} as a function of $n$, this
-interval grows quickly as $n$ increases, and for sufficiently large $n$, it
-becomes almost $(0, 1)$. For example, when $n=100$, our interval is $(0.00971,
-0.99029)$; when $n=500$, it is (0.00199, 0.99801).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{../graphs/images/restriction-p-range.png}
-  \caption{Range of possible $p$, given a fixed $n$}
-  \label{fig:sn-restriction-p-range}
-\end{figure}
-
-\section{Demonstrating Improved Accuracy}
-
-Now comes the time to justify our efforts by comparing the accuracy of our
-skew-normal approximation to that of the normal.
-
-\subsection{Visual Comparison}
-
-The first and most obvious way of judging accuracy is by visual inspection.
-Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
-\ref{fig:comparison-n100} compare the binomial, normal, and skew-normal at
-small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively. It is not
-hard to see that, especially at very small $n$ and $p$, our skew-normal curve
-follows the shape of the binomial much more closely.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n25.png}
-  \caption{Binomial, normal, and skew-normal, $n=25$}
-  \label{fig:comparison-n25}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n50.png}
-  \caption{Binomial, normal, and skew-normal, $n=50$}
-  \label{fig:comparison-n50}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/comparison-n100.png}
-  \caption{Binomial, normal, and skew-normal, $n=100$}
-  \label{fig:comparison-n100}
-\end{figure}
-
-\subsection{Maximal Absolute Error}
-
-A quantitative method would be to compare the maximal absolute errors of our
-two approximations, defined by \citet{mabs} as
-
-\begin{equation}
-  \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
-\end{equation}
-
-where $F_{B(n,p)}$ is the cdf of the binomial and $F_{\textnormal{appr}(n,p)}$
-is the cdf of either the normal or skew-normal approximation; the 0.5 is a
-continuity correction.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-n.png}
-  \caption{MABS as a function of p}
-  \label{fig:mabs-fixed-n}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../graphs/images/mabs-fixed-p.png}
-  \caption{MABS as a function of n}
-  \label{fig:mabs-fixed-p}
-\end{figure}
-
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
-skew-normal and normal approximations as a function of $p$ and $n$,
-respectively. Again, the skew-normal outperforms the normal considerably in the
-extreme ranges, with the two approximations converging as $n \rightarrow
-\infty$ or $p \rightarrow 0.5$.
-
-\clearpage
-
-\bibliography{/home/joycetipping/projects/capstone/pieces/bibliography/bibliography.bib}
-\bibliographystyle{plainnat}
-\end{document}
+becomes increasingly skewed, and one must either provide larger values of $n$
+to compensate or face growing inaccuracy. In these cases, the skew-normal
+approximation can provide a better alternative.

### 2010-12-25 project/paper/output.tex
Proofread new appendix section.

@@
 $p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
-becomes increasingly skewed, and one must either compensate by providing ever
-larger values of $n$ or face growing inaccuracy. In these cases, the
-skew-normal approximation can provide a better alternative.
+becomes increasingly skewed, and one must either provide larger values of $n$
+to compensate or face growing inaccuracy. In these cases, the skew-normal
+approximation can provide a better alternative.
 
@@
 
-A quantitative method would be to compare the maximal absolute errors of our
-two approximations, defined by \citet{mabs} as
+A quantitative method of judging accuracy is comparing the maximal absolute
+errors of our two approximations, defined by \citet{mabs} as
 
@@
 
-We leave you with a few practical resources:
+We conclude our dicussion by offering the reader a few practical resources:
 
@@
 
-Appendix \ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
-parameters by hand, for those who need an unusual combination not in the table.
+For those with an unusual combination of $n$ and $p$ not in the table, Appendix
+\ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
+parameters by hand.
 
 Finally, for rapidly approximating many binomial distributions, the author's
-Python library, which was used to compute all the values in this paper, is
-freely available online:
+Python library, which was used to compute all values presented in this paper,
+is freely available online:
 
@@
 let us denote it $f(\lambda)$. The right hand side is a constant in $n$ and
-$p$; let us call it $k_{n,p}$. Our goal is to find a value of lambda that comes
-within a certain margin of error, $e$. Since we are computing by hand, we will
-take $e$ to be a modest 0.01.
+$p$; let us call it $k_{n,p}$. Our goal is to find a value of $\lambda$ such
+that $f(\lambda)$ is within a certain margin of error, $e$, of $k_{n,p}$. Since
+we are computing by hand, we will take $e$ to be a modest 0.01.
 
@@
 
-  \item \textit{Find $a,b$ such that $f(a) > k_{n,p} > f(b)$.}
+  \item \textit{Find $a$ and $b$ such that $f(a) > k_{n,p} > f(b)$.}
 
@@
 
-  \item \textit{Bisect $(a,b)$ until $f(c)$ is within $e$ of $k_{n,p}$.}
+  \item \textit{Repeatedly bisect $(a,b)$ until $f(c)$ is within $e$ of $k_{n,p}$.}
 
@@
 \begin{equation*}
-  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} = 25 \cdot 0.1 - 2.2029 \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{2.3125}{\sqrt{1 + 2.3125^2}} = 0.8868.
+  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} = 25 \cdot 0.1 - 2.2029 \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{2.3125}{\sqrt{1 + 2.3125^2}} = 0.8867.
 \end{equation*}

### 2010-12-25 project/calc/approx_table.py

@@ -1,3 +1,6 @@
+# Written by Joyce Tipping <joyce@joycetipping.com>
+# License: MIT <http://www.opensource.org/licenses/mit-license.php>
+
 from stats import *
 
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#

### 2010-12-25 project/calc/demo_calc.py

@@ -1,49 +1,44 @@
 # Written by Joyce Tipping <joyce@joycetipping.com>
 # License: MIT <http://www.opensource.org/licenses/mit-license.php>
-#
-# This library provides helpful functions for approximating the binomial with the skew normal
 
 from __future__ import division
-from rpy import r
 import math
-r.library('sn')
+
+def lhs (skew):
+  # The left-hand-side is a decreasing function of the skew parameter
+  a = 2 / math.pi
+  b = skew**2 / (1 + skew**2)
+  return (1 - a*b)**3 / (a * b**3 * (2*a - 1)**2)
+
+def rhs (n, p):
+  # The right-hand-side is a constant in n and p
+  return n * p * (1 - p) / (1 - 2*p)**2
 
 def sn_skew (n, p):
-  # Given n and p, finds the skew parameter, lambda
-
   if (p == 0.5): return 0
   else:
-    # The left-hand-side is a decreasing function of the skew parameter
-    def lhs (skew):
-      a = 2 / math.pi
-      b = skew**2 / (1 + skew**2)
-      return (1 - a*b)**3 / (a * b**3 * (2*a - 1)**2)
-
-    # The right-hand-side is a constant in n and p
     rhs = n * p * (1 - p) / (1 - 2*p)**2
 
-    # Find upper and lower bounds
-    left_bound = right_bound = 1
-    while (lhs(left_bound)  < rhs): left_bound  /= 2
-    while (lhs(right_bound) > rhs): right_bound += 1
-
-    print "rhs", rhs
+    # Find upper and lower bounds (a, b)
+    a = b = 1
+    while (lhs(a) < rhs): a /= 2
+    while (lhs(b) > rhs): b += 1
 
     # Calculate the skew (to within 0.00001) by repeatedly bisecting our range
     error = 0.01
-    skew = (right_bound + left_bound) / 2
-    too_big = lhs(skew) < rhs - error
-    too_small = lhs(skew) > rhs + error
-    while (too_big or too_small):
-      if (too_big):
-        right_bound = skew
-        skew = (right_bound + left_bound) / 2
-      elif (too_small):
-        left_bound = skew
-        skew = (right_bound + left_bound) / 2
-      too_big = lhs(skew) < rhs - error
-      too_small = lhs(skew) > rhs + error
[…]

### 2010-12-25 project/calc/flot_data.py

@@ -1,3 +1,6 @@
+# Written by Joyce Tipping <joyce@joycetipping.com>
+# License: MIT <http://www.opensource.org/licenses/mit-license.php>
+
 # Python modules
 import json
 # My modules

### 2011-01-20 project/paper/method-of-moments.tex
Added an alt section heading without math mode.
Addressed required revisions by adding 2 paragraphs to Restrictions section.

@@
 
-\subsection{Solving for $\mu$, $\sigma$, $\lambda$}
+\subsection[Solving for mu, sigma, lambda]{Solving for $\mu$, $\sigma$, $\lambda$}
 
@@
 
-To obtain an estimate for $\lambda$, we must put a few restrictions on $n$ and
-$p$.
+Unfortunately, although better than the normal approximation, the skew-normal
+is also not universally applicable. To obtain an estimate for $\lambda$, we
+must put a few restrictions on $n$ and $p$.
 
@@
 Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
-estimate $\lambda$ as a function of $p$. As expected, it is quite large when
+estimate $\lambda$ as a function of $p$. As we would expect, it is larger when
 $p$ is small and rapidly goes to 0 as $p$ increases; for example, when $p =
@@
 
-The second scenario is when $n$ is fixed and we wish to solve for $p$. In this
-case, we return to \eqref{eq:solving-the-restriction} for further factoring:
+The second scenario, primarily of academic interest, is when $n$ is fixed and
+we wish to solve for $p$. In this case, we return to
+\eqref{eq:solving-the-restriction} for further factoring:
 
@@
 \end{figure}
+
+Although the presence of these restrictions are somewhat disappointing, we can
+console ourselves with the observation that at the same $n$ and $p$, the
+skew-normal yields substantially more accurate approximations than the normal
+(see section \ref{subsec:mabs}). Thus while imperfect, it is nevertheless an
+improvement.
+
+Finally, one last consideration that bears mentioning is that the skew-normal
+approximation will sometimes provide us with parameters that violate our
+intuition. In particular, for small $p$ and $n$, equation \eqref{eq:mu-solved}
+can yield negative values of $\mu$, which is impossible for the binomial. This
+can be explained by the fact that as $n$ and $p$ grow more extreme, so does the
+inaccuracy of our approximation. Rather than impose a hard restriction on these
+cases, we would simply advise that the reader be aware of the limits of the
+skew-normal and, if more accuracy is necessary, seek another method of
+approximation.

### 2011-01-20 project/paper/output.tex
Added an alt section heading without math mode.
Addressed required revisions by adding 2 paragraphs to Restrictions section.

@@
 
+Although the presence of these restrictions are somewhat disappointing, we can
+console ourselves with the observation that at the same $n$ and $p$, the
+skew-normal yields substantially more accurate approximations than the normal
+(see section \ref{subsec:mabs}). Thus while imperfect, it is nevertheless an
+improvement.
+
+Finally, one last consideration that bears mentioning is that the skew-normal
+approximation will sometimes provide us with parameters that violate our
+intuition. In particular, for small $p$ and $n$, equation \eqref{eq:mu-solved}
+can yield negative values of $\mu$, which is impossible for the binomial. This
+can be explained by the fact that as $n$ and $p$ grow more extreme, so does the
+inaccuracy of our approximation. Rather than impose a hard restriction on these
+cases, we would simply advise that the reader be aware of the limits of the
+skew-normal and, if more accuracy is necessary, seek another method of
+approximation.
+
 \section{Demonstrating Improved Accuracy}
+\label{sec:demonstrating-improved-accuracy}
 
@@
 \subsection{Maximal Absolute Error}
+\label{subsec:mabs}
 

### 2011-01-20 project/paper/intro.tex
Added footnotes (defn's, thm statements)

@@
 One of the most basic distributions in statistics is the binomial, $X \sim
-Bin(n,p)$, $n \in \N$, $p \in (0, 1)$ with pdf
+Bin(n,p)$, $n \in \N$, $p \in (0, 1)$ with probability density function (pdf)
 
@@
 
-where $q=1-p$. Calculating the binomial cdf, $F_X(x) = P(X \leq x) =
-\sum_{k=1}^x f_X(k)$, by hand is manageable for small $n$ but quickly becomes
-cumbersome as $n$ grows even moderately large. A common strategy is to use the
-normal distribution as an approximation:
+where $q=1-p$. Calculating the binomial cumulative distribution function (cdf),
+$F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by hand is manageable for small
+$n$ but quickly becomes cumbersome as $n$ grows even moderately large. A common
+strategy is to use the normal distribution as an approximation:
 
@@
 
-where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
+where $\Phi$ is the standard normal\footnote{Let $X \sim Z = N(0, 1)$. Then $X$
+is said to be a standard normal distribution with pdf
+
+\begin{equation*}
+  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
+\end{equation*}
+
+and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t) \; dt$. Equations 3.3.29
+and 3.3.30, \citet{textbook}.} cdf and $\mu = np$ and $\sigma =
 \sqrt{np(1-p)}$.

### 2011-01-20 project/paper/output.tex
Added footnotes (defn's, thm statements)

@@
 
-  We will now show that $\phi^2 \sim \chi^2_1$:
+  We will now show that $\phi^2 \sim \chi^2_1$ by deriving its moment
+  generating function (mgf):\footnote{If $X$ is a random variable, then the
+  expected value $M_X(t) = E(e^{tX})$ is called the moment generating function
+  (mgf) of X if this expected value exists for all values of $t$ in some
+  interval of the form $-h < t < h$ for some $h > 0$. Definition 2.5.1,
+  \citet{textbook}.}
 
@@
   can then transform each piece separately using Theorem 6.3.2 from
-  \citet{textbook}:
+  \citet{textbook}:\footnote{\textbf{Continuous transformations that are
+  one-to-one} (Theorem 6.3.2, \citealp{textbook}): Suppose that $X$ is a
+  continuous random variable with pdf $f_X(x)$, and assume that $Y = u(X)$
+  defines a one-to-one transformation from $A = \{x|f_X(x) > 0\}$ on to $B =
+  \{y|f_Y(y) > 0\}$ with inverse transformation $x = w(y)$. If the derivative
+  $(d/dy)w(y)$ is continuous and nonzero on $B$, then the pdf of $Y$ is
+
+  \begin{equation}
+    \label{eq:transformations-1-to-1}
+    f_Y(y) = f_X(w(y)) \left| \frac{d}{dy} w(y) \right| \qquad y \in B.
+  \end{equation}
+
+  \label{fnote:transformations-1-to-1}
+  }
 
@@
 
-  Then, by Theorem 6.3.10 from \citet{textbook},
+  Then, by Equation 6.3.10 from \citet{textbook},\footnote{\textbf{Continuous
+  transformations that are not one-to-one} (Equation 6.3.10,
+  \citealp{textbook}): When $u(x)$ is not one-to-one over $A$, we can replace
+  equation \eqref{eq:transformations-1-to-1} in footnote
+  \ref{fnote:transformations-1-to-1} with
+
+  \begin{equation*}
+    f_Y(y) = \sum_j f_X(w_j(y)) \left| \frac{d}{dy} w_j(y) \right|.
+  \end{equation*}
+  }
 

### 2011-01-20 project/paper/method-of-moments.tex
Addressed other suggested revisions.

@@
 estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
-and third moments about the mean of $B$ and $Y$.
+and third central moments of $B$ and $Y$.
 
-\subsection{The Moments of the Binomial}
+\subsection{The Central Moments of the Binomial}
 
-Let's start with the binomial. The first two moments are simply the mean and
-variance, which we can state from memory:
+Let's start with the binomial. The first two central moments are simply the
+mean and variance, which we can state from memory:
 
@@
 
-Having these, we can easily find
+Having these, we can easily find $E(B^2)$: Recall that $Var(B) = E(B^2) -
+[E(B)]^2$ and thus
 
@@
 
-which we will need for the third moment. We will also need $E(B^3)$, which we
-will get via the third factorial moment:
+a fact we will need for the third central moment. We will also need $E(B^3)$,
+which we will get via the third factorial moment:
 
@@
 Now, finally, we have all the building blocks necessary to obtain the third
-moment:
+central moment:
 
@@
 
-\subsection{The Moments of the Skew Normal}
+\subsection{The Central Moments of the Skew Normal}
 
-Now we'll take a look at the moments of the skew normal. Equation
+Now we'll take a look at the skew normal. Equation
 \eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
-third moment is a little more complicated:
+third central moment is a little more complicated:
 
@@
 \subsection[Solving for mu, sigma, lambda]{Solving for $\mu$, $\sigma$, $\lambda$}
+\label{subsec:solving-for-mu-sigma-lambda}
 
-Now we can set the moments of our two distributions equal to each other and,
-taking $n$ and $p$ as constants, solve for $\mu$, $\sigma$ and $\lambda$:
+To derive our approximation, we set the central moments of our two
+distributions equal to each other and, taking $n$ and $p$ as constants, solve
+for $\mu$, $\sigma$ and $\lambda$:
 
@@
 Finally, one last consideration that bears mentioning is that the skew-normal
-approximation will sometimes provide us with parameters that violate our
-intuition. In particular, for small $p$ and $n$, equation \eqref{eq:mu-solved}
-can yield negative values of $\mu$, which is impossible for the binomial. This
-can be explained by the fact that as $n$ and $p$ grow more extreme, so does the
+approximation will sometimes give us parameters that violate our intuition. In
+particular, for small $p$ and $n$, equation \eqref{eq:mu-solved} can yield
+negative values of $\mu$, which is impossible for the binomial. This can be
+explained by the fact that as $n$ and $p$ grow more extreme, so does the
 inaccuracy of our approximation. Rather than impose a hard restriction on these

### 2011-01-20 project/paper/output.tex
Addressed other suggested revisions.

@@
 
-which is the pdf of the normal distribution.
+which is the pdf of the normal distribution. Furthermore, when $\lambda > 0$,
+the curve skews to the left, and when $\lambda > 0$, it skews to the right (a
+property we will prove in section \ref{subsec:four-properties}).
 

### 2011-01-20 project/paper/method-of-moments.tex
Removed the part about negative mu, for now.

@@
 improvement.
-
-Finally, one last consideration that bears mentioning is that the skew-normal
-approximation will sometimes give us parameters that violate our intuition. In
-particular, for small $p$ and $n$, equation \eqref{eq:mu-solved} can yield
-negative values of $\mu$, which is impossible for the binomial. This can be
-explained by the fact that as $n$ and $p$ grow more extreme, so does the
-inaccuracy of our approximation. Rather than impose a hard restriction on these
-cases, we would simply advise that the reader be aware of the limits of the
-skew-normal and, if more accuracy is necessary, seek another method of
-approximation.

### 2011-01-20 project/paper/intro.tex
Added normal pdf to intro footnote.

@@
 $n$ but quickly becomes cumbersome as $n$ grows even moderately large. A common
-strategy is to use the normal distribution as an approximation:
+strategy is to use the normal distribution\footnote{A random variable $X$
+follows the normal distribution with mean $\mu$ and variance $\sigma^2$ if it
+has the pdf
+
+\begin{equation*}
+  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
+\end{equation*}
+
+for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
+\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\
+
+$N(0,1)$ is an important special case known as the standard normal (denoted
+$Z$) and has pdf
+
+\begin{equation*}
+  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
+\end{equation*}
+
+and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\
+
+Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.} as an approximation:
 
@@
 
-where $\Phi$ is the standard normal\footnote{Let $X \sim Z = N(0, 1)$. Then $X$
-is said to be a standard normal distribution with pdf
-
-\begin{equation*}
-  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
-\end{equation*}
-
-and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t) \; dt$. Equations 3.3.29
-and 3.3.30, \citet{textbook}.} cdf and $\mu = np$ and $\sigma =
+where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
 \sqrt{np(1-p)}$.

### 2011-01-20 project/paper/output.tex
Added normal pdf to intro footnote.

@@
 
-Finally, one last consideration that bears mentioning is that the skew-normal
-approximation will sometimes give us parameters that violate our intuition. In
-particular, for small $p$ and $n$, equation \eqref{eq:mu-solved} can yield
-negative values of $\mu$, which is impossible for the binomial. This can be
-explained by the fact that as $n$ and $p$ grow more extreme, so does the
-inaccuracy of our approximation. Rather than impose a hard restriction on these
-cases, we would simply advise that the reader be aware of the limits of the
-skew-normal and, if more accuracy is necessary, seek another method of
-approximation.
-
 \section{Demonstrating Improved Accuracy}

### 2011-01-20 project/paper/output.tex
Changed theorem footnote formats.

@@
   \citet{textbook}:\footnote{\textbf{Continuous transformations that are
-  one-to-one} (Theorem 6.3.2, \citealp{textbook}): Suppose that $X$ is a
-  continuous random variable with pdf $f_X(x)$, and assume that $Y = u(X)$
-  defines a one-to-one transformation from $A = \{x|f_X(x) > 0\}$ on to $B =
-  \{y|f_Y(y) > 0\}$ with inverse transformation $x = w(y)$. If the derivative
-  $(d/dy)w(y)$ is continuous and nonzero on $B$, then the pdf of $Y$ is
+  one-to-one}: Suppose that $X$ is a continuous random variable with pdf
+  $f_X(x)$, and assume that $Y = u(X)$ defines a one-to-one transformation from
+  $A = \{x|f_X(x) > 0\}$ on to $B = \{y|f_Y(y) > 0\}$ with inverse
+  transformation $x = w(y)$. If the derivative $(d/dy)w(y)$ is continuous and
+  nonzero on $B$, then the pdf of $Y$ is
 
@@
 
+  Theorem 6.3.2, \citet{textbook}.
   \label{fnote:transformations-1-to-1}
@@
   Then, by Equation 6.3.10 from \citet{textbook},\footnote{\textbf{Continuous
-  transformations that are not one-to-one} (Equation 6.3.10,
-  \citealp{textbook}): When $u(x)$ is not one-to-one over $A$, we can replace
-  equation \eqref{eq:transformations-1-to-1} in footnote
+  transformations that are not one-to-one}: When $u(x)$ is not one-to-one over
+  $A$, we can replace equation \eqref{eq:transformations-1-to-1} in footnote
   \ref{fnote:transformations-1-to-1} with
@@
   \end{equation*}
+
+  Equation 6.3.10, \citet{textbook}.
   }

### 2011-01-21 project/paper/method-of-moments.tex
Reworded central moments issue a little.

@@
 Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
-estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
-and third central moments of $B$ and $Y$.
+estimates for $\mu$, $\sigma$, and $\lambda$ using the method of moments, that
+is, by comparing the first, second, and third moments about the mean (also
+referred to as central moments) of $B$ and $Y$.
 
-\subsection{The Central Moments of the Binomial}
+\subsection{The Moments of the Binomial}
 
@@
 
-\subsection{The Central Moments of the Skew Normal}
+\subsection{The Moments of the Skew Normal}
 
@@
 
-To derive our approximation, we set the central moments of our two
-distributions equal to each other and, taking $n$ and $p$ as constants, solve
-for $\mu$, $\sigma$ and $\lambda$:
+To derive our approximation, we set the above moments of our two distributions
+equal to each other and, taking $n$ and $p$ as constants, solve for $\mu$,
+$\sigma$ and $\lambda$:
 

### 2011-01-21 project/calc/flot/seq2.js

@@ -1,19 +1,0 @@
-// <script src='http://spencertipping.com/montenegro/montenegro.client.js'></script>
-
-// This is how I would write it (modulo some line-joining and general compactness):
-$(caterwaul.clone('std seq montenegro')(function () {
-  let[ns = [1, 2, 3, 4, 5],
-      ps = [6, 7, 8];
-
-      options = {...}] in
-  seq[~ns *!~n[~ps *!p[
-    let[key = 'n#{n}p0#{p}',
-        colors = ['#fc0', '#ff0', '#7c0'],
-        labels = ['N = #{n}, P = #{p}', 'Normal', 'Skew-normal'],
-        series(data, label, color, bars) =
-          {data: data, label: label, color: color,
-           bars: bars ? {show: true} : false, lines: {show: true}}] in
-
-    $ /se[_('body').append(html[div.chart /attr('id', 'chart-n#{n}-p#{p}') /css({width: 900, height: 600})]),
-          _.plot('element', seq[~[binomial, sn, normal] *[series(_[key], labels[_i], colors[_i], _i === 0)]], options)]]]];
-}));

### 2011-01-21 project/paper/method-of-moments.tex
Redid p=0.5 --> lambda=0 paragraph

@@
 
-When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
-therefore $\mu = np = n/2$. This equation, together with \eqref{eq:mu-solved},
-implies that $\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 +
-\lambda^2}} = 0 \Ra$ either $\sigma = 0$ or $\lambda = 0$. Since the former is
-impossible, we must conclude the latter, which brings us back to the normal
-distribution.
+One notable case where the above skew-normal approximation fails is when $p =
+0.5$; the right side of \eqref{eq:solving-for-lambda} becomes undefined, and we
+are unable to obtain $\lambda$. Fortunately, here we can fall back on our
+intuition, which tells us that since the binomial is perfectly symmetrical, the
+skew should be 0. A few observations support this conclusion: When $p = 0.5$,
+equation \eqref{eq:lambda-solved} fails to yield a sign. Furthermore, when
+$\lambda = 0$, equations \eqref{eq:sigma-solved} and \eqref{eq:mu-solved}
+return us to the normal approximation ($\mu = np$ and $\sigma =
+\sqrt{np(1-p)}$, respectively), which is after all a natural choice for a
+symmetric binomial curve.
 

### 2011-01-21 project/paper/output.tex
Made sn pdf a defn, added resources, explained parameters unrelated to curve

@@
 
+\begin{defn}
   Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
   scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$; we will
-denote it $SN(\mu, \sigma, \lambda)$. Then $Y$ has pdf
+  denote it $SN(\mu, \sigma, \lambda)$.\footnotemark Then $Y$ has pdf
 
   \begin{equation} \label{eq:sn-pdf}
-  f_Y(x) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
+    f(x|\mu, \sigma, \lambda) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
   \end{equation}
 
-where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal cdf.
-Some other basic properties of $Y$, given by \citet{pewsey}, are
+  where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal
+  cdf. \citet{main}
+
+  \footnotetext{In this paper, we have followed the notation established by
+  \citet{main} in naming our parameters $\mu$, $\sigma$, and $\lambda$. It does
+  seem intuitive, after all, for the skew-normal to simply "extend" the normal
+  with an extra parameter.
+
+  An unfortunate consequence of this choice, however, is the misconception that
+  $\mu$ and $\sigma$ are related to the mean and variance the way they are in
+  the normal distribution. In the case of the skew-normal, it is more
+  productive to think of them as abstract location and scale parameters. In
+  fact, a quick comparison of figures \ref{fig:comparison-n25},
+  \ref{fig:comparison-n50}, and \ref{fig:comparison-n100} and the corresponding
+  parameters in Table \ref{tab:sn-approx-table} shows that $\mu$ and $\sigma$
+  are not visually related to the curve in any intuitive way.}
+
+\end{defn}
+
+The skew-normal was first introduced by \citet{ref-o'hagan} and further
+developed by \citet{ref-azzalini}, \citet{ref-gupta}, and \citet{ref-arnold}.
+Some of its other basic properties, given by \citet{pewsey}, are
 
@@
 \begin{equation} \label{eq:standard-sn-pdf}
-  f_Z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
+  f(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
 \end{equation}
@@
   \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
-  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) =
-  \int_{-\infty}^\infty \phi(x)$, \thinspace is not even, being 0 near
-  $-\infty$ and 1 near $\infty$. Thus,
+  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) = \int_{-\infty}^t
+  \phi(t)\;dt$, \thinspace is not even, being 0 near $-\infty$ and 1 near
+  $\infty$. Thus,
 

### 2011-01-21 project/paper/accuracy.tex
Reworked intro (added labels to other sections, renamed one)

--- 2011-01-20 project/paper/output.tex
@@
-\documentclass{article}
-\usepackage{jcapstone}
-\begin{document}
-
-\title{The Skew-Normal Approximation of the Binomial Distribution}
-\author{Joyce Tipping}
-\date{2010}
-\maketitle
-
-\section{Introduction}
-
-One of the most basic distributions in statistics is the binomial, $X \sim
-Bin(n,p)$, $n \in \N$, $p \in (0, 1)$ with probability density function (pdf)
-
-\begin{equation*}
-  f_X(x) = \binom{n}{x} p^x q^{n-x}, \quad x = 0, 1, \ldots, n,
-\end{equation*}
-
-where $q=1-p$. Calculating the binomial cumulative distribution function (cdf),
-$F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by hand is manageable for small
-$n$ but quickly becomes cumbersome as $n$ grows even moderately large. A common
-strategy is to use the normal distribution\footnote{A random variable $X$
-follows the normal distribution with mean $\mu$ and variance $\sigma^2$ if it
-has the pdf
-
-\begin{equation*}
-  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
-\end{equation*}
-
-for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
-\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\
-
-$N(0,1)$ is an important special case known as the standard normal (denoted
-$Z$) and has pdf
-
-\begin{equation*}
-  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
-\end{equation*}
-
-and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\
-
-Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.} as an approximation:
-
-\begin{equation}
-  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right),
-\end{equation}
-
-where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
-\sqrt{np(1-p)}$.
-
-This approximation works best when the binomial is perfectly symmetrical, with
-$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
-becomes increasingly skewed, and one must either provide larger values of $n$
-to compensate or face growing inaccuracy. In these cases, the skew-normal
-approximation can provide a better alternative.
-
-\section{The Skew-Normal}
-
-The skew-normal distribution is similar to the normal but with an added
-parameter for skew, allowing it to lean asymmetrically to the left or right. In
-this section, we'll acquaint ourselves with some of its basic properties.
-
-\subsection{Basics}
-
-Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
-scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$; we will
-denote it $SN(\mu, \sigma, \lambda)$. Then $Y$ has pdf
-
-\begin{equation} \label{eq:sn-pdf}
-  f_Y(x) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
-\end{equation}
-
-where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal cdf.
-Some other basic properties of $Y$, given by \citet{pewsey}, are
-
-\begin{align}
-  E(Y) &= \mu + b \delta \sigma, \nonumber \\
-  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-basic-properties} \\
-  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber \\
-  Var(Y) &= \sigma^2 (1 - b^2 \delta^2), \nonumber
-\end{align}
-
-where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}}$.
-
-The $SN(0,1,\lambda)$ distribution is called the standard skew-normal; its pdf
-is
-
-\begin{equation} \label{eq:standard-sn-pdf}
-  f_Z(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
-\end{equation}
-
-Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
-= \sigma Z + \mu$.
-
-A natural question to ask is how the skew-normal relates to the normal.
-Fortunately, the connection is very intuitive: When $\lambda = 0$, Equation
-\eqref{eq:sn-pdf} becomes
-
-\begin{align*}
-  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
-  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
-  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
-  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
-  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
-\end{align*}
-
-which is the pdf of the normal distribution. Furthermore, when $\lambda > 0$,
-the curve skews to the left, and when $\lambda > 0$, it skews to the right (a
-property we will prove in section \ref{subsec:four-properties}).
-
-\subsection{Four Properties}
-\label{subsec:four-properties}
-
-The following four properties of the skew-normal, given by \citet{main}, help
-shed light on our enigmatic new distribution:
-
-\begin{property} \label{prop:1}
-  If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
-\end{property}
-
-\begin{proof}
-  The standard normal pdf is an even function: $\phi(-x) =
-  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
-  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) =
-  \int_{-\infty}^\infty \phi(x)$, \thinspace is not even, being 0 near
-  $-\infty$ and 1 near $\infty$. Thus,
-
-  \begin{align*}
-    f_{(-Z)}(x) &= f_Z(-x) \\
-    & = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\
-    & = 2 \cdot \phi(x) \cdot \Phi (-\lambda x),
-  \end{align*}
-
-  which is the pdf of $SN(0, 1, -\lambda)$.
-\end{proof}
-
-\begin{property} \label{prop:2}
-  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
-\end{property}
-
-\begin{proof}
-  To prove our result, we make use of Lemma 1 in \citet{azzalini}, which we
-  restate here:
-
-  \begin{helper-lem}
-    If $f_0$ is a one-dimensional probability density function symmetric about
-    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
-    and is a density symmetric about 0, then
-
-    \begin{equation}
-      \label{eq:azzalini-perturbation-invariance}
-      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
-    \end{equation}
-
-    is a density function for any odd function $w(\cdot)$.
-  \end{helper-lem}
-
-  This lemma provides a very useful corollary:
-
-  \begin{helper-cor}[Perturbation Invariance]
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
-    notation $\overset{d}{=}$ denotes equality in distribution.    
-  \end{helper-cor}
-
-  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
-  \Phi(\lambda z)$ conforms to Equation
-  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
-  and $Z$ are equal in distribution.
-
-  We will now show that $\phi^2 \sim \chi^2_1$ by deriving its moment
-  generating function (mgf):\footnote{If $X$ is a random variable, then the
-  expected value $M_X(t) = E(e^{tX})$ is called the moment generating function
-  (mgf) of X if this expected value exists for all values of $t$ in some
-  interval of the form $-h < t < h$ for some $h > 0$. Definition 2.5.1,
-  \citet{textbook}.}
-
-  \begin{align*}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \\
-    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \;; \\
-    \intertext{let $u = (\sqrt{1-2t}) \, x$; then $du = (\sqrt{1-2t}) \, dx$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty, x \to \infty \Ra
-      u \to -\infty, u \to \infty$:}
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} du \right) \\
-    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
-      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
-    &= \frac{1}{\sqrt{1-2t}} \;,
-  \end{align*}
-
-  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
-  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
-
-\begin{property} \label{prop:3}
-  As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
-\end{property}
-
-To prove our theorem, it is helpful to formally define the half normal distribution:
-
-\begin{helper-lem} \label{lem:p2-half-normal}
-  Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal
-  random variable with parameter $\sigma$ and
-
-  \begin{equation*}
-    f_{|X|}(x) =
-    \begin{dcases*}
-      0              & when $-\infty < x \leq 0$ \\
-      2 \cdot f_X(x) & when $0 < x < \infty$ 
-    \end{dcases*}
-    .
-  \end{equation*}
-\end{helper-lem}
-
-\begin{proof}
-  Let $X \sim N(0, \sigma^2)$, defined over $A = (-\infty, \infty)$. Define
-
-  \begin{equation*}
-    Y = |X| =
-    \begin{dcases*}
-      -x & if $x < 0$ \\
-      0 & if $x = 0$ \\
-      x & if $x > 0$ \\
-    \end{dcases*}
-    .
-  \end{equation*}
-
-  $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
-  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such
-  that $A = A_1 \cup A_2 \cup A_3$ and $Y$ is one-to-one over each $A_i$. We
-  can then transform each piece separately using Theorem 6.3.2 from
-  \citet{textbook}:\footnote{\textbf{Continuous transformations that are
-  one-to-one}: Suppose that $X$ is a continuous random variable with pdf
-  $f_X(x)$, and assume that $Y = u(X)$ defines a one-to-one transformation from
-  $A = \{x|f_X(x) > 0\}$ on to $B = \{y|f_Y(y) > 0\}$ with inverse
-  transformation $x = w(y)$. If the derivative $(d/dy)w(y)$ is continuous and
-  nonzero on $B$, then the pdf of $Y$ is
-
-  \begin{equation}
-    \label{eq:transformations-1-to-1}
-    f_Y(y) = f_X(w(y)) \left| \frac{d}{dy} w(y) \right| \qquad y \in B.
-  \end{equation}
-
-  Theorem 6.3.2, \citet{textbook}.
-  \label{fnote:transformations-1-to-1}
-  }
-
-  On $A_1$: $y = -x \Ra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1|
-  = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
-    &= f_X(-y) \cdot 1 \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma^2}} \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma^2}} \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_1: -\infty < x < 0 \Ra -\infty < -y < 0 \Ra 0 < y < \infty :B_1$.
-
-  Similarly, on $A_2$: $y = x \Ra x = y$ and $\J = \left| \frac{dx}{dy}
-  \right| = |1| = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
-    &= f_X(y) \cdot 1 \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_2: 0 < x < \infty \Ra 0 < y < \infty :B_2$.
-
-  On $A_3$, we have $x = 0 \Ra y = 0$ and $\J = \left| \frac{dx}{dy} \right| =
-  |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
-
-  Then, by Equation 6.3.10 from \citet{textbook},\footnote{\textbf{Continuous
-  transformations that are not one-to-one}: When $u(x)$ is not one-to-one over
-  $A$, we can replace equation \eqref{eq:transformations-1-to-1} in footnote
-  \ref{fnote:transformations-1-to-1} with
-
-  \begin{equation*}
-    f_Y(y) = \sum_j f_X(w_j(y)) \left| \frac{d}{dy} w_j(y) \right|.
-  \end{equation*}
-
-  Equation 6.3.10, \citet{textbook}.
-  }
-
-  \begin{align*}
-    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \\
-    &= f_X(y) + f_X(y) \\
-    &= 2 \cdot f_X(y)
-  \end{align*}
-
-  over $B = B_1 \cup B_2 = (0, \infty)$, and 0 otherwise.
-\end{proof}
-
-With Lemma \ref{lem:p2-half-normal}, we can easily show our property:
-
-\begin{proof}[Proof of Property 3]
-  Let $Z \sim SN(0,1,\lambda)$. Recall that $f_Z(x) = 2 \cdot \phi(x) \cdot
-  \Phi(\lambda x)$.
-
-  Consider $\lim_{\lambda \to \infty} f_X(x)$. When $x$ is negative, $\lambda x
-  \to -\infty$ and thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however,
-  $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-positive-half-normal}
-    \lim_{\lambda \to \infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      0 & when $x \leq 0$ \\
-      2 \cdot \phi(x) & when $x > 0$
-    \end{dcases*}
-    \eq |N(0,1)|.
-  \end{equation}
-
-  In $\lim_{\lambda \to -\infty} f_X(x)$, the signs are reversed. When $x$ is
-  negative, $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. When $x$ is
-  positive, $\lambda x \to -\infty$ and $\Phi(\lambda x) \to 0$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-negative-half-normal}
-    \lim_{\lambda \to -\infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      2 \cdot \phi(x) & when $x < 0$ \\
-      0 & when $x \geq 0$
-    \end{dcases*}
-    \eq -|N(0,1)|.
-  \end{equation}
-\end{proof}
-
-\begin{property} \label{prop:4}
-  The MGF of $SN(0,1,\lambda)$ is
-
-  \begin{equation} \label{eq:p4-sn-mgf}
-    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2},
-  \end{equation}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
-\end{property}
-
-\begin{proof}
-  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma,
-  \lambda)$ is
-
-  \begin{equation*}
-    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t),
-  \end{equation*}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}} \in (-1, 1)$. It follows
-  that the MGF of the $SN(0, 1, \lambda)$ is
-
-  \begin{equation*}
-    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t).
-  \end{equation*}
-\end{proof}
-
-\section{Developing an Approximation}
-
-Now that we have gotten to know our new distribution a little better, we can
-use it to develop an approximation for the binomial.
-
-Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
-estimates for $\mu$, $\sigma$, and $\lambda$ by comparing the first, second,
-and third central moments of $B$ and $Y$.
-
-\subsection{The Central Moments of the Binomial}
-
-Let's start with the binomial. The first two central moments are simply the
-mean and variance, which we can state from memory:
-
-\begin{equation*}
-  E(B) = np, \quad Var(B) = np(1-p).
-\end{equation*}
-
-Having these, we can easily find $E(B^2)$: Recall that $Var(B) = E(B^2) -
-[E(B)]^2$ and thus
-
-\begin{equation*}
-  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2,
-\end{equation*}
-
-a fact we will need for the third central moment. We will also need $E(B^3)$,
-which we will get via the third factorial moment:
-
-\begin{align*}
-  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \;; \\
-  \intertext{notice that the first three terms of this sum are zero, so we can rewrite our sum beginning at $x = 3$:}
-  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \\
-  \intertext{let $y=x-3$; then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$:}
-  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
-  &= n(n-1)(n-2)p^3 \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 \;; \\
-  \intertext{further expanding the left side and solving for $E(B^3)$:}
-  E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\
-  E(B^3) - 3E(B^2) + 2E(B) &= \\
-  E(B^3) - 3(np - np^2 + n^2p^2) + 2np &= \\
-  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 + 3np - 3np^2 + 3n^2p^2 - 2np \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np.
-\end{align*}
-
-Now, finally, we have all the building blocks necessary to obtain the third
-central moment:
-
-\begin{align*}
-  E \left( [B - E(B)]^3 \right) &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
-  &= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\
-  &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
-  &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\
-  &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
-  &= 2np^3 - 3np^2 + np \\
-  &= np(p-1)(2p-1).
-\end{align*}
-
-Our hard-earned results, restated for convenience:
-
-\begin{align}
-  E(B) &= np, \nonumber \\
-  E([B - E(B)]^2) &= np(1-p), \\
-  E([B - E(B)]^3) &= np(p-1)(2p-1). \nonumber
-\end{align}
-
-\subsection{The Central Moments of the Skew Normal}
-
-Now we'll take a look at the skew normal. Equation
-\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
-third central moment is a little more complicated:
-
-\begin{align*}
-  E([Y - E(Y)]^3) &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
-  &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) \\
-  & \quad + 2\;(\mu + b \delta \sigma)^3 \\
-  &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} -
-    \cancel{6 b \delta \mu^2 \sigma} - \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} \\
-  & \quad - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
-  &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
-  &= b \delta^3 \sigma^3 (2b^2 - 1).
-\end{align*}
-
-We restate our results:
-
-\begin{alignat}{4}
-  E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;, \nonumber \\
-  E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right), \\
-  E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right). \nonumber
-\end{alignat}
-
-\subsection[Solving for mu, sigma, lambda]{Solving for $\mu$, $\sigma$, $\lambda$}
-\label{subsec:solving-for-mu-sigma-lambda}
-
-To derive our approximation, we set the central moments of our two
-distributions equal to each other and, taking $n$ and $p$ as constants, solve
-for $\mu$, $\sigma$ and $\lambda$:
-
-\begin{subequations}
-\begin{align}
-  np &= \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \label{eq:first-moment-set} \\
-  np(1-p) &= \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:second-moment-set} \\
-  np(p-1)(2p-1) &= \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \label{eq:third-moment-set}
-\end{align}
-\end{subequations}
-
-To get $\lambda$, we divide the cube of \eqref{eq:second-moment-set} by the
-square of \eqref{eq:third-moment-set}:
-
-\begin{align}
-  \frac{\sigma^6 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right)^3}{\sigma^6 \cdot \frac{2}{\pi} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^6 \left(
-    \frac{4}{\pi} - 1 \right)^2} &= \frac{n^3p^3(1-p)^3}{n^2p^2(p-1)^2(2p-1)^2} \nonumber \\
-  \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-    \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \;. \label{eq:solving-for-lambda}
-\end{align}
-
-The above equation \eqref{eq:solving-for-lambda} is a rational expression in
-$\lambda^2$ that can be solved with either a considerable amount of manual
-labor or, more efficiently, with a computer algebra system. Once we have
-$\lambda^2$, then $\lambda$ is simply either the positive or negative square
-root, as determined by the sign of $(1-2p)$. The sign can be explained with a
-little assistance from Property \ref{prop:3}: When $p \to 0$, the binomial
-skews left and converges toward the positive half normal, which by
-\eqref{eq:p2-positive-half-normal} corresponds to a positive $\lambda$. When $p
-\to 1$, the binomial skews right and converges toward the negative half normal,
-which by \eqref{eq:p2-negative-half-normal} corresponds to a negative
-$\lambda$. When $p = 0.5$, the binomial is symmetric and $\lambda$ is 0,
-eliminating the need for a sign. Thus:
-
-\begin{equation}
-  \label{eq:lambda-solved}
-  \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}.
-\end{equation}
-
-Having secured $\lambda$, we can find $\sigma$ using
-\eqref{eq:second-moment-set}:
-
-\begin{equation}
-  \label{eq:sigma-solved}
-  np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
-  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} \;.
-\end{equation}
-
-And with both $\lambda$ and $\sigma$, a simple rearrangement of
-\eqref{eq:first-moment-set} yields $\mu$:
-
-\begin{equation}
-  \label{eq:mu-solved}
-  np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
-  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;.
-\end{equation}
-
-When $p = 0.5$, we would expect the binomial to be perfectly symmetrical and
-therefore $\mu = np = n/2$. This equation, together with \eqref{eq:mu-solved},
-implies that $\sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 +
-\lambda^2}} = 0 \Ra$ either $\sigma = 0$ or $\lambda = 0$. Since the former is
-impossible, we must conclude the latter, which brings us back to the normal
-distribution.
-
-\subsection{Restrictions}
-
-Unfortunately, although better than the normal approximation, the skew-normal
-is also not universally applicable. To obtain an estimate for $\lambda$, we
-must put a few restrictions on $n$ and $p$.
-
-If we let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u$, we can rewrite the
-left hand side of \eqref{eq:solving-for-lambda} as
-
-\begin{alignat}{3}
-  \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2}
-    &= \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. & \nonumber \\
-  &= \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 & \nonumber \\
-  &= \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) & \nonumber \\
-  &= \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) &= g(v). \label{eq:lhs-solving-for-lambda}
-\end{alignat}
-
-We can see that $g(v)$ is increasing in $v$, which is always $\geq 1$.
-Therefore:
-
-\begin{equation}
-  \min_{v} g(v) = g(v)|_{v=1} = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1,
-\end{equation}
-
-which means that the right hand side of \eqref{eq:solving-for-lambda}, which is
-supposed to be equal to the left hand side of \eqref{eq:solving-for-lambda},
-can't ever be less than 1. Unfortunately, it sometimes is; in particular,
-$\frac{np(1-p)}{(1-2p)^2} \to 0$ when $p \to 0$ or $p \to 1$. So if we want a
-solution, we must restrict $n$ and $p$ such that
-
-\begin{align}
-  \textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\
-  \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
-  np(1-p) &\geq (1-2p)^2. \label{eq:solving-the-restriction}
-\end{align}
-
-Here, two scenarios arise. The first is when we have a fixed $p$ and wish to
-find the minimum $n$ necessary to derive a skew-normal approximation. From
-\eqref{eq:solving-the-restriction}, solving for $n$ is very simple:
-
-\begin{equation}
-  n \geq \frac{(1-2p)^2}{p(1-p)} \;. \label{eq: n for a given p}
-\end{equation}
-
-Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
-estimate $\lambda$ as a function of $p$. As we would expect, it is larger when
-$p$ is small and rapidly goes to 0 as $p$ increases; for example, when $p =
-0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a
-trivial requirement to meet.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{../images/restriction-least-n.png}
-  \caption{Least possible $n$, given a fixed $p$}
-  \label{fig:sn-restriction-least-n}
-\end{figure}
-
-The second scenario, primarily of academic interest, is when $n$ is fixed and
-we wish to solve for $p$. In this case, we return to
-\eqref{eq:solving-the-restriction} for further factoring:
-
-\begin{align}
-  np(1-p) &\geq (1-2p)^2 \nonumber \\
-  np - np^2 &\geq 1 - 4p + 4p^2 \nonumber \\
-  1 - 4p + 4p^2 - np + np^2 &\leq 0 \nonumber \\
-  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq: solving for p}.
-\end{align}
-
-We then apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
-
-\begin{align*}
-  p &= \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
-  &= \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
-  &= \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n+4)} \\
-  &= \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
-  &= \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}} \;.
-\end{align*}
-
-Let $r_1 = \frac12 - \frac12 \sqrt{\frac{n}{n+4}}$ and $r_2 = \frac12 + \frac12
-\sqrt{\frac{n}{n+4}}$. (Note that $r_1 < r_2$.) Now we can rewrite \eqref{eq:
-solving for p} as
-
-\begin{equation*}
-  (p - r_1)(p - r_2) \leq 0.
-\end{equation*}
-
-Examining the left hand side, when $p < r_1$, both terms are negative and so
-their product is positive; when $p > r_2$, both terms are positive, again
-leading the product to be positive. Therefore, our solution lies where $r_1
-\leq p \leq r_2$, or more explicitly,
-
-\begin{equation}
- \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}} \;.
-\end{equation}
-
-Shown in figure \ref{fig:sn-restriction-p-range} as a function of $n$, this
-interval grows quickly as $n$ increases, and for sufficiently large $n$, it
-becomes almost $(0, 1)$. For example, when $n=100$, our interval is $(0.00971,
-0.99029)$; when $n=500$, it is (0.00199, 0.99801).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{../images/restriction-p-range.png}
-  \caption{Range of possible $p$, given a fixed $n$}
-  \label{fig:sn-restriction-p-range}
-\end{figure}
-
-Although the presence of these restrictions are somewhat disappointing, we can
-console ourselves with the observation that at the same $n$ and $p$, the
-skew-normal yields substantially more accurate approximations than the normal
-(see section \ref{subsec:mabs}). Thus while imperfect, it is nevertheless an
-improvement.
-
 \section{Demonstrating Improved Accuracy}
-\label{sec:demonstrating-improved-accuracy}
+\label{sec:accuracy}
 
@@
 \clearpage
-
-\section{Practical Resources}
-\label{sec:practical-resources}
-
-We conclude our dicussion by offering the reader a few practical resources:
-
-Table \ref{tab:sn-approx-table} shows estimations of $SN(\mu, \sigma, \lambda)$
-for common binomial distributions.
-
-For those with an unusual combination of $n$ and $p$ not in the table, Appendix
-\ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
-parameters by hand.
-
-Finally, for rapidly approximating many binomial distributions, the author's
-Python library, which was used to compute all values presented in this paper,
-is freely available online:
-
-\url{http://github.com/joycetipping/skew-normal-capstone/}
-
-\begin{sidewaystable}
-  \caption{Estimations of $SN(\mu, \sigma, \lambda)$ for $Bin(n,p)$}
-  \centering
-  \renewcommand{\arraystretch}{1.3}
-  \begin{tabular}
-    { r r | r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l }
-    \hline \hline
-    & & \multicolumn{5}{c}{} & \multicolumn{5}{c}{} & \multicolumn{5}{c}{$n$} & \multicolumn{5}{c}{} & \multicolumn{5}{c}{}\\
-    \multirow{20}{*}{$p$} & & \multicolumn{5}{c}{25} & \multicolumn{5}{c}{50} & \multicolumn{5}{c}{100} & \multicolumn{5}{c}{250} & \multicolumn{5}{c}{500} \\
-    \hline
-    & 0.05 & ( & -0.11 & 1.74 & 4.56 & ) & ( & 0.79 & 2.30 & 2.54 & ) & ( & 2.85 & 3.06 & 1.86 & ) & ( & 9.58 & 4.52 & 1.38 & ) & ( & 21.32 & 6.11 & 1.15 & ) \\
-    & 0.10 & ( & 0.89 & 2.20 & 2.31 & ) & ( & 2.97 & 2.94 & 1.74 & ) & ( & 7.44 & 3.94 & 1.40 & ) & ( & 21.53 & 5.88 & 1.10 & ) & ( & 45.62 & 8.01 & 0.94 & ) \\
-    & 0.15 & ( & 2.02 & 2.49 & 1.79 & ) & ( & 5.32 & 3.34 & 1.43 & ) & ( & 12.25 & 4.51 & 1.19 & ) & ( & 33.77 & 6.77 & 0.96 & ) & ( & 70.30 & 9.27 & 0.82 & ) \\
-    & 0.20 & ( & 3.23 & 2.67 & 1.50 & ) & ( & 7.76 & 3.61 & 1.24 & ) & ( & 17.18 & 4.89 & 1.04 & ) & ( & 46.18 & 7.39 & 0.85 & ) & ( & 95.18 & 10.16 & 0.74 & ) \\
-    & 0.25 & ( & 4.49 & 2.79 & 1.29 & ) & ( & 10.28 & 3.78 & 1.09 & ) & ( & 22.20 & 5.15 & 0.93 & ) & ( & 58.71 & 7.83 & 0.76 & ) & ( & 120.22 & 10.80 & 0.67 & ) \\
-    & 0.30 & ( & 5.80 & 2.85 & 1.12 & ) & ( & 12.86 & 3.88 & 0.95 & ) & ( & 27.31 & 5.32 & 0.82 & ) & ( & 71.34 & 8.12 & 0.68 & ) & ( & 145.39 & 11.24 & 0.60 & ) \\
-    & 0.35 & ( & 7.17 & 2.86 & 0.96 & ) & ( & 15.50 & 3.92 & 0.83 & ) & ( & 32.49 & 5.39 & 0.72 & ) & ( & 84.09 & 8.28 & 0.60 & ) & ( & 170.70 & 11.50 & 0.53 & ) \\
-    & 0.40 & ( & 8.59 & 2.83 & 0.80 & ) & ( & 18.23 & 3.89 & 0.70 & ) & ( & 37.76 & 5.39 & 0.61 & ) & ( & 96.96 & 8.32 & 0.51 & ) & ( & 196.18 & 11.60 & 0.45 & ) \\
-    & 0.45 & ( & 10.12 & 2.73 & 0.61 & ) & ( & 21.08 & 3.79 & 0.53 & ) & ( & 43.21 & 5.29 & 0.47 & ) & ( & 110.07 & 8.23 & 0.40 & ) & ( & 221.93 & 11.54 & 0.35 & ) \\
-    & 0.50 & ( & 12.50 & 2.50 & 0.00 & ) & ( & 25.00 & 3.54 & 0.00 & ) & ( & 50.00 & 5.00 & 0.00 & ) & ( & 125.00 & 7.91 & 0.00 & ) & ( & 250.00 & 11.18 & 0.00 & ) \\
-    & 0.55 & ( & 14.88 & 2.73 & -0.61 & ) & ( & 28.92 & 3.79 & -0.53 & ) & ( & 56.79 & 5.29 & -0.47 & ) & ( & 139.93 & 8.23 & -0.40 & ) & ( & 278.07 & 11.54 & -0.35 & ) \\
-    & 0.60 & ( & 16.41 & 2.83 & -0.80 & ) & ( & 31.77 & 3.89 & -0.70 & ) & ( & 62.24 & 5.39 & -0.61 & ) & ( & 153.04 & 8.32 & -0.51 & ) & ( & 303.82 & 11.60 & -0.45 & ) \\
-    & 0.65 & ( & 17.83 & 2.86 & -0.96 & ) & ( & 34.50 & 3.92 & -0.83 & ) & ( & 67.51 & 5.39 & -0.72 & ) & ( & 165.91 & 8.28 & -0.60 & ) & ( & 329.30 & 11.50 & -0.53 & ) \\
-    & 0.70 & ( & 19.20 & 2.85 & -1.12 & ) & ( & 37.14 & 3.88 & -0.95 & ) & ( & 72.69 & 5.32 & -0.82 & ) & ( & 178.66 & 8.12 & -0.68 & ) & ( & 354.61 & 11.24 & -0.60 & ) \\
-    & 0.75 & ( & 20.51 & 2.79 & -1.29 & ) & ( & 39.72 & 3.78 & -1.09 & ) & ( & 77.80 & 5.15 & -0.93 & ) & ( & 191.29 & 7.83 & -0.76 & ) & ( & 379.78 & 10.80 & -0.67 & ) \\
-    & 0.80 & ( & 21.77 & 2.67 & -1.50 & ) & ( & 42.24 & 3.61 & -1.24 & ) & ( & 82.82 & 4.89 & -1.04 & ) & ( & 203.82 & 7.39 & -0.85 & ) & ( & 404.82 & 10.16 & -0.74 & ) \\
-    & 0.85 & ( & 22.98 & 2.49 & -1.79 & ) & ( & 44.68 & 3.34 & -1.43 & ) & ( & 87.75 & 4.51 & -1.19 & ) & ( & 216.23 & 6.77 & -0.96 & ) & ( & 429.70 & 9.27 & -0.82 & ) \\
-    & 0.90 & ( & 24.11 & 2.20 & -2.31 & ) & ( & 47.03 & 2.94 & -1.74 & ) & ( & 92.56 & 3.94 & -1.40 & ) & ( & 228.47 & 5.88 & -1.10 & ) & ( & 454.38 & 8.01 & -0.94 & ) \\
-    & 0.95 & ( & 25.11 & 1.74 & -4.56 & ) & ( & 49.21 & 2.30 & -2.54 & ) & ( & 97.15 & 3.06 & -1.86 & ) & ( & 240.42 & 4.52 & -1.38 & ) & ( & 478.68 & 6.11 & -1.15 & ) \\
-  \end{tabular}
-  \label{tab:sn-approx-table}
-\end{sidewaystable}
-
-\clearpage
-
-\appendix
-\section{Calculating a Skew-Normal Approximation}
-\label{app:calc-sn-approx}
-
-Although easier with a computer program, calculating estimates for $\mu$,
-$\sigma$, and $\lambda$ by hand is perfectly possible. Here, we will
-demonstrate using $n=25$, $p=0.1$.
-
-By far the largest battle is finding $\lambda$. We will use Equation
-\eqref{eq:solving-for-lambda} but with the simplified left hand side given by
-\eqref{eq:lhs-solving-for-lambda}:
-
-\begin{equation}
-  \label{eq:calculating-lambda}
-  \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = \frac{np(1-p)}{(1-2p)^2} \;.
-\end{equation}
-
-The closed-formed solution to this equation is long, hideous, and hard to work
-with, so for this demonstration, we will take a numerical approach.
-
-The left hand side of \eqref{eq:calculating-lambda} is a function of lambda;
-let us denote it $f(\lambda)$. The right hand side is a constant in $n$ and
-$p$; let us call it $k_{n,p}$. Our goal is to find a value of $\lambda$ such
-that $f(\lambda)$ is within a certain margin of error, $e$, of $k_{n,p}$. Since
-we are computing by hand, we will take $e$ to be a modest 0.01.
-
-Recall that the sign of $\lambda$ is determined independently of the value. In
-fact, $f$ is never affected by the sign of $\lambda$, as all terms are squared.
-Thus, we can restrict our search for $\lambda$ to the interval $(0, \infty)$.
-
-Next, by taking $f$'s derivative, we can show that it is monotonically
-decreasing for positive $\lambda$:
-
-\begin{align*}
-  \frac{d}{d\lambda} \left[ \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \right] &= \left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot
-    3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2 \cdot \left( \frac{2\lambda}{\lambda^2} - \frac{2(1+\lambda^2)}{\lambda^3} \right) \\
-  &= \left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot 3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2 \cdot
-    \left( \cancel{\frac{2}{\lambda}} - \frac{2}{\lambda^3} - \cancel{\frac{2}{\lambda}} \right) \\
-  &= \underbrace{\left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot 3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2}_\textnormal{Always positive} \quad \cdot \quad
-     \underbrace{\left( -\frac{2}{\lambda^3} \right)}_{\mathclap{\textnormal{Negative when $\lambda > 0$}}}.
-\end{align*}
-
-This convenient fact allows us to find lower and upper bounds for $\lambda$ and
-repeatedly bisect our interval until we are within $e$ of $k_{n,p}$.
-
-(For the following calculations, it is helpful to keep in mind that because $f$
-is decreasing in $\lambda$, smaller values of $\lambda$ will produce larger
-values of $f$, and vice versa.)
-
-\begin{enumerate}
-  \item \textit{Find $k_{n,p}$.}
-
-    Our value: $\displaystyle k_{n,p} = \frac{25 \cdot 0.1 \cdot 0.9}{(1 - 2\cdot0.1)^2} = 3.5156$.
-
-  \item \textit{Find $a$ and $b$ such that $f(a) > k_{n,p} > f(b)$.}
-
-    Our values: $a=1$, $b=3$.
-
-  \item \textit{Repeatedly bisect $(a,b)$ until $f(c)$ is within $e$ of $k_{n,p}$.}
-
-    Calculate $c=\frac{a+b}{2}$.
-
-    \begin{itemize}
-      \item If $f(c) \leq k_{n,p} - 0.01$, we need a small value of $c$, so we
-      take our new interval to be $(a, c)$.
-
-      \item If $f(c) \geq k_{n,p} + 0.01$, we need a larger value of $c$, so we
-      take our new interval to be $(c, b)$.
-    \end{itemize}
-
-    Repeat this step until $f(c)$ is within $e$ of $k_{n,p}$, or more precisely
-    $k_{n,p} - 0.01 < f(c) < k_{n,p} + 0.01$.
-
-    The following table shows our iterations:
-
-    \renewcommand{\arraystretch}{1.3}
-    \begin{center}
-      \begin{tabular}{c c c c c c c}
-        Iteration & $a$  & $b$   & $c$    & $f(c)$ & $f(c) \leq k_{n,p} - 0.01$ & $f(c) \geq k_{n,p} + 0.01$ \\
-        \hline
-        1         & 2.00 & 3.000 & 2.5000 & 3.0164 & True                       & False \\
-        2         & 2.00 & 2.500 & 2.2500 & 3.7129 & False                      & True \\
-        3         & 2.25 & 2.500 & 2.3750 & 3.3252 & True                       & False \\
-        4         & 2.25 & 2.375 & 2.3125 & 3.5076 & False                      & False \\
-      \end{tabular}
-    \end{center}
-
-    We take the last value of $c$: 2.3125.
-
-  \item \textit{Find the sign of $(1-2p)$.}
-
-    Our $p = 0.1 \Ra (1 - 2\cdot0.1) = 0.8 \Ra$ positive.
-
-  \item \textit{Final answer: \{sign of $(1-2p)$\}$\lambda$}
-
-    Our final answer: $\lambda = 2.3125$.
-\end{enumerate}
-
-Once we have $\lambda$, we can easily find $\sigma$:
-
-\begin{equation*}
-  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} = \sqrt{\frac{25 \cdot 0.1 \cdot 0.9}{1 - \frac{2}{\pi} \cdot \frac{2.3125^2}{1 + 2.3125^2}}} = 2.2029. \\
-\end{equation*}
-
-And with $\lambda$ and $\sigma$, we can also find $\mu$:
-
-\begin{equation*}
-  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} = 25 \cdot 0.1 - 2.2029 \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{2.3125}{\sqrt{1 + 2.3125^2}} = 0.8867.
-\end{equation*}
-
-\clearpage
-\bibliography{bibliography.bib}
-\bibliographystyle{plainnat}
-\end{document}

### 2011-01-21 project/paper/intro.tex
Reworked intro (added labels to other sections, renamed one)

@@
 One of the most basic distributions in statistics is the binomial, $X \sim
-Bin(n,p)$, $n \in \N$, $p \in (0, 1)$ with probability density function (pdf)
+Bin(n,p)$, $n = 0, 1, 2 \ldots$, $p \in (0, 1)$ with probability density
+function (pdf)
 
@@
 $n$ but quickly becomes cumbersome as $n$ grows even moderately large. A common
-strategy is to use the normal distribution\footnote{A random variable $X$
-follows the normal distribution with mean $\mu$ and variance $\sigma^2$ if it
-has the pdf
+strategy is to use the normal distribution\footnotemark as an approximation:
+
+\footnotetext{A random variable $X$ follows the normal distribution with mean
+$\mu$ and variance $\sigma^2$ if it has the pdf
 
@@
 
-Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.} as an approximation:
+Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}
 
@@
 becomes increasingly skewed, and one must either provide larger values of $n$
-to compensate or face growing inaccuracy. In these cases, the skew-normal
-approximation can provide a better alternative.
+to compensate or face growing inaccuracy.
+
+To protect against these cases, many textbooks impose a condition on the normal
+approximation, often stated as either (1) $np(1-p) > 9$ \; or \; (2) $np > 5$
+for $0 < p \leq 0.5$, and $n(1-p) > 5$ for $0.5 < p < 1$. However, \citet{mabs}
+show that even when these conditions are met, the inaccuracy of the normal
+approximation can be surprisingly large. So, the natural question arises: Can
+we do better?
+
+Perhaps so. Intuitively speaking, the main problem with the normal
+approximation is that the normal is always symmetric while the binomial is
+sometimes skewed. This naturally suggests the skew-normal distribution, which
+adds an extra parameter to capture an assymetrical lean.
+
+In this paper, we will explore the aptness of the skew-normal as a method of
+approximating the binomial. First, we'll acquaint ourselves with its basic
+properties (section \ref{sec:properties}). We'll then derive an approximation
+via the method of moments (section \ref{sec:method-of-moments}) and compare its
+accuracy to that of the normal approximation (section \ref{sec:accuracy}).
+Finally, we will leave the reader with a few practical resources for applying
+our new method (section \ref{sec:resources}).

### 2011-01-21 project/paper/output.tex
Reworked intro (added labels to other sections, renamed one)

@@
 becomes increasingly skewed, and one must either provide larger values of $n$
-to compensate or face growing inaccuracy. In these cases, the skew-normal
-approximation can provide a better alternative.
+to compensate or face growing inaccuracy.
+
+To protect against these cases, many textbooks impose a condition on the normal
+approximation, often stated as either (1) $np(1-p) > 9$ \; or \; (2) $np > 5$
+for $0 < p \leq 0.5$, and $n(1-p) > 5$ for $0.5 < p < 1$. However, \citet{mabs}
+show that even when these conditions are met, the inaccuracy of the normal
+approximation can be surprisingly large. So, the natural question arises: Can
+we do better?
+
+Perhaps so. Intuitively speaking, the main problem with the normal
+approximation is that the normal is always symmetric while the binomial is
+sometimes skewed. This naturally suggests the skew-normal distribution, which
+adds an extra parameter to capture an assymetrical lean.
+
+In this paper, we will explore the aptness of the skew-normal as a method of
+approximating the binomial. First, we'll acquaint ourselves with its basic
+properties (section \ref{sec:properties}). We'll then derive an approximation
+via the method of moments (section \ref{sec:method-of-moments}) and compare its
+accuracy to that of the normal approximation (section \ref{sec:accuracy}).
+Finally, we will leave the reader with a few practical resources for applying
+our new method (section \ref{sec:resources}).
 
 \section{The Skew-Normal}
+\label{sec:properties}
 
@@
 \section{Developing an Approximation}
+\label{sec:method-of-moments}
 
@@
 \section{Demonstrating Improved Accuracy}
-\label{sec:demonstrating-improved-accuracy}
+\label{sec:accuracy}
 
@@
 \section{Practical Resources}
-\label{sec:practical-resources}
+\label{sec:resources}
 

### 2011-01-21 project/paper/output.tex
Tweaked intro to properties section.

@@
 The skew-normal distribution is similar to the normal but with an added
-parameter for skew, allowing it to lean asymmetrically to the left or right. In
-this section, we'll acquaint ourselves with some of its basic properties.
+parameter for skew that allows it to lean to the left or right. In this
+section, we'll get to know some of its basic properties.
 

### 2011-01-21 project/paper/properties.tex
Reworked intro (added labels to other sections, renamed one)
Tweaked intro to properties section.

@@
 \section{The Skew-Normal}
+\label{sec:properties}
 
 The skew-normal distribution is similar to the normal but with an added
-parameter for skew, allowing it to lean asymmetrically to the left or right. In
-this section, we'll acquaint ourselves with some of its basic properties.
+parameter for skew that allows it to lean to the left or right. In this
+section, we'll get to know some of its basic properties.
 

### 2011-01-21 project/paper/accuracy.tex
Reworked accuracy section. Abstracted graphs into separate file.

@@
 Now comes the time to justify our efforts by comparing the accuracy of our
-skew-normal approximation to that of the normal.
+skew-normal approximation to that of the normal. Naturally, we are primarily
+interested in cases where the normal approximation performs poorly, that is
+binomials where $n$ is small and $p$ is either close to 0 or 1.\footnotemark
+
+\footnotetext{Again, we examine only $p \in (0, 0.5)$. (See footnote
+\ref{fnote:half-p-range}.)}
 
@@
 \ref{fig:comparison-n100} compare the binomial, normal, and skew-normal at
-small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively. It is not
-hard to see that, especially at very small $n$ and $p$, our skew-normal curve
-follows the shape of the binomial much more closely.
+small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/comparison-n25.png}
-  \caption{Binomial, normal, and skew-normal, $n=25$}
-  \label{fig:comparison-n25}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/comparison-n50.png}
-  \caption{Binomial, normal, and skew-normal, $n=50$}
-  \label{fig:comparison-n50}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/comparison-n100.png}
-  \caption{Binomial, normal, and skew-normal, $n=100$}
-  \label{fig:comparison-n100}
-\end{figure}
+At very small $n$ and $p$, our skew-normal curve follows the shape of the
+binomial much more closely than the normal. However, as $n$ grows, the Central
+Limit Theorem begins to exert its effect; even at a moderate $n = 100$ and a
+smallish $p = 0.2$, the normal and skew-normal become nearly identical. Thus,
+as we would expect, the skew-normal method is most valuable at small $n$ and
+extreme $p$.
 
@@
 
-A quantitative method of judging accuracy is comparing the maximal absolute
-errors of our two approximations, defined by \citet{mabs} as
+Another more quantitative method of judging accuracy is comparing the maximal
+absolute errors of our two approximations, defined by \citet{mabs} as
 
@@
 \infty$ or $p \rightarrow 0.5$.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/mabs-fixed-n.png}
-  \caption{MABS as a function of p}
-  \label{fig:mabs-fixed-n}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/mabs-fixed-p.png}
-  \caption{MABS as a function of n}
-  \label{fig:mabs-fixed-p}
-\end{figure}
-
-\clearpage

### 2011-01-21 project/paper/method-of-moments.tex
Reworked intro (added labels to other sections, renamed one)
Reworked accuracy section. Abstracted graphs into separate file.

@@
 Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
-estimate $\lambda$ as a function of $p$. As we would expect, it is larger when
-$p$ is small and rapidly goes to 0 as $p$ increases; for example, when $p =
-0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a
-trivial requirement to meet.
+estimate $\lambda$ as a function of $p$.\footnotemark As we would expect, it is
+larger when $p$ is small and rapidly goes to 0 as $p$ approaches 0.5; for
+example, when $p = 0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need
+only be $\geq 3$, a trivial requirement to meet.
+
+\footnotetext{Since $Bin(n, p)$ and $Bin(n, 1-p)$ are mirror image curves, it
+is often only necessary to examine either $p \in (0, 0.5)$ or $p \in (0.5, 1)$.
+We will usually consider the former range of $p$'s. \label{fnote:half-p-range}}
 

### 2011-01-21 project/paper/output.tex
Reworked accuracy section. Abstracted graphs into separate file.

@@
 \ref{fig:comparison-n100} compare the binomial, normal, and skew-normal at
-small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively. It is not
-hard to see that, especially at very small $n$ and $p$, our skew-normal curve
-follows the shape of the binomial much more closely.
+small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively.
+
+At very small $n$ and $p$, our skew-normal curve follows the shape of the
+binomial much more closely than the normal. However, as $n$ grows, the Central
+Limit Theorem begins to exert its effect; even at a moderate $n = 100$ and a
+smallish $p = 0.2$, the normal and skew-normal become nearly identical. Thus,
+as we would expect, the skew-normal method is most valuable at small $n$ and
+extreme $p$.
+
+\subsection{Maximal Absolute Error}
+\label{subsec:mabs}
+
+Another more quantitative method of judging accuracy is comparing the maximal
+absolute errors of our two approximations, defined by \citet{mabs} as
+
+\begin{equation}
+  \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
+\end{equation}
+
+where $F_{B(n,p)}$ is the cdf of the binomial and $F_{\textnormal{appr}(n,p)}$
+is the cdf of either the normal or skew-normal approximation; the 0.5 is a
+continuity correction.
+
+Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
+skew-normal and normal approximations as a function of $p$ and $n$,
+respectively. Again, the skew-normal outperforms the normal considerably in the
+extreme ranges, with the two approximations converging as $n \rightarrow
+\infty$ or $p \rightarrow 0.5$.
+
+\section{Practical Resources}
+\label{sec:resources}
+
+We conclude our dicussion by offering the reader a few practical resources:
+
+Table \ref{tab:sn-approx-table} shows estimations of $SN(\mu, \sigma, \lambda)$
+for common binomial distributions.
+
+For those with an unusual combination of $n$ and $p$ not in the table, Appendix
+\ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
+parameters by hand.
+
+Finally, for rapidly approximating many binomial distributions, the author's
+Python library, which was used to compute all values presented in this paper,
+is freely available online:
+
+\url{http://github.com/joycetipping/skew-normal-capstone/}
 
@@
 
-\subsection{Maximal Absolute Error}
-\label{subsec:mabs}
-
-A quantitative method of judging accuracy is comparing the maximal absolute
-errors of our two approximations, defined by \citet{mabs} as
-
-\begin{equation}
-  \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
-\end{equation}
-
-where $F_{B(n,p)}$ is the cdf of the binomial and $F_{\textnormal{appr}(n,p)}$
-is the cdf of either the normal or skew-normal approximation; the 0.5 is a
-continuity correction.
-
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
-skew-normal and normal approximations as a function of $p$ and $n$,
-respectively. Again, the skew-normal outperforms the normal considerably in the
-extreme ranges, with the two approximations converging as $n \rightarrow
-\infty$ or $p \rightarrow 0.5$.
-
 \begin{figure}
@@
 \end{figure}
-
-\clearpage
-
-\section{Practical Resources}
-\label{sec:resources}
-
-We conclude our dicussion by offering the reader a few practical resources:
-
-Table \ref{tab:sn-approx-table} shows estimations of $SN(\mu, \sigma, \lambda)$
-for common binomial distributions.
-
-For those with an unusual combination of $n$ and $p$ not in the table, Appendix
-\ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
-parameters by hand.
-
-Finally, for rapidly approximating many binomial distributions, the author's
-Python library, which was used to compute all values presented in this paper,
-is freely available online:
-
-\url{http://github.com/joycetipping/skew-normal-capstone/}
 

### 2011-01-21 project/calc/approx-table/approx_table.py
Rearranged calc folder.

@@ -1,6 +1,8 @@
 # Written by Joyce Tipping <joyce@joycetipping.com>
 # License: MIT <http://www.opensource.org/licenses/mit-license.php>
 
+import sys
+sys.path.append('..')
 from stats import *
 
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
@@ -8,7 +10,7 @@ from stats import *
 #
 
 def build_approximation_table (ns, ps):
-  f = open('approx-table/approx-table-data.txt', 'w')
+  f = open('approx-table-data.txt', 'w')
   f.write('{ r r | ' + 'r@{}r@{,\\;}r@{,\\;}r@{}l '*len(ns) + '}\n')
   f.write('\\hline \\hline\n')
   f.write('& & ' + '\\multicolumn{5}{c}{} & '*2 + '\\multicolumn{5}{c}{$n$}' + ' & \\multicolumn{5}{c}{}'*2 + '\\\\\n')

### 2011-01-21 project/calc/check/check.js

@@ -1,0 +1,3 @@
+binomial = [[0, 0.27738957312183404], [1, 0.36498628042346593], [2, 0.2305176507937679], [3, 0.09301589417994148], [4, 0.026925653578404096], [5, 0.005951986580489327]];
+normal = [[-2.2999999999999989, 0.0018158902218712231], [-2.1999999999999993, 0.0024383282717041922], [-2.0999999999999996, 0.0032466654668062431], [-2.0, 0.0042867256778411772], [-1.8999999999999986, 0.0056125035213041505], [-1.7999999999999989, 0.0072866908436532603], [-1.6999999999999993, 0.0093809505046099518], [-1.5999999999999996, 0.011975843956093591], [-1.5, 0.015160313978738623], [-1.3999999999999986, 0.01903062477929374], [-1.2999999999999989, 0.023688670135246819], [-1.1999999999999993, 0.029239577817796958], [-1.0999999999999996, 0.035788566089543263], [-1.0, 0.043437045933710075], [-0.89999999999999858, 0.052278010213200894], [-0.79999999999999893, 0.062390806519552228], [-0.69999999999999929, 0.073835451266829874], [-0.59999999999999964, 0.086646704726210833], [-0.5, 0.10082818534841768], [-0.39999999999999858, 0.11634685138962576], [-0.29999999999999893, 0.13312821280856266], [-0.19999999999999929, 0.15105265119043998], [-0.099999999999999645, 0.16995321550470713], [0.0, 0.18961522371860304], [0.10000000000000142, 0.20977793357596308], [0.20000000000000107, 0.23013845153193152], [0.30000000000000071, 0.2503579308476519], [0.40000000000000036, 0.27006997470594329], [0.5, 0.28889101667248257], [0.60000000000000142, 0.30643230931771337], [0.70000000000000107, 0.32231302358107095], [0.80000000000000071, 0.33617385758162033], [0.90000000000000036, 0.34769048390524482], [1.0, 0.35658613652140003], [1.1000000000000014, 0.36264265688118158], [1.2000000000000011, 0.3657093841944532], [1.3000000000000007, 0.3657093841944532], [1.4000000000000004, 0.36264265688118147], [1.5, 0.35658613652140003], [1.6000000000000014, 0.34769048390524465], [1.7000000000000011, 0.33617385758162011], [1.8000000000000007, 0.32231302358107067], [1.9000000000000004, 0.30643230931771309], [2.0, 0.28889101667248257], [2.100000000
[…]

### 2011-01-21 project/calc/check/check.py

@@ -1,0 +1,35 @@
+# Written by Joyce Tipping <joyce@joycetipping.com>
+# License: MIT <http://www.opensource.org/licenses/mit-license.php>
+
+import json
+import sys
+sys.path.append('..')
+from stats import *
+
+#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
+# Comparison Graphs
+#
+def comparison_graph (n, p):
+  # Builds data for one comparison graph (binomial, normal, and skew-normal)
+  # and writes it to an appropriately-named json file
+
+  (binomial, normal, sn) = frame( binomial_pmf(n, p, pairs=True),
+                                  normal_pdf(n, p, pairs=True),
+                                  sn_pdf(n, p, pairs=True) )
+  np = 'n' + str(n) + 'p' + str(p).replace('.', '')
+  f = open('check.js', 'w')
+  f.write('binomial = ' + json.dumps(binomial) + ';\n')
+  f.write('normal = ' + json.dumps(normal) + ';\n')
+  f.write('sn = ' + json.dumps(sn) + ';\n')
+  f.close()
+
+def frame (*args):
+  # Chops off the tails where all three graphs are less than 0.001
+  tmp = map(lambda list: filter(lambda point: point[1] > 0.001, list), args)
+  left = right = 0
+  for i, v in enumerate(tmp):
+    if v[0][0] < left: left = v[0][0]
+    if v[-1][0] > right: right = v[-1][0]
+  return map(lambda list: filter(lambda point: left < point[0] < right, list), args)
+
+comparison_graph(25, 0.05)

### 2011-01-21 project/calc/flot/flot_data.py

@@ -1,9 +1,9 @@
 # Written by Joyce Tipping <joyce@joycetipping.com>
 # License: MIT <http://www.opensource.org/licenses/mit-license.php>
 
-# Python modules
 import json
-# My modules
+import sys
+sys.path.append('..')
 from stats import *
 
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
@@ -21,7 +21,7 @@ def sn_restriction_p_range_graph ():
   p_top_points = map(lambda range_pt: [range_pt[0], range_pt[1]], p_range_bars)
   p_bottom_points = map(lambda range_pt: [range_pt[0], range_pt[2]], p_range_bars)
 
-  f = open('flot/data/restriction-p-range.js', 'w');
+  f = open('data/restriction-p-range.js', 'w');
   f.write('var p_range_bars = ' + json.dumps(p_range_bars) + ';\n')
   f.write('var p_top_points = ' + json.dumps(p_top_points) + ';\n')
   f.write('var p_bottom_points = ' + json.dumps(p_bottom_points) + ';\n')
@@ -34,7 +34,7 @@ def sn_restriction_least_n_graph ():
   ps = r.seq(0.01, 0.5, 0.01)
   points = map(lambda p: [p, sn_restriction_least_n(p)], ps)
 
-  f = open('flot/data/restriction-least-n.js', 'w')
+  f = open('data/restriction-least-n.js', 'w')
   f.write('var least_n_points = ' + json.dumps(points) + ';\n')
   f.close()
 
@@ -53,7 +53,7 @@ def comparison_graph (n, p):
                                   normal_pdf(n, p, pairs=True),
                                   sn_pdf(n, p, pairs=True) )
   np = 'n' + str(n) + 'p' + str(p).replace('.', '')
-  f = open('flot/data/comparison-' + np + '.js', 'w')
+  f = open('data/comparison-' + np + '.js', 'w')
   f.write('binomial.' + np + ' = ' + json.dumps(binomial) + ';\n')
   f.write('normal.' + np + ' = ' + json.dumps(normal) + ';\n')
   f.write('sn.' + np + ' = ' + json.dumps(sn) + ';\n')
@@ -74,7 +74,7 @@ def compile_comparison_data ():
   ps = [0.05, 0.1, 0.2]
[…]

### 2011-01-21 project/paper/method-of-moments.tex
Tweaked a few small issues.

@@
   &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed from 0 to $n-3$] = 1}}} \\
+  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \\
   &= n(n-1)(n-2)p^3 \\
   &= n^3p^3 - 3n^2p^3 + 2np^3 \;; \\
-  \intertext{further expanding the left side and solving for $E(B^3)$:}
+  \intertext{We now expand the left side of the previous equation and solve for $E(B^3)$:}
   E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\

### 2011-01-21 project/paper/output.tex
Few small tweaks to properties section.

@@
 
-The skew-normal was first introduced by \citet{ref-o'hagan} and further
-developed by \citet{ref-azzalini}, \citet{ref-gupta}, and \citet{ref-arnold}.
-Some of its other basic properties, given by \citet{pewsey}, are
+The skew-normal was first introduced by \citet{o'hagan} and was most notably
+further developed by \citet{azzalini-1985}. Some of its other basic properties,
+given by \citet{pewsey}, are
 
@@
 \begin{equation} \label{eq:standard-sn-pdf}
-  f(x) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
+  f(x|\lambda) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
 \end{equation}
@@
 \begin{align*}
-  f_Y(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
+  f(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
   &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
@@
 which is the pdf of the normal distribution. Furthermore, when $\lambda > 0$,
-the curve skews to the left, and when $\lambda > 0$, it skews to the right (a
+the curve skews to the left, and when $\lambda < 0$, it skews to the right (a
 property we will prove in section \ref{subsec:four-properties}).

### 2011-01-21 project/paper/intro.tex
Changed footnote intro.

@@
 One of the most basic distributions in statistics is the binomial, $X \sim
-Bin(n,p)$, $n = 0, 1, 2 \ldots$, $p \in (0, 1)$ with probability density
-function (pdf)
+Bin(n,p)$, $n \in \N$\footnote{That is, integers greater than 0.}, $p \in (0,
+1)$ with probability density function (pdf)
 
@@
 \footnotetext{A random variable $X$ follows the normal distribution with mean
-$\mu$ and variance $\sigma^2$ if it has the pdf
-
-\begin{equation*}
-  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
-\end{equation*}
-
-for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
-\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\
+$\mu$ and variance $\sigma^2$ (denoted $X \sim N(\mu,\sigma^2)$) if it has the
+pdf $f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \;
+e^{-[(x-\mu)/\sigma]^2/2}$ for $-\infty < x < \infty$, where $-\infty < \mu <
+\infty$ and $0 < \sigma < \infty$.
 
 $N(0,1)$ is an important special case known as the standard normal (denoted
-$Z$) and has pdf
-
-\begin{equation*}
-  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
-\end{equation*}
-
-and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\
-
+$Z$) and has pdf $\phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty
+< z < \infty$ and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.
 Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}

### 2011-01-21 project/paper/output.tex
Changed footnote intro.

@@
 \footnotetext{A random variable $X$ follows the normal distribution with mean
-$\mu$ and variance $\sigma^2$ if it has the pdf
-
-\begin{equation*}
-  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
-\end{equation*}
-
-for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
-\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\
+$\mu$ and variance $\sigma^2$ (denoted $X \sim N(\mu,\sigma^2)$) if it has the
+pdf $f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \;
+e^{-[(x-\mu)/\sigma]^2/2}$ for $-\infty < x < \infty$, where $-\infty < \mu <
+\infty$ and $0 < \sigma < \infty$.
 
 $N(0,1)$ is an important special case known as the standard normal (denoted
-$Z$) and has pdf
+$Z$) and has pdf $\phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty
+< z < \infty$ and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.
+Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}
 
-\begin{equation*}
-  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
-\end{equation*}
-
-and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\
-
-Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}
+%\footnotetext{A random variable $X$ follows the normal distribution with mean
+%$\mu$ and variance $\sigma^2$ if it has the pdf
+%
+%\begin{equation*}
+%  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
+%\end{equation*}
+%
+%for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
+%\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\
+%
+%$N(0,1)$ is an important special case known as the standard normal (denoted
+%$Z$) and has pdf
+%
+%\begin{equation*}
+%  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
+%\end{equation*}
+%
+%and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\
+%
+%Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}
 

### 2011-01-22 project/paper/method-of-moments.tex
Redid images. Extensively.

@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{../images/restriction-least-n.png}
-  \caption{Least possible $n$, given a fixed $p$}
-  \label{fig:sn-restriction-least-n}
-\end{figure}
-
 The second scenario, primarily of academic interest, is when $n$ is fixed and
@@
 
-Shown in figure \ref{fig:sn-restriction-p-range} as a function of $n$, this
-interval grows quickly as $n$ increases, and for sufficiently large $n$, it
-becomes almost $(0, 1)$. For example, when $n=100$, our interval is $(0.00971,
-0.99029)$; when $n=500$, it is (0.00199, 0.99801).
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{../images/restriction-p-range.png}
-  \caption{Range of possible $p$, given a fixed $n$}
-  \label{fig:sn-restriction-p-range}
-\end{figure}
+Figure \ref{fig:sn-restriction-p-range} in appendix \ref{app:graphs} shows this
+range as a function of $n$, this interval grows quickly as $n$ increases, and
+for sufficiently large $n$, it becomes almost $(0, 1)$. For example, when
+$n=100$, our interval is $(0.00971, 0.99029)$; when $n=500$, it is (0.00199,
+0.99801).
 

### 2011-01-22 project/paper/output.tex
Cleaning up a little bit.
Few more tweaks.
Redid images. Extensively.

@@
 Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}
-
-%\footnotetext{A random variable $X$ follows the normal distribution with mean
-%$\mu$ and variance $\sigma^2$ if it has the pdf
-%
-%\begin{equation*}
-%  f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \; e^{-[(x-\mu)/\sigma]^2/2}
-%\end{equation*}
-%
-%for $-\infty < x < \infty$, where $-\infty < \mu < \infty$ and $0 < \sigma <
-%\infty$. This is denoted by $X \sim N(\mu,\sigma^2)$.\\
-%
-%$N(0,1)$ is an important special case known as the standard normal (denoted
-%$Z$) and has pdf
-%
-%\begin{equation*}
-%  \phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty < z < \infty
-%\end{equation*}
-%
-%and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.\\
-%
-%Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}
 
@@
 The skew-normal was first introduced by \citet{o'hagan} and was most notably
-further developed by \citet{azzalini-1985}. Some of its other basic properties,
-given by \citet{pewsey}, are
+developed by \citet{azzalini-1985}. Some of its other basic properties, given
+by \citet{pewsey}, are
 
@@
   \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
-  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) = \int_{-\infty}^t
+  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) = \int_{-\infty}^x
   \phi(t)\;dt$, \thinspace is not even, being 0 near $-\infty$ and 1 near
@@
 
+\clearpage
+
+\appendix
+\section{Figures}
+\label{app:figures}
+
+\begin{figure}[h]
+  \centering
+  \subfloat[Least possible $n$, given a fixed $p$]{\label{fig:sn-restriction-least-n}\includegraphics[width=0.76\textwidth]{../images/restriction-least-n.png}}
+  \\ \vspace{5mm}
+  \subfloat[Range of possible $p$, given a fixed $n$]{\label{fig:sn-restriction-p-range}\includegraphics[width=0.76\textwidth]{../images/restriction-p-range.png}}
+  \caption{Restrictions on $n$ and $p$ necessary to obtain $\lambda$}
+  \label{fig:sn-restriction}
+\end{figure}
+
 \begin{figure}
@@
   \centering
-  \includegraphics[width=\textwidth]{../images/mabs-fixed-n.png}
+  \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-n.png}
   \caption{MABS as a function of p}
@@
   \centering
-  \includegraphics[width=\textwidth]{../images/mabs-fixed-p.png}
+  \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-p.png}
   \caption{MABS as a function of n}
@@
 \end{figure}
+
+%\begin{figure}
+%  \centering
+%  \subfloat{\label{fig:mabs-n25}\includegraphics[width=0.8\textwidth]{../images/mabs-n25.png}}                
+%  \\ \vspace{5mm}
+%  \subfloat{\label{fig:mabs-n100}\includegraphics[width=0.8\textwidth]{../images/mabs-n100.png}}
+%  \caption{MABS as a function of p}
+%  \label{fig:mabs-fixed-n}
+%\end{figure}
+%
+%\begin{figure}
+%  \centering
+%  \subfloat{\label{fig:mabs-p0.05}\includegraphics[width=0.8\textwidth]{../images/mabs-p005.png}}                
+%  \\ \vspace{5mm}
+%  \subfloat{\label{fig:mabs-p0.1}\includegraphics[width=0.8\textwidth]{../images/mabs-p01.png}}
+%  \caption{MABS as a function of n}
+%  \label{fig:mabs-fixed-p}
+%\end{figure}
 
@@
 \clearpage
-
-\appendix
 \section{Calculating a Skew-Normal Approximation}

### 2011-01-22 project/calc/flot/data/mabs-n100.js

@@ -1,2 +1,2 @@
-sn.n100 = [[0.019709662154539891, 0.0069206165930497665], [0.029709662154539893, 0.0050456440483724052], [0.039709662154539888, 0.0039757942590482043], [0.04970966215453989, 0.0032820657744922488], [0.059709662154539891, 0.0028626210230579541], [0.069709662154539886, 0.0028377401959075454], [0.079709662154539895, 0.0027186106445759861], [0.089709662154539904, 0.0025668038617868705], [0.099709662154539885, 0.002408189730698812], [0.10970966215453989, 0.0022537798857286684], [0.1197096621545399, 0.0021080343182064698], [0.12970966215453988, 0.0019724221432679545], [0.13970966215453989, 0.0018470414216291975], [0.1497096621545399, 0.0017313722983716973], [0.15970966215453991, 0.0016246547814472989], [0.16970966215453989, 0.001526059895853471], [0.1797096621545399, 0.0014347769503024743], [0.18970966215453991, 0.0013500496566723474], [0.19970966215453989, 0.001271193852114938], [0.2097096621545399, 0.0012050466986987529], [0.21970966215453991, 0.0011479739734885086], [0.22970966215453989, 0.001092061611453421], [0.2397096621545399, 0.0010374946972736276], [0.24970966215453991, 0.00098437936338635623], [0.25970966215453989, 0.00093276711303491577], [0.2697096621545399, 0.00088267133099353967], [0.27970966215453991, 0.00083408029220938262], [0.28970966215453992, 0.00078696502019903747], [0.29970966215453992, 0.00074128628969041821], [0.30970966215453988, 0.00069699856852742381], [0.31970966215453989, 0.00065405387898431755], [0.3297096621545399, 0.00061240403149653844], [0.3397096621545399, 0.00057200256289002827], [0.34970966215453991, 0.00053280634695807016], [0.35970966215453992, 0.00049477686886334471], [0.36970966215453993, 0.00045788152667466941], [0.37970966215453988, 0.00042209470737047949], [0.38970966215453989, 0.00038739926510134026], [0.3997096621545399, 0.0003537882538213466], [0.40970966215453991, 0.00032126707401192167], [0.41970966215453992, 0.00030337074998354474], [0.42970966215453993, 0.00029638103932283499], [0.43970966215453988, 0.00028984225968553545], [0.44970966215453989, 0.00028489030032019524], [0.4597096621545399, 0.00028088232160639048], [0.46970966215453991, 0.
[…]

### 2011-01-22 project/calc/flot/data/mabs-n25.js

@@ -1,2 +1,2 @@
-sn.n25 = [[0.04576165455737035, 0.0076707886207594278], [0.055761654557370352, 0.0056998856478755466], [0.065761654557370347, 0.0081118679633594704], [0.075761654557370356, 0.0067610317876842796], [0.085761654557370351, 0.0041226562692983915], [0.095761654557370346, 0.0039345383905926568], [0.10576165455737035, 0.0051430519792643181], [0.11576165455737036, 0.0051447549440509222], [0.12576165455737034, 0.004326466568962406], [0.13576165455737035, 0.0031076552766322596], [0.14576165455737036, 0.0039130477517766438], [0.15576165455737034, 0.0040862622688435379], [0.16576165455737035, 0.0037487635462088997], [0.17576165455737036, 0.0030608685753005516], [0.18576165455737037, 0.0031453091989917525], [0.19576165455737035, 0.0033235390045406876], [0.20576165455737036, 0.0031554228868615197], [0.21576165455737037, 0.0027230872295835595], [0.22576165455737035, 0.0025857881681195516], [0.23576165455737036, 0.0027324160230712824], [0.24576165455737037, 0.0026293377248905736], [0.25576165455737032, 0.0023253863233147765], [0.26576165455737033, 0.0021406750372194305], [0.27576165455737034, 0.0022481712633557471], [0.28576165455737035, 0.0021681078989882752], [0.29576165455737036, 0.0019329705605580227], [0.30576165455737037, 0.0017652939395343403], [0.31576165455737037, 0.0018343261740297878], [0.32576165455737038, 0.0017587160079293451], [0.33576165455737034, 0.0015620608688619586], [0.34576165455737035, 0.0014354729958023227], [0.35576165455737035, 0.0014693348627546343], [0.36576165455737036, 0.00139000628384231], [0.37576165455737037, 0.001215838848954709], [0.38576165455737038, 0.0011836179174229411], [0.39576165455737039, 0.0011408554757689204], [0.40576165455737034, 0.0011218144675472219], [0.41576165455737035, 0.001140029271661791], [0.42576165455737036, 0.0011292492919786623], [0.43576165455737037, 0.0010888001043022344], [0.44576165455737038, 0.0010822763492390752], [0.45576165455737039, 0.001104390606557426], [0.46576165455737034, 0.0011038755072330098], [0.47576165455737035, 0.0010798829307170354], [0.48576165455737036, 0.0010602297572412933], [0.49576165455737037, 0.001096602
[…]

### 2011-01-22 project/calc/flot/data/mabs-p005.js

@@ -1,2 +1,2 @@
-sn.p005 = [[18, 0.0080695146795372041], [23, 0.0075582492795404077], [28, 0.0055311444228898221], [33, 0.0078827958756394756], [38, 0.0070466999868247782], [43, 0.0049009668832437209], [48, 0.0036757803722735627], [53, 0.0044764215153411113], [58, 0.0050876275372231661], [63, 0.0048598812712371264], [68, 0.0040899775103753477], [73, 0.0031685057754435308], [78, 0.003903644470671791], [83, 0.0041393672785301205], [88, 0.0039665822920267602], [93, 0.0034974965436802563], [98, 0.0031461336809829876], [103, 0.0035155219345159583], [108, 0.003589742864307105], [113, 0.0034187551309338426], [118, 0.0030617826717353192], [123, 0.0030275345392536956], [128, 0.0032113816229867032], [133, 0.00319942723315364], [138, 0.0030241414775116215], [143, 0.0027225002002202459], [148, 0.002879352509362415], [153, 0.0029555134221951884], [158, 0.0028928513322859506], [163, 0.0027145056959977654], [168, 0.0025970902383762318], [173, 0.0027231041310544768], [178, 0.0027318309874033719], [183, 0.0026378624009835427], [188, 0.0024586332975732039], [193, 0.0025124549116604389], [198, 0.002567228225213436]];
[…]

### 2011-01-22 project/calc/flot/data/mabs-p01.js

@@ -1,2 +1,2 @@
-sn.p01 = [[8, 0.0082143136918395587], [13, 0.0070733617898700862], [18, 0.0072476797267480575], [23, 0.0035193521242329329], [28, 0.0052388262152361087], [33, 0.003955724279050471], [38, 0.0039723749844487455], [43, 0.0038663005967027597], [48, 0.0031667556334776803], [53, 0.0034961807167636083], [58, 0.0028811869834089454], [63, 0.0031195684512512201], [68, 0.0028618733316133904], [73, 0.0027888156990080737], [78, 0.0027433388447820894], [83, 0.0025081955095563324], [88, 0.0025921527169648628], [93, 0.002280926509532738], [98, 0.0024356492835662658], [103, 0.0022513919853785758], [108, 0.0022850895767289048], [113, 0.0021929653951576755], [118, 0.0021447939285834938], [123, 0.0021202161431108368], [128, 0.0020159762506221091], [133, 0.0020413566246103854], [138, 0.0018984849890800737], [143, 0.0019610558679556689], [148, 0.0018404467562605498], [153, 0.0018819546885684157], [158, 0.0018040977678382975], [163, 0.0018055086264969489], [168, 0.0017622170504175971], [173, 0.0017324732509724494], [178, 0.0017172501167735943], [183, 0.0016631853709518085], [188, 0.0016708412953861107], [193, 0.0015977321461745353], [198, 0.001624097761914578]];
[…]

### 2011-01-22 project/calc/flot/data/mabs.js

@@ -4,11 +4,11 @@ var ps = ["005", "01"];
 var normal = {}; var sn = {};
 var ns = ["25", "100"];
 var ps = ["005", "01"];
-sn.n100 = [[0.019709662154539891, 0.0069206165930497665], [0.029709662154539893, 0.0050456440483724052], [0.039709662154539888, 0.0039757942590482043], [0.04970966215453989, 0.0032820657744922488], [0.059709662154539891, 0.0028626210230579541], [0.069709662154539886, 0.0028377401959075454], [0.079709662154539895, 0.0027186106445759861], [0.089709662154539904, 0.0025668038617868705], [0.099709662154539885, 0.002408189730698812], [0.10970966215453989, 0.0022537798857286684], [0.1197096621545399, 0.0021080343182064698], [0.12970966215453988, 0.0019724221432679545], [0.13970966215453989, 0.0018470414216291975], [0.1497096621545399, 0.0017313722983716973], [0.15970966215453991, 0.0016246547814472989], [0.16970966215453989, 0.001526059895853471], [0.1797096621545399, 0.0014347769503024743], [0.18970966215453991, 0.0013500496566723474], [0.19970966215453989, 0.001271193852114938], [0.2097096621545399, 0.0012050466986987529], [0.21970966215453991, 0.0011479739734885086], [0.22970966215453989, 0.001092061611453421], [0.2397096621545399, 0.0010374946972736276], [0.24970966215453991, 0.00098437936338635623], [0.25970966215453989, 0.00093276711303491577], [0.2697096621545399, 0.00088267133099353967], [0.27970966215453991, 0.00083408029220938262], [0.28970966215453992, 0.00078696502019903747], [0.29970966215453992, 0.00074128628969041821], [0.30970966215453988, 0.00069699856852742381], [0.31970966215453989, 0.00065405387898431755], [0.3297096621545399, 0.00061240403149653844], [0.3397096621545399, 0.00057200256289002827], [0.34970966215453991, 0.00053280634695807016], [0.35970966215453992, 0.00049477686886334471], [0.36970966215453993, 0.00045788152667466941], [0.37970966215453988, 0.00042209470737047949], [0.38970966215453989, 0.00038739926510134026], [0.3997096621545399, 0.0003537882538213466], [0.40970966215453991, 0.00032126707401192167], [0.41970966215453992, 0.00030337074998354474], [0.42970966215453993, 0.00029638103932283499], [0.43970966215453988, 0.000289842259685
[…]

### 2011-01-22 project/calc/flot/data/restriction-least-n.js

@@ -1,1 +1,1 @@
-var least_n_points = [[0.01, 98], [0.02, 48], [0.029999999999999999, 31], [0.040000000000000001, 23], [0.050000000000000003, 18], [0.060000000000000005, 14], [0.069999999999999993, 12], [0.080000000000000002, 10], [0.089999999999999997, 9], [0.099999999999999992, 8], [0.11, 7], [0.12, 6], [0.13, 5], [0.14000000000000001, 5], [0.15000000000000002, 4], [0.16, 4], [0.17000000000000001, 4], [0.18000000000000002, 3], [0.19, 3], [0.20000000000000001, 3], [0.21000000000000002, 3], [0.22, 2], [0.23000000000000001, 2], [0.24000000000000002, 2], [0.25, 2], [0.26000000000000001, 2], [0.27000000000000002, 2], [0.28000000000000003, 1], [0.29000000000000004, 1], [0.29999999999999999, 1], [0.31, 1], [0.32000000000000001, 1], [0.33000000000000002, 1], [0.34000000000000002, 1], [0.35000000000000003, 1], [0.36000000000000004, 1], [0.37, 1], [0.38, 1], [0.39000000000000001, 1], [0.40000000000000002, 1], [0.41000000000000003, 1], [0.42000000000000004, 1], [0.42999999999999999, 1], [0.44, 1], [0.45000000000000001, 1], [0.46000000000000002, 1], [0.47000000000000003, 1], [0.48000000000000004, 1], [0.48999999999999999, 1], [0.5, 0]];
[…]

### 2011-01-22 project/calc/flot/data/restriction-p-range.js

@@ -1,3 +1,3 @@
-var p_range_bars = [[0, 0.5, 0.5], [1, 0.27639320225002106, 0.72360679774997894], [2, 0.21132486540518713, 0.78867513459481287], [3, 0.17267316464601146, 0.82732683535398854], [4, 0.14644660940672621, 0.85355339059327373], [5, 0.12732200375003505, 0.87267799624996489], [6, 0.1127016653792583, 0.8872983346207417], [7, 0.1011379823912672, 0.89886201760873274], [8, 0.091751709536136983, 0.90824829046386302], [9, 0.083974852831078139, 0.91602514716892181], [10, 0.077422872635741713, 0.92257712736425823], [11, 0.071825580711162407, 0.92817441928883759], [12, 0.066987298107780702, 0.9330127018922193], [13, 0.062762683902396921, 0.93723731609760308], [14, 0.059041448155901566, 0.94095855184409838], [15, 0.055738341680680703, 0.9442616583193193], [16, 0.052786404500042072, 0.94721359549995787], [17, 0.050132294578781322, 0.94986770542121868], [18, 0.047732983133354556, 0.95226701686664539], [19, 0.045553370426807127, 0.95444662957319282], [20, 0.043564535412361549, 0.95643546458763851], [21, 0.041742430504416006, 0.95825756949558394], [22, 0.040066894496100069, 0.95993310550389999], [23, 0.038520896504551372, 0.96147910349544863], [24, 0.03708995011372429, 0.96291004988627571], [25, 0.035761654557370348, 0.96423834544262965], [26, 0.034525331874368625, 0.96547466812563143], [27, 0.033371737371308607, 0.96662826262869139], [28, 0.032292826653257334, 0.96770717334674261], [29, 0.031281566719453979, 0.96871843328054608], [30, 0.030331781686137871, 0.96966821831386207], [31, 0.029438025942839896, 0.97056197405716005], [32, 0.028595479208968322, 0.97140452079103168], [33, 0.027799859198482491, 0.97220014080151751], [34, 0.027047348536541338, 0.97295265146345866], [35, 0.026334533284329054, 0.973665466715671], [36, 0.025658350974743116, 0.97434164902525688], [37, 0.025016046484135468, 0.97498395351586453], [38, 0.024405134394329064, 0.97559486560567099], [39, 0.023823366757133257, 0.97617663324286674], [40, 0.023268705377203824, 0.97673129462279618], [41, 0.022739297890788213, 0.97726070210921
[…]

### 2011-01-22 project/calc/flot/data/restriction.js

@@ -1,4 +1,4 @@
-var least_n_points = [[0.01, 98], [0.02, 48], [0.029999999999999999, 31], [0.040000000000000001, 23], [0.050000000000000003, 18], [0.060000000000000005, 14], [0.069999999999999993, 12], [0.080000000000000002, 10], [0.089999999999999997, 9], [0.099999999999999992, 8], [0.11, 7], [0.12, 6], [0.13, 5], [0.14000000000000001, 5], [0.15000000000000002, 4], [0.16, 4], [0.17000000000000001, 4], [0.18000000000000002, 3], [0.19, 3], [0.20000000000000001, 3], [0.21000000000000002, 3], [0.22, 2], [0.23000000000000001, 2], [0.24000000000000002, 2], [0.25, 2], [0.26000000000000001, 2], [0.27000000000000002, 2], [0.28000000000000003, 1], [0.29000000000000004, 1], [0.29999999999999999, 1], [0.31, 1], [0.32000000000000001, 1], [0.33000000000000002, 1], [0.34000000000000002, 1], [0.35000000000000003, 1], [0.36000000000000004, 1], [0.37, 1], [0.38, 1], [0.39000000000000001, 1], [0.40000000000000002, 1], [0.41000000000000003, 1], [0.42000000000000004, 1], [0.42999999999999999, 1], [0.44, 1], [0.45000000000000001, 1], [0.46000000000000002, 1], [0.47000000000000003, 1], [0.48000000000000004, 1], [0.48999999999999999, 1], [0.5, 0]];
[…]

### 2011-01-22 project/calc/flot/flot_data.py

@@ -16,7 +16,7 @@ def sn_restriction_p_range_graph ():
   def range_pt (n):
     range = sn_restriction_p_range(n)
     return [n, range[0], range[1]]
-  ns = r.seq(0, 50)
+  ns = r.seq(0, 100)
   p_range_bars = map(range_pt, ns)
   p_top_points = map(lambda range_pt: [range_pt[0], range_pt[1]], p_range_bars)
   p_bottom_points = map(lambda range_pt: [range_pt[0], range_pt[2]], p_range_bars)
@@ -31,7 +31,7 @@ def sn_restriction_least_n_graph ():
   # Builds data for the "fixed p, least n" graph and writes it to an
   # appropriately named json file
 
-  ps = r.seq(0.01, 0.5, 0.01)
+  ps = r.seq(0.01, 0.5, 0.005)
   points = map(lambda p: [p, sn_restriction_least_n(p)], ps)
 
   f = open('data/restriction-least-n.js', 'w')
@@ -91,7 +91,7 @@ def mabs_fixed_n_graph (n):
   # an appropriately-named file
 
   least_p = sn_restriction_p_range(n)[0]
-  ps = r.seq(least_p + 0.01, 0.5, 0.01)
+  ps = r.seq(least_p + 0.01, 0.5, 0.005)
   sn_mabs_points = map(lambda p: [p, mabs_sn(n, p)], ps)
   normal_mabs_points = map(lambda p: [p, mabs_normal(n, p)], ps)
 
@@ -106,7 +106,7 @@ def mabs_fixed_p_graph (p):
   # an appropriately-named file
 
   least_n = sn_restriction_least_n(p)
-  ns = r.seq(least_n, 200, 5)
+  ns = r.seq(least_n, 200, 2)
   sn_mabs_points = map(lambda n: [n, mabs_sn(n, p)], ns)
   normal_mabs_points = map(lambda n: [n, mabs_normal(n, p)], ns)
 

### 2011-01-22 project/paper/accuracy.tex
Updated references to figures.

@@
 Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
-\ref{fig:comparison-n100} compare the binomial, normal, and skew-normal at
-small values of $p$ for $n=25$, $n=50$, and $n=100$, respectively.
+\ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
+normal, and skew-normal at small values of $p$ for $n=25$, $n=50$, and $n=100$,
+respectively.
 
@@
 
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
-skew-normal and normal approximations as a function of $p$ and $n$,
-respectively. Again, the skew-normal outperforms the normal considerably in the
-extreme ranges, with the two approximations converging as $n \rightarrow
-\infty$ or $p \rightarrow 0.5$.
+Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
+\ref{app:figures} shows the MABS of the skew-normal and normal approximations
+as a function of $p$ and $n$, respectively. Again, the skew-normal outperforms
+the normal considerably in the extreme ranges, with the two approximations
+converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.

### 2011-01-22 project/paper/method-of-moments.tex
Updated references to figures.

@@
 
-Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
-estimate $\lambda$ as a function of $p$.\footnotemark As we would expect, it is
-larger when $p$ is small and rapidly goes to 0 as $p$ approaches 0.5; for
-example, when $p = 0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need
-only be $\geq 3$, a trivial requirement to meet.
+Figure \ref{fig:sn-restriction-least-n} in appendix \ref{app:figures} shows the
+least sample size required to estimate $\lambda$ as a function of
+$p$.\footnotemark As we would expect, it is larger when $p$ is small and
+rapidly goes to 0 as $p$ approaches 0.5; for example, when $p = 0.01$, $n$ must
+be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a trivial
+requirement to meet.
 
@@
 
-Figure \ref{fig:sn-restriction-p-range} in appendix \ref{app:graphs} shows this
-range as a function of $n$, this interval grows quickly as $n$ increases, and
-for sufficiently large $n$, it becomes almost $(0, 1)$. For example, when
+Figure \ref{fig:sn-restriction-p-range} in appendix \ref{app:figures} shows
+this range as a function of $n$, this interval grows quickly as $n$ increases,
+and for sufficiently large $n$, it becomes almost $(0, 1)$. For example, when
 $n=100$, our interval is $(0.00971, 0.99029)$; when $n=500$, it is (0.00199,

### 2011-01-22 project/paper/output.tex
Updated references to figures.

@@
 
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} shows the MABS of the
-skew-normal and normal approximations as a function of $p$ and $n$,
-respectively. Again, the skew-normal outperforms the normal considerably in the
-extreme ranges, with the two approximations converging as $n \rightarrow
-\infty$ or $p \rightarrow 0.5$.
+Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
+\ref{app:figures} shows the MABS of the skew-normal and normal approximations
+as a function of $p$ and $n$, respectively. Again, the skew-normal outperforms
+the normal considerably in the extreme ranges, with the two approximations
+converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.
 
@@
 
-Table \ref{tab:sn-approx-table} shows estimations of $SN(\mu, \sigma, \lambda)$
-for common binomial distributions.
+Table \ref{tab:sn-approx-table} in appendix \ref{app:figures} shows estimations
+of $SN(\mu, \sigma, \lambda)$ for common binomial distributions.
 
-For those with an unusual combination of $n$ and $p$ not in the table, Appendix
+For those with an unusual combination of $n$ and $p$ not in the table, appendix
 \ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
@@
 \end{figure}
-
-%\begin{figure}
-%  \centering
-%  \subfloat{\label{fig:mabs-n25}\includegraphics[width=0.8\textwidth]{../images/mabs-n25.png}}                
-%  \\ \vspace{5mm}
-%  \subfloat{\label{fig:mabs-n100}\includegraphics[width=0.8\textwidth]{../images/mabs-n100.png}}
-%  \caption{MABS as a function of p}
-%  \label{fig:mabs-fixed-n}
-%\end{figure}
-%
-%\begin{figure}
-%  \centering
-%  \subfloat{\label{fig:mabs-p0.05}\includegraphics[width=0.8\textwidth]{../images/mabs-p005.png}}                
-%  \\ \vspace{5mm}
-%  \subfloat{\label{fig:mabs-p0.1}\includegraphics[width=0.8\textwidth]{../images/mabs-p01.png}}
-%  \caption{MABS as a function of n}
-%  \label{fig:mabs-fixed-p}
-%\end{figure}
 

### 2011-01-22 project/paper/intro.tex
Small tweaks to intro.

@@
 
-One of the most basic distributions in statistics is the binomial, $X \sim
-Bin(n,p)$, $n \in \N$\footnote{That is, integers greater than 0.}, $p \in (0,
-1)$ with probability density function (pdf)
+One of the most basic distributions in probability and statistics is the
+binomial, $X \sim Bin(n,p)$, $n = 1, 2, \ldots$, $p \in (0, 1)$ with
+probability density function (pdf)
 

### 2011-01-22 project/paper/output.tex
Tweaks to properties.

@@
 
-\section{The Skew-Normal}
+\section{The Skew-Normal Distribution}
 \label{sec:properties}
@@
 
-\subsection{Basics}
+\subsection{Foundations}
 
@@
 
-which is the pdf of the normal distribution. Furthermore, when $\lambda > 0$,
-the curve skews to the left, and when $\lambda < 0$, it skews to the right (a
-property we will prove in section \ref{subsec:four-properties}).
+which is the pdf of the normal distribution ($\mu$, $\sigma$). Furthermore,
+when $\lambda > 0$, the curve skews to the left, and when $\lambda < 0$, it
+skews to the right (a property we will prove in section
+\ref{subsec:four-properties}).
 
-\subsection{Four Properties}
+\subsection{Properties of the Standard Skew-Normal Distribution}
 \label{subsec:four-properties}
 
-The following four properties of the skew-normal, given by \citet{main}, help
-shed light on our enigmatic new distribution:
+The following four properties of the standard skew-normal, given by
+\citet{main}, help shed light on our enigmatic new distribution:
 
@@
 \begin{proof}
-  To prove our result, we make use of Lemma 1 in \citet{azzalini}, which we
-  restate here:
+  To prove our result, we begin by examining Lemma 1 in \citet{azzalini}, which
+  we restate here:
 
@@
 
-  This lemma provides a very useful corollary:
+  This lemma is extended by a corollary which gives a very helpful result for
+  the above defined $f_0$ and $f$:
 
@@
 
-  which is the MGF of the $\chi^2_1$. Since $Z$ is equal in distribution to
+  which is the mgf of the $\chi^2_1$. Since $Z$ is equal in distribution to
   $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
@@
 
-  On $A_1$: $y = -x \Ra x = -y$ and $\J = \left| \frac{dx}{dy} \right| = |-1|
-  = 1$, yielding
+  On $A_1$: $y = -x \Ra x = -y$ and the Jacobian $\J = \left| \frac{dx}{dy}
+  \right| = |-1| = 1$, yielding
 
@@
 
-  Similarly, on $A_2$: $y = x \Ra x = y$ and $\J = \left| \frac{dx}{dy}
-  \right| = |1| = 1$, yielding
+  Similarly, on $A_2$: $y = x \Ra x = y$ and the Jacobian $\J = \left|
+  \frac{dx}{dy} \right| = |1| = 1$, yielding
 
@@
 
-  On $A_3$, we have $x = 0 \Ra y = 0$ and $\J = \left| \frac{dx}{dy} \right| =
-  |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
+  On $A_3$, we have $x = 0 \Ra y = 0$ and Jacobian $\J = \left| \frac{dx}{dy}
+  \right| = |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
 
@@
 \begin{property} \label{prop:4}
-  The MGF of $SN(0,1,\lambda)$ is
+  The moment generating function of $SN(0,1,\lambda)$ is
 
@@
 \begin{proof}
-  According to Equation 5 in \citet{azzalini}, the MGF of $SN(\mu, \sigma,
+  According to Equation 5 in \citet{azzalini}, the mgf of $SN(\mu, \sigma,
   \lambda)$ is
@@
   where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}} \in (-1, 1)$. It follows
-  that the MGF of the $SN(0, 1, \lambda)$ is
+  that the mgf of the $SN(0, 1, \lambda)$ is
 

### 2011-01-22 project/paper/properties.tex
Few more tweaks.
Tweaks to properties.

@@
-\section{The Skew-Normal}
+\section{The Skew-Normal Distribution}
 \label{sec:properties}

### 2011-01-22 project/paper/method-of-moments.tex
Tweaks to method of moments section.

@@
 
-\subsection{The Moments of the Binomial}
+\subsection{The Moments of the Binomial Distribution}
 
@@
 
-a fact we will need for the third central moment. We will also need $E(B^3)$,
-which we will get via the third factorial moment:
+a fact we will need for the third central moment.
+
+We will also need $E(B^3)$, which we will get via the third factorial moment:
 
@@
 
-\subsection{The Moments of the Skew Normal}
+\subsection{The Moments of the Skew Normal Distribution}
 
@@
 
-We can see that $g(v)$ is increasing in $v$, which is always $\geq 1$.
-Therefore:
+We can see that $g(v)$ is increasing in $v = \frac{1+\lambda^2}{\lambda^2} \geq
+1$. Therefore:
 

### 2011-01-22 project/paper/accuracy.tex
Reworked accuracy section.

@@
 Now comes the time to justify our efforts by comparing the accuracy of our
-skew-normal approximation to that of the normal. Naturally, we are primarily
-interested in cases where the normal approximation performs poorly, that is
-binomials where $n$ is small and $p$ is either close to 0 or 1.\footnotemark
+skew-normal approximation to that of the normal.
+
+We are naturally most interested in cases where other solutions perform poorly.
+Recall that when $n$ is small, it is feasible to calculate the binomial
+directly, and when $n$ is large or $p$ is close to 0.5, the normal distribution
+provides an adequate approximation. Therefore, our interest is primarily in
+cases where $n$ is moderate and $p$ is extreme (close to 0 or 1).\footnotemark
 
@@
 
-At very small $n$ and $p$, our skew-normal curve follows the shape of the
-binomial much more closely than the normal. However, as $n$ grows, the Central
-Limit Theorem begins to exert its effect; even at a moderate $n = 100$ and a
-smallish $p = 0.2$, the normal and skew-normal become nearly identical. Thus,
-as we would expect, the skew-normal method is most valuable at small $n$ and
-extreme $p$.
+The graphs show that at moderate $n$ and small $p$, our skew-normal curve
+follows the shape of the binomial much more closely than the normal. As $n$
+grows, however, the Central Limit Theorem begins to exert its effect and the
+normal distribution "catches up" in accuracy. Thus as we would expect, the
+skew-normal approximation is of greatest value in the former set of cases.
 
@@
 
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
+Figure \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
 \ref{app:figures} shows the MABS of the skew-normal and normal approximations
-as a function of $p$ and $n$, respectively. Again, the skew-normal outperforms
-the normal considerably in the extreme ranges, with the two approximations
-converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.
+as a function of $p$ and $n$, respectively.
+
+In figure \ref{fig:mabs-fixed-n}, the MABS of the normal approximation is more
+than four times that of the skew-normal when $p$ is very close to 0. The two
+error curves converge and eventually meet as $p$ approaches 0.5 and the
+binomial becomes symmetrical.
+
+Similarly, in figure \ref{fig:mabs-fixed-p}, the normal MABS is roughly six
+times the skew-normal MABS. Interesting, the error curves converge much more
+slowly this time, leading to the pleasant (if surprising) conclusion that when
+$p$ is extreme, the skew-normal gains us a measure of accuracy even at very
+large $n$.

### 2011-01-22 project/paper/output.tex
Expanded fixed-p mabs graphs to n=500

@@
 
-  On $A_1$: $y = -x \Ra x = -y$ and the Jacobian $\J = \left| \frac{dx}{dy}
-  \right| = |-1| = 1$, yielding
+  On $A_1$: $y = -x \Ra x = -y$ and Jacobian $\J = \left| \frac{dx}{dy} \right|
+  = |-1| = 1$, yielding
 
@@
 
-  Similarly, on $A_2$: $y = x \Ra x = y$ and the Jacobian $\J = \left|
+  Similarly, on $A_2$: $y = x \Ra x = y$ and Jacobian $\J = \left|
   \frac{dx}{dy} \right| = |1| = 1$, yielding
@@
 
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
+Figure \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
 \ref{app:figures} shows the MABS of the skew-normal and normal approximations
-as a function of $p$ and $n$, respectively. Again, the skew-normal outperforms
-the normal considerably in the extreme ranges, with the two approximations
-converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.
+as a function of $p$ and $n$, respectively.
+
+In figure \ref{fig:mabs-fixed-n}, the MABS of the normal approximation is more
+than four times that of the skew-normal when $p$ is very close to 0. The two
+error curves converge and eventually meet as $p$ approaches 0.5 and the
+binomial becomes symmetrical.
+
+Similarly, in figure \ref{fig:mabs-fixed-p}, the normal MABS is roughly six
+times the skew-normal MABS. Interesting, the error curves converge much more
+slowly this time, leading to the pleasant (if surprising) conclusion that when
+$p$ is extreme, the skew-normal gains us a measure of accuracy even at very
+large $n$.
 

### 2011-01-22 project/calc/flot/data/mabs-p005.js

@@ -1,2 +1,2 @@
-sn.p005 = [[18, 0.0080695146795372041], [20, 0.0076114038940560125], [22, 0.007685108339799851], [24, 0.0073282825125927653], [26, 0.0065873296840593953], [28, 0.0055311444228898221], [30, 0.0069593434097530993], [32, 0.0077335502881293317], [34, 0.0079020645770075393], [36, 0.007627673132724444], [38, 0.0070466999868247782], [40, 0.0062671291198119483], [42, 0.0053718101997506373], [44, 0.0044228579418931074], [46, 0.0038687969433837122], [48, 0.0036757803722735627], [50, 0.0035992157823511728], [52, 0.0042294650858928917], [54, 0.0046793637638755659], [56, 0.0049601238118869573], [58, 0.0050876275372231661], [60, 0.0050804518801175758], [62, 0.0049581205555147834], [64, 0.0047400841183960762], [66, 0.0044449500211201087], [68, 0.0040899775103753477], [70, 0.0036907418326289354], [72, 0.0032611952025528718], [74, 0.0033582427401747106], [76, 0.0036731296377265354], [78, 0.003903644470671791], [80, 0.0040536184047119672], [82, 0.00412831157379423], [84, 0.0041340156370742176], [86, 0.0040776762672039002], [88, 0.0039665822920267602], [90, 0.0038081242889409506], [92, 0.0036095855397768051], [94, 0.0033779942668543395], [96, 0.0031199915318605997], [98, 0.0031461336809829876], [100, 0.0033317627505034531], [102, 0.0034665646298605579], [104, 0.0035526043758232484], [106, 0.0035926025813043938], [108, 0.003589742864307105], [110, 0.0035475515989158435], [112, 0.0034697783560210527], [114, 0.003360295960357168], [116, 0.0032230037326313188], [118, 0.0030617826717353192], [120, 0.0028803980579533428], [122, 0.0029650525423788876], [124, 0.0030812398549019682], [126, 0.0031628939163899084], [128, 0.0032113816229867032], [130, 0.0032284382816492874], [132, 0.0032160204109127899], [134, 0.0031762874509333738], [136, 0.0031115336101923685], [138, 0.0030241414775116215], [140, 0.0029165303020245725], [142, 0.0027911235219180985], [144, 0.0027061366301621148], [146, 0.0028057493266885891], [148, 0.002879352509362415], [150, 0.0029277801803170023], [152, 0.0029520579214380172]
[…]

### 2011-01-22 project/calc/flot/data/mabs-p01.js

@@ -1,2 +1,2 @@
-sn.p01 = [[8, 0.0082143136918395587], [10, 0.0068684998438764966], [12, 0.006230864626041055], [14, 0.0082175517502896533], [16, 0.0085320452829990845], [18, 0.0072476797267480575], [20, 0.0052870817473360809], [22, 0.0036526333578188463], [24, 0.0040675761606465133], [26, 0.0049822177590519989], [28, 0.0052388262152361087], [30, 0.0049775539804181868], [32, 0.0043558339089236342], [34, 0.0035174575809682196], [36, 0.0035032514605277121], [38, 0.0039723749844487455], [40, 0.0041242626241707603], [42, 0.0040073470459777716], [44, 0.0036803172479234758], [46, 0.0032030054861701407], [48, 0.0031667556334776803], [50, 0.0034396587152370484], [52, 0.0035203757906991651], [54, 0.0034337790518879918], [56, 0.0032100741870374205], [58, 0.0028811869834089454], [60, 0.0029234740405205684], [62, 0.003087390052445349], [64, 0.0031209033289494037], [66, 0.0030395644466031102], [68, 0.0028618733316133904], [70, 0.0026075798944198703], [72, 0.0027283951800620154], [74, 0.0028244089079703938], [76, 0.002825776574055805], [78, 0.0027433388447820894], [80, 0.0025897149003800413], [82, 0.0024336468410707801], [84, 0.0025625686327562791], [86, 0.0026132777987642186], [88, 0.0025921527169648628], [90, 0.0025073163258642062], [92, 0.0023679866648257941], [94, 0.0023359914948927196], [96, 0.0024165680723292338], [98, 0.0024356492835662658], [100, 0.0023984817542888615], [102, 0.0023114314750079246], [104, 0.0021815682834406547], [106, 0.0022392995733047649], [108, 0.0022850895767289048], [110, 0.0022814054844857434], [112, 0.002232653906655252], [114, 0.0021439834729307661], [116, 0.0020811426122303023], [118, 0.0021447939285834938], [120, 0.0021648807649105317], [122, 0.0021444620031784989], [124, 0.0020872982549304253], [126, 0.0019976544428025045], [128, 0.0020159762506221091], [130, 0.0020530686361330541], [132, 0.0020537938690178281], [134, 0.0020209023915758184], [136, 0.0019576439221340447], [138, 0.0018984849890800737], [140, 0.0019477857436150103], [142, 0.001964399285725
[…]

### 2011-01-22 project/calc/flot/data/mabs.js

@@ -8,7 +8,7 @@ sn.n100 = [[0.019709662154539891, 0.0069206165930497665], [0.024709662154539892,
 normal.n100 = [[0.019709662154539891, 0.04389599472062905], [0.024709662154539892, 0.042304073401033593], [0.029709662154539893, 0.035670846348494045], [0.03470966215453989, 0.034785732501581568], [0.039709662154539888, 0.030577468222939663], [0.044709662154539892, 0.029975898910840737], [0.04970966215453989, 0.026998458264699265], [0.054709662154539894, 0.026542929302237006], [0.059709662154539891, 0.024290147399225193], [0.064709662154539882, 0.023921467994508006], [0.069709662154539886, 0.022137642679971148], [0.074709662154539891, 0.021825640054679685], [0.079709662154539895, 0.02036591601793869], [0.0847096621545399, 0.020093363479950166], [0.089709662154539904, 0.018868746244825874], [0.094709662154539881, 0.018624973868067385], [0.099709662154539885, 0.017577371785944984], [0.10470966215453989, 0.017355351969263411], [0.10970966215453989, 0.016445017684575014], [0.1147096621545399, 0.016239893794839033], [0.1197096621545399, 0.015438588021580324], [0.12470966215453988, 0.015246871197602041], [0.12970966215453988, 0.014533902947906574], [0.13470966215453989, 0.014353005534252894], [0.13970966215453989, 0.013712819937351794], [0.1447096621545399, 0.013540770383071332], [0.1497096621545399, 0.012961416604778897], [0.15470966215453991, 0.01279667775831872], [0.15970966215453991, 0.012268801066655566], [0.16470966215453989, 0.012110150175793311], [0.16970966215453989, 0.011626308595877599], [0.1747096621545399, 0.011472755606441787], [0.1797096621545399, 0.011026944432774965], [0.18470966215453991, 0.010877674873623233], [0.18970966215453991, 0.010464988214103355], [0.19470966215453991, 0.010319322334276237], [0.19970966215453989, 0.0099357073240870508], [0.2047096621545399, 0.009793070252075986], [0.2097096621545399, 0.0094351453636822846], [0.2147096621545399, 0.0092950449129158841], [0.21970966215453991, 0.0089599634962216901], [0.22470966215453991, 0.0088219733825779523], [0.22970966215453989, 0.008507319700733762], [0.23470966215453989, 0.0083710666600617101], [0.2397096621545399, 0.008074
[…]

### 2011-01-22 project/calc/flot/flot_data.py

@@ -106,7 +106,7 @@ def mabs_fixed_p_graph (p):
   # an appropriately-named file
 
   least_n = sn_restriction_least_n(p)
-  ns = r.seq(least_n, 200, 2)
+  ns = r.seq(least_n, 500, 5)
   sn_mabs_points = map(lambda n: [n, mabs_sn(n, p)], ns)
   normal_mabs_points = map(lambda n: [n, mabs_normal(n, p)], ns)
 

### 2011-01-22 project/paper/properties.tex
Tweaked wording about jacobian.
Tweak to properties.
Derived variance, changed references to match.

@@
 The skew-normal was first introduced by \citet{o'hagan} and was most notably
-developed by \citet{azzalini-1985}. Some of its other basic properties, given
-by \citet{pewsey}, are
+developed by \citet{azzalini-1985}.
+
+The skew-normal's first three moments about the origin, given by
+\citet{pewsey}, are
 
@@
   E(Y) &= \mu + b \delta \sigma, \nonumber \\
-  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-basic-properties} \\
-  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber \\
-  Var(Y) &= \sigma^2 (1 - b^2 \delta^2), \nonumber
+  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-moments-about-origin} \\
+  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber
 \end{align}
@@
 where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}}$.
+\lambda^2}}$. Using these facts, we can easily derive $Var(Y)$:
+
+\begin{align}
+  Var(Y) &= E(Y^2) - [E(Y)]^2 \nonumber \\
+  &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 - (\mu + b \delta \sigma)^2 \nonumber \\
+  &= \cancel{\mu^2} + \cancel{2b \delta \mu \sigma} + \sigma^2 - \cancel{\mu^2} - \cancel{2b \delta \mu \sigma} - b^2 \delta^2 \sigma^2 \nonumber \\
+  &= \sigma^2 - b^2 \delta^2 \sigma^2 \nonumber \\
+  &= \sigma^2 (1 - b^2 \delta^2). \label{eq:sn-variance}
+\end{align}
 
@@
 \begin{align*}
-  f(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
+  f(x|\mu, \sigma, \lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
   &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\

### 2011-01-22 project/paper/method-of-moments.tex
Derived variance, changed references to match.
Rewrote E(B^3) equation.

@@
 
-\begin{align*}
-  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \;; \\
-  \intertext{notice that the first three terms of this sum are zero, so we can rewrite our sum beginning at $x = 3$:}
-  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \\
+\begin{align}
+  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\}. \nonumber \\
+  \intertext{Notice that the first three terms of the sum on the right hand side are zero, so we can rewrite it beginning at $x = 3$:}
+  E[B(B-1)(B-2)] &= \sum_{x=3}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\}. \nonumber \\
+  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \nonumber \\
+  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \nonumber \\
+  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \nonumber \\
   \intertext{let $y=x-3$; then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$:}
-  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \\
-  &= n(n-1)(n-2)p^3 \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 \;; \\
-  \intertext{We now expand the left side of the previous equation and solve for $E(B^3)$:}
-  E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\
-  E(B^3) - 3E(B^2) + 2E(B) &= \\
-  E(B^3) - 3(np - np^2 + n^2p^2) + 2np &= \\
-  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 + 3np - 3np^2 + 3n^2p^2 - 2np \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np.
-\end{align*}
+  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \nonumber \\
+  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \nonumber \\
+  &= n(n-1)(n-2)p^3 \nonumber \\
+  &= n^3p^3 - 3n^2p^3 + 2np^3. \label{eq:binomial-third-moment-rhs}
+\end{align}
+
+Here we take a moment to expand the left side of the previous equation:
+
+\begin{align}
+  E[B(B-1)(B-2)] &= E \left[ B^3 - 3B^2 + 2B \right] \nonumber \\
+  &= E(B^3) - 3E(B^2) + 2E(B) \nonumber \\
+  &= E(B^3) - 3(np - np^2 + n^2p^2) + 2np \nonumber \\
+  &= E(B^3) - 3np + 3np^2 - 3n^2p^2 + 2np \nonumber \\
+  &= E(B^3) + 3np^2 - 3n^2p^2 - np. \label{eq:binomial-third-moment-lhs}
+\end{align}
+
+We now set the left hand side \eqref{eq:binomial-third-moment-lhs} and right
+hand side \eqref{eq:binomial-third-moment-rhs} equal to each other and solve
+for $E(B^3)$:
+
+\begin{align}
+  E(B^3) + 3np^2 - 3n^2p^2 - np &= n^3p^3 - 3n^2p^3 + 2np^3 \nonumber \\
+  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np. \label{eq:binomial-third-moment}
+\end{align}
 
@@
 
-Now we'll take a look at the skew normal. Equation
-\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
-third central moment is a little more complicated:
+Now we'll take a look at the skew normal. Equations
+\eqref{eq:sn-moments-about-origin} and \eqref{eq:sn-variance} takes care of the
+mean and variance; again the third central moment is a little more complicated:
 

### 2011-01-22 project/paper/method-of-moments.tex
Wording tweaks.

@@
 Let's start with the binomial. The first two central moments are simply the
-mean and variance, which we can state from memory:
+mean and variance:
 
@@
 
-Having these, we can easily find $E(B^2)$: Recall that $Var(B) = E(B^2) -
-[E(B)]^2$ and thus
+From these, we can find $E(B^2)$: Recall that $Var(B) = E(B^2) - [E(B)]^2$ and
+thus
 
 \begin{equation*}
-  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2,
+  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2.
 \end{equation*}
-
-a fact we will need for the third central moment.
 
@@
 
-Now, finally, we have all the building blocks necessary to obtain the third
-central moment:
+Now, finally, we have all the information necessary to obtain the third central
+moment:
 

### 2011-01-22 project/paper/method-of-moments.tex
Reworded moments using the terms central and raw

@@
 estimates for $\mu$, $\sigma$, and $\lambda$ using the method of moments, that
-is, by comparing the first, second, and third moments about the mean (also
-referred to as central moments) of $B$ and $Y$.
+is, by comparing the first, second, and third moments about the mean (central
+moments) of $B$ and $Y$.
 
-\subsection{The Moments of the Binomial Distribution}
+\subsection{The Central Moments of the Binomial Distribution}
 
-Let's start with the binomial. The first two central moments are simply the
-mean and variance:
+The first two central moments of the binomial are simply the mean and variance:
 
@@
 
-\subsection{The Moments of the Skew Normal Distribution}
+\subsection{The Central Moments of the Skew Normal Distribution}
 

### 2011-01-22 project/paper/accuracy.tex
Rewrote accuracy section (again)

@@
 We are naturally most interested in cases where other solutions perform poorly.
-Recall that when $n$ is small, it is feasible to calculate the binomial
-directly, and when $n$ is large or $p$ is close to 0.5, the normal distribution
-provides an adequate approximation. Therefore, our interest is primarily in
-cases where $n$ is moderate and $p$ is extreme (close to 0 or 1).\footnotemark
+Recall that when $n$ is small, it is feasible to execute the binomial
+calculations directly, and when $n$ is large or $p$ is close to 0.5, the normal
+distribution provides an adequate approximation. Therefore, our interest is
+primarily in cases where $n$ is moderate and $p$ is extreme (close to 0 or
+1).\footnotemark
 
@@
 
-Figure \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
-\ref{app:figures} shows the MABS of the skew-normal and normal approximations
-as a function of $p$ and $n$, respectively.
+Figure \ref{fig:mabs-fixed-n} in appendix \ref{app:figures} shows the MABS of
+the skew-normal and the normal approximations as a function of $p$ for $n=25$
+and $n=100$. When $p$ is very close to 0, the MABS of the normal approximation
+is more than four times that of the skew-normal, again demonstrating the
+benefit of using the skew-normal approximation for moderate $n$ and extreme
+$p$. The two error curves converge and eventually meet as $p$ approaches 0.5.
 
-In figure \ref{fig:mabs-fixed-n}, the MABS of the normal approximation is more
-than four times that of the skew-normal when $p$ is very close to 0. The two
-error curves converge and eventually meet as $p$ approaches 0.5 and the
-binomial becomes symmetrical.
-
-Similarly, in figure \ref{fig:mabs-fixed-p}, the normal MABS is roughly six
-times the skew-normal MABS. Interesting, the error curves converge much more
-slowly this time, leading to the pleasant (if surprising) conclusion that when
-$p$ is extreme, the skew-normal gains us a measure of accuracy even at very
-large $n$.
+Figure \ref{fig:mabs-fixed-p}, on the other hand, shows the MABS of our two
+approximations as a function of $n$ for $p=0.05$ and $p=0.1$. At small to
+moderate $n$, the normal MABS is roughly six times the skew-normal MABS.
+Interestingly, the error curves converge much more slowly this time, leading to
+the pleasant (if surprising) conclusion that when $p$ is extreme, the
+skew-normal gains us a measure of accuracy even at large $n$.

### 2011-01-25 project/paper/intro.tex
Proofreading.
Tweaks to intro.

@@
 where $q=1-p$. Calculating the binomial cumulative distribution function (cdf),
-$F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by hand is manageable for small
+$F_X(x) = P(X \leq x) = \sum_{k=0}^x f_X(k)$, by hand is manageable for small
 $n$ but quickly becomes cumbersome as $n$ grows even moderately large. A common
@@
 approximation is that the normal is always symmetric while the binomial is
-sometimes skewed. This naturally suggests the skew-normal distribution, which
-adds an extra parameter to capture an assymetrical lean.
+skewed for all values of $p$ not equal to 0.5. This fact suggests using the
+skew-normal distribution, which adds an extra parameter to capture an
+assymetrical lean.
 

### 2011-01-25 project/paper/properties.tex
Wording tweaks to variance derivation
Reworded moments using the terms central and raw
Tweaks to properties.

@@
 
-The skew-normal's first three moments about the origin, given by
+The skew-normal's first three moments about the origin (raw moments), given by
 \citet{pewsey}, are
@@
 where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}}$. Using these facts, we can easily derive $Var(Y)$:
+\lambda^2}}$. Using these raw moments, we can derive $Var(Y)$:
 
@@
   \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) = \int_{-\infty}^x
-  \phi(t)\;dt$, \thinspace is not even, being 0 near $-\infty$ and 1 near
-  $\infty$. Thus,
+  \phi(t)\;dt$, \thinspace is not even, approaching 0 as $x \to -\infty$ and
+  approaching 1 as $x \to \infty$. Thus,
 
@@
 
-  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
-  \Phi(\lambda z)$ conforms to Equation
-  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
-  and $Z$ are equal in distribution.
+  Let $X \sim N(0,1)$. Take $f_0 = \phi$, and $G = \Phi$. Then, $f_Z(z) = 2
+  \cdot \phi(z) \cdot \Phi(\lambda z)$ conforms to Equation
+  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $X$ and
+  $Z$ are equal in distribution.
 
-  We will now show that $\phi^2 \sim \chi^2_1$ by deriving its moment
-  generating function (mgf):\footnote{If $X$ is a random variable, then the
-  expected value $M_X(t) = E(e^{tX})$ is called the moment generating function
-  (mgf) of X if this expected value exists for all values of $t$ in some
-  interval of the form $-h < t < h$ for some $h > 0$. Definition 2.5.1,
-  \citet{textbook}.}
+  We will now show that $X^2 \sim \chi^2_1$ by deriving its moment generating
+  function (mgf):\footnote{If $X$ is a random variable, then the expected value
+  $M_X(t) = E(e^{tX})$ is called the moment generating function (mgf) of X if
+  this expected value exists for all values of $t$ in some interval of the form
+  $-h < t < h$ for some $h > 0$. Definition 2.5.1, \citet{textbook}.}
 
   \begin{align*}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \\
+    M_{X^2}(t) &= E[e^{tX^2}] \\
     &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
@@
   which is the mgf of the $\chi^2_1$. Since $Z$ is equal in distribution to
-  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
+  $X$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
 
@@
 
-  On $A_1$: $y = -x \Ra x = -y$ and Jacobian $\J = \left| \frac{dx}{dy} \right|
-  = |-1| = 1$, yielding
+  On $A_1$: $y = -x \Ra x = -y$, and the absolute value of the Jacobian $|\J| =
+  \left| \frac{dx}{dy} \right| = |-1| = 1$, yielding
 
@@
 
-  Similarly, on $A_2$: $y = x \Ra x = y$ and Jacobian $\J = \left|
-  \frac{dx}{dy} \right| = |1| = 1$, yielding
+  Similarly, on $A_2$: $y = x \Ra x = y$, and the absolute value of the
+  Jacobian $|\J| = \left| \frac{dx}{dy} \right| = |1| = 1$, yielding
 
@@
 
-  On $A_3$, we have $x = 0 \Ra y = 0$ and Jacobian $\J = \left| \frac{dx}{dy}
-  \right| = |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
+  On $A_3$, we have $x = 0 \Ra y = 0$, and the absolute value of the Jacobian
+  $|\J| = \left| \frac{dx}{dy} \right| = |0| = 0$, yielding $f_Y(y) = f_X(x)
+  \cdot \J = f_X(x) \cdot 0 = 0$.
 

### 2011-01-25 project/paper/method-of-moments.tex
Proofreading.
Tweaks to method of moments section.

@@
 
-From these, we can find $E(B^2)$: Recall that $Var(B) = E(B^2) - [E(B)]^2$ and
-thus
+From these facts, we can find $E(B^2)$: Recall that $Var(B) = E[(B - E(B))^2] =
+E(B^2) - [E(B)]^2$ and thus
 
@@
 
-We now set the left hand side \eqref{eq:binomial-third-moment-lhs} and right
-hand side \eqref{eq:binomial-third-moment-rhs} equal to each other and solve
-for $E(B^3)$:
+Since \eqref{eq:binomial-third-moment-rhs} and
+\eqref{eq:binomial-third-moment-lhs} are equal, we can solve for $E(B^3)$:
 
@@
 labor or, more efficiently, with a computer algebra system. Once we have
-$\lambda^2$, then $\lambda$ is simply either the positive or negative square
-root, as determined by the sign of $(1-2p)$. The sign can be explained with a
-little assistance from Property \ref{prop:3}: When $p \to 0$, the binomial
-skews left and converges toward the positive half normal, which by
+$\lambda^2$, then $\lambda$ is simply the positive or negative square root, as
+determined by the sign of $(1-2p)$.
+
+The sign can be explained with a little assistance from Property \ref{prop:3}:
+When $p \to 0$, the binomial shifts its weight towards the smaller values on
+the left and converges toward the positive half normal, which by
 \eqref{eq:p2-positive-half-normal} corresponds to a positive $\lambda$. When $p
-\to 1$, the binomial skews right and converges toward the negative half normal,
-which by \eqref{eq:p2-negative-half-normal} corresponds to a negative
-$\lambda$. When $p = 0.5$, the binomial is symmetric and $\lambda$ is 0,
-eliminating the need for a sign. Thus:
+\to 1$, the binomial shifts its weight towards the the larger values on the
+right and converges toward the negative half normal, which by
+\eqref{eq:p2-negative-half-normal} corresponds to a negative $\lambda$. When $p
+= 0.5$, the binomial is symmetric and $\lambda$ is 0, eliminating the need for
+a sign. Thus:
 
@@
 \sqrt{np(1-p)}$, respectively), which is after all a natural choice for a
-symmetric binomial curve.
+symmetric binomial distribution.
 
@@
 
-Unfortunately, although better than the normal approximation, the skew-normal
-is also not universally applicable. To obtain an estimate for $\lambda$, we
-must put a few restrictions on $n$ and $p$.
+Unfortunately, the skew-normal is also not universally applicable. To obtain an
+estimate for $\lambda$, we must put a few restrictions on $n$ and $p$.
 

### 2011-01-25 project/paper/properties.tex
Added explanation for the origins of the skew-normal.

@@
 \subsection{Foundations}
+
+\label{subsec:foundations}
 
@@
   are not visually related to the curve in any intuitive way.}
-
 \end{defn}
@@
 The skew-normal was first introduced by \citet{o'hagan} and was most notably
-developed by \citet{azzalini-1985}.
+developed by \citet{azzalini-1985}. It belongs to a class of skewed
+distributions conforming to the following guidelines:
+
+\begin{lem}
+  \label{lem:azzalini-lemma-1}
+
+  If $f_0$ is a one-dimensional probability density function symmetric about
+  0, and $G$ is a one-dimensional distribution function such that $G'$ exists
+  and is a density symmetric about 0, then
+
+  \begin{equation}
+    \label{eq:azzalini-skewed-distribution}
+    f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
+  \end{equation}
+
+  is a density function for any odd function $w(\cdot)$. (Lemma 1,
+  \citealp{azzalini})
+\end{lem}
+
+In equation \eqref{eq:azzalini-skewed-distribution}, $f_0$ acts as a weighting
+function referred to as a kernel. When $f_0 = \phi$, the distribution is said
+to be generated by the normal kernel. $G$ does not necessarily have to be taken
+from the same distribution as $f_0$; for example, the normal kernel has been
+paired with cdf's from various other distributions, such as Student's t,
+Cauchy, Laplace, and uniform. In the case of our skew-normal, however, both
+$f_0$ and $G$ come from the normal distribution.
 
@@
 \begin{proof}
-  To prove our result, we begin by examining Lemma 1 in \citet{azzalini}, which
-  we restate here:
+  Lemma \ref{lem:azzalini-lemma-1} from section \ref{subsec:foundations}
+  provides a very useful result for the above defined $f_0$ and $f$, which we
+  restate here as a corollary:
 
-  \begin{helper-lem}
-    If $f_0$ is a one-dimensional probability density function symmetric about
-    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
-    and is a density symmetric about 0, then
+  \begin{cor}[Perturbation Invariance]
+    \label{eq:azzalini-perturbation-invariance}
 
-    \begin{equation}
-      \label{eq:azzalini-perturbation-invariance}
-      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
-    \end{equation}
-
-    is a density function for any odd function $w(\cdot)$.
-  \end{helper-lem}
-
-  This lemma is extended by a corollary which gives a very helpful result for
-  the above defined $f_0$ and $f$:
-
-  \begin{helper-cor}[Perturbation Invariance]
     If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
-    notation $\overset{d}{=}$ denotes equality in distribution.    
-  \end{helper-cor}
+    notation $\overset{d}{=}$ denotes equality in distribution. (Page 161,
+    \citealp{azzalini})
+  \end{cor}
 
@@
   \cdot \phi(z) \cdot \Phi(\lambda z)$ conforms to Equation
-  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $X$ and
-  $Z$ are equal in distribution.
+  \eqref{eq:azzalini-skewed-distribution}, and we can conclude that $X$ and $Z$
+  are equal in distribution.
 

### 2011-01-30 project/calc/flot-pres/data/comparison-headers.js
Added flot files and images for beamer presentation

@@ -1,0 +1,3 @@
+var binomial = {}; var normal = {}; var sn = {};
+var ns = ["25", "500"];
+var ps = ["0.05", "0.5"];

### 2011-01-30 project/calc/flot-pres/data/comparison-n25p05.js

@@ -1,0 +1,3 @@
+binomial.n25p05 = [[0, 2.9802322387695299e-08], [1, 7.4505805969238398e-07], [2, 8.9406967163085887e-06], [3, 6.8545341491699219e-05], [4, 0.00037699937820434603], [5, 0.0015833973884582498], [6, 0.0052779912948608364], [7, 0.014325976371765123], [8, 0.032233446836471509], [9, 0.060885399580001845], [10, 0.097416639328002888], [11, 0.13284087181091306], [12, 0.15498101711273193], [13, 0.15498101711273193], [14, 0.13284087181091311], [15, 0.097416639328002888], [16, 0.060885399580001845], [17, 0.032233446836471495], [18, 0.014325976371765135], [19, 0.0052779912948608416], [20, 0.0015833973884582498], [21, 0.00037699937820434603], [22, 6.8545341491699219e-05], [23, 8.9406967163085887e-06], [24, 7.4505805969238398e-07], [25, 2.9802322387695299e-08]];
+normal.n25p05 = [[-12.5, 3.0778394506825677e-23], [-12.4, 4.5879250992958145e-23], [-12.300000000000001, 6.8279731581743959e-23], [-12.199999999999999, 1.0145475816795948e-22], [-12.1, 1.5050750751694145e-22], [-12.0, 2.2292000090882762e-22], [-11.9, 3.2964389534035635e-22], [-11.800000000000001, 4.8668299010249154e-22], [-11.699999999999999, 7.1738522291748712e-22], [-11.6, 1.0557566227027385e-21], [-11.5, 1.5512447726987843e-21], [-11.4, 2.2756317082077838e-21], [-11.300000000000001, 3.3329496336528395e-21], [-11.199999999999999, 4.87372088665097e-21], [-11.1, 7.1153732360386862e-21], [-11.0, 1.0371458804401484e-20], [-10.9, 1.5093401896002006e-20], [-10.800000000000001, 2.1930046609333164e-20], [-10.699999999999999, 3.1812448892795117e-20], [-10.6, 4.6074409517652996e-20], [-10.5, 6.6623521295197154e-20], [-10.4, 9.6183486775425917e-20], [-10.300000000000001, 1.3863681719331418e-19], [-10.199999999999999, 1.995086687558436e-19], [-10.1, 2.8664877556044265e-19], [-10.0, 4.1119094286675663e-19], [-9.9000000000000004, 5.8890076430177032e-19], [-9.80000000
[…]

### 2011-01-30 project/presentation/presentation.tex
Rearranged extensively.

\documentclass{beamer}
%\usetheme{Boadilla}

\title[The Skew-Normal Approx of the Binomial]{The Skew-Normal Approximation\\of the Binomial Distribution}
\author{Joyce Tipping}
\institute{Truman State University}
\date{Spring 2011}

\begin{document}

\frame{\titlepage}

\begin{frame}
  Frame 1
  \begin{alertblock}{Text!!!}
    Stuff.
  \end{alertblock}
\end{frame}

\end{document}

### 2011-02-08 project/presentation/presentation.tex
First pass over intro.

@@
 \documentclass{beamer}
-%\usetheme{Boadilla}
+\usepackage{jmath}
 
+\usetheme{default}
+\usefonttheme{structuresmallcapsserif}
+\setbeamertemplate{blocks}[rounded][shadow=true]
+
+\newcommand{\vsep}{\vspace{0.2cm}}
+
+\begin{document}
 \title[The Skew-Normal Approx of the Binomial]{The Skew-Normal Approximation\\of the Binomial Distribution}
@@
 
-\begin{document}
-
 \frame{\titlepage}
 
-\begin{frame}
-  Frame 1
-  \begin{alertblock}{Text!!!}
-    Stuff.
-  \end{alertblock}
-\end{frame}
+%% Introduction
+\frame{
+  \frametitle{Introduction}
+  $X \sim Bin(n,p)$ where $0<p<1$ and $n = 1, 2, 3, \ldots$
 
+  \pause
+  \begin{align*}
+    \uncover<2->{f_X(x) &= \binom{n}{x} \; p^x q^{n-x} \\}
+    \uncover<3->{F_X(x) &= P(X \leq x) = \sum_{k=0}^x f_X(k)}
+  \end{align*}
+}
+\frame{
+  \frametitle{Introduction}
+  The binomial cdf is easy to calculate for small $n$ ...
+
+  \pause
+  But as $n$ gets larger, it becomes increasingly difficult.
+
+  \pause
+  For example ...
+}
+\frame{
+  \frametitle{Introduction}
+  When $n=3$,
+  \begin{equation*}
+    F(1) = \binom{3}{1} \; p^1 q^2 + \binom{3}{0} \; p^0 q^3
+  \end{equation*}
+
+  \pause
+  When $n=25$,
+  \begin{align*}
+    F(12) =& \binom{25}{12} \; p^{12} q^{13} + \binom{25}{11} \; p^{11} q^{14} + \binom{25}{10} \; p^{10} q^{15} + \binom{25}{9} \; p^9 q^{16} \\
+          +& \binom{25}{8} \; p^8 q^{17} + \binom{25}{7} \; p^7 q^{18} + \binom{25}{6} \; p^6 q^{19} + \binom{25}{5} \; p^5 q^{20} \\
+          +& \binom{25}{4} \; p^4 q^{21} + \binom{25}{3} \; p^3 q^{22} + \binom{25}{2} \; p^2 q^{23} + \binom{25}{1} \; p^1 q^{24} \\
+          +& \binom{25}{0} \; p^0 q^{25}
+  \end{align*}
+}
+\frame{
+  \frametitle{Introduction}
+  Normal Approximation of the Binomial:
+
+  \begin{equation*}
+    F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right),
+  \end{equation*}
+
+  where $\mu = np$, $\sigma = \sqrt{np(1-p)}$, and $\Phi$ is the standard
+  normal cdf.
+
+  \vsep
+  When does this work well? ... \pause In a nutshell, when the binomial is symmetric.
+}
+\frame{
+  \frametitle{Introduction}
+
+  The binomial is symmetric when
+  \only<1->{$p=0.5$}
+  \only<2>{or $n$ is very large.}
+
+  \begin{center}
+    \only<1>{\includegraphics[width=\textwidth]{../images/binomial-normal-1.png}}
+    \only<2>{\includegraphics[width=\textwidth]{../images/binomial-normal-2.png}}
+  \end{center}
+}
+\frame{
+  \frametitle{Introduction}
+
+  However, when $n$ is medium and $p$ is extreme ...
+
+  \begin{center}
+    \only<1>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-1.png}}
+    \only<2-3>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-2.png}}
+    \only<4>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-3.png}}
+  \end{center}
+
+  \only<1>{the binomial is very skewed.}
+  \only<2>{the normal approximation doesn't work very well.}
+  \only<3->{\textbf{Can we do better?}}
+  \only<4>{Introducing ... the skew-normal distribution.}
+}
+
+%% Outline
+\frame{
+  \frametitle{Outline}
+  What we're going to cover:
+  \pause
+  \begin{enumerate}[<+->]
+    \item Skew-Normal distribution -- basic properties
+    \item Method of Moments -- derive an approximation
+    \item Accuracy -- compare to the normal approximation
+  \end{enumerate}
+}
+
+%% The Skew-Normal Distribution
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+  \begin{definition}[Skew-normal]
+    Let $Y$ be a skew-normal distribution, with location parameter $\mu \in
+    \R$, scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$.
+    Then $Y$ has pdf
+
+    \begin{equation*}
+      f(x|\mu, \sigma, \lambda) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
+    \end{equation*}
+
+    where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal
+    cdf.
+
+    \vsep
+    We write $Y \sim SN(\mu, \sigma, \lambda)$.
+  \end{definition}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+  A few notes:
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+}
 \end{document}

### 2011-02-08 project/paper/accuracy.tex
Made some minor changes, as requested by second reader.

@@
 \ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
-normal, and skew-normal at small values of $p$ for $n=25$, $n=50$, and $n=100$,
-respectively.
+normal, and skew-normal at the small values of $p=0.05$, $p=0.1$, and $p=0.2$
+for $n=25$, $n=50$, and $n=100$, respectively.
 
-The graphs show that at moderate $n$ and small $p$, our skew-normal curve
-follows the shape of the binomial much more closely than the normal. As $n$
-grows, however, the Central Limit Theorem begins to exert its effect and the
-normal distribution "catches up" in accuracy. Thus as we would expect, the
-skew-normal approximation is of greatest value in the former set of cases.
+The graphs in figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
+\ref{fig:comparison-n100} indicate that at moderate $n$ and small $p$, our
+skew-normal curve follows the shape of the binomial much more closely than the
+normal. As $n$ grows for each value of $p$, however, the Central Limit Theorem
+begins to exert its effect and the normal distribution "catches up" in
+accuracy, slowly for for more extreme values of $p$ and faster as $p$
+approaches 0.5. Thus as we would expect, the skew-normal approximation is of
+greatest value when $n$ is moderate and $p$ is extreme.
 

### 2011-02-08 project/paper/intro.tex
Typo, very small tweak.

@@
 skew-normal distribution, which adds an extra parameter to capture an
-assymetrical lean.
+asymetrical lean.
 
@@
 approximating the binomial. First, we'll acquaint ourselves with its basic
-properties (section \ref{sec:properties}). We'll then derive an approximation
+properties (section \ref{sec:skew-normal}). We'll then derive an approximation
 via the method of moments (section \ref{sec:method-of-moments}) and compare its

### 2011-02-08 project/paper/accuracy.tex

@@
 \ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
-normal, and skew-normal at the small values of $p=0.05$, $p=0.1$, and $p=0.2$
-for $n=25$, $n=50$, and $n=100$, respectively.
+normal, and skew-normal at small values of $p=0.05$, $p=0.1$, and $p=0.2$ for
+each of $n=25$, $n=50$, and $n=100$, respectively.
 

### 2011-02-12 project/presentation/intro.tex
Partitioned presentation into sections, created build script

--- 2011-02-08 project/presentation/presentation.tex
@@
-\documentclass{beamer}
-\usepackage{jmath}
-
-\usetheme{default}
-\usefonttheme{structuresmallcapsserif}
-\setbeamertemplate{blocks}[rounded][shadow=true]
-
-\newcommand{\vsep}{\vspace{0.2cm}}
-
-\begin{document}
-\title[The Skew-Normal Approx of the Binomial]{The Skew-Normal Approximation\\of the Binomial Distribution}
-\author{Joyce Tipping}
-\institute{Truman State University}
-\date{Spring 2011}
-
 \frame{\titlepage}
@@
 }
-
-%% The Skew-Normal Distribution
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-  \begin{definition}[Skew-normal]
-    Let $Y$ be a skew-normal distribution, with location parameter $\mu \in
-    \R$, scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$.
-    Then $Y$ has pdf
-
-    \begin{equation*}
-      f(x|\mu, \sigma, \lambda) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
-    \end{equation*}
-
-    where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal
-    cdf.
-
-    \vsep
-    We write $Y \sim SN(\mu, \sigma, \lambda)$.
-  \end{definition}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-  A few notes:
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\end{document}

### 2011-02-12 project/presentation/skew-normal.tex
Partitioned presentation into sections, created build script

--- 2011-01-30 project/presentation/presentation.tex
@@
-\documentclass{beamer}
-%\usetheme{Boadilla}
+%% The Skew-Normal Distribution
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+  \begin{definition}[Skew-normal]
+    Let $Y$ be a skew-normal distribution, with location parameter $\mu \in
+    \R$, scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$.
+    Then $Y$ has pdf
 
-\title[The Skew-Normal Approx of the Binomial]{The Skew-Normal Approximation\\of the Binomial Distribution}
-\author{Joyce Tipping}
-\institute{Truman State University}
-\date{Spring 2011}
+    \begin{equation*}
+      f(x|\mu, \sigma, \lambda) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
+    \end{equation*}
 
-\begin{document}
+    where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal
+    cdf.
 
-\frame{\titlepage}
-
-\begin{frame}
-  Frame 1
-  \begin{alertblock}{Text!!!}
-    Stuff.
-  \end{alertblock}
-\end{frame}
-
-\end{document}
+    \vsep
+    We write $Y \sim SN(\mu, \sigma, \lambda)$.
+  \end{definition}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+  A few notes:
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+}

### 2011-02-12 project/paper/paper.tex
Reorganized build script: created headers, closers, renamed output file

--- 2011-01-22 project/paper/output.tex
@@
 \begin{document}
+
+\title{The Skew-Normal Approximation of the Binomial Distribution}
+\author{Joyce Tipping}
+\date{2010}
+\maketitle
 
@@
 approximation is that the normal is always symmetric while the binomial is
-sometimes skewed. This naturally suggests the skew-normal distribution, which
-adds an extra parameter to capture an assymetrical lean.
+skewed for all values of $p$ not equal to 0.5. This fact suggests using the
+skew-normal distribution, which adds an extra parameter to capture an
+asymetrical lean.
 
@@
 \section{The Skew-Normal Distribution}
-\label{sec:properties}
+\label{sec:skew-normal}
 
@@
 
+\label{subsec:foundations}
+
 \begin{defn}
@@
   \begin{equation} \label{eq:sn-pdf}
-    f(x|\mu, \sigma, \lambda) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
+    f_Y(x|\mu, \sigma, \lambda) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
   \end{equation}
@@
 The skew-normal was first introduced by \citet{o'hagan} and was most notably
-developed by \citet{azzalini-1985}. Some of its other basic properties, given
-by \citet{pewsey}, are
+developed by \citet{azzalini-1985}. It belongs to a class of skewed
+distributions conforming to the following guidelines:
+
+\begin{lem}
+  \label{lem:azzalini-lemma-1}
+
+  If $f_0$ is a one-dimensional probability density function symmetric about
+  0, and $G$ is a one-dimensional distribution function such that $G'$ exists
+  and is a density symmetric about 0, then
+
+  \begin{equation}
+    \label{eq:azzalini-skewed-distribution}
+    f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
+  \end{equation}
+
+  is a density function for any odd function $w(\cdot)$. (Lemma 1,
+  \citealp{azzalini})
+\end{lem}
+
+In equation \eqref{eq:azzalini-skewed-distribution}, $f_0$ acts as a weighting
+function referred to as a kernel. When $f_0 = \phi$, the distribution is said
+to be generated by the normal kernel. $G$ does not necessarily have to be taken
+from the same distribution as $f_0$; for example, the normal kernel has been
+paired with cdf's from various other distributions, such as Student's t,
+Cauchy, Laplace, and uniform. In the case of our skew-normal, however, both
+$f_0$ and $G$ come from the normal distribution.
+
+The skew-normal's first three moments about the origin (raw moments), given by
+\citet{pewsey}, are
 
@@
 where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}}$.
+\lambda^2}}$. Using these raw moments, we can derive $Var(Y)$:
+
+\begin{align}
+  Var(Y) &= E(Y^2) - [E(Y)]^2 \nonumber \\
+  &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 - (\mu + b \delta \sigma)^2 \nonumber \\
+  &= \cancel{\mu^2} + \cancel{2b \delta \mu \sigma} + \sigma^2 - \cancel{\mu^2} - \cancel{2b \delta \mu \sigma} - b^2 \delta^2 \sigma^2 \nonumber \\
+  &= \sigma^2 - b^2 \delta^2 \sigma^2 \nonumber \\
+  &= \sigma^2 (1 - b^2 \delta^2). \label{eq:sn-variance}
+\end{align}
 
@@
 \begin{equation} \label{eq:standard-sn-pdf}
-  f(x|\lambda) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
+  f_Z(x|\lambda) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
 \end{equation}
@@
 which is the pdf of the normal distribution ($\mu$, $\sigma$). Furthermore,
-when $\lambda > 0$, the curve skews to the left, and when $\lambda < 0$, it
-skews to the right (a property we will prove in section
+when $\lambda > 0$, the curve skews to the right, and when $\lambda < 0$, it
+skews to the left (a property we will prove in section
 \ref{subsec:four-properties}).
@@
 \begin{proof}
-  To prove our result, we begin by examining Lemma 1 in \citet{azzalini}, which
-  we restate here:
+  Lemma \ref{lem:azzalini-lemma-1} from section \ref{subsec:foundations}
+  provides a very useful result for the above defined $f_0$ and $f$, which we
+  restate here as a corollary:
 
-  \begin{helper-lem}
-    If $f_0$ is a one-dimensional probability density function symmetric about
-    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
-    and is a density symmetric about 0, then
+  \begin{cor}[Perturbation Invariance]
+    \label{eq:azzalini-perturbation-invariance}
 
-    \begin{equation}
-      \label{eq:azzalini-perturbation-invariance}
-      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
-    \end{equation}
+    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
+    notation $\overset{d}{=}$ denotes equality in distribution. (Page 161,
+    \citealp{azzalini})
+  \end{cor}
 
-    is a density function for any odd function $w(\cdot)$.
-  \end{helper-lem}
+  Let $X \sim N(0,1)$. Take $f_0 = \phi$, and $G = \Phi$. Then, $f_Z(z) = 2
+  \cdot \phi(z) \cdot \Phi(\lambda z)$ conforms to Equation
+  \eqref{eq:azzalini-skewed-distribution}, and we can conclude that $X$ and $Z$
+  are equal in distribution.
 
-  This lemma is extended by a corollary which gives a very helpful result for
-  the above defined $f_0$ and $f$:
-
-  \begin{helper-cor}[Perturbation Invariance]
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
-    notation $\overset{d}{=}$ denotes equality in distribution.    
-  \end{helper-cor}
-
-  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
-  \Phi(\lambda z)$ conforms to Equation
-  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
-  and $Z$ are equal in distribution.
-
-  We will now show that $\phi^2 \sim \chi^2_1$ by deriving its moment
-  generating function (mgf):\footnote{If $X$ is a random variable, then the
-  expected value $M_X(t) = E(e^{tX})$ is called the moment generating function
-  (mgf) of X if this expected value exists for all values of $t$ in some
-  interval of the form $-h < t < h$ for some $h > 0$. Definition 2.5.1,
-  \citet{textbook}.}
+  We will now show that $X^2 \sim \chi^2_1$ by deriving its moment generating
+  function (mgf):\footnote{If $X$ is a random variable, then the expected value
+  $M_X(t) = E(e^{tX})$ is called the moment generating function (mgf) of X if
+  this expected value exists for all values of $t$ in some interval of the form
+  $-h < t < h$ for some $h > 0$. Definition 2.5.1, \citet{textbook}.}
 
   \begin{align*}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \\
+    M_{X^2}(t) &= E[e^{tX^2}] \\
     &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
@@
 
-  On $A_1$: $y = -x \Ra x = -y$ and the Jacobian $\J = \left| \frac{dx}{dy}
-  \right| = |-1| = 1$, yielding
+  On $A_1$: $y = -x \Ra x = -y$, and the absolute value of the Jacobian $|\J| =
+  \left| \frac{dx}{dy} \right| = |-1| = 1$, yielding
 
   \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
+    f_Y(y) &= f_X(x) \cdot |\J| \\
     &= f_X(-y) \cdot 1 \\
@@
 
-  Similarly, on $A_2$: $y = x \Ra x = y$ and the Jacobian $\J = \left|
-  \frac{dx}{dy} \right| = |1| = 1$, yielding
+  Similarly, on $A_2$: $y = x \Ra x = y$, and the absolute value of the
+  Jacobian $|\J| = \left| \frac{dx}{dy} \right| = |1| = 1$, yielding
 
   \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
+    f_Y(y) &= f_X(x) \cdot |\J| \\
     &= f_X(y) \cdot 1 \\
@@
 
-  On $A_3$, we have $x = 0 \Ra y = 0$ and Jacobian $\J = \left| \frac{dx}{dy}
-  \right| = |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
+  On $A_3$, we have $x = 0 \Ra y = 0$, and the absolute value of the Jacobian
+  $|\J| = \left| \frac{dx}{dy} \right| = |0| = 0$, yielding $f_Y(y) = f_X(x)
+  \cdot |\J| = f_X(x) \cdot 0 = 0$.
 
@@
 estimates for $\mu$, $\sigma$, and $\lambda$ using the method of moments, that
-is, by comparing the first, second, and third moments about the mean (also
-referred to as central moments) of $B$ and $Y$.
+is, by comparing the first, second, and third moments about the mean (central
+moments) of $B$ and $Y$.
 
-\subsection{The Moments of the Binomial Distribution}
+\subsection{The Central Moments of the Binomial Distribution}
 
-Let's start with the binomial. The first two central moments are simply the
-mean and variance, which we can state from memory:
+The first two central moments of the binomial are simply the mean and variance:
 
@@
 
-Having these, we can easily find $E(B^2)$: Recall that $Var(B) = E(B^2) -
-[E(B)]^2$ and thus
+From these facts, we can find $E(B^2)$: Recall that $Var(B) = E[(B - E(B))^2] =
+E(B^2) - [E(B)]^2$ and thus
 
 \begin{equation*}
-  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2,
+  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2.
 \end{equation*}
-
-a fact we will need for the third central moment.
 
@@
 
-\begin{align*}
-  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \;; \\
-  \intertext{notice that the first three terms of this sum are zero, so we can rewrite our sum beginning at $x = 3$:}
-  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \\
+\begin{align}
+  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\}. \nonumber \\
+  \intertext{Notice that the first three terms of the sum on the right hand side are zero, so we can rewrite it beginning at $x = 3$:}
+  E[B(B-1)(B-2)] &= \sum_{x=3}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\}. \nonumber \\
+  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \nonumber \\
+  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \nonumber \\
+  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \nonumber \\
   \intertext{let $y=x-3$; then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$:}
-  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \\
-  &= n(n-1)(n-2)p^3 \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 \;; \\
-  \intertext{We now expand the left side of the previous equation and solve for $E(B^3)$:}
-  E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\
-  E(B^3) - 3E(B^2) + 2E(B) &= \\
-  E(B^3) - 3(np - np^2 + n^2p^2) + 2np &= \\
-  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 + 3np - 3np^2 + 3n^2p^2 - 2np \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np.
-\end{align*}
+  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \nonumber \\
+  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \nonumber \\
+  &= n(n-1)(n-2)p^3 \nonumber \\
+  &= n^3p^3 - 3n^2p^3 + 2np^3. \label{eq:binomial-third-moment-rhs}
+\end{align}
 
-Now, finally, we have all the building blocks necessary to obtain the third
-central moment:
+Here we take a moment to expand the left side of the previous equation:
+
+\begin{align}
+  E[B(B-1)(B-2)] &= E \left[ B^3 - 3B^2 + 2B \right] \nonumber \\
+  &= E(B^3) - 3E(B^2) + 2E(B) \nonumber \\
+  &= E(B^3) - 3(np - np^2 + n^2p^2) + 2np \nonumber \\
+  &= E(B^3) - 3np + 3np^2 - 3n^2p^2 + 2np \nonumber \\
+  &= E(B^3) + 3np^2 - 3n^2p^2 - np. \label{eq:binomial-third-moment-lhs}
+\end{align}
+
+Since \eqref{eq:binomial-third-moment-rhs} and
+\eqref{eq:binomial-third-moment-lhs} are equal to each other, we can solve for
+$E(B^3)$:
+
+\begin{align}
+  E(B^3) + 3np^2 - 3n^2p^2 - np &= n^3p^3 - 3n^2p^3 + 2np^3 \nonumber \\
+  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np. \label{eq:binomial-third-moment}
+\end{align}
+
+Now, finally, we have all the information necessary to obtain the third central
+moment:
 
@@
 
-\subsection{The Moments of the Skew Normal Distribution}
+\subsection{The Central Moments of the Skew Normal Distribution}
 
-Now we'll take a look at the skew normal. Equation
-\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
-third central moment is a little more complicated:
+Now we'll take a look at the skew normal. Equations
+\eqref{eq:sn-moments-about-origin} and \eqref{eq:sn-variance} takes care of the
+mean and variance; again the third central moment is a little more complicated:
 
@@
 Now comes the time to justify our efforts by comparing the accuracy of our
-skew-normal approximation to that of the normal. Naturally, we are primarily
-interested in cases where the normal approximation performs poorly, that is
-binomials where $n$ is small and $p$ is either close to 0 or 1.\footnotemark
+skew-normal approximation to that of the normal.
+
+We are naturally most interested in cases where other solutions perform poorly.
+Recall that when $n$ is small, it is feasible to execute the binomial
+calculations directly, and when $n$ is large or $p$ is close to 0.5, the normal
+distribution provides an adequate approximation. Therefore, our interest is
+primarily in cases where $n$ is moderate and $p$ is extreme (close to 0 or
+1).\footnotemark
 
@@
 \ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
-normal, and skew-normal at small values of $p$ for $n=25$, $n=50$, and $n=100$,
-respectively.
+normal, and skew-normal at small values of $p=0.05$, $p=0.1$, and $p=0.2$ for
+each of $n=25$, $n=50$, and $n=100$, respectively.
 
-At very small $n$ and $p$, our skew-normal curve follows the shape of the
-binomial much more closely than the normal. However, as $n$ grows, the Central
-Limit Theorem begins to exert its effect; even at a moderate $n = 100$ and a
-smallish $p = 0.2$, the normal and skew-normal become nearly identical. Thus,
-as we would expect, the skew-normal method is most valuable at small $n$ and
-extreme $p$.
+The graphs in figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
+\ref{fig:comparison-n100} indicate that at moderate $n$ and small $p$, our
+skew-normal curve follows the shape of the binomial much more closely than the
+normal. As $n$ grows for each value of $p$, however, the Central Limit Theorem
+begins to exert its effect and the normal distribution "catches up" in
+accuracy, slowly for for more extreme values of $p$ and faster as $p$
+approaches 0.5. Thus as we would expect, the skew-normal approximation is of
+greatest value when $n$ is moderate and $p$ is extreme.
 
@@
 
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
-\ref{app:figures} shows the MABS of the skew-normal and normal approximations
-as a function of $p$ and $n$, respectively. Again, the skew-normal outperforms
-the normal considerably in the extreme ranges, with the two approximations
-converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.
+Figure \ref{fig:mabs-fixed-n} in appendix \ref{app:figures} shows the MABS of
+the skew-normal and the normal approximations as a function of $p$ for $n=25$
+and $n=100$. When $p$ is very close to 0, the MABS of the normal approximation
+is more than four times that of the skew-normal, again demonstrating the
+benefit of using the skew-normal approximation for moderate $n$ and extreme
+$p$. The two error curves converge and eventually meet as $p$ approaches 0.5.
+
+Figure \ref{fig:mabs-fixed-p}, on the other hand, shows the MABS of our two
+approximations as a function of $n$ for $p=0.05$ and $p=0.1$. At small to
+moderate $n$, the normal MABS is roughly six times the skew-normal MABS.
+Interestingly, the error curves converge much more slowly this time, leading to
+the pleasant (if surprising) conclusion that when $p$ is extreme, the
+skew-normal gains us a measure of accuracy even at large $n$.
 
@@
 \clearpage
+
 \bibliography{bibliography.bib}

### 2011-02-13 project/presentation/method-of-moments.tex
First draft roughly finished

--- 2011-02-12 project/paper/paper.tex
@@
-\documentclass{article}
-\usepackage{jcapstone}
-\begin{document}
+% Method of Moments
 
-\title{The Skew-Normal Approximation of the Binomial Distribution}
-\author{Joyce Tipping}
-\date{2010}
-\maketitle
-
-\title{The Skew-Normal Approximation of the Binomial Distribution}
-\author{Joyce Tipping}
-\date{2010}
-\maketitle
-
-\section{Introduction}
-
-One of the most basic distributions in probability and statistics is the
-binomial, $X \sim Bin(n,p)$, $n = 1, 2, \ldots$, $p \in (0, 1)$ with
-probability density function (pdf)
-
-\begin{equation*}
-  f_X(x) = \binom{n}{x} p^x q^{n-x}, \quad x = 0, 1, \ldots, n,
-\end{equation*}
-
-where $q=1-p$. Calculating the binomial cumulative distribution function (cdf),
-$F_X(x) = P(X \leq x) = \sum_{k=0}^x f_X(k)$, by hand is manageable for small
-$n$ but quickly becomes cumbersome as $n$ grows even moderately large. A common
-strategy is to use the normal distribution\footnotemark as an approximation:
-
-\footnotetext{A random variable $X$ follows the normal distribution with mean
-$\mu$ and variance $\sigma^2$ (denoted $X \sim N(\mu,\sigma^2)$) if it has the
-pdf $f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \;
-e^{-[(x-\mu)/\sigma]^2/2}$ for $-\infty < x < \infty$, where $-\infty < \mu <
-\infty$ and $0 < \sigma < \infty$.
-
-$N(0,1)$ is an important special case known as the standard normal (denoted
-$Z$) and has pdf $\phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty
-< z < \infty$ and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.
-Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}
-
-\begin{equation}
-  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right),
-\end{equation}
-
-where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
-\sqrt{np(1-p)}$.
-
-This approximation works best when the binomial is perfectly symmetrical, with
-$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
-becomes increasingly skewed, and one must either provide larger values of $n$
-to compensate or face growing inaccuracy.
-
-To protect against these cases, many textbooks impose a condition on the normal
-approximation, often stated as either (1) $np(1-p) > 9$ \; or \; (2) $np > 5$
-for $0 < p \leq 0.5$, and $n(1-p) > 5$ for $0.5 < p < 1$. However, \citet{mabs}
-show that even when these conditions are met, the inaccuracy of the normal
-approximation can be surprisingly large. So, the natural question arises: Can
-we do better?
-
-Perhaps so. Intuitively speaking, the main problem with the normal
-approximation is that the normal is always symmetric while the binomial is
-skewed for all values of $p$ not equal to 0.5. This fact suggests using the
-skew-normal distribution, which adds an extra parameter to capture an
-asymetrical lean.
-
-In this paper, we will explore the aptness of the skew-normal as a method of
-approximating the binomial. First, we'll acquaint ourselves with its basic
-properties (section \ref{sec:skew-normal}). We'll then derive an approximation
-via the method of moments (section \ref{sec:method-of-moments}) and compare its
-accuracy to that of the normal approximation (section \ref{sec:accuracy}).
-Finally, we will leave the reader with a few practical resources for applying
-our new method (section \ref{sec:resources}).
-
-\section{The Skew-Normal Distribution}
-\label{sec:skew-normal}
-
-The skew-normal distribution is similar to the normal but with an added
-parameter for skew that allows it to lean to the left or right. In this
-section, we'll get to know some of its basic properties.
-
-\subsection{Foundations}
-
-\label{subsec:foundations}
-
-\begin{defn}
-  Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
-  scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$; we will
-  denote it $SN(\mu, \sigma, \lambda)$.\footnotemark Then $Y$ has pdf
-
-  \begin{equation} \label{eq:sn-pdf}
-    f_Y(x|\mu, \sigma, \lambda) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
-  \end{equation}
-
-  where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal
-  cdf. \citet{main}
-
-  \footnotetext{In this paper, we have followed the notation established by
-  \citet{main} in naming our parameters $\mu$, $\sigma$, and $\lambda$. It does
-  seem intuitive, after all, for the skew-normal to simply "extend" the normal
-  with an extra parameter.
-
-  An unfortunate consequence of this choice, however, is the misconception that
-  $\mu$ and $\sigma$ are related to the mean and variance the way they are in
-  the normal distribution. In the case of the skew-normal, it is more
-  productive to think of them as abstract location and scale parameters. In
-  fact, a quick comparison of figures \ref{fig:comparison-n25},
-  \ref{fig:comparison-n50}, and \ref{fig:comparison-n100} and the corresponding
-  parameters in Table \ref{tab:sn-approx-table} shows that $\mu$ and $\sigma$
-  are not visually related to the curve in any intuitive way.}
-\end{defn}
-
-The skew-normal was first introduced by \citet{o'hagan} and was most notably
-developed by \citet{azzalini-1985}. It belongs to a class of skewed
-distributions conforming to the following guidelines:
-
-\begin{lem}
-  \label{lem:azzalini-lemma-1}
-
-  If $f_0$ is a one-dimensional probability density function symmetric about
-  0, and $G$ is a one-dimensional distribution function such that $G'$ exists
-  and is a density symmetric about 0, then
-
-  \begin{equation}
-    \label{eq:azzalini-skewed-distribution}
-    f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
-  \end{equation}
-
-  is a density function for any odd function $w(\cdot)$. (Lemma 1,
-  \citealp{azzalini})
-\end{lem}
-
-In equation \eqref{eq:azzalini-skewed-distribution}, $f_0$ acts as a weighting
-function referred to as a kernel. When $f_0 = \phi$, the distribution is said
-to be generated by the normal kernel. $G$ does not necessarily have to be taken
-from the same distribution as $f_0$; for example, the normal kernel has been
-paired with cdf's from various other distributions, such as Student's t,
-Cauchy, Laplace, and uniform. In the case of our skew-normal, however, both
-$f_0$ and $G$ come from the normal distribution.
-
-The skew-normal's first three moments about the origin (raw moments), given by
-\citet{pewsey}, are
-
-\begin{align}
-  E(Y) &= \mu + b \delta \sigma, \nonumber \\
-  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-moments-about-origin} \\
-  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber
-\end{align}
-
-where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}}$. Using these raw moments, we can derive $Var(Y)$:
-
-\begin{align}
-  Var(Y) &= E(Y^2) - [E(Y)]^2 \nonumber \\
-  &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 - (\mu + b \delta \sigma)^2 \nonumber \\
-  &= \cancel{\mu^2} + \cancel{2b \delta \mu \sigma} + \sigma^2 - \cancel{\mu^2} - \cancel{2b \delta \mu \sigma} - b^2 \delta^2 \sigma^2 \nonumber \\
-  &= \sigma^2 - b^2 \delta^2 \sigma^2 \nonumber \\
-  &= \sigma^2 (1 - b^2 \delta^2). \label{eq:sn-variance}
-\end{align}
-
-The $SN(0,1,\lambda)$ distribution is called the standard skew-normal; its pdf
-is
-
-\begin{equation} \label{eq:standard-sn-pdf}
-  f_Z(x|\lambda) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
-\end{equation}
-
-Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
-= \sigma Z + \mu$.
-
-A natural question to ask is how the skew-normal relates to the normal.
-Fortunately, the connection is very intuitive: When $\lambda = 0$, Equation
-\eqref{eq:sn-pdf} becomes
-
-\begin{align*}
-  f(x|\mu, \sigma, \lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
-  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
-  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
-  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
-  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
-\end{align*}
-
-which is the pdf of the normal distribution ($\mu$, $\sigma$). Furthermore,
-when $\lambda > 0$, the curve skews to the right, and when $\lambda < 0$, it
-skews to the left (a property we will prove in section
-\ref{subsec:four-properties}).
-
-\subsection{Properties of the Standard Skew-Normal Distribution}
-\label{subsec:four-properties}
-
-The following four properties of the standard skew-normal, given by
-\citet{main}, help shed light on our enigmatic new distribution:
-
-\begin{property} \label{prop:1}
-  If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
-\end{property}
-
-\begin{proof}
-  The standard normal pdf is an even function: $\phi(-x) =
-  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
-  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) = \int_{-\infty}^x
-  \phi(t)\;dt$, \thinspace is not even, approaching 0 as $x \to -\infty$ and
-  approaching 1 as $x \to \infty$. Thus,
-
-  \begin{align*}
-    f_{(-Z)}(x) &= f_Z(-x) \\
-    & = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\
-    & = 2 \cdot \phi(x) \cdot \Phi (-\lambda x),
-  \end{align*}
-
-  which is the pdf of $SN(0, 1, -\lambda)$.
-\end{proof}
-
-\begin{property} \label{prop:2}
-  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
-\end{property}
-
-\begin{proof}
-  Lemma \ref{lem:azzalini-lemma-1} from section \ref{subsec:foundations}
-  provides a very useful result for the above defined $f_0$ and $f$, which we
-  restate here as a corollary:
-
-  \begin{cor}[Perturbation Invariance]
-    \label{eq:azzalini-perturbation-invariance}
-
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
-    notation $\overset{d}{=}$ denotes equality in distribution. (Page 161,
-    \citealp{azzalini})
-  \end{cor}
-
-  Let $X \sim N(0,1)$. Take $f_0 = \phi$, and $G = \Phi$. Then, $f_Z(z) = 2
-  \cdot \phi(z) \cdot \Phi(\lambda z)$ conforms to Equation
-  \eqref{eq:azzalini-skewed-distribution}, and we can conclude that $X$ and $Z$
-  are equal in distribution.
-
-  We will now show that $X^2 \sim \chi^2_1$ by deriving its moment generating
-  function (mgf):\footnote{If $X$ is a random variable, then the expected value
-  $M_X(t) = E(e^{tX})$ is called the moment generating function (mgf) of X if
-  this expected value exists for all values of $t$ in some interval of the form
-  $-h < t < h$ for some $h > 0$. Definition 2.5.1, \citet{textbook}.}
-
-  \begin{align*}
-    M_{X^2}(t) &= E[e^{tX^2}] \\
-    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \;; \\
-    \intertext{let $u = (\sqrt{1-2t}) \, x$; then $du = (\sqrt{1-2t}) \, dx$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty, x \to \infty \Ra
-      u \to -\infty, u \to \infty$:}
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} du \right) \\
-    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
-      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
-    &= \frac{1}{\sqrt{1-2t}} \;,
-  \end{align*}
-
-  which is the mgf of the $\chi^2_1$. Since $Z$ is equal in distribution to
-  $X$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
-
-\begin{property} \label{prop:3}
-  As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
-\end{property}
-
-To prove our theorem, it is helpful to formally define the half normal distribution:
-
-\begin{helper-lem} \label{lem:p2-half-normal}
-  Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal
-  random variable with parameter $\sigma$ and
-
-  \begin{equation*}
-    f_{|X|}(x) =
-    \begin{dcases*}
-      0              & when $-\infty < x \leq 0$ \\
-      2 \cdot f_X(x) & when $0 < x < \infty$ 
-    \end{dcases*}
-    .
-  \end{equation*}
-\end{helper-lem}
-
-\begin{proof}
-  Let $X \sim N(0, \sigma^2)$, defined over $A = (-\infty, \infty)$. Define
-
-  \begin{equation*}
-    Y = |X| =
-    \begin{dcases*}
-      -x & if $x < 0$ \\
-      0 & if $x = 0$ \\
-      x & if $x > 0$ \\
-    \end{dcases*}
-    .
-  \end{equation*}
-
-  $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
-  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such
-  that $A = A_1 \cup A_2 \cup A_3$ and $Y$ is one-to-one over each $A_i$. We
-  can then transform each piece separately using Theorem 6.3.2 from
-  \citet{textbook}:\footnote{\textbf{Continuous transformations that are
-  one-to-one}: Suppose that $X$ is a continuous random variable with pdf
-  $f_X(x)$, and assume that $Y = u(X)$ defines a one-to-one transformation from
-  $A = \{x|f_X(x) > 0\}$ on to $B = \{y|f_Y(y) > 0\}$ with inverse
-  transformation $x = w(y)$. If the derivative $(d/dy)w(y)$ is continuous and
-  nonzero on $B$, then the pdf of $Y$ is
-
-  \begin{equation}
-    \label{eq:transformations-1-to-1}
-    f_Y(y) = f_X(w(y)) \left| \frac{d}{dy} w(y) \right| \qquad y \in B.
-  \end{equation}
-
-  Theorem 6.3.2, \citet{textbook}.
-  \label{fnote:transformations-1-to-1}
-  }
-
-  On $A_1$: $y = -x \Ra x = -y$, and the absolute value of the Jacobian $|\J| =
-  \left| \frac{dx}{dy} \right| = |-1| = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot |\J| \\
-    &= f_X(-y) \cdot 1 \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma^2}} \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma^2}} \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_1: -\infty < x < 0 \Ra -\infty < -y < 0 \Ra 0 < y < \infty :B_1$.
-
-  Similarly, on $A_2$: $y = x \Ra x = y$, and the absolute value of the
-  Jacobian $|\J| = \left| \frac{dx}{dy} \right| = |1| = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot |\J| \\
-    &= f_X(y) \cdot 1 \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_2: 0 < x < \infty \Ra 0 < y < \infty :B_2$.
-
-  On $A_3$, we have $x = 0 \Ra y = 0$, and the absolute value of the Jacobian
-  $|\J| = \left| \frac{dx}{dy} \right| = |0| = 0$, yielding $f_Y(y) = f_X(x)
-  \cdot |\J| = f_X(x) \cdot 0 = 0$.
-
-  Then, by Equation 6.3.10 from \citet{textbook},\footnote{\textbf{Continuous
-  transformations that are not one-to-one}: When $u(x)$ is not one-to-one over
-  $A$, we can replace equation \eqref{eq:transformations-1-to-1} in footnote
-  \ref{fnote:transformations-1-to-1} with
-
-  \begin{equation*}
-    f_Y(y) = \sum_j f_X(w_j(y)) \left| \frac{d}{dy} w_j(y) \right|.
-  \end{equation*}
-
-  Equation 6.3.10, \citet{textbook}.
-  }
-
-  \begin{align*}
-    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \\
-    &= f_X(y) + f_X(y) \\
-    &= 2 \cdot f_X(y)
-  \end{align*}
-
-  over $B = B_1 \cup B_2 = (0, \infty)$, and 0 otherwise.
-\end{proof}
-
-With Lemma \ref{lem:p2-half-normal}, we can easily show our property:
-
-\begin{proof}[Proof of Property 3]
-  Let $Z \sim SN(0,1,\lambda)$. Recall that $f_Z(x) = 2 \cdot \phi(x) \cdot
-  \Phi(\lambda x)$.
-
-  Consider $\lim_{\lambda \to \infty} f_X(x)$. When $x$ is negative, $\lambda x
-  \to -\infty$ and thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however,
-  $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-positive-half-normal}
-    \lim_{\lambda \to \infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      0 & when $x \leq 0$ \\
-      2 \cdot \phi(x) & when $x > 0$
-    \end{dcases*}
-    \eq |N(0,1)|.
-  \end{equation}
-
-  In $\lim_{\lambda \to -\infty} f_X(x)$, the signs are reversed. When $x$ is
-  negative, $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. When $x$ is
-  positive, $\lambda x \to -\infty$ and $\Phi(\lambda x) \to 0$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-negative-half-normal}
-    \lim_{\lambda \to -\infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      2 \cdot \phi(x) & when $x < 0$ \\
-      0 & when $x \geq 0$
-    \end{dcases*}
-    \eq -|N(0,1)|.
-  \end{equation}
-\end{proof}
-
-\begin{property} \label{prop:4}
-  The moment generating function of $SN(0,1,\lambda)$ is
-
-  \begin{equation} \label{eq:p4-sn-mgf}
-    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2},
-  \end{equation}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
-\end{property}
-
-\begin{proof}
-  According to Equation 5 in \citet{azzalini}, the mgf of $SN(\mu, \sigma,
-  \lambda)$ is
-
-  \begin{equation*}
-    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t),
-  \end{equation*}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}} \in (-1, 1)$. It follows
-  that the mgf of the $SN(0, 1, \lambda)$ is
-
-  \begin{equation*}
-    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t).
-  \end{equation*}
-\end{proof}
-
-\section{Developing an Approximation}
-\label{sec:method-of-moments}
-
-Now that we have gotten to know our new distribution a little better, we can
-use it to develop an approximation for the binomial.
-
-Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
-estimates for $\mu$, $\sigma$, and $\lambda$ using the method of moments, that
-is, by comparing the first, second, and third moments about the mean (central
-moments) of $B$ and $Y$.
-
-\subsection{The Central Moments of the Binomial Distribution}
-
-The first two central moments of the binomial are simply the mean and variance:
+%% Deriving an Approximation
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{equation*}
-
-From these facts, we can find $E(B^2)$: Recall that $Var(B) = E[(B - E(B))^2] =
-E(B^2) - [E(B)]^2$ and thus
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{equation*}
-
-We will also need $E(B^3)$, which we will get via the third factorial moment:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{align}
-
-Here we take a moment to expand the left side of the previous equation:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{align}
-
-Since \eqref{eq:binomial-third-moment-rhs} and
-\eqref{eq:binomial-third-moment-lhs} are equal to each other, we can solve for
-$E(B^3)$:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{align}
-
-Now, finally, we have all the information necessary to obtain the third central
-moment:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{align*}
-
-Our hard-earned results, restated for convenience:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{align}
-
-\subsection{The Central Moments of the Skew Normal Distribution}
-
-Now we'll take a look at the skew normal. Equations
-\eqref{eq:sn-moments-about-origin} and \eqref{eq:sn-variance} takes care of the
-mean and variance; again the third central moment is a little more complicated:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{align*}
-
-We restate our results:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{alignat}
-
-\subsection[Solving for mu, sigma, lambda]{Solving for $\mu$, $\sigma$, $\lambda$}
-\label{subsec:solving-for-mu-sigma-lambda}
-
-To derive our approximation, we set the above moments of our two distributions
-equal to each other and, taking $n$ and $p$ as constants, solve for $\mu$,
-$\sigma$ and $\lambda$:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{subequations}
-
-To get $\lambda$, we divide the cube of \eqref{eq:second-moment-set} by the
-square of \eqref{eq:third-moment-set}:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{align}
-
-The above equation \eqref{eq:solving-for-lambda} is a rational expression in
-$\lambda^2$ that can be solved with either a considerable amount of manual
-labor or, more efficiently, with a computer algebra system. Once we have
-$\lambda^2$, then $\lambda$ is simply the positive or negative square root, as
-determined by the sign of $(1-2p)$.
-
-The sign can be explained with a little assistance from Property \ref{prop:3}:
-When $p \to 0$, the binomial shifts its weight towards the smaller values on
-the left and converges toward the positive half normal, which by
-\eqref{eq:p2-positive-half-normal} corresponds to a positive $\lambda$. When $p
-\to 1$, the binomial shifts its weight towards the the larger values on the
-right and converges toward the negative half normal, which by
-\eqref{eq:p2-negative-half-normal} corresponds to a negative $\lambda$. When $p
-= 0.5$, the binomial is symmetric and $\lambda$ is 0, eliminating the need for
-a sign. Thus:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{equation}
-
-Having secured $\lambda$, we can find $\sigma$ using
-\eqref{eq:second-moment-set}:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{equation}
-
-And with both $\lambda$ and $\sigma$, a simple rearrangement of
-\eqref{eq:first-moment-set} yields $\mu$:
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   \end{equation}
+}
+\frame{
+  \frametitle{Method of Moments: Deriving an Approximation}
 
@@
   symmetric binomial distribution.
+}
 
-\subsection{Restrictions}
-
-Unfortunately, the skew-normal is also not universally applicable. To obtain an
-estimate for $\lambda$, we must put a few restrictions on $n$ and $p$.
+%% Restrictions
+\frame{
+  \frametitle{Method of Moments: Restrictions}
 
@@
   \end{alignat}
-
-We can see that $g(v)$ is increasing in $v = \frac{1+\lambda^2}{\lambda^2} \geq
-1$. Therefore:
+}
+\frame{
+  \frametitle{Method of Moments: Restrictions}
 
@@
   \end{equation}
-
-which means that the right hand side of \eqref{eq:solving-for-lambda}, which is
-supposed to be equal to the left hand side of \eqref{eq:solving-for-lambda},
-can't ever be less than 1. Unfortunately, it sometimes is; in particular,
-$\frac{np(1-p)}{(1-2p)^2} \to 0$ when $p \to 0$ or $p \to 1$. So if we want a
-solution, we must restrict $n$ and $p$ such that
+}
+\frame{
+  \frametitle{Method of Moments: Restrictions}
 
@@
   \end{align}
-
-Here, two scenarios arise. The first is when we have a fixed $p$ and wish to
-find the minimum $n$ necessary to derive a skew-normal approximation. From
-\eqref{eq:solving-the-restriction}, solving for $n$ is very simple:
+}
+\frame{
+  \frametitle{Method of Moments: Restrictions}
 
@@
   \end{equation}
-
-Figure \ref{fig:sn-restriction-least-n} in appendix \ref{app:figures} shows the
-least sample size required to estimate $\lambda$ as a function of
-$p$.\footnotemark As we would expect, it is larger when $p$ is small and
-rapidly goes to 0 as $p$ approaches 0.5; for example, when $p = 0.01$, $n$ must
-be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a trivial
-requirement to meet.
-
-\footnotetext{Since $Bin(n, p)$ and $Bin(n, 1-p)$ are mirror image curves, it
-is often only necessary to examine either $p \in (0, 0.5)$ or $p \in (0.5, 1)$.
-We will usually consider the former range of $p$'s. \label{fnote:half-p-range}}
-
-The second scenario, primarily of academic interest, is when $n$ is fixed and
-we wish to solve for $p$. In this case, we return to
-\eqref{eq:solving-the-restriction} for further factoring:
+}
+\frame{
+  \frametitle{Method of Moments: Restrictions}
 
@@
   \end{equation}
-
-Figure \ref{fig:sn-restriction-p-range} in appendix \ref{app:figures} shows
-this range as a function of $n$, this interval grows quickly as $n$ increases,
-and for sufficiently large $n$, it becomes almost $(0, 1)$. For example, when
-$n=100$, our interval is $(0.00971, 0.99029)$; when $n=500$, it is (0.00199,
-0.99801).
-
-Although the presence of these restrictions are somewhat disappointing, we can
-console ourselves with the observation that at the same $n$ and $p$, the
-skew-normal yields substantially more accurate approximations than the normal
-(see section \ref{subsec:mabs}). Thus while imperfect, it is nevertheless an
-improvement.
-
-\section{Demonstrating Improved Accuracy}
-\label{sec:accuracy}
-
-Now comes the time to justify our efforts by comparing the accuracy of our
-skew-normal approximation to that of the normal.
-
-We are naturally most interested in cases where other solutions perform poorly.
-Recall that when $n$ is small, it is feasible to execute the binomial
-calculations directly, and when $n$ is large or $p$ is close to 0.5, the normal
-distribution provides an adequate approximation. Therefore, our interest is
-primarily in cases where $n$ is moderate and $p$ is extreme (close to 0 or
-1).\footnotemark
-
-\footnotetext{Again, we examine only $p \in (0, 0.5)$. (See footnote
-\ref{fnote:half-p-range}.)}
-
-\subsection{Visual Comparison}
-
-The first and most obvious way of judging accuracy is by visual inspection.
-Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
-\ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
-normal, and skew-normal at small values of $p=0.05$, $p=0.1$, and $p=0.2$ for
-each of $n=25$, $n=50$, and $n=100$, respectively.
-
-The graphs in figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
-\ref{fig:comparison-n100} indicate that at moderate $n$ and small $p$, our
-skew-normal curve follows the shape of the binomial much more closely than the
-normal. As $n$ grows for each value of $p$, however, the Central Limit Theorem
-begins to exert its effect and the normal distribution "catches up" in
-accuracy, slowly for for more extreme values of $p$ and faster as $p$
-approaches 0.5. Thus as we would expect, the skew-normal approximation is of
-greatest value when $n$ is moderate and $p$ is extreme.
-
-\subsection{Maximal Absolute Error}
-\label{subsec:mabs}
-
-Another more quantitative method of judging accuracy is comparing the maximal
-absolute errors of our two approximations, defined by \citet{mabs} as
-
-\begin{equation}
-  \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
-\end{equation}
-
-where $F_{B(n,p)}$ is the cdf of the binomial and $F_{\textnormal{appr}(n,p)}$
-is the cdf of either the normal or skew-normal approximation; the 0.5 is a
-continuity correction.
-
-Figure \ref{fig:mabs-fixed-n} in appendix \ref{app:figures} shows the MABS of
-the skew-normal and the normal approximations as a function of $p$ for $n=25$
-and $n=100$. When $p$ is very close to 0, the MABS of the normal approximation
-is more than four times that of the skew-normal, again demonstrating the
-benefit of using the skew-normal approximation for moderate $n$ and extreme
-$p$. The two error curves converge and eventually meet as $p$ approaches 0.5.
-
-Figure \ref{fig:mabs-fixed-p}, on the other hand, shows the MABS of our two
-approximations as a function of $n$ for $p=0.05$ and $p=0.1$. At small to
-moderate $n$, the normal MABS is roughly six times the skew-normal MABS.
-Interestingly, the error curves converge much more slowly this time, leading to
-the pleasant (if surprising) conclusion that when $p$ is extreme, the
-skew-normal gains us a measure of accuracy even at large $n$.
-
-\section{Practical Resources}
-\label{sec:resources}
-
-We conclude our dicussion by offering the reader a few practical resources:
-
-Table \ref{tab:sn-approx-table} in appendix \ref{app:figures} shows estimations
-of $SN(\mu, \sigma, \lambda)$ for common binomial distributions.
-
-For those with an unusual combination of $n$ and $p$ not in the table, appendix
-\ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
-parameters by hand.
-
-Finally, for rapidly approximating many binomial distributions, the author's
-Python library, which was used to compute all values presented in this paper,
-is freely available online:
-
-\url{http://github.com/joycetipping/skew-normal-capstone/}
-
-\clearpage
-
-\appendix
-\section{Figures}
-\label{app:figures}
+}
+\frame{
+  \frametitle{Method of Moments: Restrictions}
 
@@
   \end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/comparison-n25.png}
-  \caption{Binomial, normal, and skew-normal, $n=25$}
-  \label{fig:comparison-n25}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/comparison-n50.png}
-  \caption{Binomial, normal, and skew-normal, $n=50$}
-  \label{fig:comparison-n50}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/comparison-n100.png}
-  \caption{Binomial, normal, and skew-normal, $n=100$}
-  \label{fig:comparison-n100}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-n.png}
-  \caption{MABS as a function of p}
-  \label{fig:mabs-fixed-n}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-p.png}
-  \caption{MABS as a function of n}
-  \label{fig:mabs-fixed-p}
-\end{figure}
-
-\begin{sidewaystable}
-  \caption{Estimations of $SN(\mu, \sigma, \lambda)$ for $Bin(n,p)$}
-  \centering
-  \renewcommand{\arraystretch}{1.3}
-  \begin{tabular}
-    { r r | r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l }
-    \hline \hline
-    & & \multicolumn{5}{c}{} & \multicolumn{5}{c}{} & \multicolumn{5}{c}{$n$} & \multicolumn{5}{c}{} & \multicolumn{5}{c}{}\\
-    \multirow{20}{*}{$p$} & & \multicolumn{5}{c}{25} & \multicolumn{5}{c}{50} & \multicolumn{5}{c}{100} & \multicolumn{5}{c}{250} & \multicolumn{5}{c}{500} \\
-    \hline
-    & 0.05 & ( & -0.11 & 1.74 & 4.56 & ) & ( & 0.79 & 2.30 & 2.54 & ) & ( & 2.85 & 3.06 & 1.86 & ) & ( & 9.58 & 4.52 & 1.38 & ) & ( & 21.32 & 6.11 & 1.15 & ) \\
-    & 0.10 & ( & 0.89 & 2.20 & 2.31 & ) & ( & 2.97 & 2.94 & 1.74 & ) & ( & 7.44 & 3.94 & 1.40 & ) & ( & 21.53 & 5.88 & 1.10 & ) & ( & 45.62 & 8.01 & 0.94 & ) \\
-    & 0.15 & ( & 2.02 & 2.49 & 1.79 & ) & ( & 5.32 & 3.34 & 1.43 & ) & ( & 12.25 & 4.51 & 1.19 & ) & ( & 33.77 & 6.77 & 0.96 & ) & ( & 70.30 & 9.27 & 0.82 & ) \\
-    & 0.20 & ( & 3.23 & 2.67 & 1.50 & ) & ( & 7.76 & 3.61 & 1.24 & ) & ( & 17.18 & 4.89 & 1.04 & ) & ( & 46.18 & 7.39 & 0.85 & ) & ( & 95.18 & 10.16 & 0.74 & ) \\
-    & 0.25 & ( & 4.49 & 2.79 & 1.29 & ) & ( & 10.28 & 3.78 & 1.09 & ) & ( & 22.20 & 5.15 & 0.93 & ) & ( & 58.71 & 7.83 & 0.76 & ) & ( & 120.22 & 10.80 & 0.67 & ) \\
-    & 0.30 & ( & 5.80 & 2.85 & 1.12 & ) & ( & 12.86 & 3.88 & 0.95 & ) & ( & 27.31 & 5.32 & 0.82 & ) & ( & 71.34 & 8.12 & 0.68 & ) & ( & 145.39 & 11.24 & 0.60 & ) \\
-    & 0.35 & ( & 7.17 & 2.86 & 0.96 & ) & ( & 15.50 & 3.92 & 0.83 & ) & ( & 32.49 & 5.39 & 0.72 & ) & ( & 84.09 & 8.28 & 0.60 & ) & ( & 170.70 & 11.50 & 0.53 & ) \\
-    & 0.40 & ( & 8.59 & 2.83 & 0.80 & ) & ( & 18.23 & 3.89 & 0.70 & ) & ( & 37.76 & 5.39 & 0.61 & ) & ( & 96.96 & 8.32 & 0.51 & ) & ( & 196.18 & 11.60 & 0.45 & ) \\
-    & 0.45 & ( & 10.12 & 2.73 & 0.61 & ) & ( & 21.08 & 3.79 & 0.53 & ) & ( & 43.21 & 5.29 & 0.47 & ) & ( & 110.07 & 8.23 & 0.40 & ) & ( & 221.93 & 11.54 & 0.35 & ) \\
-    & 0.50 & ( & 12.50 & 2.50 & 0.00 & ) & ( & 25.00 & 3.54 & 0.00 & ) & ( & 50.00 & 5.00 & 0.00 & ) & ( & 125.00 & 7.91 & 0.00 & ) & ( & 250.00 & 11.18 & 0.00 & ) \\
-    & 0.55 & ( & 14.88 & 2.73 & -0.61 & ) & ( & 28.92 & 3.79 & -0.53 & ) & ( & 56.79 & 5.29 & -0.47 & ) & ( & 139.93 & 8.23 & -0.40 & ) & ( & 278.07 & 11.54 & -0.35 & ) \\
-    & 0.60 & ( & 16.41 & 2.83 & -0.80 & ) & ( & 31.77 & 3.89 & -0.70 & ) & ( & 62.24 & 5.39 & -0.61 & ) & ( & 153.04 & 8.32 & -0.51 & ) & ( & 303.82 & 11.60 & -0.45 & ) \\
-    & 0.65 & ( & 17.83 & 2.86 & -0.96 & ) & ( & 34.50 & 3.92 & -0.83 & ) & ( & 67.51 & 5.39 & -0.72 & ) & ( & 165.91 & 8.28 & -0.60 & ) & ( & 329.30 & 11.50 & -0.53 & ) \\
-    & 0.70 & ( & 19.20 & 2.85 & -1.12 & ) & ( & 37.14 & 3.88 & -0.95 & ) & ( & 72.69 & 5.32 & -0.82 & ) & ( & 178.66 & 8.12 & -0.68 & ) & ( & 354.61 & 11.24 & -0.60 & ) \\
-    & 0.75 & ( & 20.51 & 2.79 & -1.29 & ) & ( & 39.72 & 3.78 & -1.09 & ) & ( & 77.80 & 5.15 & -0.93 & ) & ( & 191.29 & 7.83 & -0.76 & ) & ( & 379.78 & 10.80 & -0.67 & ) \\
-    & 0.80 & ( & 21.77 & 2.67 & -1.50 & ) & ( & 42.24 & 3.61 & -1.24 & ) & ( & 82.82 & 4.89 & -1.04 & ) & ( & 203.82 & 7.39 & -0.85 & ) & ( & 404.82 & 10.16 & -0.74 & ) \\
-    & 0.85 & ( & 22.98 & 2.49 & -1.79 & ) & ( & 44.68 & 3.34 & -1.43 & ) & ( & 87.75 & 4.51 & -1.19 & ) & ( & 216.23 & 6.77 & -0.96 & ) & ( & 429.70 & 9.27 & -0.82 & ) \\
-    & 0.90 & ( & 24.11 & 2.20 & -2.31 & ) & ( & 47.03 & 2.94 & -1.74 & ) & ( & 92.56 & 3.94 & -1.40 & ) & ( & 228.47 & 5.88 & -1.10 & ) & ( & 454.38 & 8.01 & -0.94 & ) \\
-    & 0.95 & ( & 25.11 & 1.74 & -4.56 & ) & ( & 49.21 & 2.30 & -2.54 & ) & ( & 97.15 & 3.06 & -1.86 & ) & ( & 240.42 & 4.52 & -1.38 & ) & ( & 478.68 & 6.11 & -1.15 & ) \\
-  \end{tabular}
-  \label{tab:sn-approx-table}
-\end{sidewaystable}
-
-\clearpage
-\section{Calculating a Skew-Normal Approximation}
-\label{app:calc-sn-approx}
-
-Although easier with a computer program, calculating estimates for $\mu$,
-$\sigma$, and $\lambda$ by hand is perfectly possible. Here, we will
-demonstrate using $n=25$, $p=0.1$.
-
-By far the largest battle is finding $\lambda$. We will use Equation
-\eqref{eq:solving-for-lambda} but with the simplified left hand side given by
-\eqref{eq:lhs-solving-for-lambda}:
-
-\begin{equation}
-  \label{eq:calculating-lambda}
-  \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = \frac{np(1-p)}{(1-2p)^2} \;.
-\end{equation}
-
-The closed-formed solution to this equation is long, hideous, and hard to work
-with, so for this demonstration, we will take a numerical approach.
-
-The left hand side of \eqref{eq:calculating-lambda} is a function of lambda;
-let us denote it $f(\lambda)$. The right hand side is a constant in $n$ and
-$p$; let us call it $k_{n,p}$. Our goal is to find a value of $\lambda$ such
-that $f(\lambda)$ is within a certain margin of error, $e$, of $k_{n,p}$. Since
-we are computing by hand, we will take $e$ to be a modest 0.01.
-
-Recall that the sign of $\lambda$ is determined independently of the value. In
-fact, $f$ is never affected by the sign of $\lambda$, as all terms are squared.
-Thus, we can restrict our search for $\lambda$ to the interval $(0, \infty)$.
-
-Next, by taking $f$'s derivative, we can show that it is monotonically
-decreasing for positive $\lambda$:
-
-\begin{align*}
-  \frac{d}{d\lambda} \left[ \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) \right] &= \left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot
-    3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2 \cdot \left( \frac{2\lambda}{\lambda^2} - \frac{2(1+\lambda^2)}{\lambda^3} \right) \\
-  &= \left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot 3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2 \cdot
-    \left( \cancel{\frac{2}{\lambda}} - \frac{2}{\lambda^3} - \cancel{\frac{2}{\lambda}} \right) \\
-  &= \underbrace{\left( \frac{\pi^3}{2(4-\pi)^2} \right) \cdot 3 \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^2}_\textnormal{Always positive} \quad \cdot \quad
-     \underbrace{\left( -\frac{2}{\lambda^3} \right)}_{\mathclap{\textnormal{Negative when $\lambda > 0$}}}.
-\end{align*}
-
-This convenient fact allows us to find lower and upper bounds for $\lambda$ and
-repeatedly bisect our interval until we are within $e$ of $k_{n,p}$.
-
-(For the following calculations, it is helpful to keep in mind that because $f$
-is decreasing in $\lambda$, smaller values of $\lambda$ will produce larger
-values of $f$, and vice versa.)
-
-\begin{enumerate}
-  \item \textit{Find $k_{n,p}$.}
-
-    Our value: $\displaystyle k_{n,p} = \frac{25 \cdot 0.1 \cdot 0.9}{(1 - 2\cdot0.1)^2} = 3.5156$.
-
-  \item \textit{Find $a$ and $b$ such that $f(a) > k_{n,p} > f(b)$.}
-
-    Our values: $a=1$, $b=3$.
-
-  \item \textit{Repeatedly bisect $(a,b)$ until $f(c)$ is within $e$ of $k_{n,p}$.}
-
-    Calculate $c=\frac{a+b}{2}$.
-
-    \begin{itemize}
-      \item If $f(c) \leq k_{n,p} - 0.01$, we need a small value of $c$, so we
-      take our new interval to be $(a, c)$.
-
-      \item If $f(c) \geq k_{n,p} + 0.01$, we need a larger value of $c$, so we
-      take our new interval to be $(c, b)$.
-    \end{itemize}
-
-    Repeat this step until $f(c)$ is within $e$ of $k_{n,p}$, or more precisely
-    $k_{n,p} - 0.01 < f(c) < k_{n,p} + 0.01$.
-
-    The following table shows our iterations:
-
-    \renewcommand{\arraystretch}{1.3}
-    \begin{center}
-      \begin{tabular}{c c c c c c c}
-        Iteration & $a$  & $b$   & $c$    & $f(c)$ & $f(c) \leq k_{n,p} - 0.01$ & $f(c) \geq k_{n,p} + 0.01$ \\
-        \hline
-        1         & 2.00 & 3.000 & 2.5000 & 3.0164 & True                       & False \\
-        2         & 2.00 & 2.500 & 2.2500 & 3.7129 & False                      & True \\
-        3         & 2.25 & 2.500 & 2.3750 & 3.3252 & True                       & False \\
-        4         & 2.25 & 2.375 & 2.3125 & 3.5076 & False                      & False \\
-      \end{tabular}
-    \end{center}
-
-    We take the last value of $c$: 2.3125.
-
-  \item \textit{Find the sign of $(1-2p)$.}
-
-    Our $p = 0.1 \Ra (1 - 2\cdot0.1) = 0.8 \Ra$ positive.
-
-  \item \textit{Final answer: \{sign of $(1-2p)$\}$\lambda$}
-
-    Our final answer: $\lambda = 2.3125$.
-\end{enumerate}
-
-Once we have $\lambda$, we can easily find $\sigma$:
-
-\begin{equation*}
-  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} = \sqrt{\frac{25 \cdot 0.1 \cdot 0.9}{1 - \frac{2}{\pi} \cdot \frac{2.3125^2}{1 + 2.3125^2}}} = 2.2029. \\
-\end{equation*}
-
-And with $\lambda$ and $\sigma$, we can also find $\mu$:
-
-\begin{equation*}
-  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} = 25 \cdot 0.1 - 2.2029 \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{2.3125}{\sqrt{1 + 2.3125^2}} = 0.8867.
-\end{equation*}
-
-\clearpage
-
-\bibliography{bibliography.bib}
-\bibliographystyle{plainnat}
-\end{document}
+}

### 2011-02-13 project/presentation/skew-normal.tex
First draft roughly finished

@@
-%% The Skew-Normal Distribution
+% The Skew-Normal Distribution
 \frame{
@@
   \frametitle{The Skew-Normal Distribution}
-  A few notes:
+  \begin{lem}
+    \label{lem:azzalini-lemma-1}
+
+    If $f_0$ is a one-dimensional probability density function symmetric about
+    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
+    and is a density symmetric about 0, then
+
+    \begin{equation}
+      \label{eq:azzalini-skewed-distribution}
+      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
+    \end{equation}
+
+    is a density function for any odd function $w(\cdot)$. (Lemma 1,
+    \citealp{azzalini})
+  \end{lem}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+
+  \begin{align*}
+    E(Y) &= \mu + b \delta \sigma, \\
+    E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-moments-about-origin} \\
+    E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \\
+    Var(Y) &= \sigma^2 (1 - b^2 \delta^2). \label{eq:sn-variance}
+  \end{align*}
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+
+  The $SN(0,1,\lambda)$ distribution is called the standard skew-normal; its pdf
+  is
+
+  \begin{equation} \label{eq:standard-sn-pdf}
+    f_Z(x|\lambda) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
+  \end{equation}
+
+  Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
+  = \sigma Z + \mu$.
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+
+  \begin{align*}
+    f(x|\mu, \sigma, \lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
+    &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
+    &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
+    &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
+    &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
+  \end{align*}
+
+  which is the pdf of the normal distribution ($\mu$, $\sigma$). Furthermore,
+  when $\lambda > 0$, the curve skews to the right, and when $\lambda < 0$, it
+  skews to the left (a property we will prove in section
+  \ref{subsec:four-properties}).
+}
+\frame{
+  \frametitle{The Skew-Normal Distribution}
+
+  \begin{property} \label{prop:1}
+    If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
+  \end{property}
+
+  \begin{property} \label{prop:2}
+    If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
+  \end{property}
+
+  \begin{property} \label{prop:3}
+    As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
+  \end{property}
+
+  \begin{property} \label{prop:4}
+    The moment generating function of $SN(0,1,\lambda)$ is
+
+    \begin{equation} \label{eq:p4-sn-mgf}
+      M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2},
+    \end{equation}
+
+    where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
+  \end{property}
 }
@@
 }
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}

### 2011-02-14 project/presentation/intro.tex
Presentation roughly done; compiles, need to insert figures.

@@
 %% Introduction
-\frame{
-  \frametitle{Introduction}
+\frame{ \frametitle{Introduction}
   $X \sim Bin(n,p)$ where $0<p<1$ and $n = 1, 2, 3, \ldots$
@@
 }
-\frame{
-  \frametitle{Introduction}
+\frame{ \frametitle{Introduction}
   The binomial cdf is easy to calculate for small $n$ ...
@@
 }
-\frame{
-  \frametitle{Introduction}
+\frame{ \frametitle{Introduction}
   When $n=3$,
@@
 }
-\frame{
-  \frametitle{Introduction}
+\frame{ \frametitle{Introduction}
   Normal Approximation of the Binomial:
@@
 }
-\frame{
-  \frametitle{Introduction}
+\frame{ \frametitle{Introduction}
 
@@
 %% Outline
-\frame{
-  \frametitle{Outline}
+\frame{ \frametitle{Outline}
   What we're going to cover:

### 2011-02-14 project/presentation/method-of-moments.tex
Presentation roughly done; compiles, need to insert figures.

@@
 
-%% Deriving an Approximation
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
+\frame{ \frametitle{Method of Moments: Overview}
+  Game plan:
+  \begin{enumerate}[<+->]
+    \item Find the first three central moments of the binomial and the first
+          three central moments of the skew-normal.\\
+          \vsep         
+          What are central moments?: $E(X)$, $E([X - E(X)]^2)$, $E([X -
+          E(X)]^3)$.
+    \item Set them equal to each other.
+    \item Take $n$ and $p$ to be constants; solve for $\mu$, $\sigma$, and $\lambda$.
+  \end{enumerate}
+}
 
-  \begin{equation*}
-    E(B) = np, \quad Var(B) = np(1-p).
-  \end{equation*}
+%% The Central Moments of the Binomial
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  The first two are easy:
+  \begin{align*}
+    E(B) &= np \\
+    E([B - E(B)]^2) &= Var(B) = np(1-p)
+  \end{align*}
 }
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  The third one takes some elbow grease.
 
-  \begin{equation*}
-    E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2.
-  \end{equation*}
+  First we'll need to find $E(B^2)$ and $E(B^3)$.
 }
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  \begin{align*}
+    E(B^2) &= Var(B) + [E(B)]^2 \\
+    &= np(1-p) + n^2p^2 \\
+    &= np - np^2 + n^2p^2
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  We will get $E(B^3)$ via the third factorial moment, E[B(B-1)(B-2)].
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  \begin{align*}
+    &E[B(B-1)(B-2)] \\
+    &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\
+    &= \sum_{x=3}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\
+    &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
+    &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
+    &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  Let $y=x-3$; then $x=y+3$, and $x=3$, $x=n \Ra y=0$, $y=n-3$:
+  \begin{align*}
+    &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
+    &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
+    &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \\
+    &= n(n-1)(n-2)p^3 \\
+    &= n^3p^3 - 3n^2p^3 + 2np^3
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  To get $E(B^3)$, we expand the left side of the previous equation:
+  \begin{align*}
+    &E[B(B-1)(B-2)] \\
+    &= E \left[ B^3 - 3B^2 + 2B \right] \\
+    &= E(B^3) - 3E(B^2) + 2E(B) \\
+    &= E(B^3) - 3(np - np^2 + n^2p^2) + 2np \\
+    &= E(B^3) - 3np + 3np^2 - 3n^2p^2 + 2np \\
+    &= E(B^3) + 3np^2 - 3n^2p^2 - np
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  Left side: $E(B^3) + 3np^2 - 3n^2p^2 - np$
 
-  \begin{align}
-    E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\}. \nonumber \\
-    \intertext{Notice that the first three terms of the sum on the right hand side are zero, so we can rewrite it beginning at $x = 3$:}
-    E[B(B-1)(B-2)] &= \sum_{x=3}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\}. \nonumber \\
-    &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \nonumber \\
-    &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \nonumber \\
-    &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \nonumber \\
-    \intertext{let $y=x-3$; then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$:}
-    &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \nonumber \\
-    &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \nonumber \\
-    &= n(n-1)(n-2)p^3 \nonumber \\
-    &= n^3p^3 - 3n^2p^3 + 2np^3. \label{eq:binomial-third-moment-rhs}
-  \end{align}
+  Right side: $n^3p^3 - 3n^2p^3 + 2np^3$
+
+  Set them equal and solve for $E(B^3)$:
+  \begin{align*}
+    &E(B^3) + 3np^2 - 3n^2p^2 - np = n^3p^3 - 3n^2p^3 + 2np^3 \\
+    &\Rightarrow \qquad E(B^3) = n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np
+  \end{align*}
 }
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
-
-  \begin{align}
-    E[B(B-1)(B-2)] &= E \left[ B^3 - 3B^2 + 2B \right] \nonumber \\
-    &= E(B^3) - 3E(B^2) + 2E(B) \nonumber \\
-    &= E(B^3) - 3(np - np^2 + n^2p^2) + 2np \nonumber \\
-    &= E(B^3) - 3np + 3np^2 - 3n^2p^2 + 2np \nonumber \\
-    &= E(B^3) + 3np^2 - 3n^2p^2 - np. \label{eq:binomial-third-moment-lhs}
-  \end{align}
-}
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
-
-  \begin{align}
-    E(B^3) + 3np^2 - 3n^2p^2 - np &= n^3p^3 - 3n^2p^3 + 2np^3 \nonumber \\
-    \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np. \label{eq:binomial-third-moment}
-  \end{align}
-}
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
-
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  Now we can (finally!) compute the third central moment:
   \begin{align*}
-    E \left( [B - E(B)]^3 \right) &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
+    &E \left( [B - E(B)]^3 \right) \\
+    &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
     &= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\
     &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
-    &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\
-    &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
+    &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) \\
+    &\quad - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\
+    &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np \\
+    &\quad - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
     &= 2np^3 - 3np^2 + np \\
-    &= np(p-1)(2p-1).
+    &= np(p-1)(2p-1)
   \end{align*}
 }
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
-
-  \begin{align}
-    E(B) &= np, \nonumber \\
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  Let's restate our results:
+  \begin{align*}
+    E(B) &= np, \\
     E([B - E(B)]^2) &= np(1-p), \\
-    E([B - E(B)]^3) &= np(p-1)(2p-1). \nonumber
-  \end{align}
-}
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
-
-  \begin{align*}
-    E([Y - E(Y)]^3) &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
-    &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) \\
-    & \quad + 2\;(\mu + b \delta \sigma)^3 \\
-    &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} -
-      \cancel{6 b \delta \mu^2 \sigma} - \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} \\
-    & \quad - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
-    &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
-    &= b \delta^3 \sigma^3 (2b^2 - 1).
+    E([B - E(B)]^3) &= np(p-1)(2p-1)
   \end{align*}
 }
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
 
-  \begin{alignat}{4}
-    E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;, \nonumber \\
-    E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right), \\
-    E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right). \nonumber
-  \end{alignat}
+%% The Central Moments of the Skew-Normal
+\frame{ \frametitle{Method of Moments: Central Moments of the Skew-Normal}
+  The first and second central moments are the mean and variance.
+  \begin{align*}
+    E(Y) &= \mu + b \delta \sigma \\
+    Var(Y) &= \sigma^2 (1 - b^2 \delta^2)
+  \end{align*}
 }
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
+\frame{ \frametitle{Method of Moments: Central Moments of the Skew-Normal}
+  Again, the third one is a little harder:
+  \begin{align*}
+    &E([Y - E(Y)]^3) \\
+    &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
+    &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) \\
+    &\quad - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) + 2\;(\mu + b \delta \sigma)^3 \\
+    &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} \\
+    &\quad - \cancel{6 b \delta \mu^2 \sigma} - \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} \\
+    &\quad + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
+    &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
+    &= b \delta^3 \sigma^3 (2b^2 - 1)
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Skew-Normal}
+  Our results, restated:
+  \begin{alignat*}{4}
+    E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \\
+    E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \\
+    E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right)
+  \end{alignat*}
+}
 
+%% Deriving an Approximation
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  Set the central moments of the binomial equal to the central moments of the skew-normal:
   \begin{subequations}
@@
 }
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
-
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  To get $\lambda$, divide the cube of \eqref{eq:second-moment-set} by the
+  square of \eqref{eq:third-moment-set}:
   \begin{align}
@@
     \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-      \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \;. \label{eq:solving-for-lambda}
+      \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \label{eq:solving-for-lambda}
   \end{align}
 }
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
-
-  \begin{equation}
-    \label{eq:lambda-solved}
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  Equation \eqref{eq:solving-for-lambda} can be solved for $\lambda^2$. Then take $\lambda$ to be
+  \begin{equation*}
     \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}.
-  \end{equation}
+  \end{equation*}
 }
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
-
-  \begin{equation}
-    \label{eq:sigma-solved}
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  Once you have $\lambda$, solve for $\sigma$ and then $\mu$.
+  \begin{equation*}
     np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
-    \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} \;.
-  \end{equation}
+    \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}}
+  \end{equation*}
+  \begin{equation*}
+    np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
+    \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}}
+  \end{equation*}
 }
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
-
-  \begin{equation}
-    \label{eq:mu-solved}
-    np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
-    \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;.
-  \end{equation}
-}
-\frame{
-  \frametitle{Method of Moments: Deriving an Approximation}
-
-  One notable case where the above skew-normal approximation fails is when $p =
-  0.5$; the right side of \eqref{eq:solving-for-lambda} becomes undefined, and we
-  are unable to obtain $\lambda$. Fortunately, here we can fall back on our
-  intuition, which tells us that since the binomial is perfectly symmetrical, the
-  skew should be 0. A few observations support this conclusion: When $p = 0.5$,
-  equation \eqref{eq:lambda-solved} fails to yield a sign. Furthermore, when
-  $\lambda = 0$, equations \eqref{eq:sigma-solved} and \eqref{eq:mu-solved}
-  return us to the normal approximation ($\mu = np$ and $\sigma =
-  \sqrt{np(1-p)}$, respectively), which is after all a natural choice for a
-  symmetric binomial distribution.
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  When $p = 0.5$, $\lambda=0$.
 }
@@
 %% Restrictions
-\frame{
-  \frametitle{Method of Moments: Restrictions}
+\frame{ \frametitle{Method of Moments: Restrictions}
+  Let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u = \frac{1+\lambda^2}{\lambda^2}$.
 
-  If we let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u$, we can rewrite the
-  left hand side of \eqref{eq:solving-for-lambda} as
-
-  \begin{alignat}{3}
-    \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2}
-      &= \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. & \nonumber \\
-    &= \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 & \nonumber \\
-    &= \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) & \nonumber \\
-    &= \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) &= g(v). \label{eq:lhs-solving-for-lambda}
-  \end{alignat}
+  Then we can rewrite \eqref{eq:solving-for-lambda}:
+  \begin{gather*}
+    \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2} \\
+    \vdots \\
+    (magic) \\
+    \vdots \\
+    \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = g(v)
+  \end{gather*}
 }
-\frame{
-  \frametitle{Method of Moments: Restrictions}
-
-  \begin{equation}
-    \min_{v} g(v) = g(v)|_{v=1} = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1,
-  \end{equation}
+\frame{ \frametitle{Method of Moments: Restrictions}
+  $g(v)$ is increasing in $v = \frac{1+\lambda^2}{\lambda^2} \geq 1$. Therefore:
+  \begin{equation*}
+    \min_{v} g(v) = g(1) = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1
+  \end{equation*}
 }
-\frame{
-  \frametitle{Method of Moments: Restrictions}
-
+\frame{ \frametitle{Method of Moments: Restrictions}
+  To be able to solve \eqref{eq:solving-for-lambda} for $\lambda$, we must have
   \begin{align}
@@
 }
-\frame{
-  \frametitle{Method of Moments: Restrictions}
+\frame{ \frametitle{Method of Moments: Restrictions}
+  From \eqref{eq:solving-the-restriction}, we can answer two questions:
 
-  \begin{equation}
-    n \geq \frac{(1-2p)^2}{p(1-p)} \;. \label{eq: n for a given p}
-  \end{equation}
+  Given $p$, what is the least $n$ necessary?
+  \begin{equation*}
+    n \geq \frac{(1-2p)^2}{p(1-p)}
+  \end{equation*}
+  Given $n$, what is the range of possible $p$'s?
+  \begin{equation*}
+   \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}}
+  \end{equation*}
 }
-\frame{
-  \frametitle{Method of Moments: Restrictions}
-
-  \begin{align}
-    np(1-p) &\geq (1-2p)^2 \nonumber \\
-    np - np^2 &\geq 1 - 4p + 4p^2 \nonumber \\
-    1 - 4p + 4p^2 - np + np^2 &\leq 0 \nonumber \\
-    (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq: solving for p}.
-  \end{align}
-
-  We then apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
-
-  \begin{align*}
-    p &= \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
-    &= \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
-    &= \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n+4)} \\
-    &= \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
-    &= \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}} \;.
-  \end{align*}
-
-  Let $r_1 = \frac12 - \frac12 \sqrt{\frac{n}{n+4}}$ and $r_2 = \frac12 + \frac12
-  \sqrt{\frac{n}{n+4}}$. (Note that $r_1 < r_2$.) Now we can rewrite \eqref{eq:
-  solving for p} as
-
-  \begin{equation*}
-    (p - r_1)(p - r_2) \leq 0.
-  \end{equation*}
-
-  Examining the left hand side, when $p < r_1$, both terms are negative and so
-  their product is positive; when $p > r_2$, both terms are positive, again
-  leading the product to be positive. Therefore, our solution lies where $r_1
-  \leq p \leq r_2$, or more explicitly,
-
-  \begin{equation}
-   \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}} \;.
-  \end{equation}
+\frame{ \frametitle{Method of Moments: Restrictions}
+  % figures
 }
-\frame{
-  \frametitle{Method of Moments: Restrictions}
-
-  \begin{figure}[h]
-    \centering
-    \subfloat[Least possible $n$, given a fixed $p$]{\label{fig:sn-restriction-least-n}\includegraphics[width=0.76\textwidth]{../images/restriction-least-n.png}}
-    \\ \vspace{5mm}
-    \subfloat[Range of possible $p$, given a fixed $n$]{\label{fig:sn-restriction-p-range}\includegraphics[width=0.76\textwidth]{../images/restriction-p-range.png}}
-    \caption{Restrictions on $n$ and $p$ necessary to obtain $\lambda$}
-    \label{fig:sn-restriction}
-  \end{figure}
-}

### 2011-02-14 project/presentation/presentation.tex
Presentation roughly done; compiles, need to insert figures.

@@
 \documentclass{beamer}
-\usepackage{jmath}
+\usepackage{capstone-presentation}
 
@@
 
-%% The Skew-Normal Distribution
-\frame{
-  \frametitle{The Skew-Normal Distribution}
+% The Skew-Normal Distribution
+\frame{ \frametitle{The Skew-Normal Distribution: Foundations}
   \begin{definition}[Skew-normal]
@@
 }
+\frame{ \frametitle{The Skew-Normal Distribution: Foundations}
+  \begin{lem*}
+    If $f_0$ is a one-dimensional probability density function symmetric about
+    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
+    and is a density symmetric about 0, then
+
+    \begin{equation*}
+      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
+    \end{equation*}
+
+    is a density function for any odd function $w(\cdot)$. (Lemma 1,
+    \citealp{azzalini})
+  \end{lem*}
+}
+\frame{ \frametitle{The Skew-Normal Distribution: Foundations}
+
+  Basic properties:
+
+  \begin{align*}
+    E(Y) &= \mu + b \delta \sigma \\
+    E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 \\
+    E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \\
+    Var(Y) &= \sigma^2 (1 - b^2 \delta^2)
+  \end{align*}
+
+  where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
+  \lambda^2}}$. \citep{pewsey}
+}
+\frame{ \frametitle{The Skew-Normal Distribution: Foundations}
+
+  What happens when $\lambda=0$?
+
+  \begin{align*}
+    f(x|\mu, \sigma, \lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
+    &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
+    &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
+    &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
+  \end{align*}
+
+  which is the pdf of the normal distribution ($\mu$, $\sigma$).
+}
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+
+  \begin{definition}[Standard skew-normal]
+    The $SN(0,1,\lambda)$ distribution is called the standard skew-normal and
+    has pdf
+
+    \begin{equation*}
+      f_Z(x|\lambda) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
+    \end{equation*}
+  \end{definition}
+
+  Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
+  = \sigma Z + \mu$.
+}
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+
+  \begin{property}
+    If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
+  \end{property}
+  \vsep
+  \begin{property}
+    If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
+  \end{property}
+}
+\frame{ \frametitle{The Skew-Normal Distribution}
+  \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+
+  \begin{property}
+    As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
+  \end{property}
+  \vsep
+  \begin{property}
+    The moment generating function of $SN(0,1,\lambda)$ is
+
+    \begin{equation*}
+      M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2},
+    \end{equation*}
+
+    where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
+  \end{property}
+}
+
+% Method of Moments
+
+\frame{ \frametitle{Method of Moments: Overview}
+  Game plan:
+  \begin{enumerate}[<+->]
+    \item Find the first three central moments of the binomial and the first
+          three central moments of the skew-normal.\\
+          \vsep         
+          What are central moments?: $E(X)$, $E([X - E(X)]^2)$, $E([X -
+          E(X)]^3)$.
+    \item Set them equal to each other.
+    \item Take $n$ and $p$ to be constants; solve for $\mu$, $\sigma$, and $\lambda$.
+  \end{enumerate}
+}
+
+%% The Central Moments of the Binomial
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  The first two are easy:
+  \begin{align*}
+    E(B) &= np \\
+    E([B - E(B)]^2) &= Var(B) = np(1-p)
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  The third one takes some elbow grease.
+
+  First we'll need to find $E(B^2)$ and $E(B^3)$.
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  \begin{align*}
+    E(B^2) &= Var(B) + [E(B)]^2 \\
+    &= np(1-p) + n^2p^2 \\
+    &= np - np^2 + n^2p^2
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  We will get $E(B^3)$ via the third factorial moment, E[B(B-1)(B-2)].
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  \begin{align*}
+    &E[B(B-1)(B-2)] \\
+    &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\
+    &= \sum_{x=3}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\
+    &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
+    &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
+    &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  Let $y=x-3$; then $x=y+3$, and $x=3$, $x=n \Ra y=0$, $y=n-3$:
+  \begin{align*}
+    &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
+    &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
+    &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \\
+    &= n(n-1)(n-2)p^3 \\
+    &= n^3p^3 - 3n^2p^3 + 2np^3
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  To get $E(B^3)$, we expand the left side of the previous equation:
+  \begin{align*}
+    &E[B(B-1)(B-2)] \\
+    &= E \left[ B^3 - 3B^2 + 2B \right] \\
+    &= E(B^3) - 3E(B^2) + 2E(B) \\
+    &= E(B^3) - 3(np - np^2 + n^2p^2) + 2np \\
+    &= E(B^3) - 3np + 3np^2 - 3n^2p^2 + 2np \\
+    &= E(B^3) + 3np^2 - 3n^2p^2 - np
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  Left side: $E(B^3) + 3np^2 - 3n^2p^2 - np$
+
+  Right side: $n^3p^3 - 3n^2p^3 + 2np^3$
+
+  Set them equal and solve for $E(B^3)$:
+  \begin{align*}
+    &E(B^3) + 3np^2 - 3n^2p^2 - np = n^3p^3 - 3n^2p^3 + 2np^3 \\
+    &\Rightarrow \qquad E(B^3) = n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  Now we can (finally!) compute the third central moment:
+  \begin{align*}
+    &E \left( [B - E(B)]^3 \right) \\
+    &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
+    &= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\
+    &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
+    &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) \\
+    &\quad - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\
+    &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np \\
+    &\quad - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
+    &= 2np^3 - 3np^2 + np \\
+    &= np(p-1)(2p-1)
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  Let's restate our results:
+  \begin{align*}
+    E(B) &= np, \\
+    E([B - E(B)]^2) &= np(1-p), \\
+    E([B - E(B)]^3) &= np(p-1)(2p-1)
+  \end{align*}
+}
+
+%% The Central Moments of the Skew-Normal
+\frame{ \frametitle{Method of Moments: Central Moments of the Skew-Normal}
+  The first and second central moments are the mean and variance.
+  \begin{align*}
+    E(Y) &= \mu + b \delta \sigma \\
+    Var(Y) &= \sigma^2 (1 - b^2 \delta^2)
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Skew-Normal}
+  Again, the third one is a little harder:
+  \begin{align*}
+    &E([Y - E(Y)]^3) \\
+    &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
+    &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) \\
+    &\quad - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) + 2\;(\mu + b \delta \sigma)^3 \\
+    &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} \\
+    &\quad - \cancel{6 b \delta \mu^2 \sigma} - \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} \\
+    &\quad + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
+    &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
+    &= b \delta^3 \sigma^3 (2b^2 - 1)
+  \end{align*}
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Skew-Normal}
+  Our results, restated:
+  \begin{alignat*}{4}
+    E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \\
+    E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \\
+    E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right)
+  \end{alignat*}
+}
+
+%% Deriving an Approximation
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  Set the central moments of the binomial equal to the central moments of the skew-normal:
+  \begin{subequations}
+  \begin{align}
+    np &= \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \label{eq:first-moment-set} \\
+    np(1-p) &= \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:second-moment-set} \\
+    np(p-1)(2p-1) &= \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \label{eq:third-moment-set}
+  \end{align}
+  \end{subequations}
+}
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  To get $\lambda$, divide the cube of \eqref{eq:second-moment-set} by the
+  square of \eqref{eq:third-moment-set}:
+  \begin{align}
+    \frac{\sigma^6 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right)^3}{\sigma^6 \cdot \frac{2}{\pi} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^6 \left(
+      \frac{4}{\pi} - 1 \right)^2} &= \frac{n^3p^3(1-p)^3}{n^2p^2(p-1)^2(2p-1)^2} \nonumber \\
+    \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
+      \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \;. \label{eq:solving-for-lambda}
+  \end{align}
+}
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  Equation \eqref{eq:solving-for-lambda} can be solved for $\lambda^2$. Then take
+  \begin{equation*}
+    \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}
+  \end{equation*}
+}
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  With $\lambda$, solve for $\sigma$ and then $\mu$
+  \begin{equation*}
+    np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
+    \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}}
+  \end{equation*}
+  \begin{equation*}
+    np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
+    \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}}
+  \end{equation*}
+}
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  When $p = 0.5$, $\lambda=0$.
+}
+
+%% Restrictions
+\frame{ \frametitle{Method of Moments: Restrictions}
+  Let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u = \frac{1+\lambda^2}{\lambda^2}$.
+
+  Then we can rewrite \eqref{eq:solving-for-lambda}:
+  \begin{gather*}
+    \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2} \\
+    \vdots \\
+    (magic) \\
+    \vdots \\
+    \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = g(v)
+  \end{gather*}
+}
+\frame{ \frametitle{Method of Moments: Restrictions}
+  $g(v)$ is increasing in $v = \frac{1+\lambda^2}{\lambda^2} \geq 1$. Therefore:
+  \begin{equation*}
+    \min_{v} g(v) = g(1) = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1
+  \end{equation*}
+}
+\frame{ \frametitle{Method of Moments: Restrictions}
+  To be able to solve \eqref{eq:solving-for-lambda} for $\lambda$, we must have
+  \begin{align}
+    \textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\
+    \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
+    np(1-p) &\geq (1-2p)^2. \label{eq:solving-the-restriction}
+  \end{align}
+}
+\frame{ \frametitle{Method of Moments: Restrictions}
+  From \eqref{eq:solving-the-restriction}, we can answer two questions:
+
+  Given $p$, what is the least $n$ necessary?
+  \begin{equation*}
+    n \geq \frac{(1-2p)^2}{p(1-p)}
+  \end{equation*}
+  Given $n$, what is the range of possible $p$'s?
+  \begin{equation*}
+   \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}}
+  \end{equation*}
+}
+\frame{ \frametitle{Method of Moments: Restrictions}
+  % figures
+}
+
+% Demonstrating Improved Accuracy
+
+%% Visual Inspection
+\frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
+  %figures
+}
+
+%% MABS
+\frame{ \frametitle{Demonstrating Improved Accuracy: MABS}
+  \begin{equation*}
+    \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
+  \end{equation*}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: MABS}
+  %figures
+}
+
 \frame{
-  \frametitle{The Skew-Normal Distribution}
-  A few notes:
+  \frametitle{Resources}
 }
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-}
+
+\begin{frame}[allowframebreaks]
+  \frametitle{Bibliography}
+  \nocite{*}
+  \bibliography{../bibliography.bib}
+  \bibliographystyle{plainnat}
+\end{frame}
 \end{document}

### 2011-02-14 project/presentation/skew-normal.tex
Presentation roughly done; compiles, need to insert figures.

--- 2011-02-12 project/presentation/skew-normal.tex
@@
-%% The Skew-Normal Distribution
-\frame{
-  \frametitle{The Skew-Normal Distribution}
+% The Skew-Normal Distribution
+\frame{ \frametitle{The Skew-Normal Distribution: Foundations}
   \begin{definition}[Skew-normal]
@@
 }
-\frame{
-  \frametitle{The Skew-Normal Distribution}
-  A few notes:
+\frame{ \frametitle{The Skew-Normal Distribution: Foundations}
+  \begin{lem*}
+    If $f_0$ is a one-dimensional probability density function symmetric about
+    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
+    and is a density symmetric about 0, then
+
+    \begin{equation*}
+      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
+    \end{equation*}
+
+    is a density function for any odd function $w(\cdot)$. (Lemma 1,
+    \citealp{azzalini})
+  \end{lem*}
 }
-\frame{
-  \frametitle{The Skew-Normal Distribution}
+\frame{ \frametitle{The Skew-Normal Distribution: Foundations}
+
+  Basic properties:
+
+  \begin{align*}
+    E(Y) &= \mu + b \delta \sigma \\
+    E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2 \\
+    E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3 \\
+    Var(Y) &= \sigma^2 (1 - b^2 \delta^2)
+  \end{align*}
+
+  where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
+  \lambda^2}}$. \citep{pewsey}
 }
-\frame{
-  \frametitle{The Skew-Normal Distribution}
+\frame{ \frametitle{The Skew-Normal Distribution: Foundations}
+
+  What happens when $\lambda=0$?
+
+  \begin{align*}
+    f(x|\mu, \sigma, \lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
+    &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
+    &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
+    &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
+  \end{align*}
+
+  which is the pdf of the normal distribution ($\mu$, $\sigma$).
 }
-\frame{
-  \frametitle{The Skew-Normal Distribution}
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+
+  \begin{definition}[Standard skew-normal]
+    The $SN(0,1,\lambda)$ distribution is called the standard skew-normal and
+    has pdf
+
+    \begin{equation*}
+      f_Z(x|\lambda) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
+    \end{equation*}
+  \end{definition}
+
+  Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
+  = \sigma Z + \mu$.
 }
-\frame{
-  \frametitle{The Skew-Normal Distribution}
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+
+  \begin{property}
+    If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
+  \end{property}
+  \vsep
+  \begin{property}
+    If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
+  \end{property}
 }
-\frame{
-  \frametitle{The Skew-Normal Distribution}
+\frame{ \frametitle{The Skew-Normal Distribution}
+  \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+
+  \begin{property}
+    As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
+  \end{property}
+  \vsep
+  \begin{property}
+    The moment generating function of $SN(0,1,\lambda)$ is
+
+    \begin{equation*}
+      M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2},
+    \end{equation*}
+
+    where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
+  \end{property}
 }

### 2011-02-18 project/presentation/intro.tex
Added images to presentation and tweaked a few things.

@@
 
-  \pause
   But as $n$ gets larger, it becomes increasingly difficult.
 
-  \pause
   For example ...
@@
 
-  \pause
   When $n=25$,
@@
   Normal Approximation of the Binomial:
-
   \begin{equation*}
@@
   \end{equation*}
-
   where $\mu = np$, $\sigma = \sqrt{np(1-p)}$, and $\Phi$ is the standard
@@
 \frame{ \frametitle{Introduction}
-
   The binomial is symmetric when
@@
   \only<2>{or $n$ is very large.}
-
   \begin{center}
@@
 \frame{ \frametitle{Introduction}
-
   However, when $n$ is medium and $p$ is extreme ...
-
   \begin{center}
     \only<1>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-1.png}}
-    \only<2-3>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-2.png}}
-    \only<4>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-3.png}}
+    \only<2>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-2.png}}
+    \only<3>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-3.png}}
   \end{center}
-
-  \only<1>{the binomial is very skewed.}
-  \only<2>{the normal approximation doesn't work very well.}
-  \only<3->{\textbf{Can we do better?}}
-  \only<4>{Introducing ... the skew-normal distribution.}
+  \only<1>{the binomial is very skewed ...}
+  \only<2>{and the normal approximation doesn't work very well.}
+  \only<3>{Introducing ... the skew-normal distribution.}
 }
@@
   What we're going to cover:
-  \pause
   \begin{enumerate}[<+->]

### 2011-02-18 project/presentation/method-of-moments.tex
Added images to presentation and tweaked a few things.

@@
 \frame{ \frametitle{Method of Moments: Overview}
+  Now we're going to derive the approximation!
+
   Game plan:
@@
 \frame{ \frametitle{Method of Moments: Deriving an Approximation}
-  When $p = 0.5$, $\lambda=0$.
+  When $p = 0.5$, the binomial is symmetric, so $\lambda=0$.
+
+  This takes us back to the usual normal approximation:
+  \begin{align*}
+    \sigma &= \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{0^2}{1 + 0^2}}} = \sqrt{\frac{np(1-p)}{1}} = \sqrt{np(1-p)} \\
+    \mu &= np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{0}{\sqrt{1 + 0^2}}  = np - 0 = np
+  \end{align*}
 }
@@
   \end{align}
+  From \eqref{eq:solving-the-restriction}, we can answer two questions:
 }
 \frame{ \frametitle{Method of Moments: Restrictions}
-  From \eqref{eq:solving-the-restriction}, we can answer two questions:
+  One:
 
@@
   \end{equation*}
+}
+\frame{ \frametitle{Method of Moments: Restrictions}
+  Least possible $n$, given a fixed $p$:
+  \begin{center}
+    \includegraphics[width=0.7\textwidth]{../images/restriction-least-n.png}
+  \end{center}
+}
+\frame{ \frametitle{Method of Moments: Restrictions}
+  Two:
+
   Given $n$, what is the range of possible $p$'s?
@@
 \frame{ \frametitle{Method of Moments: Restrictions}
-  % figures
+  Range of possible $p$, given a fixed $n$:
+  \begin{center}
+    \includegraphics[width=0.8\textwidth]{../images/restriction-p-range.png}
+  \end{center}
 }

### 2011-02-18 project/presentation/presentation.tex
Added images to presentation and tweaked a few things.

@@
 \frame{ \frametitle{The Skew-Normal Distribution: Foundations}
+  So where did this funny-looking pdf come from? ...
+  \pause
   \begin{lem*}
@@
 
-  \begin{property}
+  \begin{property}[1]
     If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
@@
   \vsep
-  \begin{property}
+  \begin{property}[2]
     If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
@@
 
-  \begin{property}
+  \begin{property}[3]
     As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
@@
   \vsep
-  \begin{property}
+  \begin{property}[4]
     The moment generating function of $SN(0,1,\lambda)$ is
-
     \begin{equation*}
@@
     \end{equation*}
-
     where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
@@
     \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-      \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \;. \label{eq:solving-for-lambda}
+      \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \label{eq:solving-for-lambda}
   \end{align}
@@
 \frame{ \frametitle{Method of Moments: Deriving an Approximation}
-  Equation \eqref{eq:solving-for-lambda} can be solved for $\lambda^2$. Then take
+  Equation \eqref{eq:solving-for-lambda} can be solved for $\lambda^2$. Then take $\lambda$ to be
   \begin{equation*}
-    \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}
+    \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}.
   \end{equation*}
@@
 \frame{ \frametitle{Method of Moments: Deriving an Approximation}
-  With $\lambda$, solve for $\sigma$ and then $\mu$
+  Once you have $\lambda$, solve for $\sigma$ and then $\mu$.
   \begin{equation*}
@@
 
+\frame{ \frametitle{Demonstrating Improved Accuracy}
+  We have an approximation!!
+
+  But is it more accurate? ... \pause Answer: Yes!
+}
+
 %% Visual Inspection
 \frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
-  %figures
+  The easiest way of gauging accuracy is by visual inspection.
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
+  \includegraphics[width=\textwidth]{../images/comparison-n25-p005.png}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
+  \includegraphics[width=\textwidth]{../images/comparison-n25-p01.png}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
+  \includegraphics[width=\textwidth]{../images/comparison-n25-p02.png}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
+  \includegraphics[width=\textwidth]{../images/comparison-n50-p005.png}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
+  \includegraphics[width=\textwidth]{../images/comparison-n50-p01.png}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
+  \includegraphics[width=\textwidth]{../images/comparison-n50-p02.png}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
+  \includegraphics[width=\textwidth]{../images/comparison-n100-p005.png}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
+  \includegraphics[width=\textwidth]{../images/comparison-n100-p01.png}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: Visual}
+  \includegraphics[width=\textwidth]{../images/comparison-n100-p02.png}
 }
@@
 \frame{ \frametitle{Demonstrating Improved Accuracy: MABS}
+  A more numerical way of gauging accuracy is the $MABS$, defined by \citet{mabs} as
   \begin{equation*}
-    \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
+    \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|.
   \end{equation*}
@@
 \frame{ \frametitle{Demonstrating Improved Accuracy: MABS}
-  %figures
+  MABS as a function of $p$, with fixed $n=25$:
+
+  \begin{center}
+    \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-n25.png}
+  \end{center}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: MABS}
+  MABS as a function of $p$, with fixed $n=100$:
+
+  \begin{center}
+    \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-n100.png}
+  \end{center}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: MABS}
+  MABS as a function of $n$, with fixed $p=0.05$:
+
+  \begin{center}
+    \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-p005.png}
+  \end{center}
+}
+\frame{ \frametitle{Demonstrating Improved Accuracy: MABS}
+  MABS as a function of $n$, with fixed $p=0.1$:
+
+  \begin{center}
+    \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-p01.png}
+  \end{center}
 }
 
-\frame{
-  \frametitle{Resources}
+\begin{frame}[shrink=47]{Resources}
+  \vsep
+  \vsep
+
+  Estimations of $SN(\mu, \sigma, \lambda)$ for $Bin(n,p)$
+  \vsep
+
+  \renewcommand{\arraystretch}{1.3}
+  \begin{tabular}
+    { r r | r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l }
+    \hline \hline
+    & & \multicolumn{5}{c}{} & \multicolumn{5}{c}{} & \multicolumn{5}{c}{$n$} & \multicolumn{5}{c}{} & \multicolumn{5}{c}{}\\
+    \multirow{20}{*}{$p$} & & \multicolumn{5}{c}{25} & \multicolumn{5}{c}{50} & \multicolumn{5}{c}{100} & \multicolumn{5}{c}{250} & \multicolumn{5}{c}{500} \\
+    \hline
+    & 0.05 & ( & -0.11 & 1.74 & 4.56 & ) & ( & 0.79 & 2.30 & 2.54 & ) & ( & 2.85 & 3.06 & 1.86 & ) & ( & 9.58 & 4.52 & 1.38 & ) & ( & 21.32 & 6.11 & 1.15 & ) \\
+    & 0.10 & ( & 0.89 & 2.20 & 2.31 & ) & ( & 2.97 & 2.94 & 1.74 & ) & ( & 7.44 & 3.94 & 1.40 & ) & ( & 21.53 & 5.88 & 1.10 & ) & ( & 45.62 & 8.01 & 0.94 & ) \\
+    & 0.15 & ( & 2.02 & 2.49 & 1.79 & ) & ( & 5.32 & 3.34 & 1.43 & ) & ( & 12.25 & 4.51 & 1.19 & ) & ( & 33.77 & 6.77 & 0.96 & ) & ( & 70.30 & 9.27 & 0.82 & ) \\
+    & 0.20 & ( & 3.23 & 2.67 & 1.50 & ) & ( & 7.76 & 3.61 & 1.24 & ) & ( & 17.18 & 4.89 & 1.04 & ) & ( & 46.18 & 7.39 & 0.85 & ) & ( & 95.18 & 10.16 & 0.74 & ) \\
+    & 0.25 & ( & 4.49 & 2.79 & 1.29 & ) & ( & 10.28 & 3.78 & 1.09 & ) & ( & 22.20 & 5.15 & 0.93 & ) & ( & 58.71 & 7.83 & 0.76 & ) & ( & 120.22 & 10.80 & 0.67 & ) \\
+    & 0.30 & ( & 5.80 & 2.85 & 1.12 & ) & ( & 12.86 & 3.88 & 0.95 & ) & ( & 27.31 & 5.32 & 0.82 & ) & ( & 71.34 & 8.12 & 0.68 & ) & ( & 145.39 & 11.24 & 0.60 & ) \\
+    & 0.35 & ( & 7.17 & 2.86 & 0.96 & ) & ( & 15.50 & 3.92 & 0.83 & ) & ( & 32.49 & 5.39 & 0.72 & ) & ( & 84.09 & 8.28 & 0.60 & ) & ( & 170.70 & 11.50 & 0.53 & ) \\
+    & 0.40 & ( & 8.59 & 2.83 & 0.80 & ) & ( & 18.23 & 3.89 & 0.70 & ) & ( & 37.76 & 5.39 & 0.61 & ) & ( & 96.96 & 8.32 & 0.51 & ) & ( & 196.18 & 11.60 & 0.45 & ) \\
+    & 0.45 & ( & 10.12 & 2.73 & 0.61 & ) & ( & 21.08 & 3.79 & 0.53 & ) & ( & 43.21 & 5.29 & 0.47 & ) & ( & 110.07 & 8.23 & 0.40 & ) & ( & 221.93 & 11.54 & 0.35 & ) \\
+    & 0.50 & ( & 12.50 & 2.50 & 0.00 & ) & ( & 25.00 & 3.54 & 0.00 & ) & ( & 50.00 & 5.00 & 0.00 & ) & ( & 125.00 & 7.91 & 0.00 & ) & ( & 250.00 & 11.18 & 0.00 & ) \\
+    & 0.55 & ( & 14.88 & 2.73 & -0.61 & ) & ( & 28.92 & 3.79 & -0.53 & ) & ( & 56.79 & 5.29 & -0.47 & ) & ( & 139.93 & 8.23 & -0.40 & ) & ( & 278.07 & 11.54 & -0.35 & ) \\
+    & 0.60 & ( & 16.41 & 2.83 & -0.80 & ) & ( & 31.77 & 3.89 & -0.70 & ) & ( & 62.24 & 5.39 & -0.61 & ) & ( & 153.04 & 8.32 & -0.51 & ) & ( & 303.82 & 11.60 & -0.45 & ) \\
+    & 0.65 & ( & 17.83 & 2.86 & -0.96 & ) & ( & 34.50 & 3.92 & -0.83 & ) & ( & 67.51 & 5.39 & -0.72 & ) & ( & 165.91 & 8.28 & -0.60 & ) & ( & 329.30 & 11.50 & -0.53 & ) \\
+    & 0.70 & ( & 19.20 & 2.85 & -1.12 & ) & ( & 37.14 & 3.88 & -0.95 & ) & ( & 72.69 & 5.32 & -0.82 & ) & ( & 178.66 & 8.12 & -0.68 & ) & ( & 354.61 & 11.24 & -0.60 & ) \\
+    & 0.75 & ( & 20.51 & 2.79 & -1.29 & ) & ( & 39.72 & 3.78 & -1.09 & ) & ( & 77.80 & 5.15 & -0.93 & ) & ( & 191.29 & 7.83 & -0.76 & ) & ( & 379.78 & 10.80 & -0.67 & ) \\
+    & 0.80 & ( & 21.77 & 2.67 & -1.50 & ) & ( & 42.24 & 3.61 & -1.24 & ) & ( & 82.82 & 4.89 & -1.04 & ) & ( & 203.82 & 7.39 & -0.85 & ) & ( & 404.82 & 10.16 & -0.74 & ) \\
+    & 0.85 & ( & 22.98 & 2.49 & -1.79 & ) & ( & 44.68 & 3.34 & -1.43 & ) & ( & 87.75 & 4.51 & -1.19 & ) & ( & 216.23 & 6.77 & -0.96 & ) & ( & 429.70 & 9.27 & -0.82 & ) \\
+    & 0.90 & ( & 24.11 & 2.20 & -2.31 & ) & ( & 47.03 & 2.94 & -1.74 & ) & ( & 92.56 & 3.94 & -1.40 & ) & ( & 228.47 & 5.88 & -1.10 & ) & ( & 454.38 & 8.01 & -0.94 & ) \\
+    & 0.95 & ( & 25.11 & 1.74 & -4.56 & ) & ( & 49.21 & 2.30 & -2.54 & ) & ( & 97.15 & 3.06 & -1.86 & ) & ( & 240.42 & 4.52 & -1.38 & ) & ( & 478.68 & 6.11 & -1.15 & ) \\
+  \end{tabular}
+\end{frame}
+\frame{ \frametitle{Resources}
+  All values in my project were computed using a Python library, which is freely available online:
+
+  http://github.com/joycetipping/skew-normal-capstone/
 }

### 2011-02-19 project/presentation/intro.tex
Added stepping to slides.

@@
 \frame{ \frametitle{Introduction}
-  $X \sim Bin(n,p)$ where $0<p<1$ and $n = 1, 2, 3, \ldots$
+  \begin{definition}[Binomial]
+    Let $X$ represent the number of successes in a sequence of $n$ independent Bernoulli trials with probability of success $p$ on each trial.
 
-  \pause
-  \begin{align*}
-    \uncover<2->{f_X(x) &= \binom{n}{x} \; p^x q^{n-x} \\}
-    \uncover<3->{F_X(x) &= P(X \leq x) = \sum_{k=0}^x f_X(k)}
-  \end{align*}
+    \vsep
+    \uncover<2->{
+      $X$ has discrete pdf
+      \begin{equation*}
+        f_X(x) = \binom{n}{x} \; p^x q^{n-x}
+      \end{equation*}
+    }
+    \uncover<3->{
+      and cdf
+      \begin{equation*}
+        F_X(x) = P(X \leq x) = \sum_{k=0}^x f_X(k).
+      \end{equation*}
+    }
+  \end{definition}
 }
@@
   The binomial cdf is easy to calculate for small $n$ ...
+  \pause
 
   But as $n$ gets larger, it becomes increasingly difficult.
+  \pause
 
@@
   \end{equation*}
-
+  \pause
   When $n=25$,
@@
 \frame{ \frametitle{Introduction}
-  Normal Approximation of the Binomial:
+  A common technique is to use the normal distribution as an approximation:
   \begin{equation*}
@@
   normal cdf.
+  \pause
 
@@
   The binomial is symmetric when
-  \only<1->{$p=0.5$}
-  \only<2>{or $n$ is very large.}
+  \uncover<1->{$p=0.5$}
+  \uncover<2>{or $n$ is very large.}
   \begin{center}
@@
 \frame{ \frametitle{Outline}
-  What we're going to cover:
+  Today's itinerary:
   \begin{enumerate}[<+->]

### 2011-02-19 project/presentation/method-of-moments.tex
Added stepping to slides.

@@
   Now we're going to derive the approximation!
+  \pause
 
   Game plan:
+  \pause
   \begin{enumerate}[<+->]
@@
 \frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
-  The first two are easy:
+  Let's start with the binomial ...
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  The first two central moments are just the mean and variance:
   \begin{align*}
-    E(B) &= np \\
-    E([B - E(B)]^2) &= Var(B) = np(1-p)
+    \uncover<+->{E(B) &= np \\}
+    \uncover<+->{E([B - E(B)]^2) &= Var(B) = np(1-p)}
   \end{align*}
@@
   The third one takes some elbow grease.
+  \pause
 
@@
   \begin{align*}
-    E(B^2) &= Var(B) + [E(B)]^2 \\
-    &= np(1-p) + n^2p^2 \\
-    &= np - np^2 + n^2p^2
+    \uncover<+->{E(B^2) &= Var(B) + [E(B)]^2 \\}
+    \uncover<+->{&= np(1-p) + n^2p^2 \\}
+    \uncover<+->{&= np - np^2 + n^2p^2}
   \end{align*}
@@
   \begin{align*}
-    &E[B(B-1)(B-2)] \\
-    &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\
-    &= \sum_{x=3}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\
-    &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
-    &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
-    &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
+    \uncover<+->{&E[B(B-1)(B-2)] \\}
+    \uncover<+->{&= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\}
+    \uncover<+->{&= \sum_{x=3}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \\}
+    \uncover<+->{&= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\}
+    \uncover<+->{&= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\}
+    \uncover<+->{&= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\}
   \end{align*}
@@
   Let $y=x-3$; then $x=y+3$, and $x=3$, $x=n \Ra y=0$, $y=n-3$:
+  \pause
   \begin{align*}
-    &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\
-    &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-    &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \\
-    &= n(n-1)(n-2)p^3 \\
-    &= n^3p^3 - 3n^2p^3 + 2np^3
+    \uncover<+->{&= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\}
+    \uncover<+->{&= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\}
+    \uncover<+->{&= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \\}
+    \uncover<+->{&= n(n-1)(n-2)p^3 \\}
+    \uncover<+->{&= n^3p^3 - 3n^2p^3 + 2np^3}
   \end{align*}
@@
   To get $E(B^3)$, we expand the left side of the previous equation:
+  \pause
   \begin{align*}
-    &E[B(B-1)(B-2)] \\
-    &= E \left[ B^3 - 3B^2 + 2B \right] \\
-    &= E(B^3) - 3E(B^2) + 2E(B) \\
-    &= E(B^3) - 3(np - np^2 + n^2p^2) + 2np \\
-    &= E(B^3) - 3np + 3np^2 - 3n^2p^2 + 2np \\
-    &= E(B^3) + 3np^2 - 3n^2p^2 - np
+    \uncover<+->{&E[B(B-1)(B-2)] \\}
+    \uncover<+->{&= E \left[ B^3 - 3B^2 + 2B \right] \\}
+    \uncover<+->{&= E(B^3) - 3E(B^2) + 2E(B) \\}
+    \uncover<+->{&= E(B^3) - 3(np - np^2 + n^2p^2) + 2np \\}
+    \uncover<+->{&= E(B^3) - 3np + 3np^2 - 3n^2p^2 + 2np \\}
+    \uncover<+->{&= E(B^3) + 3np^2 - 3n^2p^2 - np}
   \end{align*}
@@
   Right side: $n^3p^3 - 3n^2p^3 + 2np^3$
+  \pause
 
   Set them equal and solve for $E(B^3)$:
+  \pause
   \begin{align*}
-    &E(B^3) + 3np^2 - 3n^2p^2 - np = n^3p^3 - 3n^2p^3 + 2np^3 \\
-    &\Rightarrow \qquad E(B^3) = n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np
+    \uncover<+->{&E(B^3) + 3np^2 - 3n^2p^2 - np = n^3p^3 - 3n^2p^3 + 2np^3 \\}
+    \uncover<+->{&\Rightarrow \qquad E(B^3) = n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np}
   \end{align*}
@@
   Now we can (finally!) compute the third central moment:
+  \pause
   \begin{align*}
-    &E \left( [B - E(B)]^3 \right) \\
-    &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
-    &= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\
-    &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
-    &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) \\
-    &\quad - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\
-    &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np \\
-    &\quad - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
-    &= 2np^3 - 3np^2 + np \\
-    &= np(p-1)(2p-1)
+    \uncover<+->{&E \left( [B - E(B)]^3 \right) \\}
+    \uncover<+->{&= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\}
+    \uncover<+->{&= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\}
+    \uncover<+->{&= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\}
+    \uncover<+->{&= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) \\
+                 &\quad - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\}
+    \uncover<+->{&= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np \\
+                 &\quad - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\}
+    \uncover<+->{&= 2np^3 - 3np^2 + np \\}
+    \uncover<+->{&= np(p-1)(2p-1)}
   \end{align*}
@@
 \frame{ \frametitle{Method of Moments: Central Moments of the Skew-Normal}
-  The first and second central moments are the mean and variance.
+  Now lets move on to skew-normal ...
+}
+\frame{ \frametitle{Method of Moments: Central Moments of the Skew-Normal}
+  Again, the first and second central moments are the mean and variance.
+  \pause
   \begin{align*}
@@
   Again, the third one is a little harder:
+  \pause
   \begin{align*}
-    &E([Y - E(Y)]^3) \\
-    &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
-    &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) \\
-    &\quad - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) + 2\;(\mu + b \delta \sigma)^3 \\
-    &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} \\
+    \uncover<+->{&E([Y - E(Y)]^3) \\}
+    \uncover<+->{&= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\}
+    \uncover<+->{&= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) \\
+                 &\quad - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) + 2\;(\mu + b \delta \sigma)^3 \\}
+    \uncover<+->{&= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} \\
                  &\quad - \cancel{6 b \delta \mu^2 \sigma} - \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} \\
-    &\quad + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
-    &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
-    &= b \delta^3 \sigma^3 (2b^2 - 1)
+                 &\quad + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\}
+    \uncover<+->{&= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\}
+    \uncover<+->{&= b \delta^3 \sigma^3 (2b^2 - 1)}
   \end{align*}
@@
   Set the central moments of the binomial equal to the central moments of the skew-normal:
+  \pause
   \begin{subequations}
     \begin{align}
-    np &= \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \label{eq:first-moment-set} \\
-    np(1-p) &= \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:second-moment-set} \\
-    np(p-1)(2p-1) &= \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \label{eq:third-moment-set}
+      \uncover<+->{np &= \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \label{eq:first-moment-set} \\}
+      \uncover<+->{np(1-p) &= \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:second-moment-set} \\}
+      \uncover<+->{np(p-1)(2p-1) &= \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \label{eq:third-moment-set} \\}
+      \notag
     \end{align}
@@
   square of \eqref{eq:third-moment-set}:
+  \pause
   \begin{align}
-    \frac{\sigma^6 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right)^3}{\sigma^6 \cdot \frac{2}{\pi} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^6 \left(
-      \frac{4}{\pi} - 1 \right)^2} &= \frac{n^3p^3(1-p)^3}{n^2p^2(p-1)^2(2p-1)^2} \nonumber \\
-    \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-      \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \label{eq:solving-for-lambda}
+    \uncover<+->{\frac{\sigma^6 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right)^3}{\sigma^6 \cdot \frac{2}{\pi} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^6 \left(
+                 \frac{4}{\pi} - 1 \right)^2} &= \frac{n^3p^3(1-p)^3}{n^2p^2(p-1)^2(2p-1)^2} \nonumber \\}
+    \uncover<+->{\Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
+                 \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \label{eq:solving-for-lambda}}
   \end{align}
@@
 \frame{ \frametitle{Method of Moments: Deriving an Approximation}
-  Equation \eqref{eq:solving-for-lambda} can be solved for $\lambda^2$. Then take $\lambda$ to be
+  Equation \eqref{eq:solving-for-lambda} can be solved for $\lambda^2$.
+  \pause
+
+  Then take $\lambda$ to be
   \begin{equation*}
@@
   Once you have $\lambda$, solve for $\sigma$ and then $\mu$.
+  \pause
   \begin{equation*}
-    np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
-    \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}}
+    \uncover<+->{np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
+                 \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}}}
   \end{equation*}
   \begin{equation*}
-    np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
-    \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}}
+    \uncover<+->{np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
+                 \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}}}
   \end{equation*}
@@
   When $p = 0.5$, the binomial is symmetric, so $\lambda=0$.
+  \pause
 
   This takes us back to the usual normal approximation:
+  \pause
   \begin{align*}
-    \sigma &= \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{0^2}{1 + 0^2}}} = \sqrt{\frac{np(1-p)}{1}} = \sqrt{np(1-p)} \\
-    \mu &= np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{0}{\sqrt{1 + 0^2}}  = np - 0 = np
+    \uncover<+->{\sigma &= \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{0^2}{1 + 0^2}}} = \sqrt{\frac{np(1-p)}{1}} = \sqrt{np(1-p)} \\}
+    \uncover<+->{\mu &= np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{0}{\sqrt{1 + 0^2}}  = np - 0 = np}
   \end{align*}
@@
 \frame{ \frametitle{Method of Moments: Restrictions}
+  Unfortunately, though better than the normal approximation, our skew-normal method isn't universal.
+  \pause
+
+  To be able to solve for $\lambda$, we must put a few restrictions on $n$ and $p$.
+}
+\frame{ \frametitle{Method of Moments: Restrictions}
   Let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u = \frac{1+\lambda^2}{\lambda^2}$.
+  \pause
 
-  Then we can rewrite \eqref{eq:solving-for-lambda}:
+  \uncover<+->{Then we can rewrite \eqref{eq:solving-for-lambda}:
   \begin{gather*}
-    \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2} \\
-    \vdots \\
+    \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2} \\}
+    \uncover<+->{\vdots \\
                  (magic) \\
-    \vdots \\
-    \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = g(v)
+                 \vdots \\}
+    \uncover<+->{\left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = g(v)}
   \end{gather*}
@@
 \frame{ \frametitle{Method of Moments: Restrictions}
-  $g(v)$ is increasing in $v = \frac{1+\lambda^2}{\lambda^2} \geq 1$. Therefore:
+  $g(v)$ is increasing in $v = \frac{1+\lambda^2}{\lambda^2} \geq 1$. \pause Therefore:
   \begin{equation*}
-    \min_{v} g(v) = g(1) = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1
+    \uncover<+->{\min_{v} g(v)} \uncover<+->{= g(1)} \uncover<+->{= \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right)} \uncover<+->{= 1.009524 \approx 1}
   \end{equation*}
@@
   \begin{align}
-    \textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\
-    \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
-    np(1-p) &\geq (1-2p)^2. \label{eq:solving-the-restriction}
+    \uncover<+->{\textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\}
+    \uncover<+->{\frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\}
+    \uncover<+->{np(1-p) &\geq (1-2p)^2. \label{eq:solving-the-restriction}}
   \end{align}
-  From \eqref{eq:solving-the-restriction}, we can answer two questions:
+  \uncover<+->{From \eqref{eq:solving-the-restriction}, we can answer two questions:}
 }
@@
   Given $p$, what is the least $n$ necessary?
+  \pause
   \begin{equation*}
@@
   Given $n$, what is the range of possible $p$'s?
+  \pause
   \begin{equation*}

### 2011-02-19 project/presentation/presentation.tex
Added stepping to slides.

@@
 
+  \pause
   But as $n$ gets larger, it becomes increasingly difficult.
 
+  \pause
   For example ...
@@
 
+  \pause
   When $n=25$,
@@
 
+  \pause
   \vsep
@@
   What happens when $\lambda=0$?
-
   \begin{align*}
-    f(x|\mu, \sigma, \lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
-    &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
-    &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
+    \uncover<+->{f(x|\mu, \sigma, \lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\}
+    \uncover<+->{&= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\}
+    \uncover<+->{&= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\}
+    \uncover<+->{&= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),}
   \end{align*}
-
-  which is the pdf of the normal distribution ($\mu$, $\sigma$).
+  \uncover<+->{which is the pdf of the normal distribution ($\mu$, $\sigma$).}
 }
@@
 
+  \pause
   Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
@@
   \end{property}
+  \pause
   \vsep

### 2011-02-19 project/presentation/presentation.tex
Implemented TikZ arrows for the Lemma 1 slide

@@
 \date{Spring 2011}
+
+% TikZ
+% For every picture that defines or uses external nodes, you'll have to
+% apply the 'remember picture' style. To avoid some typing, we'll apply
+% the style to all pictures.
+\tikzstyle{every picture}+=[remember picture]
+
+% By default all math in TikZ nodes are set in inline mode. Change this to
+% displaystyle so that we don't get small fractions.
+\everymath{\displaystyle}
 
@@
   The binomial cdf is easy to calculate for small $n$ ...
+  \pause
 
+  But as $n$ gets larger, it becomes increasingly difficult.
   \pause
-  But as $n$ gets larger, it becomes increasingly difficult.
 
-  \pause
   For example ...
@@
   \end{equation*}
-
   \pause
@@
   normal cdf.
+  \pause
 
-  \pause
   \vsep
@@
 \frame{ \frametitle{The Skew-Normal Distribution: Foundations}
+  \tikzstyle{na} = [baseline=-.5ex]
+
   So where did this funny-looking pdf come from? ...
@@
     and is a density symmetric about 0, then
-
+    % Below we mix an ordinary equation with TikZ nodes. Note that we have to
+    % adjust the baseline of the nodes to get proper alignment with the rest of
+    % the equation.
     \begin{equation*}
-      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
+      f(z) = 2 \; \cdot
+            \tikz[baseline]{
+                \node[fill=blue!20,anchor=base] (t1)
+                {$f_0(z)$};
+            } \cdot
+            \tikz[baseline]{
+                \node[fill=red!20,ellipse,anchor=base] (t2)
+                {$G\{w(z)\}$};
+            }
+      \quad (-\infty < z < \infty)
     \end{equation*}
-
     is a density function for any odd function $w(\cdot)$. (Lemma 1,
@@
   \end{lem*}
+  \begin{itemize}
+    \uncover<3->{
+      \item Kernel
+        \tikz[na] \node[coordinate] (n1) {};
+    }
+    \uncover<4->{
+      \item CDF
+        \tikz[na] \node[coordinate] (n2) {};
+    }
+  \end{itemize}
+
+  % Now it's time to draw some edges between the global nodes. Note that we
+  % have to apply the 'overlay' style.
+  \begin{tikzpicture}[overlay]
+    \path[->]<3-> (n1) edge [bend right] (t1);
+    \path[->]<4-> (n2) edge [bend right] (t2);
+  \end{tikzpicture}
 }
@@
   What happens when $\lambda=0$?
+  \pause
   \begin{align*}
@@
   \end{definition}
+  \pause
 
-  \pause
   Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
@@
   \begin{enumerate}[<+->]
-    \item Find the first three central moments of the binomial and the first
-          three central moments of the skew-normal.\\
+    \item Find the first three moments about the mean (central moments) of the binomial and the skew-normal.\\
+          \pause
           \vsep
@@
   The first two central moments are just the mean and variance:
+  \pause
   \begin{align*}
-    \uncover<+->{E(B) &= np \\}
-    \uncover<+->{E([B - E(B)]^2) &= Var(B) = np(1-p)}
+    E(B) &= np \\
+    E([B - E(B)]^2) &= Var(B) = np(1-p)
   \end{align*}

### 2011-02-19 project/presentation/skew-normal.tex
Added stepping to slides.
Tweaks.
Implemented TikZ arrows for the Lemma 1 slide

@@
   What happens when $\lambda=0$?
-
+  \pause
   \begin{align*}
-    f(x|\mu, \sigma, \lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
-    &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
-    &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
+    \uncover<+->{f(x|\mu, \sigma, \lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\}
+    \uncover<+->{&= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\}
+    \uncover<+->{&= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\}
+    \uncover<+->{&= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),}
   \end{align*}
-
-  which is the pdf of the normal distribution ($\mu$, $\sigma$).
+  \uncover<+->{which is the pdf of the normal distribution ($\mu$, $\sigma$).}
 }
@@
   \end{definition}
+  \pause
 

### 2011-02-19 project/calc/flot-flyer/data/comparison-headers.js
Gave flot-flyer its own data

@@ -1,0 +1,3 @@
+var binomial = {}; var normal = {}; var sn = {};
+var ns = ["25"];
+var ps = ["0.05"];

### 2011-02-19 project/calc/flot-flyer/data/comparison.js

@@ -1,0 +1,9 @@
+var binomial = {}; var normal = {}; var sn = {};
+var ns = ["25"];
+var ps = ["0.05"];
+var binomial = {}; var normal = {}; var sn = {};
+var ns = ["25"];
+var ps = ["0.05"];
+binomial.n25p005 = [[0, 0.27738957312183404], [1, 0.36498628042346593], [2, 0.2305176507937679], [3, 0.09301589417994148], [4, 0.026925653578404096], [5, 0.005951986580489327], [6, 0.0010442081720156706], [7, 0.0001491725960022389], [8, 1.7665175842370376e-05], [9, 1.7561870720485178e-06], [10, 1.4788943764619117e-07], [11, 1.0614074472214625e-08], [12, 6.5174141496055006e-10], [13, 3.4302179734765737e-11], [14, 1.547466754951837e-12], [15, 5.9726787033228998e-14], [16, 1.9646969418825246e-15], [17, 5.4743877637593453e-17], [18, 1.2805585412302651e-18], [19, 2.4830775037705939e-20], [20, 3.9206486901640898e-22], [21, 4.9130935966968624e-24], [22, 4.7015249729156167e-26], [23, 3.2275915145873905e-28], [24, 1.415610313415518e-30], [25, 2.9802322387695536e-33]];
[…]

### 2011-02-19 project/calc/flot-flyer/flot_data.py

@@ -1,0 +1,57 @@
+# Written by Joyce Tipping <joyce@joycetipping.com>
+# License: MIT <http://www.opensource.org/licenses/mit-license.php>
+
+import json
+import sys
+sys.path.append('..')
+from stats import *
+
+
+#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
+# Comparison Graphs
+#
+def comparison_graph (n, p):
+  # Builds data for one comparison graph (binomial, normal, and skew-normal)
+  # and writes it to an appropriately-named json file
+
+#  (binomial, normal, sn) = frame( binomial_pmf(n, p, pairs=True),
+#                                  normal_pdf(n, p, pairs=True),
+#                                  sn_pdf(n, p, pairs=True) )
+  (binomial, normal, sn) = ( binomial_pmf(n, p, pairs=True),
+                             normal_pdf(n, p, pairs=True),
+                             sn_pdf(n, p, pairs=True) )
+  np = 'n' + str(n) + 'p' + str(p).replace('.', '')
+  f = open('data/comparison-' + np + '.js', 'w')
+  f.write('binomial.' + np + ' = ' + json.dumps(binomial) + ';\n')
+  f.write('normal.' + np + ' = ' + json.dumps(normal) + ';\n')
+  f.write('sn.' + np + ' = ' + json.dumps(sn) + ';\n')
+  f.close()
+
+def frame (*args):
+  # Chops off the tails where all three graphs are less than 0.001
+  tmp = map(lambda list: filter(lambda point: point[1] > 0.001, list), args)
+  left = right = 0
+  for i, v in enumerate(tmp):
+    if v[0][0] < left: left = v[0][0]
+    if v[-1][0] > right: right = v[-1][0]
+  return map(lambda list: filter(lambda point: left < point[0] < right, list), args)
+
+def compile_comparison_data ():
+  # Set ns and ps
+  ns = [25]
+  ps = [0.05]
+
+  # Write some necessary headers
+  f = open('data/comparison-headers.js', 'w')
+  f.write('var binomial = {}; var normal = {}; var sn = {};\n')
+  f.write('var ns = ' + json.dumps(map(str, ns)) + ';\n')
[…]

### 2011-02-19 project/calc/flot-flyer/flot_data.py
Cleaned up flot_data for flyer

@@ -14,9 +14,6 @@ def comparison_graph (n, p):
   # Builds data for one comparison graph (binomial, normal, and skew-normal)
   # and writes it to an appropriately-named json file
 
-#  (binomial, normal, sn) = frame( binomial_pmf(n, p, pairs=True),
-#                                  normal_pdf(n, p, pairs=True),
-#                                  sn_pdf(n, p, pairs=True) )
   (binomial, normal, sn) = ( binomial_pmf(n, p, pairs=True),
                              normal_pdf(n, p, pairs=True),
                              sn_pdf(n, p, pairs=True) )
@@ -26,15 +23,6 @@ def comparison_graph (n, p):
   f.write('normal.' + np + ' = ' + json.dumps(normal) + ';\n')
   f.write('sn.' + np + ' = ' + json.dumps(sn) + ';\n')
   f.close()
-
-def frame (*args):
-  # Chops off the tails where all three graphs are less than 0.001
-  tmp = map(lambda list: filter(lambda point: point[1] > 0.001, list), args)
-  left = right = 0
-  for i, v in enumerate(tmp):
-    if v[0][0] < left: left = v[0][0]
-    if v[-1][0] > right: right = v[-1][0]
-  return map(lambda list: filter(lambda point: left < point[0] < right, list), args)
 
 def compile_comparison_data ():
   # Set ns and ps

### 2011-02-19 project/calc/approx-table/approx_table.py
Changed stats.py api for normal_pdf and binomial_pdf

@@ -17,7 +17,7 @@ def build_approximation_table (ns, ps):
   f.write('\\multirow{' + str(len(ps) + 1) + '}{*}{$p$} & & ' + ' & '.join(map(lambda n: '\\multicolumn{5}{c}{' + str(n) + '}', ns)) + ' \\\\\n\\hline\n');
   for p in ps: f.write('& ' + '{0:.2f}'.format(p) + ' & ' + ' & '.join(table_row(ns, p)) + ' \\\\\n');
   f.close()
-    
+
 def table_row (ns, p):
   return map(lambda n: sn_params_pretty(n, p), ns)
 

### 2011-02-19 project/calc/check/check.js

@@ -1,3 +1,3 @@
 binomial = [[0, 0.27738957312183404], [1, 0.36498628042346593], [2, 0.2305176507937679], [3, 0.09301589417994148], [4, 0.026925653578404096], [5, 0.005951986580489327]];
-normal = [[-2.2999999999999989, 0.0018158902218712231], [-2.1999999999999993, 0.0024383282717041922], [-2.0999999999999996, 0.0032466654668062431], [-2.0, 0.0042867256778411772], [-1.8999999999999986, 0.0056125035213041505], [-1.7999999999999989, 0.0072866908436532603], [-1.6999999999999993, 0.0093809505046099518], [-1.5999999999999996, 0.011975843956093591], [-1.5, 0.015160313978738623], [-1.3999999999999986, 0.01903062477929374], [-1.2999999999999989, 0.023688670135246819], [-1.1999999999999993, 0.029239577817796958], [-1.0999999999999996, 0.035788566089543263], [-1.0, 0.043437045933710075], [-0.89999999999999858, 0.052278010213200894], [-0.79999999999999893, 0.062390806519552228], [-0.69999999999999929, 0.073835451266829874], [-0.59999999999999964, 0.086646704726210833], [-0.5, 0.10082818534841768], [-0.39999999999999858, 0.11634685138962576], [-0.29999999999999893, 0.13312821280856266], [-0.19999999999999929, 0.15105265119043998], [-0.099999999999999645, 0.16995321550470713], [0.0, 0.18961522371860304], [0.10000000000000142, 0.20977793357596308], [0.20000000000000107, 0.23013845153193152], [0.30000000000000071, 0.2503579308476519], [0.40000000000000036, 0.27006997470594329], [0.5, 0.28889101667248257], [0.60000000000000142, 0.30643230931771337], [0.70000000000000107, 0.32231302358107095], [0.80000000000000071, 0.33617385758162033], [0.90000000000000036, 0.34769048390524482], [1.0, 0.35658613652140003], [1.1000000000000014, 0.36264265688118158], [1.2000000000000011, 0.3657093841944532], [1.3000000000000007, 0.3657093841944532], [1.4000000000000004, 0.36264265688118147], [1.5, 0.35658613652140003], [1.6000000000000014, 0.34769048390524465], [1.7000000000000011, 0.33617385758162011], [1.8000000000000007, 0.32231302358107067], [1.9000000000000004, 0.30643230931771309], [2.0, 0.28889101667248257], [2.1000000000000014, 0.270069974
[…]

### 2011-02-19 project/calc/check/check.py

@@ -14,8 +14,8 @@ def comparison_graph (n, p):
   # and writes it to an appropriately-named json file
 
   (binomial, normal, sn) = frame( binomial_pmf(n, p, pairs=True),
-                                  normal_pdf(n, p, pairs=True),
-                                  sn_pdf(n, p, pairs=True) )
+                                  normal_approx_pdf(n, p, pairs=True),
+                                  sn_approx_pdf(n, p, pairs=True) )
   np = 'n' + str(n) + 'p' + str(p).replace('.', '')
   f = open('check.js', 'w')
   f.write('binomial = ' + json.dumps(binomial) + ';\n')

### 2011-02-19 project/calc/flot-flyer/data/comparison-n25p005.js

@@ -1,3 +1,3 @@
 binomial.n25p005 = [[0, 0.27738957312183404], [1, 0.36498628042346593], [2, 0.2305176507937679], [3, 0.09301589417994148], [4, 0.026925653578404096], [5, 0.005951986580489327], [6, 0.0010442081720156706], [7, 0.0001491725960022389], [8, 1.7665175842370376e-05], [9, 1.7561870720485178e-06], [10, 1.4788943764619117e-07], [11, 1.0614074472214625e-08], [12, 6.5174141496055006e-10], [13, 3.4302179734765737e-11], [14, 1.547466754951837e-12], [15, 5.9726787033228998e-14], [16, 1.9646969418825246e-15], [17, 5.4743877637593453e-17], [18, 1.2805585412302651e-18], [19, 2.4830775037705939e-20], [20, 3.9206486901640898e-22], [21, 4.9130935966968624e-24], [22, 4.7015249729156167e-26], [23, 3.2275915145873905e-28], [24, 1.415610313415518e-30], [25, 2.9802322387695536e-33]];
-normal.n25p005 = [[-12.5, 9.8054321018951494e-36], [-12.4, 3.1081747156909754e-35], [-12.300000000000001, 9.7698274398292087e-35], [-12.199999999999999, 3.0451672200270222e-34], [-12.1, 9.4119190353642953e-34], [-12.0, 2.884615961658899e-33], [-11.9, 8.7667900356570669e-33], [-11.800000000000001, 2.6420193357264818e-32], [-11.699999999999999, 7.8954004371765707e-32], [-11.6, 2.339672736173526e-31], [-11.5, 6.8750973269162753e-31], [-11.4, 2.0032971362962954e-30], [-11.300000000000001, 5.7883485298253466e-30], [-11.199999999999999, 1.6584667133079403e-29], [-11.1, 4.711960366639648e-29], [-11.0, 1.3275145252068531e-28], [-10.9, 3.7086830364501341e-28], [-10.800000000000001, 1.0274079862969536e-27], [-10.699999999999999, 2.8223374599449685e-27], [-10.6, 7.6880770311361977e-27], [-10.5, 2.076678638014813e-26], [-10.4, 5.5624183387114977e-26], [-10.300000000000001, 1.4774091493598664e-25], [-10.199999999999999, 3.8911744670198537e-25], [-10.1, 1.0162566632989914e-24], [-10.0, 2.6318970184755208e-24], [-9.90000000000000
[…]

### 2011-02-19 project/calc/flot-flyer/data/comparison.js

@@ -5,5 +5,5 @@ var binomial = {}; var normal = {}; var sn = {};
 var ns = ["25"];
 var ps = ["0.05"];
 binomial.n25p005 = [[0, 0.27738957312183404], [1, 0.36498628042346593], [2, 0.2305176507937679], [3, 0.09301589417994148], [4, 0.026925653578404096], [5, 0.005951986580489327], [6, 0.0010442081720156706], [7, 0.0001491725960022389], [8, 1.7665175842370376e-05], [9, 1.7561870720485178e-06], [10, 1.4788943764619117e-07], [11, 1.0614074472214625e-08], [12, 6.5174141496055006e-10], [13, 3.4302179734765737e-11], [14, 1.547466754951837e-12], [15, 5.9726787033228998e-14], [16, 1.9646969418825246e-15], [17, 5.4743877637593453e-17], [18, 1.2805585412302651e-18], [19, 2.4830775037705939e-20], [20, 3.9206486901640898e-22], [21, 4.9130935966968624e-24], [22, 4.7015249729156167e-26], [23, 3.2275915145873905e-28], [24, 1.415610313415518e-30], [25, 2.9802322387695536e-33]];
-normal.n25p005 = [[-12.5, 9.8054321018951494e-36], [-12.4, 3.1081747156909754e-35], [-12.300000000000001, 9.7698274398292087e-35], [-12.199999999999999, 3.0451672200270222e-34], [-12.1, 9.4119190353642953e-34], [-12.0, 2.884615961658899e-33], [-11.9, 8.7667900356570669e-33], [-11.800000000000001, 2.6420193357264818e-32], [-11.699999999999999, 7.8954004371765707e-32], [-11.6, 2.339672736173526e-31], [-11.5, 6.8750973269162753e-31], [-11.4, 2.0032971362962954e-30], [-11.300000000000001, 5.7883485298253466e-30], [-11.199999999999999, 1.6584667133079403e-29], [-11.1, 4.711960366639648e-29], [-11.0, 1.3275145252068531e-28], [-10.9, 3.7086830364501341e-28], [-10.800000000000001, 1.0274079862969536e-27], [-10.699999999999999, 2.8223374599449685e-27], [-10.6, 7.6880770311361977e-27], [-10.5, 2.076678638014813e-26], [-10.4, 5.5624183387114977e-26], [-10.300000000000001, 1.4774091493598664e-25], [-10.199999999999999, 3.8911744670198537e-
[…]

### 2011-02-19 project/calc/flot-flyer/flot_data.py

@@ -15,8 +15,8 @@ def comparison_graph (n, p):
   # and writes it to an appropriately-named json file
 
   (binomial, normal, sn) = ( binomial_pmf(n, p, pairs=True),
-                             normal_pdf(n, p, pairs=True),
-                             sn_pdf(n, p, pairs=True) )
+                             normal_approx_pdf(n, p, pairs=True),
+                             sn_approx_pdf(n, p, pairs=True) )
   np = 'n' + str(n) + 'p' + str(p).replace('.', '')
   f = open('data/comparison-' + np + '.js', 'w')
   f.write('binomial.' + np + ' = ' + json.dumps(binomial) + ';\n')

### 2011-02-19 project/calc/flot-paper/data/comparison-n100p005.js

@@ -1,3 +1,3 @@
-binomial.n100p005 = [[0, 0.0059205292203340226], [1, 0.03116068010702119], [2, 0.081181771857765733], [3, 0.13957567793089548], [4, 0.1781426415696955], [5, 0.18001782727042917], [6, 0.15001485605869097], [7, 0.10602553736478915], [8, 0.064870887992930129], [9, 0.034901296464032595], [10, 0.016715884095931416], [11, 0.0071982276011187795], [12, 0.0028098344583314594]];
-normal.n100p005 = [[-1.8999999999999986, 0.0012191641358520961], [-1.7999999999999972, 0.0014082897370225509], [-1.6999999999999957, 0.0016233327334031285], [-1.5999999999999943, 0.0018672771100609077], [-1.5, 0.0021433628389205886], [-1.3999999999999986, 0.0024550950794230628], [-1.2999999999999972, 0.0028062517606520752], [-1.1999999999999957, 0.0032008892034407583], [-1.0999999999999943, 0.0036433454218266445], [-1.0, 0.0041382407277875443], [-0.89999999999999858, 0.0046904752523049759], [-0.79999999999999716, 0.0053052229903312936], [-0.69999999999999574, 0.0059879219780468217], [-0.59999999999999432, 0.0067442602187242594], [-0.5, 0.0075801569893693115], [-0.39999999999999858, 0.0085017391848058645], [-0.29999999999999716, 0.0095153123896468701], [-0.19999999999999574, 0.010627326412148358], [-0.099999999999994316, 0.011844335067623455], [0.0, 0.01317295006307056], [0.10000000000000142, 0.014619788908898479], [0.20000000000000284, 0.016191416867835845], [0.30000000000000426, 0.017894283044771704], [0.40000000000000568, 0.019734650823578642], [0.5, 0.021718522966855038], [0.60000000000000142, 0.023851561810614121], [0.70000000000000284, 0.026139005106600447], [0.80000000000000426, 0.028585578188213685], [0.90000000000000568, 0.031195403259776221], [1.0, 0.033971906730703126], [1.1000000000000014, 0.036917725633414937], [1.2000000000000028, 0.040034614273825014], [1.3000000000000043, 0.043323352363105534], [1.4000000000000057, 0.04678365596628304], [1.5, 0.050414092674208842], [1.6000000000000014, 0.054212002457823774], [1.7000000000000028, 0.058173425694812882], [1.8000000000000043, 0.062293039866414518], [1.9000000000000057, 0.0665641064042
[…]

### 2011-02-19 project/calc/flot-paper/data/comparison-n100p01.js

@@ -1,3 +1,3 @@
 binomial.n100p01 = [[1, 0.00029512665430652746], [2, 0.0016231965986859026], [3, 0.0058916024693043837], [4, 0.015874595542292355], [5, 0.033865803823557056], [6, 0.059578728948850357], [7, 0.088895246368125971], [8, 0.11482302655882932], [9, 0.13041627707916414], [10, 0.13186534682448822], [11, 0.11987758802226202], [12, 0.098788012351678889], [13, 0.074302094760237095], [14, 0.051303827334449471], [15, 0.03268243815379742], [16, 0.019291716965783169], [17, 0.01059153088317509], [18, 0.0054265250821205662], [19, 0.0026021933142332601], [20, 0.0011709869914049665]];
-normal.n100p01 = [[0.10000000000000142, 0.00057418964635122809], [0.20000000000000284, 0.0006405993231173386], [0.30000000000000426, 0.00071389615734425915], [0.40000000000000568, 0.0007946960671549524], [0.5, 0.00088365865147670174], [0.60000000000000142, 0.00098148904012778813], [0.70000000000000284, 0.0010889396853999758], [0.80000000000000426, 0.0012068120760064351], [0.90000000000000568, 0.001335958352772122], [1.0, 0.0014772828039793357], [1.1000000000000014, 0.0016317432168629802], [1.2000000000000028, 0.0018003520603981317], [1.3000000000000043, 0.0019841774732586269], [1.4000000000000057, 0.002184344029671186], [1.5, 0.0024020332548697412], [1.6000000000000014, 0.0026384838609933262], [1.7000000000000028, 0.0028949916735929748], [1.8000000000000043, 0.0031729092184457413], [1.9000000000000057, 0.0034736449381408832], [2.0, 0.0037986620079324806], [2.1000000000000014, 0.0041494767206680721], [2.2000000000000028, 0.0045276564112285483], [2.3000000000000043, 0.0049348168918754536], [2.4000000000000057, 0.005372619371216354], [2.5, 0.0058427668311895132], [2.6000000000000014, 0.0063469998385500956], [2.7000000000000028, 0.006887091769826088], [2.8000000000000043, 0.0074648434316143229], [2.9000000000000057, 0.0080820770614091521], [3.0, 0.0087406296979031604], [3.1000000000000014, 0.0094423459138670701], [3.2000000000000028, 0.010189069909295179], [3.3000000000000043, 0.010982636967484792], [3.40000000
[…]

### 2011-02-19 project/calc/flot-paper/data/comparison-n100p02.js

@@ -1,3 +1,3 @@
 binomial.n100p02 = [[1, 5.0925899408361951e-09], [2, 6.3020800517847603e-08], [3, 5.1466987089575957e-07], [4, 3.1201860923055465e-06], [5, 1.4976893243066604e-05], [6, 5.9283535753805477e-05], [7, 0.00019902329860206099], [8, 0.0005784114615622392], [9, 0.0014781626239923893], [10, 0.0033628199695826867], [11, 0.0068784953923282143], [12, 0.012753876873275253], [13, 0.021583483939388855], [14, 0.033531483977264888], [15, 0.048061793700746272], [16, 0.063832069758803622], [17, 0.07885138029028689], [18, 0.090898118945747383], [19, 0.098074286230937988], [20, 0.099300214808824699], [21, 0.094571633151261603], [22, 0.084899534306246222], [23, 0.071980039955295727], [24, 0.057733990380810084], [25, 0.043877832689415662], [26, 0.031642667804867075], [27, 0.021681087199631102], [28, 0.014131422906902455], [29, 0.0087712280111808347], [30, 0.0051896432399486528], [31, 0.0029296373128742349], [32, 0.0015792576139712665]];
-normal.n100p02 = [[0.10000000000000142, 4.2103688497921958e-07], [0.20000000000000284, 4.7665022578070438e-07], [0.30000000000000426, 5.392721945591147e-07], [0.40000000000000568, 6.0974018647334344e-07], [0.5, 6.8898564938749303e-07], [0.60000000000000142, 7.7804389478723611e-07], [0.70000000000000284, 8.780648418045741e-07], [0.80000000000000426, 9.9032477275802412e-07], [0.90000000000000568, 1.1162391840711678e-06], [1.0, 1.2573768221481113e-06], [1.1000000000000014, 1.4154749997587146e-06], [1.2000000000000028, 1.5924562947167809e-06], [1.3000000000000043, 1.7904467391169912e-06], [1.4000000000000057, 2.0117956141230878e-06], [1.5, 2.2590969722628434e-06], [1.6000000000000014, 2.5352130163716896e-06], [1.7000000000000028, 2.8432994717216791e-06], [1.8000000000000043, 3.1868330954583774e-06], [1.9000000000000057, 3.569641475221975e-06], [2.0, 3.9959352767263687e-06], [2.1000000000000014, 4.4703431080810919e-06], [2.2000000000000028, 4.9979491767307147e-06], [
[…]

### 2011-02-19 project/calc/flot-paper/data/comparison-n25p005.js

@@ -1,3 +1,3 @@
 binomial.n25p005 = [[0, 0.27738957312183404], [1, 0.36498628042346593], [2, 0.2305176507937679], [3, 0.09301589417994148], [4, 0.026925653578404096], [5, 0.005951986580489327]];
-normal.n25p005 = [[-2.2999999999999989, 0.0018158902218712231], [-2.1999999999999993, 0.0024383282717041922], [-2.0999999999999996, 0.0032466654668062431], [-2.0, 0.0042867256778411772], [-1.8999999999999986, 0.0056125035213041505], [-1.7999999999999989, 0.0072866908436532603], [-1.6999999999999993, 0.0093809505046099518], [-1.5999999999999996, 0.011975843956093591], [-1.5, 0.015160313978738623], [-1.3999999999999986, 0.01903062477929374], [-1.2999999999999989, 0.023688670135246819], [-1.1999999999999993, 0.029239577817796958], [-1.0999999999999996, 0.035788566089543263], [-1.0, 0.043437045933710075], [-0.89999999999999858, 0.052278010213200894], [-0.79999999999999893, 0.062390806519552228], [-0.69999999999999929, 0.073835451266829874], [-0.59999999999999964, 0.086646704726210833], [-0.5, 0.10082818534841768], [-0.39999999999999858, 0.11634685138962576], [-0.29999999999999893, 0.13312821280856266], [-0.19999999999999929, 0.15105265119043998], [-0.099999999999999645, 0.16995321550470713], [0.0, 0.18961522371860304], [0.10000000000000142, 0.20977793357596308], [0.20000000000000107, 0.23013845153193152], [0.30000000000000071, 0.2503579308476519], [0.40000000000000036, 0.27006997470594329], [0.5, 0.28889101667248257], [0.60000000000000142, 0.30643230931771337], [0.70000000000000107, 0.32231302358107095], [0.80000000000000071, 0.33617385758162033], [0.90000000000000036, 0.34769048390524482], [1.0, 0.35658613652140003], [1.1000000000000014, 0.36264265688118158], [1.2000000000000011, 0.3657093841944532], [1.3000000000000007, 0.3657093841944532], [1.4000000000000004, 0.36264265688118147], [1.5, 0.35658613652140003], [1.6000000000000014, 0.34769048390524465], [1.7000000000000011, 0.33617385758162011], [1.8000000000000007, 0.32231302358107067], [1.9000000000000004, 0.30643230931771309], [2.0, 0.28889101667248257], [2.100000000
[…]

### 2011-02-19 project/calc/flot-paper/data/comparison-n25p01.js

@@ -1,3 +1,3 @@
 binomial.n25p01 = [[0, 0.071789798769185287], [1, 0.19941610769218129], [2, 0.26588814358957502], [3, 0.2264973075022306], [4, 0.1384150212513631], [5, 0.064593676583969487], [6, 0.023923583919988702], [7, 0.0072150491187267475], [8, 0.0018037622796816882]];
-normal.n25p01 = [[-2.3999999999999986, 0.0012811986462346772], [-2.2999999999999989, 0.0015893921343098992], [-2.1999999999999993, 0.0019629780802555763], [-2.0999999999999996, 0.0024136241520128598], [-2.0, 0.0029545656079586714], [-1.8999999999999986, 0.0036007041207962633], [-1.7999999999999989, 0.0043686880593423599], [-1.6999999999999993, 0.0052769677219866524], [-1.5999999999999996, 0.0063458184368914653], [-1.5, 0.0075973240158649612], [-1.3999999999999986, 0.0090553128224570966], [-1.2999999999999989, 0.010745238742432675], [-1.1999999999999993, 0.012693999677100191], [-1.0999999999999996, 0.014929686863228599], [-1.0, 0.017481259395806321], [-0.89999999999999858, 0.020378139818590359], [-0.79999999999999893, 0.023649728564154322], [-0.69999999999999929, 0.027324837363481486], [-0.59999999999999964, 0.03143104447724774], [-0.5, 0.035993977675458706], [-0.39999999999999858, 0.041036534232898242], [-0.29999999999999893, 0.046578050713943504], [-0.19999999999999929, 0.052633438867262808], [-0.099999999999999645, 0.059212307393727931], [0.0, 0.066318092528499115], [0.10000000000000142, 0.073947223119637168], [0.20000000000000107, 0.082088348017233137], [0.30000000000000071, 0.090721654941518792], [0.40000000000000036, 0.099818310423829965], [0.5, 0.10934004978399575], [0.60000000000000142, 0.11923894432969383], [0.70000000000000107, 0.12945736998880875], [0.80000000000000071, 0.13992819741648291], [0.90000000000000036, 0.15057521831141635], [1.0, 0.16131381634609557], [1.1000000000000014, 0.17205188393549195], [1.2000000000000011, 0.18269097826468578], [1.3000000000000007, 0.19312770184098857], [1.4000000000000004, 0.20325528464034481], [1.5, 0.2129653370149015], [1.6000000000000014, 0.22214973526119988], [1.7000000000000011, 
[…]

### 2011-02-19 project/calc/flot-paper/data/comparison-n25p02.js

@@ -1,3 +1,3 @@
 binomial.n25p02 = [[0, 0.0037778931862957207], [1, 0.023611832414348225], [2, 0.070835497243044665], [3, 0.13576803638250232], [4, 0.18668105002594063], [5, 0.19601510252723772], [6, 0.16334591877269811], [7, 0.11084187345290229], [8, 0.062348553817257506], [9, 0.029442372635927135], [10, 0.011776949054370864], [11, 0.0040148689958082462], [12, 0.00117100345711074]];
-normal.n25p02 = [[-1.3999999999999986, 0.0011920441007324243], [-1.2999999999999989, 0.001397129207439726], [-1.1999999999999993, 0.0016334095280999624], [-1.0999999999999996, 0.0019048810491109052], [-1.0, 0.0022159242059690038], [-0.89999999999999858, 0.0025713204615269761], [-0.79999999999999893, 0.0029762662098879321], [-0.69999999999999929, 0.0034363833453069891], [-0.59999999999999964, 0.0039577257914899843], [-0.5, 0.0045467812507955264], [-0.39999999999999858, 0.0052104674072113071], [-0.29999999999999893, 0.0059561218038025974], [-0.19999999999999929, 0.0067914846168428168], [-0.099999999999999645, 0.0077246735671975871], [0.0, 0.0087641502467842702], [0.10000000000000142, 0.009918677195897679], [0.20000000000000107, 0.011197265147421465], [0.30000000000000071, 0.012609109957597208], [0.40000000000000036, 0.014163518870800593], [0.5, 0.015869825917833709], [0.60000000000000142, 0.017737296423115743], [0.70000000000000107, 0.019775020794685131], [0.80000000000000071, 0.021991797990213616], [0.90000000000000036, 0.024396009289591382], [1.0, 0.026995483256594031], [1.1000000000000014, 0.029797353034408083], [1.2000000000000011, 0.032807907387338332], [1.3000000000000007, 0.03603243716810902], [1.4000000000000004, 0.039475079150447089], [1.5, 0.043138659413255766], [1.6000000000000014, 0.047024538688443522], [1.7000000000000011, 0.051132462281989047], [1.8000000000000007, 0.055460417339727813], [1.9000000000000004, 0.060004500348492827], [2.0, 0.064758797832945872], [2.1000000000000014, 0.06971528322268021], [2.2000000000000011, 0.074863732817872494], [2.3000000000000007, 0.08019166367095984], [2.4000000000000004, 0.085684296023903705], [2.5,
[…]

### 2011-02-19 project/calc/flot-paper/data/comparison-n50p005.js

@@ -1,3 +1,3 @@
 binomial.n50p005 = [[0, 0.076944975276713304], [1, 0.20248677704398246], [2, 0.26110137039881948], [3, 0.21987483823058485], [4, 0.13597522890575636], [5, 0.065840637154366277], [6, 0.025989725192513007], [7, 0.0085981045749667171], [8, 0.0024323585310761071]];
-normal.n50p005 = [[-2.5, 0.0013406574558021095], [-2.3999999999999986, 0.0016513302660337973], [-2.2999999999999972, 0.0020254496215480859], [-2.1999999999999993, 0.0024738897542732939], [-2.0999999999999979, 0.0030089199233940414], [-2.0, 0.0036442848002950072], [-1.8999999999999986, 0.0043952682008083343], [-1.7999999999999972, 0.0052787348015545825], [-1.6999999999999993, 0.0063131440461368007], [-1.5999999999999979, 0.0075185301389666783], [-1.5, 0.008916441877914209], [-1.3999999999999986, 0.010529836130576051], [-1.2999999999999972, 0.012382919050131915], [-1.1999999999999993, 0.014500929689324172], [-1.0999999999999979, 0.016909861532898293], [-1.0, 0.019636118649264615], [-0.89999999999999858, 0.022706104669576822], [-0.79999999999999716, 0.026145744631882722], [-0.69999999999999929, 0.029979941859107882], [-0.59999999999999787, 0.03423197443496339], [-0.5, 0.038922838446123091], [-0.39999999999999858, 0.044070547898868148], [-0.29999999999999716, 0.049689404003351985], [-0.19999999999999929, 0.055789249243008349], [-0.099999999999997868, 0.06237472419243404], [0.0, 0.069444547288254582], [0.10000000000000142, 0.076990839564886129], [0.20000000000000284, 0.084998517614416694], [0.30000000000000071, 0.093444778600168213], [0.40000000000000213, 0.10229870094607199], [0.5, 0.1115209832610139], [0.60000000000000142, 0.12106384209020657], [0.70000000000000284, 0.13087108620049576], [0.80000000000000071, 0.14087838132833658], [0.90000000000000213, 0.15101371471431424], [1.0, 0.16119806342500592], [1.1000000000000014, 0.17134626457065114], [1.2000000000000028, 0.18136807925119974], [1.3000000000000007, 0.19116943562042285], [1.4000000000000021, 0.2006538300870899], [1.5, 0.20972385962599882], [1.6000000000000014, 0.21828285270
[…]

### 2011-02-19 project/calc/flot-paper/data/comparison-n50p01.js

@@ -1,3 +1,3 @@
 binomial.n50p01 = [[0, 0.0051537752073201179], [1, 0.028632084485111745], [2, 0.077942896653915281], [3, 0.13856514960696054], [4, 0.18090450087575399], [5, 0.18492460089521523], [6, 0.15410383407934602], [7, 0.10762807459509882], [8, 0.064277877883183995], [9, 0.033329270013502797], [10, 0.015183334117262396], [11, 0.0061346804514191425], [12, 0.0022153012741235843]];
-normal.n50p01 = [[-1.6999999999999993, 0.0012827423789119243], [-1.5999999999999979, 0.0014870258441527051], [-1.5, 0.0017200160169201504], [-1.3999999999999986, 0.0019850953262349094], [-1.2999999999999972, 0.0022859416666344795], [-1.1999999999999993, 0.0026265388064731147], [-1.0999999999999979, 0.0030111847408909502], [-1.0, 0.00344449755901534], [-0.89999999999999858, 0.0039314183717502815], [-0.79999999999999716, 0.0044772108284731023], [-0.69999999999999929, 0.0050874567392413068], [-0.59999999999999787, 0.0057680473148802461], [-0.5, 0.0065251695417308121], [-0.39999999999999858, 0.007365287222001856], [-0.29999999999999716, 0.0082951162356284368], [-0.19999999999999929, 0.0093215936162154012], [-0.099999999999997868, 0.010451840082811418], [0.0, 0.011693115731494954], [0.10000000000000142, 0.013052768666405475], [0.20000000000000284, 0.014538176438990937], [0.30000000000000071, 0.01615668026663878], [0.40000000000000213, 0.017915512116933648], [0.5, 0.019821714870604891], [0.60000000000000142, 0.021882055913474675], [0.70000000000000284, 0.024102934653665142], [0.80000000000000071, 0.026490284612879656], [0.90000000000000213, 0.029049470897229448], [1.0, 0.031785184010991327], [1.1000000000000014, 0.034701331132678315], [1.2000000000000028, 0.03780092612341629], [1.3000000000000007, 0.04108597967919389], [1.4000000000000021, 0.044557391167256599], [1.5, 0.048214843798882606], [1.6000000000000014, 0.052056704882168875], [1.7000000000000028, 0.056079932965540813], [1.8000000000000007, 0.060279993722034561], [1.9000000000000021, 0.064650786432834936], [2.0, 0.069184582903432448], [2.1000000000000014, 0.073871980584982025], [2.20000000000
[…]

### 2011-02-19 project/calc/flot-paper/data/comparison-n50p02.js

@@ -1,3 +1,3 @@
 binomial.n50p02 = [[1, 0.00017840596158824417], [2, 0.0010927365147280004], [3, 0.004370946058912006], [4, 0.012839654048054001], [5, 0.029531204310524219], [6, 0.055371008082232921], [7, 0.087011584129223205], [8, 0.11692181617364357], [9, 0.13640878553591751], [10, 0.13981900517431545], [11, 0.12710818652210495], [12, 0.10327540154921028], [13, 0.07547048574749983], [14, 0.04986442808316955], [15, 0.02991865684990171], [16, 0.016361765464789985], [17, 0.0081808827323950062], [18, 0.0037495712523476997], [19, 0.0015787668430937746]];
-normal.n50p02 = [[0.10000000000000142, 0.00030834714854106589], [0.20000000000000284, 0.00034874857737636071], [0.30000000000000071, 0.00039395088884201855], [0.40000000000000213, 0.00044445608510971965], [0.5, 0.00050080973270877826], [0.60000000000000142, 0.00056360364869912326], [0.70000000000000284, 0.00063347862237011078], [0.80000000000000071, 0.00071112715531567144], [0.90000000000000213, 0.00079729620040513299], [1.0, 0.0008927898777522479], [1.1000000000000014, 0.00099847214330080875], [1.2000000000000028, 0.0011152693831145296], [1.3000000000000007, 0.0012441729039068441], [1.4000000000000021, 0.0013862412877997726], [1.5, 0.0015426025767917133], [1.6000000000000014, 0.0017144562499758578], [1.7000000000000028, 0.0019030749542206786], [1.8000000000000007, 0.0021098059468425165], [1.9000000000000021, 0.0023360722068095311], [2.0, 0.0025833731692615088], [2.1000000000000014, 0.0028532850366584754], [2.2000000000000028, 0.0031474606187300966], [2.3000000000000007, 0.0034676286526377988], [2.4000000000000021, 0.0038155925544309877], [2.5, 0.0041932285530270133], [2.6000000000000014, 0.0046024831586201249], [2.7000000000000028, 0.0050453699186720847], [2.8000000000000007, 0.0055239654165013911], [2.9000000000000021, 0.0060404044700066934], [3.0, 0.0065968744912687964], [3.1000000000000014, 0.007195608971703845], [3.2000000000000028, 0.0078388800621085712], [3.3000000000000007, 0.0085289902223649027], [3.4000000000000021, 0.00926
[…]

### 2011-02-19 project/calc/flot-paper/flot_data.py

@@ -50,8 +50,8 @@ def comparison_graph (n, p):
   # and writes it to an appropriately-named json file
 
   (binomial, normal, sn) = frame( binomial_pmf(n, p, pairs=True),
-                                  normal_pdf(n, p, pairs=True),
-                                  sn_pdf(n, p, pairs=True) )
+                                  normal_approx_pdf(n, p, pairs=True),
+                                  sn_approx_pdf(n, p, pairs=True) )
   np = 'n' + str(n) + 'p' + str(p).replace('.', '')
   f = open('data/comparison-' + np + '.js', 'w')
   f.write('binomial.' + np + ' = ' + json.dumps(binomial) + ';\n')

### 2011-02-19 project/calc/flot-pres/data/comparison-n25p005.js

@@ -1,3 +1,3 @@
 binomial.n25p005 = [[0, 0.27738957312183404], [1, 0.36498628042346593], [2, 0.2305176507937679], [3, 0.09301589417994148], [4, 0.026925653578404096], [5, 0.005951986580489327], [6, 0.0010442081720156706], [7, 0.0001491725960022389], [8, 1.7665175842370376e-05], [9, 1.7561870720485178e-06], [10, 1.4788943764619117e-07], [11, 1.0614074472214625e-08], [12, 6.5174141496055006e-10], [13, 3.4302179734765737e-11], [14, 1.547466754951837e-12], [15, 5.9726787033228998e-14], [16, 1.9646969418825246e-15], [17, 5.4743877637593453e-17], [18, 1.2805585412302651e-18], [19, 2.4830775037705939e-20], [20, 3.9206486901640898e-22], [21, 4.9130935966968624e-24], [22, 4.7015249729156167e-26], [23, 3.2275915145873905e-28], [24, 1.415610313415518e-30], [25, 2.9802322387695536e-33]];
-normal.n25p005 = [[-12.5, 9.8054321018951494e-36], [-12.4, 3.1081747156909754e-35], [-12.300000000000001, 9.7698274398292087e-35], [-12.199999999999999, 3.0451672200270222e-34], [-12.1, 9.4119190353642953e-34], [-12.0, 2.884615961658899e-33], [-11.9, 8.7667900356570669e-33], [-11.800000000000001, 2.6420193357264818e-32], [-11.699999999999999, 7.8954004371765707e-32], [-11.6, 2.339672736173526e-31], [-11.5, 6.8750973269162753e-31], [-11.4, 2.0032971362962954e-30], [-11.300000000000001, 5.7883485298253466e-30], [-11.199999999999999, 1.6584667133079403e-29], [-11.1, 4.711960366639648e-29], [-11.0, 1.3275145252068531e-28], [-10.9, 3.7086830364501341e-28], [-10.800000000000001, 1.0274079862969536e-27], [-10.699999999999999, 2.8223374599449685e-27], [-10.6, 7.6880770311361977e-27], [-10.5, 2.076678638014813e-26], [-10.4, 5.5624183387114977e-26], [-10.300000000000001, 1.4774091493598664e-25], [-10.199999999999999, 3.8911744670198537e-25], [-10.1, 1.0162566632989914e-24], [-10.0, 2.6318970184755208e-24], [-9.90000000000000
[…]

### 2011-02-19 project/calc/flot-pres/data/comparison-n25p05.js

@@ -1,3 +1,3 @@
 binomial.n25p05 = [[0, 2.9802322387695299e-08], [1, 7.4505805969238398e-07], [2, 8.9406967163085887e-06], [3, 6.8545341491699219e-05], [4, 0.00037699937820434603], [5, 0.0015833973884582498], [6, 0.0052779912948608364], [7, 0.014325976371765123], [8, 0.032233446836471509], [9, 0.060885399580001845], [10, 0.097416639328002888], [11, 0.13284087181091306], [12, 0.15498101711273193], [13, 0.15498101711273193], [14, 0.13284087181091311], [15, 0.097416639328002888], [16, 0.060885399580001845], [17, 0.032233446836471495], [18, 0.014325976371765135], [19, 0.0052779912948608416], [20, 0.0015833973884582498], [21, 0.00037699937820434603], [22, 6.8545341491699219e-05], [23, 8.9406967163085887e-06], [24, 7.4505805969238398e-07], [25, 2.9802322387695299e-08]];
-normal.n25p05 = [[-12.5, 3.0778394506825677e-23], [-12.4, 4.5879250992958145e-23], [-12.300000000000001, 6.8279731581743959e-23], [-12.199999999999999, 1.0145475816795948e-22], [-12.1, 1.5050750751694145e-22], [-12.0, 2.2292000090882762e-22], [-11.9, 3.2964389534035635e-22], [-11.800000000000001, 4.8668299010249154e-22], [-11.699999999999999, 7.1738522291748712e-22], [-11.6, 1.0557566227027385e-21], [-11.5, 1.5512447726987843e-21], [-11.4, 2.2756317082077838e-21], [-11.300000000000001, 3.3329496336528395e-21], [-11.199999999999999, 4.87372088665097e-21], [-11.1, 7.1153732360386862e-21], [-11.0, 1.0371458804401484e-20], [-10.9, 1.5093401896002006e-20], [-10.800000000000001, 2.1930046609333164e-20], [-10.699999999999999, 3.1812448892795117e-20], [-10.6, 4.6074409517652996e-20], [-10.5, 6.6623521295197154e-20], [-10.4, 9.6183486775425917e-20], [-10.300000000000001, 1.3863681719331418e-19], [-10.199999999999999, 1.995086687558436e-19], [-10.1, 2.8664877556044265e-19], [-10.0, 4.1119094286675663e-19], [-9.9000000000000004, 5.8890076430177032e-19], [-9.80000000
[…]

### 2011-02-19 project/calc/flot-pres/flot_data.py

@@ -3,6 +3,7 @@
 
 import json
 import sys
+sys.path.append('..')
 from stats import *
 
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
@@ -12,27 +13,15 @@ def comparison_graph (n, p):
   # Builds data for one comparison graph (binomial, normal, and skew-normal)
   # and writes it to an appropriately-named json file
 
-#  (binomial, normal, sn) = frame( binomial_pmf(n, p, pairs=True),
-#                                  normal_pdf(n, p, pairs=True),
-#                                  sn_pdf(n, p, pairs=True) )
   (binomial, normal, sn) = ( binomial_pmf(n, p, pairs=True),
-                             normal_pdf(n, p, pairs=True),
-                             sn_pdf(n, p, pairs=True) )
+                             normal_approx_pdf(n, p, pairs=True),
+                             sn_approx_pdf(n, p, pairs=True) )
   np = 'n' + str(n) + 'p' + str(p).replace('.', '')
   f = open('data/comparison-' + np + '.js', 'w')
   f.write('binomial.' + np + ' = ' + json.dumps(binomial) + ';\n')
   f.write('normal.' + np + ' = ' + json.dumps(normal) + ';\n')
   f.write('sn.' + np + ' = ' + json.dumps(sn) + ';\n')
   f.close()
-
-def frame (*args):
-  # Chops off the tails where all three graphs are less than 0.001
-  tmp = map(lambda list: filter(lambda point: point[1] > 0.001, list), args)
-  left = right = 0
-  for i, v in enumerate(tmp):
-    if v[0][0] < left: left = v[0][0]
-    if v[-1][0] > right: right = v[-1][0]
-  return map(lambda list: filter(lambda point: left < point[0] < right, list), args)
 
 def compile_comparison_data ():
   # Set ns and ps
@@ -48,6 +37,18 @@ def compile_comparison_data ():
 
   # Write our graphs
   map(lambda n: map(lambda p: comparison_graph(n, p), ps), ns)
+
+#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
+# Common helpers
+#
+def frame (*args):
[…]

### 2011-02-19 project/calc/stats.py

@@ -23,13 +23,18 @@ def binomial_pmf (n, p, pairs=False):
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # Normal Approximation
 #
-def normal_pdf (n, p, pairs=False):
+def normal_pdf (mu, sigma, pairs=False):
+  # Given mu and sigma, returns a normal pdf in two arrays of xs and ys, respectively
+  # If pairs is True, it returns the pdf as an array of points
+  xs = r.seq(mu - 5*sigma, mu + 5*sigma, 0.1)
+  ys = r.dnorm(xs, mu, sigma)
+  return pair(xs, ys) if pairs else {'xs':xs, 'ys':ys}
+
+def normal_approx_pdf (n, p, pairs=False):
   # Given bin(n, p), returns an approximating normal pdf in two arrays of xs and ys, respectively
   # If pairs is True, it returns the pdf as an array of points
   (mu, sigma) = normal_params(n, p)
-  xs = r.seq(-n/2, 1.5*n, 0.1)
-  ys = r.dnorm(xs, mu, sigma)
-  return pair(xs, ys) if pairs else {'xs':xs, 'ys':ys}
+  return normal_pdf(mu, sigma, pairs)
 
 def normal_params (n, p):
   # Given n and p, returns the parameters of the normal approximation as a tuple (mu, sigma)
@@ -39,13 +44,18 @@ def normal_params (n, p):
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # Skew-normal Approximation
 #
-def sn_pdf (n, p, pairs=False):
+def sn_pdf (mu, sigma, skew, pairs=False):
+  # Given mu, sigma, and skew, returns a skew-normal pdf in two arrays of xs and ys, respectively
+  # If pairs is True, it returns the pdf as an array of points
+  xs = r.seq(mu - 5*sigma, mu + 5*sigma, 0.1)
+  ys = r.dsn(xs, mu, sigma, skew)
+  return pair(xs, ys) if pairs else {'xs':xs, 'ys':ys}
+
+def sn_approx_pdf (n, p, pairs=False):
[…]

### 2011-02-19 project/calc/flot-flyer/flot_data.py
Changed all method names to begin with verbs

@@ -10,7 +10,7 @@ from stats import *
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # Comparison Graphs
 #
-def comparison_graph (n, p):
+def write_comparison_graph (n, p):
   # Builds data for one comparison graph (binomial, normal, and skew-normal)
   # and writes it to an appropriately-named json file
 
@@ -37,7 +37,7 @@ def compile_comparison_data ():
   f.close()
 
   # Write our graphs
-  map(lambda n: map(lambda p: comparison_graph(n, p), ps), ns)
+  map(lambda n: map(lambda p: write_comparison_graph(n, p), ps), ns)
 
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # Action, baby!

### 2011-02-19 project/calc/flot-paper/flot_data.py

@@ -9,7 +9,7 @@ from stats import *
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # Skew-normal Restriction Graphs
 #
-def sn_restriction_p_range_graph ():
+def write_sn_restriction_p_range_graph ():
   # Builds data for the "fixed n, viable p range" graph and writes it to an
   # appropriately named json file
 
@@ -27,7 +27,7 @@ def sn_restriction_p_range_graph ():
   f.write('var p_bottom_points = ' + json.dumps(p_bottom_points) + ';\n')
   f.close()
 
-def sn_restriction_least_n_graph ():
+def write_sn_restriction_least_n_graph ():
   # Builds data for the "fixed p, least n" graph and writes it to an
   # appropriately named json file
 
@@ -39,13 +39,13 @@ def sn_restriction_least_n_graph ():
   f.close()
 
 def compile_sn_restriction_data ():
-  sn_restriction_p_range_graph()
-  sn_restriction_least_n_graph()
+  write_sn_restriction_p_range_graph()
+  write_sn_restriction_least_n_graph()
 
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # Comparison Graphs
 #
-def comparison_graph (n, p):
+def write_comparison_graph (n, p):
   # Builds data for one comparison graph (binomial, normal, and skew-normal)
   # and writes it to an appropriately-named json file
 
@@ -81,12 +81,12 @@ def compile_comparison_data ():
   f.close()
 
   # Write our graphs
-  map(lambda n: map(lambda p: comparison_graph(n, p), ps), ns)
+  map(lambda n: map(lambda p: write_comparison_graph(n, p), ps), ns)
 
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # MABS
 #
-def mabs_fixed_n_graph (n):
+def write_mabs_fixed_n_graph (n):
   # Builds data for one mabs graph with fixed n and varying p, and writes it to
   # an appropriately-named file
 
[…]

### 2011-02-19 project/calc/flot-pres/flot_data.py

@@ -9,7 +9,7 @@ from stats import *
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # Comparison Graphs
 #
-def comparison_graph (n, p):
+def write_comparison_graph (n, p):
   # Builds data for one comparison graph (binomial, normal, and skew-normal)
   # and writes it to an appropriately-named json file
 
@@ -36,13 +36,36 @@ def compile_comparison_data ():
   f.close()
 
   # Write our graphs
-  map(lambda n: map(lambda p: comparison_graph(n, p), ps), ns)
+  map(lambda n: map(lambda p: write_comparison_graph(n, p), ps), ns)
+
+#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
+# Property Graphs:
+#
+def write_property_graph (mu, sigma, skew):
+  str_skew = str(skew) if skew > 0 else 'neg' + str(-skew)
+  sn_graph = frame( sn_pdf(mu, sigma, skew, pairs=True) )
+  #sn_graph = sn_pdf(mu, sigma, skew, pairs=True)
+
+  f = open('data/properties-skew' + str_skew + '.js', 'w')
+  f.write('std_sn.skew' + str_skew + ' = ' + json.dumps(sn_graph) + ';\n')
+
+def compile_property_graphs_data ():
+  skews = [-1000, -100, -10, -5, -3, -2, -1, 1, 2, 3, 5, 10, 100, 1000]
+
+  # Write some necessary headers
+  f = open('data/properties-headers.js', 'w')
+  f.write('var std_sn = {};\n')
+  f.write('var skews = ' + json.dumps(map(str, skews)) + ';\n')
+  f.close()
+
+  # Write our graphs
+  map(lambda skew: write_property_graph(0, 1, skew), skews)
 
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # Common helpers
 #
 def frame (*args):
-  # Chops off the tails where all three graphs are less than 0.001
+  # Chops off the tails where all three graphs are less than 0.00001
[…]

### 2011-02-19 project/calc/check/check.py
Fixed a bug in the way the results from frame were being assigned.

@@ -13,7 +13,7 @@ def comparison_graph (n, p):
   # Builds data for one comparison graph (binomial, normal, and skew-normal)
   # and writes it to an appropriately-named json file
 
-  (binomial, normal, sn) = frame( binomial_pmf(n, p, pairs=True),
+  [binomial, normal, sn] = frame( binomial_pmf(n, p, pairs=True),
                                   normal_approx_pdf(n, p, pairs=True),
                                   sn_approx_pdf(n, p, pairs=True) )
   np = 'n' + str(n) + 'p' + str(p).replace('.', '')

### 2011-02-19 project/calc/flot-paper/flot_data.py

@@ -49,7 +49,7 @@ def write_comparison_graph (n, p):
   # Builds data for one comparison graph (binomial, normal, and skew-normal)
   # and writes it to an appropriately-named json file
 
-  (binomial, normal, sn) = frame( binomial_pmf(n, p, pairs=True),
+  [binomial, normal, sn] = frame( binomial_pmf(n, p, pairs=True),
                                   normal_approx_pdf(n, p, pairs=True),
                                   sn_approx_pdf(n, p, pairs=True) )
   np = 'n' + str(n) + 'p' + str(p).replace('.', '')

### 2011-02-20 project/calc/flot-pres/data/properties-sn-skew10.js
Implemented property graphs: skew-normal, half-normal, and sn reflection

@@ -1,0 +1,1 @@
+std_sn.skew10 = [[-5.0, 0.0], [-4.9900000000000002, 0.0], [-4.9800000000000004, 0.0], [-4.9699999999999998, 0.0], [-4.96, 0.0], [-4.9500000000000002, 0.0], [-4.9400000000000004, 0.0], [-4.9299999999999997, 0.0], [-4.9199999999999999, 0.0], [-4.9100000000000001, 0.0], [-4.9000000000000004, 0.0], [-4.8899999999999997, 0.0], [-4.8799999999999999, 0.0], [-4.8700000000000001, 0.0], [-4.8600000000000003, 0.0], [-4.8499999999999996, 0.0], [-4.8399999999999999, 0.0], [-4.8300000000000001, 0.0], [-4.8200000000000003, 0.0], [-4.8099999999999996, 0.0], [-4.7999999999999998, 0.0], [-4.79, 0.0], [-4.7800000000000002, 0.0], [-4.7699999999999996, 0.0], [-4.7599999999999998, 0.0], [-4.75, 0.0], [-4.7400000000000002, 0.0], [-4.7300000000000004, 0.0], [-4.7199999999999998, 0.0], [-4.71, 0.0], [-4.7000000000000002, 0.0], [-4.6900000000000004, 0.0], [-4.6799999999999997, 0.0], [-4.6699999999999999, 0.0], [-4.6600000000000001, 0.0], [-4.6500000000000004, 0.0], [-4.6399999999999997, 0.0], [-4.6299999999999999, 0.0], [-4.6200000000000001, 0.0], [-4.6100000000000003, 0.0], [-4.5999999999999996, 0.0], [-4.5899999999999999, 0.0], [-4.5800000000000001, 0.0], [-4.5700000000000003, 0.0], [-4.5599999999999996, 0.0], [-4.5499999999999998, 0.0], [-4.54, 0.0], [-4.5300000000000002, 0.0], [-4.5199999999999996, 0.0], [-4.5099999999999998, 0.0], [-4.5, 0.0], [-4.4900000000000002, 0.0], [-4.4800000000000004, 0.0], [-4.4699999999999998, 0.0], [-4.46, 0.0], [-4.4500000000000002, 0.0], [-4.4399999999999995, 0.0], [-4.4299999999999997, 0.0], [-4.4199999999999999, 0.0], [-4.4100000000000001, 0.0], [-4.4000000000000004, 0.0], [-4.3899999999
[…]

### 2011-02-20 project/calc/flot-pres/data/properties-sn-skew1000.js

@@ -1,0 +1,1 @@
+std_sn.skew1000 = [[-5.0, 0.0], [-4.9900000000000002, 0.0], [-4.9800000000000004, 0.0], [-4.9699999999999998, 0.0], [-4.96, 0.0], [-4.9500000000000002, 0.0], [-4.9400000000000004, 0.0], [-4.9299999999999997, 0.0], [-4.9199999999999999, 0.0], [-4.9100000000000001, 0.0], [-4.9000000000000004, 0.0], [-4.8899999999999997, 0.0], [-4.8799999999999999, 0.0], [-4.8700000000000001, 0.0], [-4.8600000000000003, 0.0], [-4.8499999999999996, 0.0], [-4.8399999999999999, 0.0], [-4.8300000000000001, 0.0], [-4.8200000000000003, 0.0], [-4.8099999999999996, 0.0], [-4.7999999999999998, 0.0], [-4.79, 0.0], [-4.7800000000000002, 0.0], [-4.7699999999999996, 0.0], [-4.7599999999999998, 0.0], [-4.75, 0.0], [-4.7400000000000002, 0.0], [-4.7300000000000004, 0.0], [-4.7199999999999998, 0.0], [-4.71, 0.0], [-4.7000000000000002, 0.0], [-4.6900000000000004, 0.0], [-4.6799999999999997, 0.0], [-4.6699999999999999, 0.0], [-4.6600000000000001, 0.0], [-4.6500000000000004, 0.0], [-4.6399999999999997, 0.0], [-4.6299999999999999, 0.0], [-4.6200000000000001, 0.0], [-4.6100000000000003, 0.0], [-4.5999999999999996, 0.0], [-4.5899999999999999, 0.0], [-4.5800000000000001, 0.0], [-4.5700000000000003, 0.0], [-4.5599999999999996, 0.0], [-4.5499999999999998, 0.0], [-4.54, 0.0], [-4.5300000000000002, 0.0], [-4.5199999999999996, 0.0], [-4.5099999999999998, 0.0], [-4.5, 0.0], [-4.4900000000000002, 0.0], [-4.4800000000000004, 0.0], [-4.4699999999999998, 0.0], [-4.46, 0.0], [-4.4500000000000002, 0.0], [-4.4399999999999995, 0.0], [-4.4299999999999997, 0.0], [-4.4199999999999999, 0.0], [-4.4100000000000001, 0.0], [-4.4000000000000004, 0.0], [-4.3899999999999
[…]

### 2011-02-20 project/calc/flot-pres/data/properties-sn-skew2.js

@@ -1,0 +1,1 @@
+std_sn.skew2 = [[-5.0, 2.2657168380853218e-29], [-4.9900000000000002, 2.9142280062158718e-29], [-4.9800000000000004, 3.7465016020668587e-29], [-4.9699999999999998, 4.8140746879000159e-29], [-4.96, 6.1827863211532139e-29], [-4.9500000000000002, 7.9367037464463703e-29], [-4.9400000000000004, 1.0183114499306215e-28], [-4.9299999999999997, 1.3058870519625938e-28], [-4.9199999999999999, 1.6738446267828043e-28], [-4.9100000000000001, 2.1444168623117992e-28], [-4.9000000000000004, 2.7459197169998333e-28], [-4.8899999999999997, 3.5143985811121942e-28], [-4.8799999999999999, 4.4957148593913794e-28], [-4.8700000000000001, 5.748189437958257e-28], [-4.8600000000000003, 7.3459499269587139e-28], [-4.8499999999999996, 9.3831668514099541e-28], [-4.8399999999999999, 1.1979412096546031e-27], [-4.8300000000000001, 1.5286433404352052e-27], [-4.8200000000000003, 1.9496714696329646e-27], [-4.8099999999999996, 2.4854287378385985e-27], [-4.7999999999999998, 3.1668377457794986e-27], [-4.79, 4.0330623376538872e-27], [-4.7800000000000002, 5.1336787561670711e-27], [-4.7699999999999996, 6.5314120318523061e-27], [-4.7599999999999998, 8.3055829698192177e-27], [-4.75, 1.0556448012355907e-26], [-4.7400000000000002, 1.3410660424672467e-26], [-4.7300000000000004, 1.7028138962174962e-26], [-4.7199999999999998, 2.1610702277857262e-26], [-4.71, 2.7412917357003061e-26], [-4.7000000000000002, 3.475572262115334e-26], [-4.6900000000000004, 4.4043526485544328e-26], [-4.6799999999999997, 5.5785656862522107e-26], [-4.6699999999999999, 7.0623254786406254e-26], [-4.6600000000000001, 8.9362976418102132e-26], [-4.6500000000000004, 1.1301920508836835e-25], [-4.6399999999999997, 1.4286689475531754e-25], [-4.6299999999999999, 1.8050768808613701e-25], [-4.6200000000000001, 2.2795260082154007e-25], [-4.6100000000000003, 2.8772536943071222e-25], [-4.5999999999999996, 3.6299
[…]

### 2011-02-20 project/calc/flot-pres/data/properties-sn-skewneg1000.js

@@ -1,0 +1,1 @@
+std_sn.skewneg1000 = [[-5.0, 2.9734390294685954e-06], [-4.9900000000000002, 3.1257342178985803e-06], [-4.9800000000000004, 3.2855011760901427e-06], [-4.9699999999999998, 3.4530890433541468e-06], [-4.96, 3.6288623803640607e-06], [-4.9500000000000002, 3.8132018062456215e-06], [-4.9400000000000004, 4.0065046598969788e-06], [-4.9299999999999997, 4.209185686366259e-06], [-4.9199999999999999, 4.4216777491368424e-06], [-4.9100000000000001, 4.6444325691959939e-06], [-4.9000000000000004, 4.8779214917867044e-06], [-4.8899999999999997, 5.1226362817690886e-06], [-4.8799999999999999, 5.3790899485430466e-06], [-4.8700000000000001, 5.6478176015116419e-06], [-4.8600000000000003, 5.9293773370905459e-06], [-4.8499999999999996, 6.2243511582978889e-06], [-4.8399999999999999, 6.5333459279865503e-06], [-4.8300000000000001, 6.8569943568100778e-06], [-4.8200000000000003, 7.1959560270424949e-06], [-4.8099999999999996, 7.550918453402698e-06], [-4.7999999999999998, 7.9225981820641506e-06], [-4.79, 8.3117419290624021e-06], [-4.7800000000000002, 8.7191277593432733e-06], [-4.7699999999999996, 9.1455663077282891e-06], [-4.7599999999999998, 9.5919020431050434e-06], [-4.75, 1.0059014577184891e-05], [-4.7400000000000002, 1.0547820019202607e-05], [-4.7300000000000004, 1.1059272377968103e-05], [-4.7199999999999998, 1.1594365012714574e-05], [-4.71, 1.215413213422223e-05], [-4.7000000000000002, 1.273965035773418e-05], [-4.6900000000000004, 1.3352040309214922e-05], [-4.6799999999999997, 1.399246828654081e-05], [-4.6699999999999999, 1.466214797724789e-05], [-4.6600000000000001, 1.5362342234500911e-05], [-4.6500000000000004, 1.609436491298459e-05], [-4.6399999999999997, 1.6859582766457543e-05], [-4.6299999999999999, 1.7659417408748196e-05], [-4.6200000000000001, 1.8495347340011233e-05], [-4.6100000000000003, 1.9368910040102874e-05], [-4.5999999999999996, 2
[…]

### 2011-02-20 project/calc/flot-pres/data/properties-sn-skewneg5.js

@@ -1,0 +1,1 @@
+std_sn.skewneg5 = [[-5.0, 2.9734390294685954e-06], [-4.9900000000000002, 3.1257342178985803e-06], [-4.9800000000000004, 3.2855011760901427e-06], [-4.9699999999999998, 3.4530890433541468e-06], [-4.96, 3.6288623803640607e-06], [-4.9500000000000002, 3.8132018062456215e-06], [-4.9400000000000004, 4.0065046598969788e-06], [-4.9299999999999997, 4.209185686366259e-06], [-4.9199999999999999, 4.4216777491368424e-06], [-4.9100000000000001, 4.6444325691959939e-06], [-4.9000000000000004, 4.8779214917867044e-06], [-4.8899999999999997, 5.1226362817690886e-06], [-4.8799999999999999, 5.3790899485430466e-06], [-4.8700000000000001, 5.6478176015116419e-06], [-4.8600000000000003, 5.9293773370905459e-06], [-4.8499999999999996, 6.2243511582978889e-06], [-4.8399999999999999, 6.5333459279865503e-06], [-4.8300000000000001, 6.8569943568100778e-06], [-4.8200000000000003, 7.1959560270424949e-06], [-4.8099999999999996, 7.550918453402698e-06], [-4.7999999999999998, 7.9225981820641506e-06], [-4.79, 8.3117419290624021e-06], [-4.7800000000000002, 8.7191277593432733e-06], [-4.7699999999999996, 9.1455663077282891e-06], [-4.7599999999999998, 9.5919020431050434e-06], [-4.75, 1.0059014577184891e-05], [-4.7400000000000002, 1.0547820019202607e-05], [-4.7300000000000004, 1.1059272377968103e-05], [-4.7199999999999998, 1.1594365012714574e-05], [-4.71, 1.215413213422223e-05], [-4.7000000000000002, 1.273965035773418e-05], [-4.6900000000000004, 1.3352040309214922e-05], [-4.6799999999999997, 1.399246828654081e-05], [-4.6699999999999999, 1.466214797724789e-05], [-4.6600000000000001, 1.5362342234500911e-05], [-4.6500000000000004, 1.609436491298459e-05], [-4.6399999999999997, 1.6859582766457543e-05], [-4.6299999999999999, 1.7659417408748196e-05], [-4.6200000000000001, 1.8495347340011233e-05], [-4.6100000000000003, 1.9368910040102874e-05], [-4.5999999999999996, 2.
[…]

### 2011-02-20 project/calc/flot-pres/flot_data.py

@@ -13,9 +13,10 @@ def write_comparison_graph (n, p):
   # Builds data for one comparison graph (binomial, normal, and skew-normal)
   # and writes it to an appropriately-named json file
 
-  (binomial, normal, sn) = ( binomial_pmf(n, p, pairs=True),
-                             normal_approx_pdf(n, p, pairs=True),
-                             sn_approx_pdf(n, p, pairs=True) )
+  binomial = binomial_pmf(n, p, pairs=True)
+  normal   = normal_approx_pdf(n, p, pairs=True)
+  sn       = sn_approx_pdf(n, p, pairs=True)
+
   np = 'n' + str(n) + 'p' + str(p).replace('.', '')
   f = open('data/comparison-' + np + '.js', 'w')
   f.write('binomial.' + np + ' = ' + json.dumps(binomial) + ';\n')
@@ -41,16 +42,35 @@ def compile_comparison_data ():
 #*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#*#
 # Property Graphs:
 #
-def write_property_graph (mu, sigma, skew):
-  str_skew = str(skew) if skew > 0 else 'neg' + str(-skew)
-  sn_graph = frame( sn_pdf(mu, sigma, skew, pairs=True) )
-  #sn_graph = sn_pdf(mu, sigma, skew, pairs=True)
+def write_std_sn_graph (skew):
+  # Builds data for a standard skew-normal graph and writes it to an
+  # appropriately-named json file
 
-  f = open('data/properties-skew' + str_skew + '.js', 'w')
-  f.write('std_sn.skew' + str_skew + ' = ' + json.dumps(sn_graph) + ';\n')
+  str_skew = str(skew) if skew > 0 else 'neg' + str(-skew)
+  std_sn_pdf = sn_pdf(0, 1, skew, pairs=True)
+
+  f = open('data/properties-sn-skew' + str_skew + '.js', 'w')
+  f.write('std_sn.skew' + str_skew + ' = ' + json.dumps(std_sn_pdf) + ';\n')
+
+def write_half_normal_graphs ():
+  # Builds data for the positive and negative half normal graphs and writes
+  # them to an appropriately-named json file
+  std_normal_pdf = normal_pdf(0,1, pairs=True)
+
[…]

### 2011-02-20 project/presentation/presentation.tex
Added graphs and proofs to properties section

@@
 \documentclass{beamer}
-\usepackage{capstone-presentation}
+\usepackage{jbib, jmath, jtable, tikz}
 
+% Beamer Style
 \usetheme{default}
@@
 \setbeamertemplate{blocks}[rounded][shadow=true]
+%\setbeamertemplate{proof}[rounded=false][shadow=false]
 
+% Bibliography
+\bibpunct{(}{)}{;}{a}{,}{,}
+% We have to define \newblock so that natbib will work with beamer
+\def\newblock{\hskip .11em plus .33em minus .07em}
+
+% Math
+\theoremstyle{plain}
+\newtheorem{property}{Property}
+\newtheorem{helper-lem}{Lemma}[property]
+\newtheorem{helper-cor}{Corollary}[property]
+\newenvironment{pf}[1][]{\textrm{\textit{Short proof:\\}}}{\hfill $\mathcal{Q.E.D.}$\newline}
+
+% TikZ
+\usetikzlibrary{arrows,shapes}
+% For every picture that defines or uses external nodes, you'll have to
+% apply the 'remember picture' style. To avoid some typing, we'll apply
+% the style to all pictures.
+\tikzstyle{every picture}+=[remember picture]
+% By default all math in TikZ nodes are set in inline mode. Change this to
+% displaystyle so that we don't get small fractions.
+\everymath{\displaystyle}
+
+% Misc
 \newcommand{\vsep}{\vspace{0.2cm}}
@@
 \date{Spring 2011}
-
-% TikZ
-% For every picture that defines or uses external nodes, you'll have to
-% apply the 'remember picture' style. To avoid some typing, we'll apply
-% the style to all pictures.
-\tikzstyle{every picture}+=[remember picture]
-
-% By default all math in TikZ nodes are set in inline mode. Change this to
-% displaystyle so that we don't get small fractions.
-\everymath{\displaystyle}
 
@@
 \frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
-
   \begin{property}[1]
@@
   \pause
-  \vsep
+  \begin{pf}
+    \pause
+    \begin{align*}
+      \uncover<+->{f_{(-Z)}(x) &= f_Z(-x) \\}
+      \uncover<+->{& = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\}
+      \uncover<+->{& = 2 \cdot \phi(x) \cdot \Phi (-\lambda x),}
+    \end{align*}
+    \uncover<+->{which is the pdf of $SN(0, 1, -\lambda)$.}
+  \end{pf}
+}
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+  \textit{Property 1}:\; $-SN(0, 1, \lambda) \sim SN(0, 1, -\lambda)$
+
+  \includegraphics[width=\textwidth]{../images/std-sn-reflection.png}
+}
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
   \begin{property}[2]
@@
   \end{property}
+  \pause
+  \begin{pf}
+    \pause
+    We will use a result from page 161, \citet{azzalini}:
+
+    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
+    notation $\overset{d}{=}$ denotes equality in distribution.
+
+    \pause
+    Let $X \sim N(0,1)$. Since $X^2 \sim \chi^2_1$ and $|X| \overset{d}{=}
+    |Z|$, then $Z^2 \sim \chi^2_1$.
+  \end{pf}
 }
-\frame{ \frametitle{The Skew-Normal Distribution}
-  \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
-
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
   \begin{property}[3]
@@
   \pause
-  \vsep
+    Let $X \sim |N(0, 1)|$. Then
+    \begin{equation*}
+      f_X(x) =
+      \begin{dcases*}
+        0      & when $-\infty < x \leq 0$ \\
+        2 \phi & when $0 < x < \infty$ 
+      \end{dcases*}
+      .
+    \end{equation*}
+}
+% For some reason, I was obliged to split the following slide into 3 slides, to prevent bumping in between the images.
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+  \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow +|N(0,1)|$ as $\lambda \rightarrow \infty$:
+
+  \only<1>{\includegraphics[width=\textwidth]{../images/positive-half-normal.png}}
+}
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+  \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow +|N(0,1)|$ as $\lambda \rightarrow \infty$:
+
+  \only<1>{\includegraphics[width=\textwidth]{../images/std-sn-skew2.png}}
+  \only<2>{\includegraphics[width=\textwidth]{../images/std-sn-skew5.png}}
+}
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+  \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow +|N(0,1)|$ as $\lambda \rightarrow \infty$:
+
+  \only<1>{\includegraphics[width=\textwidth]{../images/std-sn-skew10.png}}
+  \only<2>{\includegraphics[width=\textwidth]{../images/std-sn-skew1000.png}}
+}
+% end
+% Same bumping issue for this slide
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+  \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow -|N(0,1)|$ as $\lambda \rightarrow -\infty$:
+
+  \only<1>{\includegraphics[width=\textwidth]{../images/negative-half-normal.png}}
+}
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+  \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow -|N(0,1)|$ as $\lambda \rightarrow -\infty$:
+
+  \only<1>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg2.png}}
+  \only<2>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg5.png}}
+}
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+  \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow -|N(0,1)|$ as $\lambda \rightarrow -\infty$:
+
+  \only<1>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg10.png}}
+  \only<2>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg1000.png}}
+}
+% end
+\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
   \begin{property}[4]
@@
   \end{property}
+  According to Equation 5 in \citet{azzalini}, the mgf of $SN(\mu, \sigma, \lambda)$ is
+  \begin{equation*}
+    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t).
+  \end{equation*}
+  Our result follows.
 }

### 2011-02-20 project/presentation/skew-normal.tex
Added graphs and proofs to properties section

@@
   \end{property}
+  \pause
+  According to Equation 5 in \citet{azzalini}, the mgf of $SN(\mu, \sigma, \lambda)$ is
+  \begin{equation*}
+    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t).
+  \end{equation*}
+  Our result follows.
 }

### 2011-02-20 project/presentation/method-of-moments.tex
Tweaks.
Added explanation for lambda sign.

@@
   \end{equation*}
+
+  \pause
+  Why?
+  \pause
+  Recall Property 3 ...
+}
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  \begin{center}
+    \includegraphics[width=\textwidth]{../images/binomial-sn-n25p005.png}
+  \end{center}
+  When $p < 0.5$:
+  \pause
+  \begin{itemize}[<+->]
+    \item $(1-2p)$ is positive
+    \item The binomial skews right (weight shifts left) and approaches $+|N(0,1)|$ $\lra$ $\lambda$ is positive
+  \end{itemize}
+}
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  \begin{center}
+    \includegraphics[width=\textwidth]{../images/binomial-sn-n25p095.png}
+  \end{center}
+  When $p > 0.5$:
+  \pause
+  \begin{itemize}[<+->]
+    \item $(1-2p)$ is negative
+    \item The binomial skews left (weight shifts right) and approaches $-|N(0,1)|$ $\lra$ $\lambda$ is negative
+  \end{itemize}
 }

### 2011-02-20 project/presentation/presentation.tex
Added explanation for lambda sign.

@@
   \end{property}
+  \pause
   According to Equation 5 in \citet{azzalini}, the mgf of $SN(\mu, \sigma, \lambda)$ is

### 2011-02-20 project/presentation/method-of-moments.tex
Tweaks.

@@
   \pause
-  \begin{enumerate}[<+->]
-    \item Find the first three moments about the mean (central moments) of the binomial and the skew-normal.\\
-          \pause
-          \vsep
-          What are central moments?: $E(X)$, $E([X - E(X)]^2)$, $E([X -
-          E(X)]^3)$.
-    \item Set them equal to each other.
-    \item Take $n$ and $p$ to be constants; solve for $\mu$, $\sigma$, and $\lambda$.
+  \begin{enumerate}
+    \uncover<+->{\item Find the first three moments about the mean (central moments) of the binomial and the skew-normal.\\}
+          \uncover<+->{\vsep
+                       What are central moments?: $E(X)$, $E([X - E(X)]^2)$, $E([X - E(X)]^3)$.}
+    \uncover<+->{\item Set them equal to each other.}
+    \uncover<+->{\item Take $n$ and $p$ to be constants; solve for $\mu$, $\sigma$, and $\lambda$.}
   \end{enumerate}
@@
 \frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
+  Recall that $Var(B) = E(B^2) - [E(B)]^2$. \pause Thus
   \begin{align*}
@@
     \uncover<+->{&= np(1-p) + n^2p^2 \\}
-    \uncover<+->{&= np - np^2 + n^2p^2}
+    \uncover<+->{&= np - np^2 + n^2p^2.}
   \end{align*}
@@
 \frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
-  Let $y=x-3$; then $x=y+3$, and $x=3$, $x=n \Ra y=0$, $y=n-3$:
-  \pause
   \begin{align*}
-    \uncover<+->{&= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \\}
+    \uncover<+->{&= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x}}
+    \uncover<+->{\intertext{Let $y=x-3$; then $x=y+3$, and $x=3$, $x=n \Ra y=0$, $y=n-3$:}}
     \uncover<+->{&= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\}
@@
 \frame{ \frametitle{Method of Moments: Deriving an Approximation}
-  Set the central moments of the binomial equal to the central moments of the skew-normal:
+  We're finally ready to derive our approximation!
+}
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  We start by setting the central moments of the binomial equal to the central moments of the skew-normal.
   \pause
@@
   \begin{itemize}[<+->]
+    \item The binomial skews right (weight shifts left) and approaches $+|N(0,1)|$ $\lra$ $\lambda$ is positive
     \item $(1-2p)$ is positive
-    \item The binomial skews right (weight shifts left) and approaches $+|N(0,1)|$ $\lra$ $\lambda$ is positive
   \end{itemize}
@@
   \begin{itemize}[<+->]
+    \item The binomial skews left (weight shifts right) and approaches $-|N(0,1)|$ $\lra$ $\lambda$ is negative
     \item $(1-2p)$ is negative
-    \item The binomial skews left (weight shifts right) and approaches $-|N(0,1)|$ $\lra$ $\lambda$ is negative
   \end{itemize}
@@
     \uncover<+->{\frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\}
-    \uncover<+->{np(1-p) &\geq (1-2p)^2. \label{eq:solving-the-restriction}}
+    \uncover<+->{np(1-p) &\geq \frac{1}{(1-2p)^2}. \label{eq:solving-the-restriction}}
   \end{align}

### 2011-02-20 project/presentation/presentation.tex
Tweaks.

@@
     \item Method of Moments -- derive an approximation
-    \item Accuracy -- compare to the normal approximation
+    \item Accuracy -- examine the accuracy of our approximation
   \end{enumerate}
@@
     \pause
-    We will use a result from page 161, \citet{azzalini}:
+    Lemma 1 comes with a handy result, (\citealp{azzalini}, page 161):
 

### 2011-02-20 project/presentation/method-of-moments.tex
Took out algebra in Restrictions section

@@
   Unfortunately, though better than the normal approximation, our skew-normal method isn't universal.
-  \pause
-
-  To be able to solve for $\lambda$, we must put a few restrictions on $n$ and $p$.
 }
 \frame{ \frametitle{Method of Moments: Restrictions}
-  Let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u = \frac{1+\lambda^2}{\lambda^2}$.
+  To be able to solve for $\lambda$, we must restrict $n$ and $p$ by the following equation:
   \pause
-
-  \uncover<+->{Then we can rewrite \eqref{eq:solving-for-lambda}:
-  \begin{gather*}
-    \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2} \\}
-    \uncover<+->{\vdots \\
-                 (magic) \\
-                 \vdots \\}
-    \uncover<+->{\left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = g(v)}
-  \end{gather*}
+  \begin{equation}
+    np(1-p) \geq \frac{1}{(1-2p)^2} \label{eq:solving-the-restriction}
+  \end{equation}
+  \pause
+  From \eqref{eq:solving-the-restriction}, we can answer two questions:
 }
 \frame{ \frametitle{Method of Moments: Restrictions}
-  $g(v)$ is increasing in $v = \frac{1+\lambda^2}{\lambda^2} \geq 1$. \pause Therefore:
-  \begin{equation*}
-    \uncover<+->{\min_{v} g(v)} \uncover<+->{= g(1)} \uncover<+->{= \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right)} \uncover<+->{= 1.009524 \approx 1}
-  \end{equation*}
-}
-\frame{ \frametitle{Method of Moments: Restrictions}
-  To be able to solve \eqref{eq:solving-for-lambda} for $\lambda$, we must have
-  \begin{align}
-    \uncover<+->{\textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\}
-    \uncover<+->{\frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\}
-    \uncover<+->{np(1-p) &\geq \frac{1}{(1-2p)^2}. \label{eq:solving-the-restriction}}
-  \end{align}
-  \uncover<+->{From \eqref{eq:solving-the-restriction}, we can answer two questions:}
-}
-\frame{ \frametitle{Method of Moments: Restrictions}
-  One:
-
-  Given $p$, what is the least $n$ necessary?
+  \vspace{5mm}
+  One: Given $p$, what is the least $n$ necessary?
   \pause
@@
   \end{equation*}
-}
-\frame{ \frametitle{Method of Moments: Restrictions}
-  Least possible $n$, given a fixed $p$:
+  \pause
   \begin{center}
@@
 \frame{ \frametitle{Method of Moments: Restrictions}
-  Two:
-
-  Given $n$, what is the range of possible $p$'s?
+  \vspace{5mm}
+  Two: Given $n$, what is the range of possible $p$'s?
   \pause
@@
   \end{equation*}
-}
-\frame{ \frametitle{Method of Moments: Restrictions}
-  Range of possible $p$, given a fixed $n$:
+  \pause
   \begin{center}
-    \includegraphics[width=0.8\textwidth]{../images/restriction-p-range.png}
+    \includegraphics[width=0.7\textwidth]{../images/restriction-p-range.png}
   \end{center}

### 2011-02-20 project/paper/demo.tex
Merged capstone-paper.sty into headers, renamed demo

--- 2011-01-22 project/paper/output.tex
@@
-\documentclass{article}
-\usepackage{jcapstone}
-\begin{document}
-
-\title{The Skew-Normal Approximation of the Binomial Distribution}
-\author{Joyce Tipping}
-\date{2010}
-\maketitle
-
-\section{Introduction}
-
-One of the most basic distributions in probability and statistics is the
-binomial, $X \sim Bin(n,p)$, $n = 1, 2, \ldots$, $p \in (0, 1)$ with
-probability density function (pdf)
-
-\begin{equation*}
-  f_X(x) = \binom{n}{x} p^x q^{n-x}, \quad x = 0, 1, \ldots, n,
-\end{equation*}
-
-where $q=1-p$. Calculating the binomial cumulative distribution function (cdf),
-$F_X(x) = P(X \leq x) = \sum_{k=1}^x f_X(k)$, by hand is manageable for small
-$n$ but quickly becomes cumbersome as $n$ grows even moderately large. A common
-strategy is to use the normal distribution\footnotemark as an approximation:
-
-\footnotetext{A random variable $X$ follows the normal distribution with mean
-$\mu$ and variance $\sigma^2$ (denoted $X \sim N(\mu,\sigma^2)$) if it has the
-pdf $f(x;\mu,\sigma) = \frac{1}{\sqrt{2\pi}\,\sigma} \;
-e^{-[(x-\mu)/\sigma]^2/2}$ for $-\infty < x < \infty$, where $-\infty < \mu <
-\infty$ and $0 < \sigma < \infty$.
-
-$N(0,1)$ is an important special case known as the standard normal (denoted
-$Z$) and has pdf $\phi(z) = \frac{1}{\sqrt{2\pi}} \; e^{-z^2/2}, \quad -\infty
-< z < \infty$ and cdf given by $\Phi(z) = \int_{-\infty}^z \phi(t)\;dt$.
-Equations 3.3.27, 3.3.29, and 3.3.30, \citet{textbook}.}
-
-\begin{equation}
-  F_X(x) \approx \Phi \left( \frac{x + 0.5 - \mu}{\sigma} \right),
-\end{equation}
-
-where $\Phi$ is the standard normal cdf and $\mu = np$ and $\sigma =
-\sqrt{np(1-p)}$.
-
-This approximation works best when the binomial is perfectly symmetrical, with
-$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
-becomes increasingly skewed, and one must either provide larger values of $n$
-to compensate or face growing inaccuracy.
-
-To protect against these cases, many textbooks impose a condition on the normal
-approximation, often stated as either (1) $np(1-p) > 9$ \; or \; (2) $np > 5$
-for $0 < p \leq 0.5$, and $n(1-p) > 5$ for $0.5 < p < 1$. However, \citet{mabs}
-show that even when these conditions are met, the inaccuracy of the normal
-approximation can be surprisingly large. So, the natural question arises: Can
-we do better?
-
-Perhaps so. Intuitively speaking, the main problem with the normal
-approximation is that the normal is always symmetric while the binomial is
-sometimes skewed. This naturally suggests the skew-normal distribution, which
-adds an extra parameter to capture an assymetrical lean.
-
-In this paper, we will explore the aptness of the skew-normal as a method of
-approximating the binomial. First, we'll acquaint ourselves with its basic
-properties (section \ref{sec:properties}). We'll then derive an approximation
-via the method of moments (section \ref{sec:method-of-moments}) and compare its
-accuracy to that of the normal approximation (section \ref{sec:accuracy}).
-Finally, we will leave the reader with a few practical resources for applying
-our new method (section \ref{sec:resources}).
-
-\section{The Skew-Normal Distribution}
-\label{sec:properties}
-
-The skew-normal distribution is similar to the normal but with an added
-parameter for skew that allows it to lean to the left or right. In this
-section, we'll get to know some of its basic properties.
-
-\subsection{Foundations}
-
-\begin{defn}
-  Let $Y$ be a skew-normal distribution, with location parameter $\mu \in \R$,
-  scale parameter $\sigma > 0$, and shape parameter $\lambda \in \R$; we will
-  denote it $SN(\mu, \sigma, \lambda)$.\footnotemark Then $Y$ has pdf
-
-  \begin{equation} \label{eq:sn-pdf}
-    f(x|\mu, \sigma, \lambda) = \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi \left( \frac{\lambda(x-\mu)}{\sigma} \right), \quad x \in \R,
-  \end{equation}
-
-  where $\phi$ is the standard normal pdf and $\Phi$ is the standard normal
-  cdf. \citet{main}
-
-  \footnotetext{In this paper, we have followed the notation established by
-  \citet{main} in naming our parameters $\mu$, $\sigma$, and $\lambda$. It does
-  seem intuitive, after all, for the skew-normal to simply "extend" the normal
-  with an extra parameter.
-
-  An unfortunate consequence of this choice, however, is the misconception that
-  $\mu$ and $\sigma$ are related to the mean and variance the way they are in
-  the normal distribution. In the case of the skew-normal, it is more
-  productive to think of them as abstract location and scale parameters. In
-  fact, a quick comparison of figures \ref{fig:comparison-n25},
-  \ref{fig:comparison-n50}, and \ref{fig:comparison-n100} and the corresponding
-  parameters in Table \ref{tab:sn-approx-table} shows that $\mu$ and $\sigma$
-  are not visually related to the curve in any intuitive way.}
-
-\end{defn}
-
-The skew-normal was first introduced by \citet{o'hagan} and was most notably
-developed by \citet{azzalini-1985}. Some of its other basic properties, given
-by \citet{pewsey}, are
-
-\begin{align}
-  E(Y) &= \mu + b \delta \sigma, \nonumber \\
-  E(Y^2) &= \mu^2 + 2b \delta \mu \sigma + \sigma^2, \label{eq:sn-basic-properties} \\
-  E(Y^3) &= \mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3, \nonumber \\
-  Var(Y) &= \sigma^2 (1 - b^2 \delta^2), \nonumber
-\end{align}
-
-where $b = \sqrt{\frac{2}{\pi}}$ and $\delta = \frac{\lambda}{\sqrt{1 +
-\lambda^2}}$.
-
-The $SN(0,1,\lambda)$ distribution is called the standard skew-normal; its pdf
-is
-
-\begin{equation} \label{eq:standard-sn-pdf}
-  f(x|\lambda) = 2 \cdot \phi(x) \cdot \Phi (\lambda x), \quad x \in \R.
-\end{equation}
-
-Similar to the normal and standard normal, $Z = \frac{Y - \mu}{\sigma}$ and $Y
-= \sigma Z + \mu$.
-
-A natural question to ask is how the skew-normal relates to the normal.
-Fortunately, the connection is very intuitive: When $\lambda = 0$, Equation
-\eqref{eq:sn-pdf} becomes
-
-\begin{align*}
-  f(x|\lambda=0) &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot \Phi(0) \\
-  &= \frac2\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \cdot 0.5 \\
-  &= \frac1\sigma \cdot \phi \left( \frac{x-\mu}{\sigma} \right) \\
-  &= \frac1\sigma \cdot \frac{1}{\sqrt{2\pi}} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right) \\
-  &= \frac{1}{\sqrt{2\pi}\sigma} \;\cdot\; \exp \left( -\frac{(x-\mu)^2}{2\sigma^2} \right),
-\end{align*}
-
-which is the pdf of the normal distribution ($\mu$, $\sigma$). Furthermore,
-when $\lambda > 0$, the curve skews to the left, and when $\lambda < 0$, it
-skews to the right (a property we will prove in section
-\ref{subsec:four-properties}).
-
-\subsection{Properties of the Standard Skew-Normal Distribution}
-\label{subsec:four-properties}
-
-The following four properties of the standard skew-normal, given by
-\citet{main}, help shed light on our enigmatic new distribution:
-
-\begin{property} \label{prop:1}
-  If $Z \sim SN(0, 1, \lambda)$, then $(-Z) \sim SN(0, 1, -\lambda)$.
-\end{property}
-
-\begin{proof}
-  The standard normal pdf is an even function: $\phi(-x) =
-  \frac{1}{\sqrt{2\pi}}\;e^{-(-x)^2/2} = \frac{1}{\sqrt{2\pi}}\;e^{-x^2/2} =
-  \phi(x)$. But the standard normal cdf, \thinspace $\Phi(x) = \int_{-\infty}^x
-  \phi(t)\;dt$, \thinspace is not even, being 0 near $-\infty$ and 1 near
-  $\infty$. Thus,
-
-  \begin{align*}
-    f_{(-Z)}(x) &= f_Z(-x) \\
-    & = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\
-    & = 2 \cdot \phi(x) \cdot \Phi (-\lambda x),
-  \end{align*}
-
-  which is the pdf of $SN(0, 1, -\lambda)$.
-\end{proof}
-
-\begin{property} \label{prop:2}
-  If $Z \sim SN(0, 1, \lambda)$, then $Z^2 \sim \chi^2_1$ (chi-square with 1 degree of freedom).
-\end{property}
-
-\begin{proof}
-  To prove our result, we begin by examining Lemma 1 in \citet{azzalini}, which
-  we restate here:
-
-  \begin{helper-lem}
-    If $f_0$ is a one-dimensional probability density function symmetric about
-    0, and $G$ is a one-dimensional distribution function such that $G'$ exists
-    and is a density symmetric about 0, then
-
-    \begin{equation}
-      \label{eq:azzalini-perturbation-invariance}
-      f(z) = 2 \cdot f_0(z) \cdot G\{w(z)\} \quad (-\infty < z < \infty)
-    \end{equation}
-
-    is a density function for any odd function $w(\cdot)$.
-  \end{helper-lem}
-
-  This lemma is extended by a corollary which gives a very helpful result for
-  the above defined $f_0$ and $f$:
-
-  \begin{helper-cor}[Perturbation Invariance]
-    If $Y \sim f_0$ and $Z \sim f$, then $|Y| \overset{d}{=} |Z|$, where the
-    notation $\overset{d}{=}$ denotes equality in distribution.    
-  \end{helper-cor}
-
-  Let $f_0 = \phi$ and $G = \Phi$. Then, $f_Z(z) = 2 \cdot \phi(z) \cdot
-  \Phi(\lambda z)$ conforms to Equation
-  \eqref{eq:azzalini-perturbation-invariance}, and we can conclude that $\phi$
-  and $Z$ are equal in distribution.
-
-  We will now show that $\phi^2 \sim \chi^2_1$ by deriving its moment
-  generating function (mgf):\footnote{If $X$ is a random variable, then the
-  expected value $M_X(t) = E(e^{tX})$ is called the moment generating function
-  (mgf) of X if this expected value exists for all values of $t$ in some
-  interval of the form $-h < t < h$ for some $h > 0$. Definition 2.5.1,
-  \citet{textbook}.}
-
-  \begin{align*}
-    M_{\phi^2}(t) &= E[e^{tx^2}] \\
-    &= \int_{-\infty}^\infty \; e^{tx^2} \left[ \frac{1}{\sqrt{2\pi}} e^{-x^2/2} \right] dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{tx^2 - x^2/2} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{x^2}{2}(1 - 2t)} \; dx \\
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-\frac{1}{2}(\sqrt{1-2t} \; x)^2} \; dx \;; \\
-    \intertext{let $u = (\sqrt{1-2t}) \, x$; then $du = (\sqrt{1-2t}) \, dx$, \enspace $dx = \frac{du}{\sqrt{1-2t}}$, \enspace and our limits become $x \to -\infty, x \to \infty \Ra
-      u \to -\infty, u \to \infty$:}
-    &= \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; \left( \frac{1}{\sqrt{1-2t}} du \right) \\
-    &= \frac{1}{\sqrt{1-2t}} \; \underbrace{\left( \int_{-\infty}^\infty \; \frac{1}{\sqrt{2\pi}} \; e^{-u^2/2} \; du \right)}_{\mathclap{\textnormal{$\phi(u)$ integrated over
-      $(-\infty,\infty)$ = 1}}} \label{phi-pdf} \\
-    &= \frac{1}{\sqrt{1-2t}} \;,
-  \end{align*}
-
-  which is the mgf of the $\chi^2_1$. Since $Z$ is equal in distribution to
-  $\phi$, we can also conclude that $Z^2 \sim \chi^2_1$. \end{proof}
-
-\begin{property} \label{prop:3}
-  As $\lambda \to \pm \infty$, \thinspace $SN(0,1,\lambda)$ tends to the half normal distribution, $\pm |N(0,1)|$.
-\end{property}
-
-To prove our theorem, it is helpful to formally define the half normal distribution:
-
-\begin{helper-lem} \label{lem:p2-half-normal}
-  Let $X \sim N(0, \sigma^2)$. Then the distribution of $|X|$ is a half-normal
-  random variable with parameter $\sigma$ and
-
-  \begin{equation*}
-    f_{|X|}(x) =
-    \begin{dcases*}
-      0              & when $-\infty < x \leq 0$ \\
-      2 \cdot f_X(x) & when $0 < x < \infty$ 
-    \end{dcases*}
-    .
-  \end{equation*}
-\end{helper-lem}
-
-\begin{proof}
-  Let $X \sim N(0, \sigma^2)$, defined over $A = (-\infty, \infty)$. Define
-
-  \begin{equation*}
-    Y = |X| =
-    \begin{dcases*}
-      -x & if $x < 0$ \\
-      0 & if $x = 0$ \\
-      x & if $x > 0$ \\
-    \end{dcases*}
-    .
-  \end{equation*}
-
-  $Y$ is not one-to-one over $A$. However, we can partition $A$ into disjoint
-  subsets $A_1 = (-\infty, 0)$, $A_2 = (0, \infty)$, and $A_3 = \{0\}$ such
-  that $A = A_1 \cup A_2 \cup A_3$ and $Y$ is one-to-one over each $A_i$. We
-  can then transform each piece separately using Theorem 6.3.2 from
-  \citet{textbook}:\footnote{\textbf{Continuous transformations that are
-  one-to-one}: Suppose that $X$ is a continuous random variable with pdf
-  $f_X(x)$, and assume that $Y = u(X)$ defines a one-to-one transformation from
-  $A = \{x|f_X(x) > 0\}$ on to $B = \{y|f_Y(y) > 0\}$ with inverse
-  transformation $x = w(y)$. If the derivative $(d/dy)w(y)$ is continuous and
-  nonzero on $B$, then the pdf of $Y$ is
-
-  \begin{equation}
-    \label{eq:transformations-1-to-1}
-    f_Y(y) = f_X(w(y)) \left| \frac{d}{dy} w(y) \right| \qquad y \in B.
-  \end{equation}
-
-  Theorem 6.3.2, \citet{textbook}.
-  \label{fnote:transformations-1-to-1}
-  }
-
-  On $A_1$: $y = -x \Ra x = -y$ and the Jacobian $\J = \left| \frac{dx}{dy}
-  \right| = |-1| = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
-    &= f_X(-y) \cdot 1 \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{(-y)^2}{2\sigma^2}} \\
-    &= \frac{1}{\sqrt{2\pi}\sigma} \; e^{-\frac{y^2}{2\sigma^2}} \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_1: -\infty < x < 0 \Ra -\infty < -y < 0 \Ra 0 < y < \infty :B_1$.
-
-  Similarly, on $A_2$: $y = x \Ra x = y$ and the Jacobian $\J = \left|
-  \frac{dx}{dy} \right| = |1| = 1$, yielding
-
-  \begin{align*}
-    f_Y(y) &= f_X(x) \cdot \J \\
-    &= f_X(y) \cdot 1 \\
-    &= f_X(y)
-  \end{align*}
-
-  over the domain $A_2: 0 < x < \infty \Ra 0 < y < \infty :B_2$.
-
-  On $A_3$, we have $x = 0 \Ra y = 0$ and Jacobian $\J = \left| \frac{dx}{dy}
-  \right| = |0| = 0$, yielding $f_Y(y) = f_X(x) \cdot \J = f_X(x) \cdot 0 = 0$.
-
-  Then, by Equation 6.3.10 from \citet{textbook},\footnote{\textbf{Continuous
-  transformations that are not one-to-one}: When $u(x)$ is not one-to-one over
-  $A$, we can replace equation \eqref{eq:transformations-1-to-1} in footnote
-  \ref{fnote:transformations-1-to-1} with
-
-  \begin{equation*}
-    f_Y(y) = \sum_j f_X(w_j(y)) \left| \frac{d}{dy} w_j(y) \right|.
-  \end{equation*}
-
-  Equation 6.3.10, \citet{textbook}.
-  }
-
-  \begin{align*}
-    f_Y(y) &= \{ f_Y(y) \textrm{ over } A_1 \} + \{ f_Y(y) \textrm{ over } A_2 \} \\
-    &= f_X(y) + f_X(y) \\
-    &= 2 \cdot f_X(y)
-  \end{align*}
-
-  over $B = B_1 \cup B_2 = (0, \infty)$, and 0 otherwise.
-\end{proof}
-
-With Lemma \ref{lem:p2-half-normal}, we can easily show our property:
-
-\begin{proof}[Proof of Property 3]
-  Let $Z \sim SN(0,1,\lambda)$. Recall that $f_Z(x) = 2 \cdot \phi(x) \cdot
-  \Phi(\lambda x)$.
-
-  Consider $\lim_{\lambda \to \infty} f_X(x)$. When $x$ is negative, $\lambda x
-  \to -\infty$ and thus $\Phi(\lambda x) \to 0$. When $x$ is positive, however,
-  $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-positive-half-normal}
-    \lim_{\lambda \to \infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      0 & when $x \leq 0$ \\
-      2 \cdot \phi(x) & when $x > 0$
-    \end{dcases*}
-    \eq |N(0,1)|.
-  \end{equation}
-
-  In $\lim_{\lambda \to -\infty} f_X(x)$, the signs are reversed. When $x$ is
-  negative, $\lambda x \to \infty$ and $\Phi(\lambda x) \to 1$. When $x$ is
-  positive, $\lambda x \to -\infty$ and $\Phi(\lambda x) \to 0$. Thus,
-
-  \begin{equation}
-    \label{eq:p2-negative-half-normal}
-    \lim_{\lambda \to -\infty} 2 \cdot \phi(x) \cdot \Phi(\lambda x) \eq
-    \begin{dcases*}
-      2 \cdot \phi(x) & when $x < 0$ \\
-      0 & when $x \geq 0$
-    \end{dcases*}
-    \eq -|N(0,1)|.
-  \end{equation}
-\end{proof}
-
-\begin{property} \label{prop:4}
-  The moment generating function of $SN(0,1,\lambda)$ is
-
-  \begin{equation} \label{eq:p4-sn-mgf}
-    M(t|\lambda) = 2 \cdot \Phi (\delta t) \cdot e^{t^2/2},
-  \end{equation}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}}$ and $t \in (-\infty, \infty)$.
-\end{property}
-
-\begin{proof}
-  According to Equation 5 in \citet{azzalini}, the mgf of $SN(\mu, \sigma,
-  \lambda)$ is
-
-  \begin{equation*}
-    M(t) \eq E\{e^{tY}\} \eq 2 \cdot \exp \left( \mu t + \frac{\sigma^2 t^2}{2} \right) \cdot \Phi(\delta \sigma t),
-  \end{equation*}
-
-  where $\delta = \frac{\lambda}{\sqrt{1 + \lambda^2}} \in (-1, 1)$. It follows
-  that the mgf of the $SN(0, 1, \lambda)$ is
-
-  \begin{equation*}
-    2 \cdot \exp \left( 0 \cdot t + \frac{1 \cdot t^2}{2} \right) \cdot \Phi(\delta \cdot 1 \cdot t) \eq 2 \cdot e^{t^2/2} \cdot \Phi(\delta t).
-  \end{equation*}
-\end{proof}
-
-\section{Developing an Approximation}
-\label{sec:method-of-moments}
-
-Now that we have gotten to know our new distribution a little better, we can
-use it to develop an approximation for the binomial.
-
-Let $B \sim Bin(n, p)$ and $Y \sim SN(\mu, \sigma, \lambda)$. We will find
-estimates for $\mu$, $\sigma$, and $\lambda$ using the method of moments, that
-is, by comparing the first, second, and third moments about the mean (also
-referred to as central moments) of $B$ and $Y$.
-
-\subsection{The Moments of the Binomial Distribution}
-
-Let's start with the binomial. The first two central moments are simply the
-mean and variance, which we can state from memory:
-
-\begin{equation*}
-  E(B) = np, \quad Var(B) = np(1-p).
-\end{equation*}
-
-Having these, we can easily find $E(B^2)$: Recall that $Var(B) = E(B^2) -
-[E(B)]^2$ and thus
-
-\begin{equation*}
-  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2,
-\end{equation*}
-
-a fact we will need for the third central moment.
-
-We will also need $E(B^3)$, which we will get via the third factorial moment:
-
-\begin{align*}
-  E[B(B-1)(B-2)] &= \sum_{x=0}^n x (x-1) (x-2) \cdot \left\{ \binom{n}{x} p^x q^{n-x} \right\} \;; \\
-  \intertext{notice that the first three terms of this sum are zero, so we can rewrite our sum beginning at $x = 3$:}
-  &= \sum_{x=3}^n x(x-1)(x-2) \cdot \frac{n!}{x!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n \frac{n!}{(x-3)!\;(n-x)!} \; p^x q^{n-x} \\
-  &= \sum_{x=3}^n n(n-1)(n-2) p^3 \cdot \frac{(n-3)!}{(x-3)!\;(n-x)!} \; p^{x-3}q^{n-x} \;; \\
-  \intertext{let $y=x-3$; then $x=y+3$, and $x=3, x=n \Ra y=0, y=n-3$:}
-  &= n(n-1)(n-2)p^3 \cdot \sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;(n-(y+3))!} \; p^y q^{n-(y+3)} \\
-  &= n(n-1)(n-2)p^3 \cdot \underbrace {\sum_{y=0}^{n-3} \frac{(n-3)!}{y!\;((n-3)-y)!} \; p^y q^{(n-3)-y}}_{\mathclap{\textnormal{[pdf of $Bin(n-3,p)$ summed over its domain] = 1}}} \\
-  &= n(n-1)(n-2)p^3 \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 \;; \\
-  \intertext{We now expand the left side of the previous equation and solve for $E(B^3)$:}
-  E \left[ B^3 - 3B^2 + 2B \right] &= n^3p^3 - 3n^2p^3 + 2np^3 \\
-  E(B^3) - 3E(B^2) + 2E(B) &= \\
-  E(B^3) - 3(np - np^2 + n^2p^2) + 2np &= \\
-  \Rightarrow \qquad E(B^3) &= n^3p^3 - 3n^2p^3 + 2np^3 + 3np - 3np^2 + 3n^2p^2 - 2np \\
-  &= n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np.
-\end{align*}
-
-Now, finally, we have all the building blocks necessary to obtain the third
-central moment:
-
-\begin{align*}
-  E \left( [B - E(B)]^3 \right) &= E \left( B^3 - 3B^2 E(B) + 3B [E(B)]^2 - [E(B)]^3 \right) \\
-  &= E(B^3) - 3 E(B^2) E(B) + 3 E(B) [E(B)]^2 - [E(B)]^3 \\
-  &= E(B^3) - 3 E(B^2) E(B) + 2 [E(B)]^3 \\
-  &= (n^3p^3 - 3n^2p^3 + 2np^3 - 3np^2 + 3n^2p^2 + np) - 3(np - np^2 + n^2p^2)(np) + 2(np)^3 \\
-  &= \cancel{n^3p^3} - \cancel{3n^2p^3} + 2np^3 - 3np^2 + \cancel{3n^2p^2} + np - \cancel{3n^2p^2} + \cancel{3n^2p^3} - \cancel{3n^3p^3} + \cancel{2n^3p^3} \\
-  &= 2np^3 - 3np^2 + np \\
-  &= np(p-1)(2p-1).
-\end{align*}
-
-Our hard-earned results, restated for convenience:
-
-\begin{align}
-  E(B) &= np, \nonumber \\
-  E([B - E(B)]^2) &= np(1-p), \\
-  E([B - E(B)]^3) &= np(p-1)(2p-1). \nonumber
-\end{align}
-
-\subsection{The Moments of the Skew Normal Distribution}
-
-Now we'll take a look at the skew normal. Equation
-\eqref{eq:sn-basic-properties} takes care of the mean and variance; again the
-third central moment is a little more complicated:
-
-\begin{align*}
-  E([Y - E(Y)]^3) &= E(Y^3) - 3E(Y^2)E(Y) + 2[E(Y)]^3 \\
-  &= (\mu^3 + 3 b \delta \mu^2 \sigma + 3 \mu \sigma^2 + 3 b \delta \sigma^3 - b \delta^3 \sigma^3) - 3 (\mu^2 + 2b \delta \mu \sigma + \sigma^2) (\mu + b \delta \sigma) \\
-  & \quad + 2\;(\mu + b \delta \sigma)^3 \\
-  &= \cancel{\mu^3} + \cancel{3 b \delta \mu^2 \sigma} + \cancel{3 \mu \sigma^2} + \cancel{3 b \delta \sigma^3} - b \delta^3 \sigma^3 - \cancel{3 \mu^3} - \cancel{3 b \delta \mu^2 \sigma} -
-    \cancel{6 b \delta \mu^2 \sigma} - \cancel{6 b^2 \delta^2 \mu \sigma^2} - \cancel{3 \mu \sigma^2} \\
-  & \quad - \cancel{3 b \delta \sigma^3} + \cancel{2 \mu^3} + \cancel{6 b \delta \mu^2 \sigma} + \cancel{6 b^2 \delta^2 \mu \sigma^2} + 2 b^3 \delta^3 \sigma^3 \\
-  &= 2 b^3 \delta^3 \sigma^3 - b \delta^3 \sigma^3 \\
-  &= b \delta^3 \sigma^3 (2b^2 - 1).
-\end{align*}
-
-We restate our results:
-
-\begin{alignat}{4}
-  E(Y) &= \mu + b \delta \sigma \;&=&\; \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;, \nonumber \\
-  E([Y - E(Y)]^2) &= \sigma^2 (1 - b^2 \delta^2) \;&=&\; \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right), \\
-  E([Y - E(Y)]^3) &= b \delta^3 \sigma^3 (2b^2 - 1) \;&=&\; \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right). \nonumber
-\end{alignat}
-
-\subsection[Solving for mu, sigma, lambda]{Solving for $\mu$, $\sigma$, $\lambda$}
-\label{subsec:solving-for-mu-sigma-lambda}
-
-To derive our approximation, we set the above moments of our two distributions
-equal to each other and, taking $n$ and $p$ as constants, solve for $\mu$,
-$\sigma$ and $\lambda$:
-
-\begin{subequations}
-\begin{align}
-  np &= \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \label{eq:first-moment-set} \\
-  np(1-p) &= \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \label{eq:second-moment-set} \\
-  np(p-1)(2p-1) &= \sigma^3 \sqrt{\frac{2}{\pi}} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^3 \left( \frac{4}{\pi} - 1 \right) \label{eq:third-moment-set}
-\end{align}
-\end{subequations}
-
-To get $\lambda$, we divide the cube of \eqref{eq:second-moment-set} by the
-square of \eqref{eq:third-moment-set}:
-
-\begin{align}
-  \frac{\sigma^6 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right)^3}{\sigma^6 \cdot \frac{2}{\pi} \left( \frac{\lambda}{\sqrt{1 + \lambda^2}} \right)^6 \left(
-    \frac{4}{\pi} - 1 \right)^2} &= \frac{n^3p^3(1-p)^3}{n^2p^2(p-1)^2(2p-1)^2} \nonumber \\
-  \Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-    \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \;. \label{eq:solving-for-lambda}
-\end{align}
-
-The above equation \eqref{eq:solving-for-lambda} is a rational expression in
-$\lambda^2$ that can be solved with either a considerable amount of manual
-labor or, more efficiently, with a computer algebra system. Once we have
-$\lambda^2$, then $\lambda$ is simply either the positive or negative square
-root, as determined by the sign of $(1-2p)$. The sign can be explained with a
-little assistance from Property \ref{prop:3}: When $p \to 0$, the binomial
-skews left and converges toward the positive half normal, which by
-\eqref{eq:p2-positive-half-normal} corresponds to a positive $\lambda$. When $p
-\to 1$, the binomial skews right and converges toward the negative half normal,
-which by \eqref{eq:p2-negative-half-normal} corresponds to a negative
-$\lambda$. When $p = 0.5$, the binomial is symmetric and $\lambda$ is 0,
-eliminating the need for a sign. Thus:
-
-\begin{equation}
-  \label{eq:lambda-solved}
-  \lambda = \textnormal{\{sign of $(1-2p)$\}} \sqrt{\lambda^2}.
-\end{equation}
-
-Having secured $\lambda$, we can find $\sigma$ using
-\eqref{eq:second-moment-set}:
-
-\begin{equation}
-  \label{eq:sigma-solved}
-  np(1-p) = \sigma^2 \left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2} \right) \quad\Rightarrow\quad
-  \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} \;.
-\end{equation}
-
-And with both $\lambda$ and $\sigma$, a simple rearrangement of
-\eqref{eq:first-moment-set} yields $\mu$:
-
-\begin{equation}
-  \label{eq:mu-solved}
-  np = \mu + \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \quad\Rightarrow\quad
-  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \;.
-\end{equation}
-
-One notable case where the above skew-normal approximation fails is when $p =
-0.5$; the right side of \eqref{eq:solving-for-lambda} becomes undefined, and we
-are unable to obtain $\lambda$. Fortunately, here we can fall back on our
-intuition, which tells us that since the binomial is perfectly symmetrical, the
-skew should be 0. A few observations support this conclusion: When $p = 0.5$,
-equation \eqref{eq:lambda-solved} fails to yield a sign. Furthermore, when
-$\lambda = 0$, equations \eqref{eq:sigma-solved} and \eqref{eq:mu-solved}
-return us to the normal approximation ($\mu = np$ and $\sigma =
-\sqrt{np(1-p)}$, respectively), which is after all a natural choice for a
-symmetric binomial curve.
-
-\subsection{Restrictions}
-
-Unfortunately, although better than the normal approximation, the skew-normal
-is also not universally applicable. To obtain an estimate for $\lambda$, we
-must put a few restrictions on $n$ and $p$.
-
-If we let $u = \frac{\lambda^2}{1+\lambda^2}$ and $v = 1/u$, we can rewrite the
-left hand side of \eqref{eq:solving-for-lambda} as
-
-\begin{alignat}{3}
-  \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2}
-    &= \left. \left( 1 - \frac{2}{\pi} u \right)^3 \middle/ \frac{2}{\pi} u^3 \left( \frac{4}{\pi} - 1 \right)^2 \right. & \nonumber \\
-  &= \left( 1 - \frac{2}{\pi} u \right)^3 \cdot v^3 \cdot \frac{\pi}{2} \cdot \left( \frac{\pi}{4-\pi} \right)^2 & \nonumber \\
-  &= \left[ v \left( 1 - \frac{2}{\pi} u \right) \right]^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) & \nonumber \\
-  &= \left( v - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) &= g(v). \label{eq:lhs-solving-for-lambda}
-\end{alignat}
-
-We can see that $g(v)$ is increasing in $v = \frac{1+\lambda^2}{\lambda^2} \geq
-1$. Therefore:
-
-\begin{equation}
-  \min_{v} g(v) = g(v)|_{v=1} = \left( 1 - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = 1.009524 \approx 1,
-\end{equation}
-
-which means that the right hand side of \eqref{eq:solving-for-lambda}, which is
-supposed to be equal to the left hand side of \eqref{eq:solving-for-lambda},
-can't ever be less than 1. Unfortunately, it sometimes is; in particular,
-$\frac{np(1-p)}{(1-2p)^2} \to 0$ when $p \to 0$ or $p \to 1$. So if we want a
-solution, we must restrict $n$ and $p$ such that
-
-\begin{align}
-  \textnormal{\{right hand side of \eqref{eq:solving-for-lambda}\}} &\geq \textnormal{\{min of left hand side of \eqref{eq:solving-for-lambda}\}} \nonumber \\
-  \frac{np(1-p)}{(1-2p)^2} &\geq 1 \nonumber \\
-  np(1-p) &\geq (1-2p)^2. \label{eq:solving-the-restriction}
-\end{align}
-
-Here, two scenarios arise. The first is when we have a fixed $p$ and wish to
-find the minimum $n$ necessary to derive a skew-normal approximation. From
-\eqref{eq:solving-the-restriction}, solving for $n$ is very simple:
-
-\begin{equation}
-  n \geq \frac{(1-2p)^2}{p(1-p)} \;. \label{eq: n for a given p}
-\end{equation}
-
-Figure \ref{fig:sn-restriction-least-n} in appendix \ref{app:figures} shows the
-least sample size required to estimate $\lambda$ as a function of
-$p$.\footnotemark As we would expect, it is larger when $p$ is small and
-rapidly goes to 0 as $p$ approaches 0.5; for example, when $p = 0.01$, $n$ must
-be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a trivial
-requirement to meet.
-
-\footnotetext{Since $Bin(n, p)$ and $Bin(n, 1-p)$ are mirror image curves, it
-is often only necessary to examine either $p \in (0, 0.5)$ or $p \in (0.5, 1)$.
-We will usually consider the former range of $p$'s. \label{fnote:half-p-range}}
-
-The second scenario, primarily of academic interest, is when $n$ is fixed and
-we wish to solve for $p$. In this case, we return to
-\eqref{eq:solving-the-restriction} for further factoring:
-
-\begin{align}
-  np(1-p) &\geq (1-2p)^2 \nonumber \\
-  np - np^2 &\geq 1 - 4p + 4p^2 \nonumber \\
-  1 - 4p + 4p^2 - np + np^2 &\leq 0 \nonumber \\
-  (n+4)p^2 - (n+4)p + 1 &\leq 0 \label{eq: solving for p}.
-\end{align}
-
-We then apply the quadratic formula with $a = n+4$, $b = -(n+4)$, and $c = 1$:
-
-\begin{align*}
-  p &= \frac{(n+4) \pm \sqrt{(n+4)^2 - 4 \cdot (n+4) \cdot 1}}{2(n+4)} \\
-  &= \frac{(n+4) \pm \sqrt{n^2 + 8n + 16 - 4n - 16}}{2(n+4)} \\
-  &= \frac{(n+4) \pm \sqrt{n^2 + 4n}}{2(n+4)} \\
-  &= \frac{n+4}{2(n+4)} \pm \frac12 \sqrt{\frac{n(n+4)}{(n+4)^2}} \\
-  &= \frac12 \pm \frac12 \sqrt{\frac{n}{n+4}} \;.
-\end{align*}
-
-Let $r_1 = \frac12 - \frac12 \sqrt{\frac{n}{n+4}}$ and $r_2 = \frac12 + \frac12
-\sqrt{\frac{n}{n+4}}$. (Note that $r_1 < r_2$.) Now we can rewrite \eqref{eq:
-solving for p} as
-
-\begin{equation*}
-  (p - r_1)(p - r_2) \leq 0.
-\end{equation*}
-
-Examining the left hand side, when $p < r_1$, both terms are negative and so
-their product is positive; when $p > r_2$, both terms are positive, again
-leading the product to be positive. Therefore, our solution lies where $r_1
-\leq p \leq r_2$, or more explicitly,
-
-\begin{equation}
- \frac12 - \frac12 \sqrt{\frac{n}{n+4}} \; \leq \; p \; \leq \; \frac12 + \frac12 \sqrt{\frac{n}{n+4}} \;.
-\end{equation}
-
-Figure \ref{fig:sn-restriction-p-range} in appendix \ref{app:figures} shows
-this range as a function of $n$, this interval grows quickly as $n$ increases,
-and for sufficiently large $n$, it becomes almost $(0, 1)$. For example, when
-$n=100$, our interval is $(0.00971, 0.99029)$; when $n=500$, it is (0.00199,
-0.99801).
-
-Although the presence of these restrictions are somewhat disappointing, we can
-console ourselves with the observation that at the same $n$ and $p$, the
-skew-normal yields substantially more accurate approximations than the normal
-(see section \ref{subsec:mabs}). Thus while imperfect, it is nevertheless an
-improvement.
-
-\section{Demonstrating Improved Accuracy}
-\label{sec:accuracy}
-
-Now comes the time to justify our efforts by comparing the accuracy of our
-skew-normal approximation to that of the normal. Naturally, we are primarily
-interested in cases where the normal approximation performs poorly, that is
-binomials where $n$ is small and $p$ is either close to 0 or 1.\footnotemark
-
-\footnotetext{Again, we examine only $p \in (0, 0.5)$. (See footnote
-\ref{fnote:half-p-range}.)}
-
-\subsection{Visual Comparison}
-
-The first and most obvious way of judging accuracy is by visual inspection.
-Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
-\ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
-normal, and skew-normal at small values of $p$ for $n=25$, $n=50$, and $n=100$,
-respectively.
-
-At very small $n$ and $p$, our skew-normal curve follows the shape of the
-binomial much more closely than the normal. However, as $n$ grows, the Central
-Limit Theorem begins to exert its effect; even at a moderate $n = 100$ and a
-smallish $p = 0.2$, the normal and skew-normal become nearly identical. Thus,
-as we would expect, the skew-normal method is most valuable at small $n$ and
-extreme $p$.
-
-\subsection{Maximal Absolute Error}
-\label{subsec:mabs}
-
-Another more quantitative method of judging accuracy is comparing the maximal
-absolute errors of our two approximations, defined by \citet{mabs} as
-
-\begin{equation}
-  \textnormal{MABS}(n, p) \eq \max_{k \in \{0, 1,...,n\}} \left| F_{B(n,p)} (k) -  F_{\textnormal{appr}(n,p)}(k + 0.5) \right|
-\end{equation}
-
-where $F_{B(n,p)}$ is the cdf of the binomial and $F_{\textnormal{appr}(n,p)}$
-is the cdf of either the normal or skew-normal approximation; the 0.5 is a
-continuity correction.
-
-Figures \ref{fig:mabs-fixed-n} and \ref{fig:mabs-fixed-p} in appendix
-\ref{app:figures} shows the MABS of the skew-normal and normal approximations
-as a function of $p$ and $n$, respectively. Again, the skew-normal outperforms
-the normal considerably in the extreme ranges, with the two approximations
-converging as $n \rightarrow \infty$ or $p \rightarrow 0.5$.
-
-\section{Practical Resources}
-\label{sec:resources}
-
-We conclude our dicussion by offering the reader a few practical resources:
-
-Table \ref{tab:sn-approx-table} in appendix \ref{app:figures} shows estimations
-of $SN(\mu, \sigma, \lambda)$ for common binomial distributions.
-
-For those with an unusual combination of $n$ and $p$ not in the table, appendix
-\ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
-parameters by hand.
-
-Finally, for rapidly approximating many binomial distributions, the author's
-Python library, which was used to compute all values presented in this paper,
-is freely available online:
-
-\url{http://github.com/joycetipping/skew-normal-capstone/}
-
-\clearpage
-
-\appendix
-\section{Figures}
-\label{app:figures}
-
-\begin{figure}[h]
-  \centering
-  \subfloat[Least possible $n$, given a fixed $p$]{\label{fig:sn-restriction-least-n}\includegraphics[width=0.76\textwidth]{../images/restriction-least-n.png}}
-  \\ \vspace{5mm}
-  \subfloat[Range of possible $p$, given a fixed $n$]{\label{fig:sn-restriction-p-range}\includegraphics[width=0.76\textwidth]{../images/restriction-p-range.png}}
-  \caption{Restrictions on $n$ and $p$ necessary to obtain $\lambda$}
-  \label{fig:sn-restriction}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/comparison-n25.png}
-  \caption{Binomial, normal, and skew-normal, $n=25$}
-  \label{fig:comparison-n25}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/comparison-n50.png}
-  \caption{Binomial, normal, and skew-normal, $n=50$}
-  \label{fig:comparison-n50}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\textwidth]{../images/comparison-n100.png}
-  \caption{Binomial, normal, and skew-normal, $n=100$}
-  \label{fig:comparison-n100}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-n.png}
-  \caption{MABS as a function of p}
-  \label{fig:mabs-fixed-n}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.8\textwidth]{../images/mabs-fixed-p.png}
-  \caption{MABS as a function of n}
-  \label{fig:mabs-fixed-p}
-\end{figure}
-
-\begin{sidewaystable}
-  \caption{Estimations of $SN(\mu, \sigma, \lambda)$ for $Bin(n,p)$}
-  \centering
-  \renewcommand{\arraystretch}{1.3}
-  \begin{tabular}
-    { r r | r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l r@{}r@{,\;}r@{,\;}r@{}l }
-    \hline \hline
-    & & \multicolumn{5}{c}{} & \multicolumn{5}{c}{} & \multicolumn{5}{c}{$n$} & \multicolumn{5}{c}{} & \multicolumn{5}{c}{}\\
-    \multirow{20}{*}{$p$} & & \multicolumn{5}{c}{25} & \multicolumn{5}{c}{50} & \multicolumn{5}{c}{100} & \multicolumn{5}{c}{250} & \multicolumn{5}{c}{500} \\
-    \hline
-    & 0.05 & ( & -0.11 & 1.74 & 4.56 & ) & ( & 0.79 & 2.30 & 2.54 & ) & ( & 2.85 & 3.06 & 1.86 & ) & ( & 9.58 & 4.52 & 1.38 & ) & ( & 21.32 & 6.11 & 1.15 & ) \\
-    & 0.10 & ( & 0.89 & 2.20 & 2.31 & ) & ( & 2.97 & 2.94 & 1.74 & ) & ( & 7.44 & 3.94 & 1.40 & ) & ( & 21.53 & 5.88 & 1.10 & ) & ( & 45.62 & 8.01 & 0.94 & ) \\
-    & 0.15 & ( & 2.02 & 2.49 & 1.79 & ) & ( & 5.32 & 3.34 & 1.43 & ) & ( & 12.25 & 4.51 & 1.19 & ) & ( & 33.77 & 6.77 & 0.96 & ) & ( & 70.30 & 9.27 & 0.82 & ) \\
-    & 0.20 & ( & 3.23 & 2.67 & 1.50 & ) & ( & 7.76 & 3.61 & 1.24 & ) & ( & 17.18 & 4.89 & 1.04 & ) & ( & 46.18 & 7.39 & 0.85 & ) & ( & 95.18 & 10.16 & 0.74 & ) \\
-    & 0.25 & ( & 4.49 & 2.79 & 1.29 & ) & ( & 10.28 & 3.78 & 1.09 & ) & ( & 22.20 & 5.15 & 0.93 & ) & ( & 58.71 & 7.83 & 0.76 & ) & ( & 120.22 & 10.80 & 0.67 & ) \\
-    & 0.30 & ( & 5.80 & 2.85 & 1.12 & ) & ( & 12.86 & 3.88 & 0.95 & ) & ( & 27.31 & 5.32 & 0.82 & ) & ( & 71.34 & 8.12 & 0.68 & ) & ( & 145.39 & 11.24 & 0.60 & ) \\
-    & 0.35 & ( & 7.17 & 2.86 & 0.96 & ) & ( & 15.50 & 3.92 & 0.83 & ) & ( & 32.49 & 5.39 & 0.72 & ) & ( & 84.09 & 8.28 & 0.60 & ) & ( & 170.70 & 11.50 & 0.53 & ) \\
-    & 0.40 & ( & 8.59 & 2.83 & 0.80 & ) & ( & 18.23 & 3.89 & 0.70 & ) & ( & 37.76 & 5.39 & 0.61 & ) & ( & 96.96 & 8.32 & 0.51 & ) & ( & 196.18 & 11.60 & 0.45 & ) \\
-    & 0.45 & ( & 10.12 & 2.73 & 0.61 & ) & ( & 21.08 & 3.79 & 0.53 & ) & ( & 43.21 & 5.29 & 0.47 & ) & ( & 110.07 & 8.23 & 0.40 & ) & ( & 221.93 & 11.54 & 0.35 & ) \\
-    & 0.50 & ( & 12.50 & 2.50 & 0.00 & ) & ( & 25.00 & 3.54 & 0.00 & ) & ( & 50.00 & 5.00 & 0.00 & ) & ( & 125.00 & 7.91 & 0.00 & ) & ( & 250.00 & 11.18 & 0.00 & ) \\
-    & 0.55 & ( & 14.88 & 2.73 & -0.61 & ) & ( & 28.92 & 3.79 & -0.53 & ) & ( & 56.79 & 5.29 & -0.47 & ) & ( & 139.93 & 8.23 & -0.40 & ) & ( & 278.07 & 11.54 & -0.35 & ) \\
-    & 0.60 & ( & 16.41 & 2.83 & -0.80 & ) & ( & 31.77 & 3.89 & -0.70 & ) & ( & 62.24 & 5.39 & -0.61 & ) & ( & 153.04 & 8.32 & -0.51 & ) & ( & 303.82 & 11.60 & -0.45 & ) \\
-    & 0.65 & ( & 17.83 & 2.86 & -0.96 & ) & ( & 34.50 & 3.92 & -0.83 & ) & ( & 67.51 & 5.39 & -0.72 & ) & ( & 165.91 & 8.28 & -0.60 & ) & ( & 329.30 & 11.50 & -0.53 & ) \\
-    & 0.70 & ( & 19.20 & 2.85 & -1.12 & ) & ( & 37.14 & 3.88 & -0.95 & ) & ( & 72.69 & 5.32 & -0.82 & ) & ( & 178.66 & 8.12 & -0.68 & ) & ( & 354.61 & 11.24 & -0.60 & ) \\
-    & 0.75 & ( & 20.51 & 2.79 & -1.29 & ) & ( & 39.72 & 3.78 & -1.09 & ) & ( & 77.80 & 5.15 & -0.93 & ) & ( & 191.29 & 7.83 & -0.76 & ) & ( & 379.78 & 10.80 & -0.67 & ) \\
-    & 0.80 & ( & 21.77 & 2.67 & -1.50 & ) & ( & 42.24 & 3.61 & -1.24 & ) & ( & 82.82 & 4.89 & -1.04 & ) & ( & 203.82 & 7.39 & -0.85 & ) & ( & 404.82 & 10.16 & -0.74 & ) \\
-    & 0.85 & ( & 22.98 & 2.49 & -1.79 & ) & ( & 44.68 & 3.34 & -1.43 & ) & ( & 87.75 & 4.51 & -1.19 & ) & ( & 216.23 & 6.77 & -0.96 & ) & ( & 429.70 & 9.27 & -0.82 & ) \\
-    & 0.90 & ( & 24.11 & 2.20 & -2.31 & ) & ( & 47.03 & 2.94 & -1.74 & ) & ( & 92.56 & 3.94 & -1.40 & ) & ( & 228.47 & 5.88 & -1.10 & ) & ( & 454.38 & 8.01 & -0.94 & ) \\
-    & 0.95 & ( & 25.11 & 1.74 & -4.56 & ) & ( & 49.21 & 2.30 & -2.54 & ) & ( & 97.15 & 3.06 & -1.86 & ) & ( & 240.42 & 4.52 & -1.38 & ) & ( & 478.68 & 6.11 & -1.15 & ) \\
-  \end{tabular}
-  \label{tab:sn-approx-table}
-\end{sidewaystable}
-
-\clearpage
 \section{Calculating a Skew-Normal Approximation}
@@
 \clearpage
-\bibliography{bibliography.bib}
-\bibliographystyle{plainnat}
-\end{document}

### 2011-02-20 project/presentation/intro.tex
Tweaks.
Got rid of \vsep command
Redid a few slides with the [t] top alignment options.

@@
 
-    \vsep
+    \vspace{3mm}
     \uncover<2->{
@@
   normal cdf.
+
   \pause
-
-  \vsep
+  \vspace{3mm}
   When does this work well? ... \pause In a nutshell, when the binomial is symmetric.
@@
 }
-\frame{ \frametitle{Introduction}
+\begin{frame}[t]{Introduction}
   However, when $n$ is medium and $p$ is extreme ...
   \begin{center}
-    \only<1>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-1.png}}
-    \only<2>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-2.png}}
-    \only<3>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-3.png}}
+    \only<2>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-1.png}}
+    \only<3>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-2.png}}
+    \only<4>{\includegraphics[width=\textwidth]{../images/binomial-normal-sn-3.png}}
   \end{center}
-  \only<1>{the binomial is very skewed ...}
-  \only<2>{and the normal approximation doesn't work very well.}
-  \only<3>{Introducing ... the skew-normal distribution.}
-}
+  \only<2>{the binomial is very skewed ...}
+  \only<3>{and the normal approximation doesn't work very well.}
+  \only<4>{Introducing ... the skew-normal distribution.}
+\end{frame}
 

### 2011-02-20 project/presentation/skew-normal.tex
Tweaks.
Got rid of \vsep command
Redid a few slides with the [t] top alignment options.

@@
 
-    \vsep
+    \vspace{2mm}
     We write $Y \sim SN(\mu, \sigma, \lambda)$.
@@
 }
-% For some reason, I was obliged to split the following slide into 3 slides, to prevent bumping in between the images.
-\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+\begin{frame}[t]{The Skew-Normal Distribution: The Standard Skew-Normal}
+  % This frame needs to be top-aligned to prevent bumping in between images.
+  \vspace{5mm}
   \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow +|N(0,1)|$ as $\lambda \rightarrow \infty$:
@@
   \only<1>{\includegraphics[width=\textwidth]{../images/positive-half-normal.png}}
-}
-\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
-  \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow +|N(0,1)|$ as $\lambda \rightarrow \infty$:
-
-  \only<1>{\includegraphics[width=\textwidth]{../images/std-sn-skew2.png}}
-  \only<2>{\includegraphics[width=\textwidth]{../images/std-sn-skew5.png}}
-}
-\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
-  \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow +|N(0,1)|$ as $\lambda \rightarrow \infty$:
-
-  \only<1>{\includegraphics[width=\textwidth]{../images/std-sn-skew10.png}}
-  \only<2>{\includegraphics[width=\textwidth]{../images/std-sn-skew1000.png}}
-}
-% end
-% Same bumping issue for this slide
-\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
+  \only<2>{\includegraphics[width=\textwidth]{../images/std-sn-skew2.png}}
+  \only<3>{\includegraphics[width=\textwidth]{../images/std-sn-skew5.png}}
+  \only<4>{\includegraphics[width=\textwidth]{../images/std-sn-skew10.png}}
+  \only<5>{\includegraphics[width=\textwidth]{../images/std-sn-skew1000.png}}
+\end{frame}
+\begin{frame}[t]{The Skew-Normal Distribution: The Standard Skew-Normal}
+  % This frame needs to be top-aligned to prevent bumping in between images.
+  \vspace{5mm}
   \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow -|N(0,1)|$ as $\lambda \rightarrow -\infty$:
@@
   \only<1>{\includegraphics[width=\textwidth]{../images/negative-half-normal.png}}
-}
-\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
-  \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow -|N(0,1)|$ as $\lambda \rightarrow -\infty$:
-
-  \only<1>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg2.png}}
-  \only<2>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg5.png}}
-}
-\frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}
-  \textit{Property 3}: $SN(0, 1, \lambda) \rightarrow -|N(0,1)|$ as $\lambda \rightarrow -\infty$:
-
-  \only<1>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg10.png}}
-  \only<2>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg1000.png}}
-}
-% end
+  \only<2>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg2.png}}
+  \only<3>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg5.png}}
+  \only<4>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg10.png}}
+  \only<5>{\includegraphics[width=\textwidth]{../images/std-sn-skewneg1000.png}}
+\end{frame}
 \frame{ \frametitle{The Skew-Normal Distribution: The Standard Skew-Normal}

### 2011-02-20 project/presentation/demo.tex
Added demo

% Calculating a Skew-Normal Approximation
\frame{ \frametitle{Calculating a Skew-Normal Approximation}
  Although easier with a computer program, calculating estimates for $\mu$, $\sigma$, and $\lambda$ by hand is perfectly possible.
}
\begin{frame}[t]{Calculating a Skew-Normal Approximation: Finding $\lambda$}
  % This frame needs to be top-aligned to prevent bumping when the braces appear.
  \vspace{1cm}
  By far the biggest battle is $\lambda$.
  \pause

  We'll use a simplified version of equation \eqref{eq:solving-for-lambda}:
  \pause
  \begin{equation} \label{eq:calculating-lambda}
    \only<+>{\left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = \frac{np(1-p)}{(1-2p)^2}}
    \only<+>{\underbrace{ \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) }_\text{$f(\lambda)$}
              = \frac{np(1-p)}{(1-2p)^2}}
    \only<+->{\underbrace{ \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) }_\text{$f(\lambda)$}
              =
              \underbrace{ \frac{np(1-p)}{(1-2p)^2} }_\text{$k_{n,p}$}}
  \end{equation}

  \uncover<+->{The closed form solution to \eqref{eq:calculating-lambda} is pretty hideous, so we'll take a numerical approach.}

  \uncover<+->{Our goal is to find $\lambda$ such that $f(\lambda)$ is within a certain margin of error ($e$) of $k_{n,p}$.}
\end{frame}
\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
  Recall that the sign of $\lambda$ is determined independently of the value.
  \pause

  It is possible to show, by taking its derivative, that $f$ is monotonically decreasing for positive $\lambda$.
  \pause

  This convenient fact allows us to find lower and upper bounds for $\lambda$ and repeatedly bisect our interval until we are within $e$ of $k_{n,p}$.
}
\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
  For this demonstration, we will take $n=25$ and $p=0.1$.
  \pause

  Since we're doing this by hand, we'll take our error margin $e$ to be a modest 0.1.
}
\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
  \textit{Step 1}: Find $k_{n,p}$.
  \pause

  Our value: $\displaystyle k_{n,p} = \frac{25 \cdot 0.1 \cdot 0.9}{(1 - 2\cdot0.1)^2} = 3.5156$.
  \pause

  \vspace{1cm}
  \textit{Step 2}: Find $a$ and $b$ such that $f(a) > k_{n,p} > f(b)$.
  \pause

  Our values: $a=1$, $b=3$.
}
\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
  \textit{Step 3}: Repeatedly bisect $(a,b)$ until $f(c)$ is within $e$ of $k_{n,p}$.
  \pause

  Calculate $c=\frac{a+b}{2}$.
  \pause
  \begin{itemize}[<+->]
    \item If $f(c) \leq k_{n,p} - 0.01$, we need a small value of $c$, so we take our new interval to be $(a, c)$.
    \item If $f(c) \geq k_{n,p} + 0.01$, we need a larger value of $c$, so we take our new interval to be $(c, b)$.
  \end{itemize}

  \uncover<+->{Repeat this step until $f(c)$ is within $e$ of $k_{n,p}$, or more precisely $k_{n,p} - 0.01 < f(c) < k_{n,p} + 0.01$.}
}
\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
  \textit{(Step 3)}

  The following table shows our iterations:
  \renewcommand{\arraystretch}{1.3}
  \begin{center}
    \scriptsize
    \begin{tabular}{c c c c c c c}
      \uncover<+->{Iteration & $a$  & $b$   & $c$    & $f(c)$ & $f(c) \leq k_{n,p} - 0.01$ & $f(c) \geq k_{n,p} + 0.01$ \\
                   \hline}
      \uncover<+->{1         & 2.00 & 3.000 & 2.5000 & 3.0164 & True                       & False \\}
      \uncover<+->{2         & 2.00 & 2.500 & 2.2500 & 3.7129 & False                      & True \\}
      \uncover<+->{3         & 2.25 & 2.500 & 2.3750 & 3.3252 & True                       & False \\}
      \uncover<+->{4         & 2.25 & 2.375 & 2.3125 & 3.5076 & False                      & False \\}
    \end{tabular}
  \end{center}

  \uncover<+->{We take the last value of $c$: 2.3125.}
}
\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
  \textit{Step 5}: Find the sign of $(1-2p)$.
  \pause

  Our $p = 0.1 \Ra (1 - 2\cdot0.1) = 0.8 \Ra$ positive.
  \pause

  \vspace{1cm}
  \textit{Step 6}: Final answer: \{sign of $(1-2p)$\}$\lambda$
  \pause

  Our final answer: $\lambda = 2.3125$.
}
\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\sigma$}
  Once we have $\lambda$, we can easily find $\sigma$:
  \pause
  \begin{equation*}
    \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} = \sqrt{\frac{25 \cdot 0.1 \cdot 0.9}{1 - \frac{2}{\pi} \cdot \frac{2.3125^2}{1 + 2.3125^2}}} = 2.2029.
  \end{equation*}
}
\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\mu$}
  And with $\lambda$ and $\sigma$, we can also find $\mu$:
  \pause
  \begin{align*}
    \mu &= np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \\
    &= 25 \cdot 0.1 - 2.2029 \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{2.3125}{\sqrt{1 + 2.3125^2}} \\
    &= 0.8867.
  \end{align*}
}

### 2011-02-21 project/presentation/presentation.tex
Tweaks
Got rid of \vsep command
Tweaks.

@@
 
-% Misc
-\newcommand{\vsep}{\vspace{0.2cm}}
-
 \begin{document}
@@
 
-  \vsep
+  \vspace{3mm}
   When does this work well? ... \pause In a nutshell, when the binomial is symmetric.
@@
     notation $\overset{d}{=}$ denotes equality in distribution.
+    \pause
 
-    \pause
     Let $X \sim N(0,1)$. Since $X^2 \sim \chi^2_1$ and $|X| \overset{d}{=}
@@
     \uncover<+->{\item Find the first three moments about the mean (central moments) of the binomial and the skew-normal.\\}
-          \uncover<+->{\vsep
+          \uncover<+->{\vspace{2mm}
                        What are central moments?: $E(X)$, $E([X - E(X)]^2)$, $E([X - E(X)]^3)$.}
@@
     \uncover<+->{\Rightarrow \quad \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1
-                 \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \label{eq:solving-for-lambda}}
+                 \right)^2} &= \frac{np(1-p)}{(1-2p)^2} \label{eq:solving-for-lambda} \\}
+    \notag
   \end{align}
@@
   \end{equation*}
+  \pause
 
-  \pause
   Why?
@@
   We have an approximation!!
+  \pause
 
-  But is it more accurate? ... \pause Answer: Yes!
+  But is it more accurate? ...
+  \pause
+  Answer: Yes!
 }
@@
   \end{equation*}
+  \pause
+
+  \vspace{1cm}
+  (In English: The biggest vertical distance between the binomial cdf and the approximation curve.)
 }
@@
 
+\frame{ \frametitle{Resources}
+  A few resources you might find helpful ...
+}
 \begin{frame}[shrink=47]{Resources}
-  \vsep
-  \vsep
-
+  \vspace{5mm}
   Estimations of $SN(\mu, \sigma, \lambda)$ for $Bin(n,p)$
-  \vsep
+  \vspace{2mm}
 
@@
 
+% Bibliography (first time)
+\begin{frame}[allowframebreaks]
+  \frametitle{Bibliography}
+  \nocite{*}
+  \bibliography{../bibliography.bib}
+  \bibliographystyle{plainnat}
+\end{frame}
+
+% Calculating a Skew-Normal Approximation
+\frame{
+  \textit{Appendix}
+
+  Calculating a skew-normal approximation
+}
+\frame{ \frametitle{Calculating a Skew-Normal Approximation}
+  Although easier with a computer program, calculating estimates for $\mu$, $\sigma$, and $\lambda$ by hand is perfectly possible.
+  \pause
+
+  Here's an example!
+}
+\begin{frame}[t]{Calculating a Skew-Normal Approximation: Finding $\lambda$}
+  % This frame needs to be top-aligned to prevent bumping when the braces appear.
+  \vspace{1cm}
+  By far the biggest battle is $\lambda$.
+  \pause
+
+  We'll use a simplified version of equation \eqref{eq:solving-for-lambda}:
+  \pause
+  \begin{equation} \label{eq:calculating-lambda}
+    \only<+>{\left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) = \frac{np(1-p)}{(1-2p)^2}}
+    \only<+>{\underbrace{ \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) }_\text{$f(\lambda)$}
+              = \frac{np(1-p)}{(1-2p)^2}}
+    \only<+->{\underbrace{ \left( \frac{1+\lambda^2}{\lambda^2} - \frac{2}{\pi} \right)^3 \left( \frac{\pi^3}{2(4-\pi)^2} \right) }_\text{$f(\lambda)$}
+              =
+              \underbrace{ \frac{np(1-p)}{(1-2p)^2} }_\text{$k_{n,p}$}}
+  \end{equation}
+
+  \uncover<+->{The closed form solution to \eqref{eq:calculating-lambda} is pretty hideous, so we'll take a numerical approach.}
+
+  \uncover<+->{Our goal is to find $\lambda$ such that $f(\lambda)$ is within a certain margin of error ($e$) of $k_{n,p}$.}
+\end{frame}
+\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
+  Recall that the sign of $\lambda$ is determined independently of the value.
+  \pause
+
+  It is possible to show, by taking its derivative, that $f$ is monotonically decreasing for positive $\lambda$.
+  \pause
+
+  This convenient fact allows us to find lower and upper bounds for $\lambda$ and repeatedly bisect our interval until we are within $e$ of $k_{n,p}$.
+}
+\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
+  For this demonstration, we will take $n=25$ and $p=0.1$.
+  \pause
+
+  Since we're doing this by hand, we'll take our error margin $e$ to be a modest 0.1.
+}
+\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
+  \textit{Step 1}: Find $k_{n,p}$.
+  \pause
+
+  Our value: $\displaystyle k_{n,p} = \frac{25 \cdot 0.1 \cdot 0.9}{(1 - 2\cdot0.1)^2} = 3.5156$.
+  \pause
+
+  \vspace{1cm}
+  \textit{Step 2}: Find $a$ and $b$ such that $f(a) > k_{n,p} > f(b)$.
+  \pause
+
+  Our values: $a=1$, $b=3$.
+}
+\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
+  \textit{Step 3}: Repeatedly bisect $(a,b)$ until $f(c)$ is within $e$ of $k_{n,p}$.
+  \pause
+
+  Calculate $c=\frac{a+b}{2}$.
+  \pause
+  \begin{itemize}[<+->]
+    \item If $f(c) \leq k_{n,p} - 0.01$, we need a small value of $c$, so we take our new interval to be $(a, c)$.
+    \item If $f(c) \geq k_{n,p} + 0.01$, we need a larger value of $c$, so we take our new interval to be $(c, b)$.
+  \end{itemize}
+
+  \uncover<+->{Repeat this step until $f(c)$ is within $e$ of $k_{n,p}$, or more precisely $k_{n,p} - 0.01 < f(c) < k_{n,p} + 0.01$.}
+}
+\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
+  \textit{(Step 3)}
+
+  The following table shows our iterations:
+  \renewcommand{\arraystretch}{1.3}
+  \begin{center}
+    \scriptsize
+    \begin{tabular}{c c c c c c c}
+      \uncover<+->{Iteration & $a$  & $b$   & $c$    & $f(c)$ & $f(c) \leq k_{n,p} - 0.01$ & $f(c) \geq k_{n,p} + 0.01$ \\
+                   \hline}
+      \uncover<+->{1         & 2.00 & 3.000 & 2.5000 & 3.0164 & True                       & False \\}
+      \uncover<+->{2         & 2.00 & 2.500 & 2.2500 & 3.7129 & False                      & True \\}
+      \uncover<+->{3         & 2.25 & 2.500 & 2.3750 & 3.3252 & True                       & False \\}
+      \uncover<+->{4         & 2.25 & 2.375 & 2.3125 & 3.5076 & False                      & False \\}
+    \end{tabular}
+  \end{center}
+
+  \uncover<+->{We take the last value of $c$: 2.3125.}
+}
+\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
+  \textit{Step 5}: Find the sign of $(1-2p)$.
+  \pause
+
+  Our $p = 0.1 \Ra (1 - 2\cdot0.1) = 0.8 \Ra$ positive.
+  \pause
+
+  \vspace{1cm}
+  \textit{Step 6}: Final answer: \{sign of $(1-2p)$\}$\lambda$
+  \pause
+
+  Our final answer: $\lambda = 2.3125$.
+}
+\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\sigma$}
+  Once we have $\lambda$, we can easily find $\sigma$:
+  \pause
+  \begin{equation*}
+    \sigma = \sqrt{\frac{np(1-p)}{1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1 + \lambda^2}}} = \sqrt{\frac{25 \cdot 0.1 \cdot 0.9}{1 - \frac{2}{\pi} \cdot \frac{2.3125^2}{1 + 2.3125^2}}} = 2.2029.
+  \end{equation*}
+}
+\frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\mu$}
+  And with $\lambda$ and $\sigma$, we can also find $\mu$:
+  \pause
+  \begin{align*}
+    \mu &= np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} \\
+    &= 25 \cdot 0.1 - 2.2029 \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{2.3125}{\sqrt{1 + 2.3125^2}} \\
+    &= 0.8867.
+  \end{align*}
+}
+
+\frame{
+  Here's the bibliography again ...
+}
 \begin{frame}[allowframebreaks]

### 2011-02-22 project/presentation/method-of-moments.tex
Got rid of \vsep command
Tweak pause spacing. :)
Tweaks.

@@
 \frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
-  The first two central moments are just the mean and variance:
+  Let $B \sim Bin(n,p$.
+  \pause
+
+  The first two central moments of $B$ are just the mean and variance:
   \pause
@@
 \frame{ \frametitle{Method of Moments: Central Moments of the Skew-Normal}
-  Again, the first and second central moments are the mean and variance.
+  Let $Y \sim SN(\mu, \sigma, \lambda)$.
+  \pause
+
+  Again, the first and second central moments of $Y$ are the mean and variance.
   \pause

### 2011-02-22 project/presentation/presentation.tex
Tweaks.

@@
   \end{definition}
+  \pause
+  \textit{Note:} $\mu$ and $\sigma$ are not intuitively related to the mean and variance.
 }
@@
     \uncover<3->{
-      \item Kernel
-        \tikz[na] \node[coordinate] (n1) {};
+      \item \tikz[na] \node[coordinate] (n1) {};
+            A pdf symmetric about 0 (kernel)
     }
     \uncover<4->{
-      \item CDF
+      \item A cdf whose derivative is symmetric about 0
             \tikz[na] \node[coordinate] (n2) {};
@@
   \begin{tikzpicture}[overlay]
-    \path[->]<3-> (n1) edge [bend right] (t1);
+    \path[->]<3-> (n1) edge [bend left] (t1);
     \path[->]<4-> (n2) edge [bend right] (t2);
@@
     \begin{align*}
-      \uncover<+->{f_{(-Z)}(x) &= f_Z(-x) \\}
-      \uncover<+->{& = 2 \cdot \phi(-x) \cdot \Phi (-\lambda x) \\}
-      \uncover<+->{& = 2 \cdot \phi(x) \cdot \Phi (-\lambda x),}
+      \uncover<+->{f_{(-Z)}(z) &= f_Z(-z) \\}
+      \uncover<+->{& = 2 \cdot \phi(-z) \cdot \Phi (-\lambda z) \\}
+      \uncover<+->{& = 2 \cdot \phi(z) \cdot \Phi (-\lambda z),}
     \end{align*}
@@
 \frame{ \frametitle{Demonstrating Improved Accuracy: MABS}
-  A more numerical way of gauging accuracy is the $MABS$, defined by \citet{mabs} as
+  A more numerical way of gauging accuracy is the maximal absolute error ($MABS$), defined as
   \begin{equation*}

### 2011-02-23 project/presentation/method-of-moments.tex
Tweaks.

@@
 \frame{ \frametitle{Method of Moments: Central Moments of the Binomial}
-  Let $B \sim Bin(n,p$.
+  Let $B \sim Bin(n,p)$.
   \pause
@@
 \frame{ \frametitle{Method of Moments: Deriving an Approximation}
-  When $p = 0.5$, the binomial is symmetric, so $\lambda=0$.
+  When $p = 0.5$, the right hand side of \eqref{eq:solving-for-lambda}
+  \begin{equation*}
+    \frac{\left( 1 - \frac{2}{\pi} \cdot \frac{\lambda^2}{1+\lambda^2} \right)^3}{\frac{2}{\pi} \left( \frac{\lambda^2}{1+\lambda^2} \right)^3 \left( \frac{4}{\pi} - 1 \right)^2}
+    = \frac{np(1-p)}{(1-2p)^2}
+  \end{equation*}
+  is undefined.
+  \pause
+
+  Uh-oh.
+}
+\frame{ \frametitle{Method of Moments: Deriving an Approximation}
+  Fortunately, our intuition rescues us:
+  \pause
+
+  When $p=0.5$, the binomial is symmetric, so $\lambda$ should equal 0.
   \pause
@@
   \begin{equation}
-    np(1-p) \geq \frac{1}{(1-2p)^2} \label{eq:solving-the-restriction}
+    np(1-p) \geq (1-2p)^2 \label{eq:solving-the-restriction}
   \end{equation}

### 2011-02-23 project/presentation/presentation.tex
Tweaks.

@@
 \frame{ \frametitle{Calculating a Skew-Normal Approximation: Finding $\lambda$}
-  Recall that the sign of $\lambda$ is determined independently of the value.
+  Recall that the sign of $\lambda$ is determined independently of the value. Thus, we can consider only $\lambda > 0$.
   \pause
@@
 
-  Since we're doing this by hand, we'll take our error margin $e$ to be a modest 0.1.
+  Since we're doing this by hand, we'll take our error margin $e$ to be a modest 0.01.
 }
